### 2021-03-22 outputs/documents/paper.Rmd

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    toc: false
    fig_caption: true
    latex_engine: xelatex
    template: templates/svm-latex-ms.tex
bibliography: "references.bib"
header-includes:
  -  \usepackage{hyperref}
  -  \usepackage{amsmath}
biblio-style: apalike
title: "Detecting Hate Speech with GPT-3"
thanks: "Code and data are available at: https://github.com/kelichiu/GPT3-hate-speech-detection. We gratefully acknowledge the support of Gillian Hadfield and the Schwartz Reisman Institute for Technology and Society. We thank Amy Farrow, Haoluan Chen, Mauricio Vargas Sepúlveda, and Tom Davidson for helpful suggestions. Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper are welcome at: rohan.alexander@utoronto.ca."
author:
- name: Ke-Li Chiu
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: University of Toronto and Schwartz Reisman Institute
abstract: "Sophisticated language models such as OpenAI's GPT-3 can generate hateful text that targets marginalized groups. Given this capacity, we are interested in whether large language models can be used to identify hate speech and classify text as sexist or racist? We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning. We find that with zero- and one-shot learning, GPT-3 is able to identify sexist or racist text with an accuracy between 48 per cent and 69 per cent. With few-shot learning and an instruction included in the prompt, the model's accuracy can be as high as 78 per cent. We conclude that large language models have a role to play in hate speech detection, and that with further development language models could be used to counter hate speech and even self-police."
keywords: "GPT-3; natural language processing; quantitative analysis; hate speech."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
endnote: no
graphics: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=80), echo = FALSE, warning = FALSE)
# library(dplyr)
library(tidyverse)
# library(tidyr)
# library(readr)
```

# Introduction

Sophisticated natural language processing (NLP) models, such as OpenAI's GPT-3, can produce hateful text. In particular, there have been many examples of text being generated that targets marginalized groups based on their sex, race, sexual orientation, and other characteristics. Large language models are trained on enormous datasets from various sources. This means that untruthful statements, human biases, and abusive language are inevitably included. Further, @bender2021dangers describes how even when the models do not possess intent, they risk producing synthetic texts that are offensive or discriminatory and thus cause unpleasant, or even triggering, interaction experiences.

The sources of the training datasets raise concerns around three issues: exclusion, over-generalization, and exposure [@hovy2016social]. Exclusion happens due to the demographic bias in the dataset. In the case of language models that are trained on US and UK English scraped from the Internet, datasets may be disproportionately white, male, and young. Therefore, it is not surprising to see white supremacist, misogynistic, and ageist content being over-represented in training datasets [@bender2021dangers]. Over-generalization stems from the assumption that what we see in the dataset represents what occurs in the real world. Words such as 'always', 'never', 'everybody', or 'nobody' are frequently used for rhetorical purpose instead of their literal meanings. However, language models do not always recognize this and make inference based on generalized statements using these words. For instance, hate speech commonly uses generalized language for targeting a group such as 'all' and 'every', and a model trained on these statements may generate similarly generalized and harmful statements. Finally, exposure refers to the relative attention, and hence considerations of importance, given to something. In the context of NLP this may be reflected in the emphasis on English-language created under particular circumstances, rather than another languages or circumstances that may be more prevalent.

While these, and other, issues give us pause, the dual-use problem, which is that the same technology can be applied to both good and bad uses, provides motivation. For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text [@hovy2016social]. In this paper we are interested in whether given large language models can produce harmful language, can they also identify, or learn to identify, harmful language?

Even though large NLP models do not have a real understanding of language, the vocabularies and the construction patterns of harmful languages can be thought of as known to them. We show that this knowledge can be used to identify abusive language and even hate speech. In particular we consider 120 different extracts that have been categorized as 'racist', 'sexist', or 'neither' in the single-category settings and 240 different extracts in the mixed-category settings. We ask GPT-3 to classify these based on zero-, one-, and few-shot learning, with and without instruction. We find that the model performs best with few-shot learning when an instruction is included. In that setting the model is able to accurately classify around 78 per cent of the extracts. If language models can be used to identify abusive language, then not only is there potential for them to counter the production of abusive language by humans, but they could also potentially self-police.

# Background

## Language models, Transformers and GPT-3

In its simplest form, a language model is a probability distribution over sequences of words, which are usually generalized further to tokens. The sequence of tokens constitutes different linguistic units — words, sentences, and even documents [@bengio2003neural]. Language models predict the next token based on inputs. If we consider each token in a vocabulary as a dimension, then the dimensionality of language quickly becomes large [@rosenfeld2000two]. Over time a variety of statistical language models have been created to nonetheless enable prediction. The n-gram is one of the earliest language models. It works by considering the co-occurrence of tokens in a sequence. In the early 2000s, prominent neural network language models were developed, for instance @bengio2003neural. These were then built on by word embeddings language models in the 2010s in which the distance between tokens represents how related those tokens are, for instance @turian2010word. In 2017, @vaswani2017attention introduced the Transformer, which marked a new era for language models. The Transformer is a network architecture for neural networks that can be trained more quickly than many other approaches [@vaswani2017attention]. Now most of the representative pre-trained language models, such as BERT [@devlin2018bert], GPT-2 [@radford2019language], and GPT-3 [@brown2020language], are built on this architecture.

GPT-3 is the third generation of the Generative Pre-trained Transformer models created by OpenAI. Until January 11, when @fedus2021switch announced a Transformer model with a trillion parameters, GPT-3 was the largest, publicly-known, Transformer language model. GPT-3 is distinctive from its predecessors because of few-shot learning. This means that GPT-3 can 'learn' to perform a new task based on only a few examples, expressed in natural language, instead of a fine-tuning process that can require a large amount of data. GPT-3 has led to unexpected NLP applications, such as computational code generation given natural language prompts. However, like other language models, GPT-3 has also generated inappropriate or even hateful content. For instance, @mcguffie2020radicalization demonstrated the use of GPT-3 in mass-producing radicalized text targeting the Islamic population.

## Hate speech detection

Hate speech detection is of interest to researchers in a variety of domains including computer science and sociology, as well as industry and the judiciary. Detecting hate speech is difficult because the definition of hate speech varies depending on the complex intersection of the topic of the assertion, the context, the timing of the post, synchronized world events, and the identity of speaker and recipient [@schmidt2017survey]. Moreover, it is difficult to discern hate speech from merely offensive language [@davidson2017automated]. Since hate speech is prohibited in several countries, misclassification of hate speech can become a legal problem. For instance, in Canada, speech that contains 'public incitement of hatred' or 'wilful promotion of hatred' is specified by the Criminal Code [@act2021justice]. Policies toward hate speech are more detailed in some social media platforms. For instance, the Twitter Hateful Conduct Policy states:

> You may not promote violence against or directly attack or threaten other people on the basis of race, ethnicity, national origin, caste, sexual orientation, gender, gender identity, religious affiliation, age, disability, or serious disease. We also do not allow accounts whose primary purpose is inciting harm towards others on the basis of these categories.
>
> @twitterpolicy2017

There has been a large amount of research focused on detecting hate speech. And as part of this various hate speech datasets have been created and examined. For instance, @waseem2016hateful create a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation, and @davidson2017automated trains a classifier to distinguish between hate speech and offensive language. And it is important to note that even these datasets have bias. For instance, @davidson2019racial found racial bias in five different sets of Twitter data annotated for hate speech and abusive language. They found that tweets written in African American English are more likely to be labeled as abusive.

# Methods

We examine the ability of GPT-3 to identity hate speech in zero-shot, one-shot, and few-shot settings. There are a variety of parameters, such as temperature, that control the degree of text variation. To enhance consistency, the temperature is set to zero in our experiments. There are two categories of hate speech that are of interest in this paper. The first targets the race of the recipient, and the other targets the gender of the recipient. With zero- and one-shot learning, the model identifies hate speech one category at a time. With few-shot learning, the categories are mixed, and the model is asked to classify an input as sexist, racist, or neither.

## Dataset

We use the ETHOS dataset created by @mollas2020ethos. ETHOS is based on comments found in YouTube and Reddit. The ETHOS YouTube data is collected through Hatebusters [@anagnostou2018hatebusters]. Hatebusters is a platform that collects comments from YouTube and assigns a 'hate' score to them using a support vector machine. The Reddit data is collected from the Public Reddit Data Repository [@baumgartner2020pushshift]. The dataset has two variants: binary and multi-label. In the binary dataset comments are classified as hate or non-hate. In the multi-label variant, the comments are evaluated on measures that include violence, gender, race, ability, religion, and sexual orientation. The examples provided in this paper are from the ETHOS dataset and hence contain typos, misspelling, and offensive content.

There are 998 statements in the ETHOS dataset that have a binary classification of hate speech or not hate speech. Of these, the 433 statements that contain hate speech additionally have multiple labels that classify the content, for instance, does the comment have to do with violence, gender, race, nationality, disability, etc. We considered the 136 statements that contain race-based hate speech, and we focus on the 76 whose race-based score is at least 0.5. Similarly, we considered the 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5. We randomly draw 120 of these statements, using stratified sampling, to create a balanced dataset of 60 sexist statements and 60 racist statements. For comparison purposes, we randomly draw 120 statements that are classified as not hate speech.

## Zero-shot learning

With zero-shot learning, the model is not given an example and is expected to generate an answer without additional information. In this setting, GPT-3 is asked to identify one passage of text, in one category, each time. A simple instruction is given asking the model to answer only 'Yes' or 'No'. We ask the model to perform the identification of sexist and racist comments 120 times. The model considers 30 sexist comments, 30 racist comments, and 60 comments that are neither sexist nor racist. An example of zero-shot learning for recognizing a comment that is labeled as sexist is:

Prompt:

> Is the following text sexist? Answer yes or no.
>
> 'The thing is women are not equal to us men and their place is the home and kitchen'
>
> Answer:

GPT-3 response:

> Yes.

## One-shot learning

With one-shot learning, similarly to the zero-shot learning case, the model is asked to identify one passage of text in one category at a time. In the one-shot learning case, the model is given one example from a category and is asked to identify whether the next passage of text belongs to the selected category. Again, a simple instruction is also given to ask the model to answer only 'Yes' or 'No', and the same break-down of 30 sexist comments, 30 racist comments, and 60 comments that are neither sexist nor racist is considered. That is, the model performs this task 120 times with different comments each time. An example of one-shot learning for recognizing a comment that is labeled as sexist is:

Prompt:

> The following text in quotes is sexist:
> 
> 'Feminism is a very terrible disease'
> 
> Is the following text sexist? Answer yes or no.
> 
> 'She is heavily relying on him to turn the other cheek...tough talking demon infested woman.'
> 
> Answer:

GPT-3 response:

> Yes.

## Few-shot learning

Under the few-shot setting, three examples are provided to the model. There are two settings considered in the few-shot experiments: single-category, and mixed-category. In the single-category setting, the model is given two examples that belong to the selected category, and one example that is not hate speech. The answer is expected to be binary. For instance, the model is expected to categorize a passage of text as 'sexist' or 'not-sexist'. An example of this is:

Prompt:

> 'Too bad women don’t know how to kill themselves': sexist.
>
> 'You should use your time to arrest murderers not little kids': not-sexist.
> 
> 'Now they know better than this shit lol they dudes. The stronger sex. The man supremacy': sexist.
> 
> 'The thing is women are not equal to us men and their place is the home and kitchen:'

GPT-3 response:

> sexist.

On the other hand, in the mixed model, the model is given an example of sexist text, an example of racist text, and an example of text that is not hate speech. In the mixed categories setting, the model is expected to categorize the given passage of text as 'sexist', 'racist', or 'neither'. There are ten sets of examples; each set of examples is used for the model to classify 60 racist comments, 60 sexist comments, and 120 comments that are in neither category This results in 2,400 responses in total. The ten sets of examples are available in Table \@ref(tab:appendixa) in the Appendix. An example of this is:

Prompt:

> 'That girl still need a good ass whooping, stupid ass bitch!!': sexist. 
>
> 'U SUCK SHIT YOU BLACK FUCK': racist. 
>
> 'You deserve way more subscribers. The shit you say is fucking gold.': neither. 
>
> 'Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With dicks and stuff.':

GPT-3 response:

> sexist.

Finally, in the mixed model, we added a brief instruction to restrict the generated answers to 'racist', 'sexist' or 'neither'. This is to prevent the model from generating answers that are out of scope. An example of this is:

Prompt:

> Classify the following texts into 'racist', 'sexist' or 'neither'. 
>
> 'That girl still need a good ass whooping, stupid ass bitch!!': sexist. 
>
> 'U SUCK SHIT YOU BLACK FUCK': racist. 
>
> 'You deserve way more subscribers. The shit you say is fucking gold.': neither. 
>
> 'Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With dicks and stuff.':

GPT-3 response:

> sexist.

# Result

## Zero-shot learning

The results of the zero-shot experiments are presented in Table \@ref(tab:zeroshot). The model has 35 matches and 25 mismatches in the sexist category, and 23 matches and 37 mismatches in the racist category. The model performs better when identifying sexist comments compared with identifying racist comments. However, the overall ratio of matches and mismatches is 58:62. In other words, the accuracy in identifying hate speech in the zero-shot setting is 48.3 per cent.

```{r zeroshot}
zero_shot_result <- read.csv(here::here("outputs/data/zero_shot_results.csv"))

zero_shot_result <- 
  zero_shot_result %>%
  filter(temperature == 0) %>%
  select(category, label, answer, temperature) %>%
  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
  mutate(result = case_when(answer_yn==label_yn ~ "Match",
                            answer_yn!=label_yn ~ "Mismatch"
                            )) %>%
  group_by(result, category) %>%
  summarise(result_cnt = n(), .groups="drop") %>% 
  mutate(category = case_when(category == "racist" ~ "Racist",
                              category == "sexist" ~ "Sexist"
                              )) %>%
  rename(Result = result,
         Category = category,
         Count = result_cnt)

zero_shot_result %>% 
  knitr::kable(caption = "Classification of statements with zero-shot learning",
               booktabs = TRUE)
```

## One-shot learning

The results of the one-shot learning experiments are presented in Table \@ref(tab:oneshot). The model has 46 matches and 14 mismatches in the racist category, and 37 matches and 23 mismatches in the sexist category. In contrast with the result generated from zero-shot learning, the model performs slightly better in identifying racist comments compared with identifying sexist comments. The general performance in the one-shot setting is also better than in the zero-shot setting. The overall ratio of matches and mismatches is 83:37. In other words, the accuracy of identifying hate speech in the one-shot setting is 69.2 per cent.

```{r oneshot}
one_shot_result <- read.csv(here::here("outputs/data/one_shot_results.csv"))

one_shot_result <- 
  one_shot_result %>%
  filter(temperature == 0) %>%
  select(category, label, answer) %>%
  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
  mutate(result = case_when(answer_yn==label_yn ~ "Match",
                            answer_yn!=label_yn ~ "Mismatch"
                            )) %>%
  group_by(result, category) %>%
  summarise(result_cnt = n(), .groups = "drop") %>% 
  mutate(category = case_when(category == "racist" ~ "Racist",
                              category == "sexist" ~ "Sexist"
                              )) %>%
  rename(Result = result,
         Category = category,
         Count = result_cnt)

one_shot_result %>% 
  knitr::kable(caption = "Classification of statements with one-shot learning", 
             booktabs = TRUE)
```

## Few-shot learning -- single category

The results of the single-category, few-shot learning, experiments are presented in Table \@ref(tab:fewshotsingle). The model has 41 matches and 19 mismatches in the racist category, and 42 matches and 18 mismatches in the sexist category. Here, the model performs almost equally well at identifying racist comments compared with identifying sexist comments. The general performance in the few-shot learning setting is similar to the performance in the one-shot learning setting. The overall ratio of matches and mismatches is 83:37, or around 69.2 per cent, however the composition is different, compared with the one-shot learning setting.

```{r fewshotsingle}
few_shot_single_result <- read.csv(here::here("outputs/data/few_shot_single_results.csv"))

few_shot_single_result <- 
  few_shot_single_result %>%
  filter(temperature == 0) %>%
  select(category, label, answer) %>%
  mutate(label_yn = ifelse(grepl("not", label), "No", "Yes")) %>%
  mutate(answer_yn = ifelse(grepl("not", answer), "No", "Yes")) %>%
  mutate(result = case_when(answer_yn==label_yn ~ "Match",
                            answer_yn!=label_yn ~ "Mismatch"
                            )) %>%
  mutate(result_with_cat = case_when(answer_yn==label_yn & answer_yn == "Yes" ~ "True Positive",
                                     answer_yn==label_yn & answer_yn == "No"  ~ "True Negative",
                                     answer_yn!=label_yn & answer_yn == "Yes" ~ "False Positive",
                                     answer_yn!=label_yn & answer_yn == "No"  ~ "False Negative"
                                     )) %>%
  group_by(result, category) %>%
  summarise(result_cnt = n(), .groups = "drop") %>% 
  mutate(category = case_when(category == "racist" ~ "Racist",
                              category == "sexist" ~ "Sexist"
                              )) %>%
  rename(Result = result,
         Category = category,
         Count = result_cnt)

few_shot_single_result %>% 
  knitr::kable(
    caption = "Classification of statements with single-category few-shot learning", 
    booktabs = TRUE)
```

## Few-shot learning -- mixed category

The results of the mixed-category few-shot experiments are presented in Table \@ref(tab:fewshotmixed). Among the ten sets of examples, Example Set 2 yields the best performance, as the model has the highest number of matches, 180, and the lowest number of mismatches, 60. In other words, the accuracy under the mixed category few-shot setting with Example Set 2 is 75 per cent. The example set that yields the worst results is Example Set 9, in which there are 137 matches and 103 mismatches. The accuracy rate with Example Set 9 is 57.1 per cent. The difference between Example Sets 2 and 9 suggests that, although the models are provided with same number of examples, the content of the examples also affects how the model makes inferences.

```{r fewshotmixed}
few_shot_mixed_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))

few_shot_mixed_result <- 
  few_shot_mixed_result %>%
  filter(temperature == 0) %>%
  select(category, label, answer, example_set) %>%
  mutate(example_set = example_set+1) %>%
  mutate(result = ifelse(trimws(label)==trimws(answer), "Match", "Mismatch")) %>%
  mutate(label = case_when(label == "racist" ~ "Racist",
                           label == "sexist" ~ "Sexist",
                           label == "neither" ~ "Neither"
                           )) %>%
  group_by(example_set, result) %>%#, label) %>%
  summarise(result_cnt = n(), .groups = "drop") %>% 
  rename(Result = result,
         "Example Set" = example_set,
         Count = result_cnt)

knitr::kable(few_shot_mixed_result, 
             caption = "Classification of statements with mixed-category few-shot learning", 
             booktabs = TRUE,
             linesep = "",
             align = 'llr')
```

The unique generated answers are listed in Table \@ref(tab:fewshotmixedanswersnoinstruct). Under the mixed-category setting, the model is observed to generate answers that are out of scope. For instance, other than 'sexist', 'racist', and 'neither', we also see answers such as 'transphobic', 'hypocritical', 'Islamophobic', and 'ableist'. In some cases, the model even classifies a text passage into more than one category, such as 'sexist, racist' and 'sexist, misogynistic'. The full list contains eighty different answers instead of three.

```{r fewshotmixedanswersnoinstruct, warning = FALSE, message = FALSE}
few_shot_mixed_result <-
  readr::read_csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))

few_shot_mixed_result <- few_shot_mixed_result %>% 
  select(answer) %>% 
  distinct() %>% 
  rename(Answer = answer)# %>% 
few_shot_mixed_result <-list(few_shot_mixed_result$Answer)

df <- as.data.frame("Answer")
df <- rbind(df$Answer,paste(unlist(few_shot_mixed_result[[1]]), collapse=' | '))
df %>% 
  knitr::kable(
  caption = "Classifications generated by GPT-3 under mixed-category few-shot learning without instructions",
  booktabs = TRUE,
  linesep = "") %>% 
  kableExtra::column_spec(column = 1, width = "40em")
```

## Few-shot learning -- mixed category with instruction

To reduce the chance of the model generating answers that are out of scope, a brief instruction is added to the prompt, specifying that the answers be: 'sexist', 'racist', or 'neither'. The addition of an instruction successfully restricts the generated answers within the specified terms. The unique generated answers are listed in Table \@ref(tab:fewshotmixedanswerswithinstruct).

```{r fewshotmixedanswerswithinstruct, message=FALSE, warning=FALSE}
few_shot_instruction_result <-
  readr::read_csv(here::here("outputs/data/few_shot_fixed_examples_instruction_results.csv"))

few_shot_instruction_result %>% 
  select(answer) %>% 
  distinct() %>% 
  rename(Answer = answer) %>% 
  knitr::kable(caption = "Classifications generated by GPT-3 under mixed-category few-shot learning with instructions", 
             booktabs = TRUE,
             linesep = "",
             align = 'llr')
```

The results of the mixed-category, few-shot learning, with instruction, experiments are presented in Table \@ref(tab:fewshotmixedinstruct). With the addition of an instruction in the prompt, the example set that yields the best result is Example Set 1 instead of Example Set 2. The addition of the instruction in the prompt increases the highest number of matches from 180 to 187; the highest accuracy rate is increased from 75 per cent to 78 per cent. In almost all cases the accuracy of the model increases (Figure \ref{fig:comparison})

```{r fewshotmixedinstruct}
few_shot_instruction_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_instruction_results.csv"))

few_shot_instruction_result <- 
  few_shot_instruction_result %>%
  filter(temperature == 0) %>%
  select(category, label, answer, example_set) %>%
  mutate(example_set = example_set+1) %>%
  mutate(result = ifelse(trimws(label)==trimws(answer), "Match", "Mismatch")) %>%
  mutate(label = case_when(label == "racist" ~ "Racist",
                         label == "sexist" ~ "Sexist",
                         label == "neither" ~ "Neither"
                         )) %>%
  group_by(example_set, result) %>% 
  summarise(result_cnt = n(), .groups = "drop") %>% 
  rename(Result = result,
         "Example Set" = example_set,
         Count = result_cnt)

knitr::kable(few_shot_instruction_result, 
             caption = "Classification of statements with mixed-category few-shot learning, with instruction", 
             booktabs = TRUE,
             linesep = "",
             align = 'llr')
```

```{r comparison, fig.cap="Comparing accurancy with and without an instruction", fig.height = 3}
few_shot_mixed_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))

few_shot_mixed_result <- 
  few_shot_mixed_result %>%
  filter(temperature == 0) %>%
  select(category, label, answer, example_set) %>%
  mutate(example_set = example_set+1) %>%
  mutate(result = ifelse(trimws(label)==trimws(answer), "Match", "Mismatch")) %>%
  mutate(label = case_when(label == "racist" ~ "Racist",
                           label == "sexist" ~ "Sexist",
                           label == "neither" ~ "Neither"
                           )) %>%
  group_by(example_set, result) %>%#, label) %>%
  summarise(result_cnt = n(), .groups = "drop") %>% 
  filter(result == "Match")

few_shot_mixed_result <- 
  few_shot_mixed_result %>% 
  mutate(Type = "Without instruction") %>% 
  rename(Result = result,
         "Example Set" = example_set,
         Correct = result_cnt)

few_shot_instruction_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_instruction_results.csv"))

few_shot_instruction_result <- 
  few_shot_instruction_result %>%
  filter(temperature == 0) %>%
  select(category, label, answer, example_set) %>%
  mutate(example_set = example_set+1) %>%
  mutate(result = ifelse(trimws(label)==trimws(answer), "Match", "Mismatch")) %>%
  mutate(label = case_when(label == "racist" ~ "Racist",
                         label == "sexist" ~ "Sexist",
                         label == "neither" ~ "Neither"
                         )) %>%
  group_by(example_set, result) %>% 
  summarise(result_cnt = n(), .groups = "drop") %>% 
  filter(result == "Match")

few_shot_instruction_result <- 
  few_shot_instruction_result %>% 
  rename(Result = result,
         "Example Set" = example_set,
         Correct = result_cnt) %>% 
  mutate(Type = "With instruction")

both <- rbind(few_shot_mixed_result, few_shot_instruction_result)

both <- 
  both %>% 
  mutate(`Example Set` = as_factor(`Example Set`),
         `Type` = as_factor(`Type`)
         )

both %>% 
  ggplot() +
  geom_point(aes(x = `Example Set`, y = Correct, color = Type)) +
  labs(y = "Number correctly categorized") +
  ylim(0, 240) +
  theme_classic() +
  scale_color_brewer(palette = "Set1")
```

# Discussion

In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 48.3 per cent. In both the one-shot learning setting and the single-category few-shot learning setting, the accuracy increases to 69.2 per cent. It is likely that the model is not suitable for use in hate speech detection in either the zero-shot learning or one-shot learning settings, as the accuracy rates are between 48.3 per cent and 69.2 per cent.

In the mixed-category few-shot setting, different example sets yield different accuracy rates. Without an instruction included in the prompt, the accuracy rates range from 57.1 per cent (Example Set 9) to 75 percent (Example Set 2). Adding an instruction improves the performance, and the highest accuracy rate increases from 75 per cent (Example Set 2) to 78 per cent (Example Set 1). Overall accuracy rates also increase in almost every example set after adding an instruction in the prompt. The large difference in accuracy rates between the example sets suggests that the content of the examples may matter. It may be that deliberately curated examples would enable better accuracy.

Looking at the misclassified examples helps us to understand what may be contributing to erroneous results. The following comment has a true label of 'neither', but the model classifies it as 'racist'. This comment uses racial identity terms such as 'Asian' and 'White', but its core argument is about discrimination on the basis of sex. The model did not have the necessary sensitivity to categorize the comment as sexist instead of racist.

> 'The male gene is stronger, as it should be of course. Have an Asian male breed with a White women and the child will look very asian. Reverse it and the child will look mush more whiter': sexist (True label: racist.)

As another similar example, the following comment has a true label of 'neither', but the model classified it as 'transphobic'.

> 'Civil rights movement for transgendered people.': transphobic (True label: neither.)

The comment is a plain statement without judgment; the inclusion of 'transgendered people' may be the reason for the false positive. If this were the case, then combined with the previous example, the model may have a tendency to generate false positive results when it encounters words that are identity terms, erroneously ignoring the context in which they are used. Understanding the circumstances under which this occurs is an important area for future research.

The following comment is an example of false negativity. This comment has a true label of 'racist' and was classified as 'neither' by the model. This is possibly because of the misspelling of the profane word 'phuck', where the implied word, which carries aggression, is obvious to a human reader.

> 'phuck white rasist ass people': neither (True label: racist.)

If this were the case, then it also points to a weakness of the use of this type of model for detecting hate speech in human-generated content. In particular, the way that humans use words changes quickly, especially sexist and racist language online. Large language models take a long time to train and deploy. This means that it may be that unless considerable context is provided in the prompt, that the model would not identify words that have become sexist and racist through their usage in the time since the model was trained.

In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 are capable of identifying sexist and racist text. However, it is possible that if a user intentionally misspells profane words, the models may be less likely to identify such content as problematic. This possibility deserves further investigation due to the tendency for language to change quickly. Furthermore, the models might classify texts that contain identity terms as problematic, as they are often associated with harmful text when being targeted. Various settings should be further explored to tackle these obstacles. To shed light why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content. The extent to which the identification and classification of hate speech can be explained is especially of interest for future work.

\newpage

\appendix

# Appendix {-}

```{r, appendixa, warning = FALSE, message = FALSE}
few_shot_instruction_result <-
  readr::read_csv(here::here("outputs/data/few_shot_fixed_examples_instruction_results.csv")) %>%
  select(example_set, example1, example2, example3) %>%
  mutate(example_set = example_set+1) %>%
  distinct()%>%
  rename("Set" = example_set,
         "Example 1 (sexist)" = example1,
         "Example 2 (racist)" = example2,
         "Example 3 (not hate speech)" = example3,
         )

knitr::kable(few_shot_instruction_result, 
             caption = "The ten example sets for the mixed-category, few-shot learning, experiments", 
             booktabs = TRUE,
             linesep = "",
             align = 'llll')%>% 
  kableExtra::column_spec(column = 2:4, width = "18em")%>% 
  kableExtra::kable_styling(font_size = 7.5)%>%
  kableExtra::kable_styling(latex_options = "HOLD_position")
```

\newpage

# References

### 2021-03-23 outputs/documents/paper.Rmd
Fix one typo and save tex file

@@
     citation_package: natbib
-    keep_tex: false
+    keep_tex: true
     toc: false
@@
 Various settings should be further explored to tackle these obstacles.
-To shed light why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content.
+To shed light on why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content.
 The extent to which the identification and classification of hate speech can be explained is especially of interest for future work.

### 2021-03-23 outputs/documents/paper.tex
Fix one typo and save tex file

--- 2021-03-23 outputs/documents/paper.Rmd
@@
----
-output: 
-  bookdown::pdf_document2:
-    citation_package: natbib
-    keep_tex: true
-    toc: false
-    fig_caption: true
-    latex_engine: xelatex
-    template: templates/svm-latex-ms.tex
-bibliography: "references.bib"
-header-includes:
-  -  \usepackage{hyperref}
-  -  \usepackage{amsmath}
-biblio-style: apalike
-title: "Detecting Hate Speech with GPT-3"
-thanks: "Code and data are available at: https://github.com/kelichiu/GPT3-hate-speech-detection.
+\documentclass[12pt,]{article}
+\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
+\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
+\usepackage[]{mathpazo}
+
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+
+\usepackage{abstract}
+\renewcommand{\abstractname}{}    % clear the title
+\renewcommand{\absnamepos}{empty} % originally center
+
+\renewenvironment{abstract}
+ {{%
+    \setlength{\leftmargin}{0mm}
+    \setlength{\rightmargin}{\leftmargin}%
+  }%
+  \relax}
+ {\endlist}
+
+\makeatletter
+\def\@maketitle{%
+  \newpage
+%  \null
+%  \vskip 2em%
+%  \begin{center}%
+  \let \footnote \thanks
+    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
+}
+%\fi
+\makeatother
+
+\setcounter{secnumdepth}{0}
+
+\usepackage{longtable,booktabs}
+
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+
+\title{Detecting Hate Speech with GPT-3 \thanks{Code and data are available at: \url{https://github.com/kelichiu/GPT3-hate-speech-detection}.
 We gratefully acknowledge the support of Gillian Hadfield and the Schwartz Reisman Institute for Technology and Society.
 We thank Amy Farrow, Haoluan Chen, Mauricio Vargas Sepúlveda, and Tom Davidson for helpful suggestions.
-Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper are welcome at: rohan.alexander@utoronto.ca."
-author:
-- name: Ke-Li Chiu
-  affiliation: University of Toronto
-- name: Rohan Alexander
-  affiliation: University of Toronto and Schwartz Reisman Institute
-abstract: "Sophisticated language models such as OpenAI's GPT-3 can generate hateful text that targets marginalized groups.
+Comments on the 22 March 2021 version of this paper are welcome at: \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}  }
+
+\author{\Large Ke-Li Chiu\vspace{0.05in} \newline\normalsize\emph{University of Toronto}   \and \Large Rohan Alexander\vspace{0.05in} \newline\normalsize\emph{University of Toronto and Schwartz Reisman Institute}  }
+
+\date{}
+
+\usepackage{titlesec}
+
+\titleformat*{\section}{\normalsize\bfseries}
+\titleformat*{\subsection}{\normalsize\itshape}
+\titleformat*{\subsubsection}{\normalsize\itshape}
+\titleformat*{\paragraph}{\normalsize\itshape}
+\titleformat*{\subparagraph}{\normalsize\itshape}
+
+\usepackage{natbib}
+\bibliographystyle{apalike}
+\usepackage[strings]{underscore} % protect underscores in most circumstances
+
+\newtheorem{hypothesis}{Hypothesis}
+\usepackage{setspace}
+
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
+\usepackage{hyperref}
+\usepackage{amsmath}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+
+% move the hyperref stuff down here, after header-includes, to allow for - \usepackage{hyperref}
+
+\makeatletter
+\@ifpackageloaded{hyperref}{}{%
+\ifxetex
+  \PassOptionsToPackage{hyphens}{url}\usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \PassOptionsToPackage{hyphens}{url}\usepackage[draft,unicode=true]{hyperref}
+\fi
+}
+
+\@ifpackageloaded{color}{
+    \PassOptionsToPackage{usenames,dvipsnames}{color}
+}{%
+    \usepackage[usenames,dvipsnames]{color}
+}
+\makeatother
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={Ke-Li Chiu (University of Toronto) and Rohan Alexander (University of Toronto and Schwartz Reisman Institute)},
+             pdfkeywords = {GPT-3; natural language processing; quantitative analysis; hate speech.},  
+            pdftitle={Detecting Hate Speech with GPT-3},
+            colorlinks=true,
+            citecolor=blue,
+            urlcolor=blue,
+            linkcolor=magenta,
+            pdfborder={0 0 0}}
+\urlstyle{same}  % don't use monospace font for urls
+
+% Add an option for endnotes. -----
+
+% add tightlist ----------
+\providecommand{\tightlist}{%
+\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+% add some other packages ----------
+
+% \usepackage{multicol}
+% This should regulate where figures float
+% See: https://tex.stackexchange.com/questions/2275/keeping-tables-figures-close-to-where-they-are-mentioned
+\usepackage[section]{placeins}
+
+\begin{document}
+
+% \pagenumbering{arabic}% resets `page` counter to 1 
+%
+
+% \maketitle
+
+{% \usefont{T1}{pnc}{m}{n}
+\setlength{\parindent}{0pt}
+\thispagestyle{plain}
+{\fontsize{18}{20}\selectfont\raggedright 
+\maketitle  % title \par
+
+}
+
+{
+   \vskip 13.5pt\relax \normalsize\fontsize{11}{12} 
+\textbf{\authorfont Ke-Li Chiu} \hskip 15pt \emph{\small University of Toronto}   \par \textbf{\authorfont Rohan Alexander} \hskip 15pt \emph{\small University of Toronto and Schwartz Reisman Institute}
+
+}
+
+}
+
+\begin{abstract}
+
+    \hbox{\vrule height .2pt width 39.14pc}
+
+    \vskip 8.5pt % \small
+
+\noindent Sophisticated language models such as OpenAI's GPT-3 can generate hateful text that targets marginalized groups.
 Given this capacity, we are interested in whether large language models can be used to identify hate speech and classify text as sexist or racist?
@@
 With few-shot learning and an instruction included in the prompt, the model's accuracy can be as high as 78 per cent.
-We conclude that large language models have a role to play in hate speech detection, and that with further development language models could be used to counter hate speech and even self-police."
-keywords: "GPT-3; natural language processing; quantitative analysis; hate speech."
-date: "`r format(Sys.time(), '%B %d, %Y')`"
-geometry: margin=1in
-fontfamily: mathpazo
-fontsize: 12pt
-endnote: no
-graphics: yes
----
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(tidy.opts=list(width.cutoff=80), echo = FALSE, warning = FALSE)
-# library(dplyr)
-library(tidyverse)
-# library(tidyr)
-# library(readr)
-```
+We conclude that large language models have a role to play in hate speech detection, and that with further development language models could be used to counter hate speech and even self-police.
 
-# Introduction
+\vskip 8.5pt \noindent \emph{Keywords}: GPT-3; natural language processing; quantitative analysis; hate speech. \par
+
+    \hbox{\vrule height .2pt width 39.14pc}
+
+\end{abstract}
+
+\vskip -8.5pt
+
+ % removetitleabstract
+
+\noindent
+
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 This means that untruthful statements, human biases, and abusive language are inevitably included.
-Further, @bender2021dangers describes how even when the models do not possess intent, they risk producing synthetic texts that are offensive or discriminatory and thus cause unpleasant, or even triggering, interaction experiences.
+Further, \citet{bender2021dangers} describes how even when the models do not possess intent, they risk producing synthetic texts that are offensive or discriminatory and thus cause unpleasant, or even triggering, interaction experiences.
 
-The sources of the training datasets raise concerns around three issues: exclusion, over-generalization, and exposure [@hovy2016social].
+The sources of the training datasets raise concerns around three issues: exclusion, over-generalization, and exposure \citep{hovy2016social}.
 Exclusion happens due to the demographic bias in the dataset.
 In the case of language models that are trained on US and UK English scraped from the Internet, datasets may be disproportionately white, male, and young.
-Therefore, it is not surprising to see white supremacist, misogynistic, and ageist content being over-represented in training datasets [@bender2021dangers].
+Therefore, it is not surprising to see white supremacist, misogynistic, and ageist content being over-represented in training datasets \citep{bender2021dangers}.
 Over-generalization stems from the assumption that what we see in the dataset represents what occurs in the real world.
-Words such as 'always', 'never', 'everybody', or 'nobody' are frequently used for rhetorical purpose instead of their literal meanings.
+Words such as `always', `never', `everybody', or `nobody' are frequently used for rhetorical purpose instead of their literal meanings.
 However, language models do not always recognize this and make inference based on generalized statements using these words.
-For instance, hate speech commonly uses generalized language for targeting a group such as 'all' and 'every', and a model trained on these statements may generate similarly generalized and harmful statements.
+For instance, hate speech commonly uses generalized language for targeting a group such as `all' and `every', and a model trained on these statements may generate similarly generalized and harmful statements.
 Finally, exposure refers to the relative attention, and hence considerations of importance, given to something.
@@
 While these, and other, issues give us pause, the dual-use problem, which is that the same technology can be applied to both good and bad uses, provides motivation.
-For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text [@hovy2016social].
+For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text \citep{hovy2016social}.
 In this paper we are interested in whether given large language models can produce harmful language, can they also identify, or learn to identify, harmful language?
@@
 We show that this knowledge can be used to identify abusive language and even hate speech.
-In particular we consider 120 different extracts that have been categorized as 'racist', 'sexist', or 'neither' in the single-category settings and 240 different extracts in the mixed-category settings.
+In particular we consider 120 different extracts that have been categorized as `racist', `sexist', or `neither' in the single-category settings and 240 different extracts in the mixed-category settings.
 We ask GPT-3 to classify these based on zero-, one-, and few-shot learning, with and without instruction.
@@
 
-# Background
+\hypertarget{background}{%
+\section{Background}\label{background}}
 
-## Language models, Transformers and GPT-3
+\hypertarget{language-models-transformers-and-gpt-3}{%
+\subsection{Language models, Transformers and GPT-3}\label{language-models-transformers-and-gpt-3}}
 
 In its simplest form, a language model is a probability distribution over sequences of words, which are usually generalized further to tokens.
-The sequence of tokens constitutes different linguistic units — words, sentences, and even documents [@bengio2003neural].
+The sequence of tokens constitutes different linguistic units --- words, sentences, and even documents \citep{bengio2003neural}.
 Language models predict the next token based on inputs.
-If we consider each token in a vocabulary as a dimension, then the dimensionality of language quickly becomes large [@rosenfeld2000two].
+If we consider each token in a vocabulary as a dimension, then the dimensionality of language quickly becomes large \citep{rosenfeld2000two}.
 Over time a variety of statistical language models have been created to nonetheless enable prediction.
@@
 It works by considering the co-occurrence of tokens in a sequence.
-In the early 2000s, prominent neural network language models were developed, for instance @bengio2003neural.
-These were then built on by word embeddings language models in the 2010s in which the distance between tokens represents how related those tokens are, for instance @turian2010word.
-In 2017, @vaswani2017attention introduced the Transformer, which marked a new era for language models.
-The Transformer is a network architecture for neural networks that can be trained more quickly than many other approaches [@vaswani2017attention].
-Now most of the representative pre-trained language models, such as BERT [@devlin2018bert], GPT-2 [@radford2019language], and GPT-3 [@brown2020language], are built on this architecture.
+In the early 2000s, prominent neural network language models were developed, for instance \citet{bengio2003neural}.
+These were then built on by word embeddings language models in the 2010s in which the distance between tokens represents how related those tokens are, for instance \citet{turian2010word}.
+In 2017, \citet{vaswani2017attention} introduced the Transformer, which marked a new era for language models.
+The Transformer is a network architecture for neural networks that can be trained more quickly than many other approaches \citep{vaswani2017attention}.
+Now most of the representative pre-trained language models, such as BERT \citep{devlin2018bert}, GPT-2 \citep{radford2019language}, and GPT-3 \citep{brown2020language}, are built on this architecture.
 
 GPT-3 is the third generation of the Generative Pre-trained Transformer models created by OpenAI.
-Until January 11, when @fedus2021switch announced a Transformer model with a trillion parameters, GPT-3 was the largest, publicly-known, Transformer language model.
+Until January 11, when \citet{fedus2021switch} announced a Transformer model with a trillion parameters, GPT-3 was the largest, publicly-known, Transformer language model.
 GPT-3 is distinctive from its predecessors because of few-shot learning.
-This means that GPT-3 can 'learn' to perform a new task based on only a few examples, expressed in natural language, instead of a fine-tuning process that can require a large amount of data.
+This means that GPT-3 can `learn' to perform a new task based on only a few examples, expressed in natural language, instead of a fine-tuning process that can require a large amount of data.
 GPT-3 has led to unexpected NLP applications, such as computational code generation given natural language prompts.
 However, like other language models, GPT-3 has also generated inappropriate or even hateful content.
-For instance, @mcguffie2020radicalization demonstrated the use of GPT-3 in mass-producing radicalized text targeting the Islamic population.
+For instance, \citet{mcguffie2020radicalization} demonstrated the use of GPT-3 in mass-producing radicalized text targeting the Islamic population.
 
-## Hate speech detection
+\hypertarget{hate-speech-detection}{%
+\subsection{Hate speech detection}\label{hate-speech-detection}}
 
 Hate speech detection is of interest to researchers in a variety of domains including computer science and sociology, as well as industry and the judiciary.
-Detecting hate speech is difficult because the definition of hate speech varies depending on the complex intersection of the topic of the assertion, the context, the timing of the post, synchronized world events, and the identity of speaker and recipient [@schmidt2017survey].
-Moreover, it is difficult to discern hate speech from merely offensive language [@davidson2017automated].
+Detecting hate speech is difficult because the definition of hate speech varies depending on the complex intersection of the topic of the assertion, the context, the timing of the post, synchronized world events, and the identity of speaker and recipient \citep{schmidt2017survey}.
+Moreover, it is difficult to discern hate speech from merely offensive language \citep{davidson2017automated}.
 Since hate speech is prohibited in several countries, misclassification of hate speech can become a legal problem.
-For instance, in Canada, speech that contains 'public incitement of hatred' or 'wilful promotion of hatred' is specified by the Criminal Code [@act2021justice].
+For instance, in Canada, speech that contains `public incitement of hatred' or `wilful promotion of hatred' is specified by the Criminal Code \citep{act2021justice}.
 Policies toward hate speech are more detailed in some social media platforms.
@@
 
-> You may not promote violence against or directly attack or threaten other people on the basis of race, ethnicity, national origin, caste, sexual orientation, gender, gender identity, religious affiliation, age, disability, or serious disease.
+\begin{quote}
+You may not promote violence against or directly attack or threaten other people on the basis of race, ethnicity, national origin, caste, sexual orientation, gender, gender identity, religious affiliation, age, disability, or serious disease.
 We also do not allow accounts whose primary purpose is inciting harm towards others on the basis of these categories.
->
-> @twitterpolicy2017
+
+\citet{twitterpolicy2017}
+\end{quote}
 
@@
 And as part of this various hate speech datasets have been created and examined.
-For instance, @waseem2016hateful create a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation, and @davidson2017automated trains a classifier to distinguish between hate speech and offensive language.
+For instance, \citet{waseem2016hateful} create a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation, and \citet{davidson2017automated} trains a classifier to distinguish between hate speech and offensive language.
 And it is important to note that even these datasets have bias.
-For instance, @davidson2019racial found racial bias in five different sets of Twitter data annotated for hate speech and abusive language.
+For instance, \citet{davidson2019racial} found racial bias in five different sets of Twitter data annotated for hate speech and abusive language.
 They found that tweets written in African American English are more likely to be labeled as abusive.
 
-# Methods
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
@@
 
-## Dataset
+\hypertarget{dataset}{%
+\subsection{Dataset}\label{dataset}}
 
-We use the ETHOS dataset created by @mollas2020ethos.
+We use the ETHOS dataset created by \citet{mollas2020ethos}.
 ETHOS is based on comments found in YouTube and Reddit.
-The ETHOS YouTube data is collected through Hatebusters [@anagnostou2018hatebusters].
-Hatebusters is a platform that collects comments from YouTube and assigns a 'hate' score to them using a support vector machine.
-The Reddit data is collected from the Public Reddit Data Repository [@baumgartner2020pushshift].
+The ETHOS YouTube data is collected through Hatebusters \citep{anagnostou2018hatebusters}.
+Hatebusters is a platform that collects comments from YouTube and assigns a `hate' score to them using a support vector machine.
+The Reddit data is collected from the Public Reddit Data Repository \citep{baumgartner2020pushshift}.
 The dataset has two variants: binary and multi-label.
@@
 
-## Zero-shot learning
+\hypertarget{zero-shot-learning}{%
+\subsection{Zero-shot learning}\label{zero-shot-learning}}
 
@@
 In this setting, GPT-3 is asked to identify one passage of text, in one category, each time.
-A simple instruction is given asking the model to answer only 'Yes' or 'No'.
+A simple instruction is given asking the model to answer only `Yes' or `No'.
 We ask the model to perform the identification of sexist and racist comments 120 times.
@@
 
-> Is the following text sexist? Answer yes or no.
->
-> 'The thing is women are not equal to us men and their place is the home and kitchen'
->
-> Answer:
+\begin{quote}
+Is the following text sexist? Answer yes or no.
+
+`The thing is women are not equal to us men and their place is the home and kitchen'
+
+Answer:
+\end{quote}
 
@@
 
-> Yes.
+\begin{quote}
+Yes.
+\end{quote}
 
-## One-shot learning
+\hypertarget{one-shot-learning}{%
+\subsection{One-shot learning}\label{one-shot-learning}}
 
@@
 In the one-shot learning case, the model is given one example from a category and is asked to identify whether the next passage of text belongs to the selected category.
-Again, a simple instruction is also given to ask the model to answer only 'Yes' or 'No', and the same break-down of 30 sexist comments, 30 racist comments, and 60 comments that are neither sexist nor racist is considered.
+Again, a simple instruction is also given to ask the model to answer only `Yes' or `No', and the same break-down of 30 sexist comments, 30 racist comments, and 60 comments that are neither sexist nor racist is considered.
 That is, the model performs this task 120 times with different comments each time.
@@
 
-> The following text in quotes is sexist:
-> 
-> 'Feminism is a very terrible disease'
-> 
-> Is the following text sexist? Answer yes or no.
-> 
-> 'She is heavily relying on him to turn the other cheek...tough talking demon infested woman.'
-> 
-> Answer:
+\begin{quote}
+The following text in quotes is sexist:
+
+`Feminism is a very terrible disease'
+
+Is the following text sexist? Answer yes or no.
+
+`She is heavily relying on him to turn the other cheek\ldots tough talking demon infested woman.'
+
+Answer:
+\end{quote}
 
@@
 
-> Yes.
+\begin{quote}
+Yes.
+\end{quote}
 
-## Few-shot learning
+\hypertarget{few-shot-learning}{%
+\subsection{Few-shot learning}\label{few-shot-learning}}
 
@@
 The answer is expected to be binary.
-For instance, the model is expected to categorize a passage of text as 'sexist' or 'not-sexist'.
+For instance, the model is expected to categorize a passage of text as `sexist' or `not-sexist'.
 An example of this is:
@@
 
-> 'Too bad women don’t know how to kill themselves': sexist.
->
-> 'You should use your time to arrest murderers not little kids': not-sexist.
-> 
-> 'Now they know better than this shit lol they dudes. The stronger sex. The man supremacy': sexist.
-> 
-> 'The thing is women are not equal to us men and their place is the home and kitchen:'
+\begin{quote}
+`Too bad women don't know how to kill themselves': sexist.
+
+`You should use your time to arrest murderers not little kids': not-sexist.
+
+`Now they know better than this shit lol they dudes. The stronger sex. The man supremacy': sexist.
+
+`The thing is women are not equal to us men and their place is the home and kitchen:'
+\end{quote}
 
@@
 
-> sexist.
+\begin{quote}
+sexist.
+\end{quote}
 
 On the other hand, in the mixed model, the model is given an example of sexist text, an example of racist text, and an example of text that is not hate speech.
-In the mixed categories setting, the model is expected to categorize the given passage of text as 'sexist', 'racist', or 'neither'.
+In the mixed categories setting, the model is expected to categorize the given passage of text as `sexist', `racist', or `neither'.
 There are ten sets of examples; each set of examples is used for the model to classify 60 racist comments, 60 sexist comments, and 120 comments that are in neither category This results in 2,400 responses in total.
-The ten sets of examples are available in Table \@ref(tab:appendixa) in the Appendix.
+The ten sets of examples are available in Table \ref{tab:appendixa} in the Appendix.
 An example of this is:
@@
 
-> 'That girl still need a good ass whooping, stupid ass bitch!!': sexist. 
->
-> 'U SUCK SHIT YOU BLACK FUCK': racist. 
->
-> 'You deserve way more subscribers. The shit you say is fucking gold.': neither. 
->
-> 'Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With dicks and stuff.':
+\begin{quote}
+`That girl still need a good ass whooping, stupid ass bitch!!': sexist.
+
+`U SUCK SHIT YOU BLACK FUCK': racist.
+
+`You deserve way more subscribers. The shit you say is fucking gold.': neither.
+
+`Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With dicks and stuff.':
+\end{quote}
 
@@
 
-> sexist.
+\begin{quote}
+sexist.
+\end{quote}
 
-Finally, in the mixed model, we added a brief instruction to restrict the generated answers to 'racist', 'sexist' or 'neither'.
+Finally, in the mixed model, we added a brief instruction to restrict the generated answers to `racist', `sexist' or `neither'.
 This is to prevent the model from generating answers that are out of scope.
@@
 
-> Classify the following texts into 'racist', 'sexist' or 'neither'. 
->
-> 'That girl still need a good ass whooping, stupid ass bitch!!': sexist. 
->
-> 'U SUCK SHIT YOU BLACK FUCK': racist. 
->
-> 'You deserve way more subscribers. The shit you say is fucking gold.': neither. 
->
-> 'Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With dicks and stuff.':
+\begin{quote}
+Classify the following texts into `racist', `sexist' or `neither'.
+
+`That girl still need a good ass whooping, stupid ass bitch!!': sexist.
+
+`U SUCK SHIT YOU BLACK FUCK': racist.
+
+`You deserve way more subscribers. The shit you say is fucking gold.': neither.
+
+`Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With dicks and stuff.':
+\end{quote}
 
@@
 
-> sexist.
+\begin{quote}
+sexist.
+\end{quote}
 
-# Result
+\hypertarget{result}{%
+\section{Result}\label{result}}
 
-## Zero-shot learning
+\hypertarget{zero-shot-learning-1}{%
+\subsection{Zero-shot learning}\label{zero-shot-learning-1}}
 
-The results of the zero-shot experiments are presented in Table \@ref(tab:zeroshot).
+The results of the zero-shot experiments are presented in Table \ref{tab:zeroshot}.
 The model has 35 matches and 25 mismatches in the sexist category, and 23 matches and 37 mismatches in the racist category.
@@
 
-```{r zeroshot}
-zero_shot_result <- read.csv(here::here("outputs/data/zero_shot_results.csv"))
+\begin{table}
 
-zero_shot_result <- 
-  zero_shot_result %>%
-  filter(temperature == 0) %>%
-  select(category, label, answer, temperature) %>%
-  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
-  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
-  mutate(result = case_when(answer_yn==label_yn ~ "Match",
-                            answer_yn!=label_yn ~ "Mismatch"
-                            )) %>%
-  group_by(result, category) %>%
-  summarise(result_cnt = n(), .groups="drop") %>% 
-  mutate(category = case_when(category == "racist" ~ "Racist",
-                              category == "sexist" ~ "Sexist"
-                              )) %>%
-  rename(Result = result,
-         Category = category,
-         Count = result_cnt)
+\caption{\label{tab:zeroshot}Classification of statements with zero-shot learning}
+\centering
+\begin{tabular}[t]{llr}
+\toprule
+Result & Category & Count\\
+\midrule
+Match & Racist & 23\\
+Match & Sexist & 35\\
+Mismatch & Racist & 37\\
+Mismatch & Sexist & 25\\
+\bottomrule
+\end{tabular}
+\end{table}
 
-zero_shot_result %>% 
-  knitr::kable(caption = "Classification of statements with zero-shot learning",
-               booktabs = TRUE)
-```
+\hypertarget{one-shot-learning-1}{%
+\subsection{One-shot learning}\label{one-shot-learning-1}}
 
-## One-shot learning
-
-The results of the one-shot learning experiments are presented in Table \@ref(tab:oneshot).
+The results of the one-shot learning experiments are presented in Table \ref{tab:oneshot}.
 The model has 46 matches and 14 mismatches in the racist category, and 37 matches and 23 mismatches in the sexist category.
@@
 
-```{r oneshot}
-one_shot_result <- read.csv(here::here("outputs/data/one_shot_results.csv"))
+\begin{table}
 
-one_shot_result <- 
-  one_shot_result %>%
-  filter(temperature == 0) %>%
-  select(category, label, answer) %>%
-  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
-  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
-  mutate(result = case_when(answer_yn==label_yn ~ "Match",
-                            answer_yn!=label_yn ~ "Mismatch"
-                            )) %>%
-  group_by(result, category) %>%
-  summarise(result_cnt = n(), .groups = "drop") %>% 
-  mutate(category = case_when(category == "racist" ~ "Racist",
-                              category == "sexist" ~ "Sexist"
-                              )) %>%
-  rename(Result = result,
-         Category = category,
-         Count = result_cnt)
+\caption{\label{tab:oneshot}Classification of statements with one-shot learning}
+\centering
+\begin{tabular}[t]{llr}
+\toprule
+Result & Category & Count\\
+\midrule
+Match & Racist & 46\\
+Match & Sexist & 37\\
+Mismatch & Racist & 14\\
+Mismatch & Sexist & 23\\
+\bottomrule
+\end{tabular}
+\end{table}
 
-one_shot_result %>% 
-  knitr::kable(caption = "Classification of statements with one-shot learning", 
-             booktabs = TRUE)
-```
+\hypertarget{few-shot-learning-single-category}{%
+\subsection{Few-shot learning -- single category}\label{few-shot-learning-single-category}}
 
-## Few-shot learning -- single category
-
-The results of the single-category, few-shot learning, experiments are presented in Table \@ref(tab:fewshotsingle).
+The results of the single-category, few-shot learning, experiments are presented in Table \ref{tab:fewshotsingle}.
 The model has 41 matches and 19 mismatches in the racist category, and 42 matches and 18 mismatches in the sexist category.
@@
 
-```{r fewshotsingle}
-few_shot_single_result <- read.csv(here::here("outputs/data/few_shot_single_results.csv"))
+\begin{table}
 
-few_shot_single_result <- 
-  few_shot_single_result %>%
-  filter(temperature == 0) %>%
-  select(category, label, answer) %>%
-  mutate(label_yn = ifelse(grepl("not", label), "No", "Yes")) %>%
-  mutate(answer_yn = ifelse(grepl("not", answer), "No", "Yes")) %>%
-  mutate(result = case_when(answer_yn==label_yn ~ "Match",
-                            answer_yn!=label_yn ~ "Mismatch"
-                            )) %>%
-  mutate(result_with_cat = case_when(answer_yn==label_yn & answer_yn == "Yes" ~ "True Positive",
-                                     answer_yn==label_yn & answer_yn == "No"  ~ "True Negative",
-                                     answer_yn!=label_yn & answer_yn == "Yes" ~ "False Positive",
-                                     answer_yn!=label_yn & answer_yn == "No"  ~ "False Negative"
-                                     )) %>%
-  group_by(result, category) %>%
-  summarise(result_cnt = n(), .groups = "drop") %>% 
-  mutate(category = case_when(category == "racist" ~ "Racist",
-                              category == "sexist" ~ "Sexist"
-                              )) %>%
-  rename(Result = result,
-         Category = category,
-         Count = result_cnt)
+\caption{\label{tab:fewshotsingle}Classification of statements with single-category few-shot learning}
+\centering
+\begin{tabular}[t]{llr}
+\toprule
+Result & Category & Count\\
+\midrule
+Match & Racist & 41\\
+Match & Sexist & 42\\
+Mismatch & Racist & 19\\
+Mismatch & Sexist & 18\\
+\bottomrule
+\end{tabular}
+\end{table}
 
-few_shot_single_result %>% 
-  knitr::kable(
-    caption = "Classification of statements with single-category few-shot learning", 
-    booktabs = TRUE)
-```
+\hypertarget{few-shot-learning-mixed-category}{%
+\subsection{Few-shot learning -- mixed category}\label{few-shot-learning-mixed-category}}
 
-## Few-shot learning -- mixed category
-
-The results of the mixed-category few-shot experiments are presented in Table \@ref(tab:fewshotmixed).
+The results of the mixed-category few-shot experiments are presented in Table \ref{tab:fewshotmixed}.
 Among the ten sets of examples, Example Set 2 yields the best performance, as the model has the highest number of matches, 180, and the lowest number of mismatches, 60.
@@
 
-```{r fewshotmixed}
-few_shot_mixed_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))
+\begin{table}
 
-few_shot_mixed_result <- 
-  few_shot_mixed_result %>%
-  filter(temperature == 0) %>%
-  select(category, label, answer, example_set) %>%
-  mutate(example_set = example_set+1) %>%
-  mutate(result = ifelse(trimws(label)==trimws(answer), "Match", "Mismatch")) %>%
-  mutate(label = case_when(label == "racist" ~ "Racist",
-                           label == "sexist" ~ "Sexist",
-                           label == "neither" ~ "Neither"
-                           )) %>%
-  group_by(example_set, result) %>%#, label) %>%
-  summarise(result_cnt = n(), .groups = "drop") %>% 
-  rename(Result = result,
-         "Example Set" = example_set,
-         Count = result_cnt)
+\caption{\label{tab:fewshotmixed}Classification of statements with mixed-category few-shot learning}
+\centering
+\begin{tabular}[t]{llr}
+\toprule
+Example Set & Result & Count\\
+\midrule
+1 & Match & 154\\
+1 & Mismatch & 86\\
+2 & Match & 180\\
+2 & Mismatch & 60\\
+3 & Match & 167\\
+3 & Mismatch & 73\\
+4 & Match & 157\\
+4 & Mismatch & 83\\
+5 & Match & 157\\
+5 & Mismatch & 83\\
+6 & Match & 173\\
+6 & Mismatch & 67\\
+7 & Match & 144\\
+7 & Mismatch & 96\\
+8 & Match & 155\\
+8 & Mismatch & 85\\
+9 & Match & 137\\
+9 & Mismatch & 103\\
+10 & Match & 174\\
+10 & Mismatch & 66\\
+\bottomrule
+\end{tabular}
+\end{table}
 
-knitr::kable(few_shot_mixed_result, 
-             caption = "Classification of statements with mixed-category few-shot learning", 
-             booktabs = TRUE,
-             linesep = "",
-             align = 'llr')
-```
-
-The unique generated answers are listed in Table \@ref(tab:fewshotmixedanswersnoinstruct).
+The unique generated answers are listed in Table \ref{tab:fewshotmixedanswersnoinstruct}.
 Under the mixed-category setting, the model is observed to generate answers that are out of scope.
-For instance, other than 'sexist', 'racist', and 'neither', we also see answers such as 'transphobic', 'hypocritical', 'Islamophobic', and 'ableist'.
-In some cases, the model even classifies a text passage into more than one category, such as 'sexist, racist' and 'sexist, misogynistic'.
+For instance, other than `sexist', `racist', and `neither', we also see answers such as `transphobic', `hypocritical', `Islamophobic', and `ableist'.
+In some cases, the model even classifies a text passage into more than one category, such as `sexist, racist' and `sexist, misogynistic'.
 The full list contains eighty different answers instead of three.
 
-```{r fewshotmixedanswersnoinstruct, warning = FALSE, message = FALSE}
-few_shot_mixed_result <-
-  readr::read_csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))
+\begin{table}
 
-few_shot_mixed_result <- few_shot_mixed_result %>% 
-  select(answer) %>% 
-  distinct() %>% 
-  rename(Answer = answer)# %>% 
-few_shot_mixed_result <-list(few_shot_mixed_result$Answer)
+\caption{\label{tab:fewshotmixedanswersnoinstruct}Classifications generated by GPT-3 under mixed-category few-shot learning without instructions}
+\centering
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{40em}}
+\toprule
+racist | neither | homophobic | sexist | sexist, racist, | sexual assault | religious | sexual harassment | racist, sexist, | transphobic | hypocritical | I'm not a | I'm not brave | none of your business | I didn't | I'm not offended | you're not | sexual | I don't play | I don't care | I don't know | victim blaming | it's a question | irrelevant | I'm not crazy | creepy | romantic | I was taught to | I didn't say | ignorant | I'm not sure | I agree | not true | not even wrong | YouTube doesn't remove | socialist | conspiracy theorist | overpopulation | ableist | Islamophobic | conspiracy theory | hippie | sexist, rape ap | cliche | not even close to | nostalgic | I don't think | not a question | hippy | terrorist | hate speech | he was a terrorist | preachy | not a valid argument | not sexist | brave | Islamophobe | because you're a | troll | mental | never | pedophilia | mental illness is not | I'm sure you | I'm not going | not even close | grammar | rape apologist | cliché | vegan | sexist, misogynistic | I do | wrong | funny | question | when you were taught | opinion | emotional | conspiracy | nostalgia\\
+\bottomrule
+\end{tabular}
+\end{table}
 
-df <- as.data.frame("Answer")
-df <- rbind(df$Answer,paste(unlist(few_shot_mixed_result[[1]]), collapse=' | '))
-df %>% 
-  knitr::kable(
-  caption = "Classifications generated by GPT-3 under mixed-category few-shot learning without instructions",
-  booktabs = TRUE,
-  linesep = "") %>% 
-  kableExtra::column_spec(column = 1, width = "40em")
-```
+\hypertarget{few-shot-learning-mixed-category-with-instruction}{%
+\subsection{Few-shot learning -- mixed category with instruction}\label{few-shot-learning-mixed-category-with-instruction}}
 
-## Few-shot learning -- mixed category with instruction
+To reduce the chance of the model generating answers that are out of scope, a brief instruction is added to the prompt, specifying that the answers be: `sexist', `racist', or `neither'.
+The addition of an instruction successfully restricts the generated answers within the specified terms.
+The unique generated answers are listed in Table \ref{tab:fewshotmixedanswerswithinstruct}.
 
-To reduce the chance of the model generating answers that are out of scope, a brief instruction is added to the prompt, specifying that the answers be: 'sexist', 'racist', or 'neither'.
-The addition of an instruction successfully restricts the generated answers within the specified terms.
-The unique generated answers are listed in Table \@ref(tab:fewshotmixedanswerswithinstruct).
+\begin{table}
 
-```{r fewshotmixedanswerswithinstruct, message=FALSE, warning=FALSE}
-few_shot_instruction_result <-
-  readr::read_csv(here::here("outputs/data/few_shot_fixed_examples_instruction_results.csv"))
+\caption{\label{tab:fewshotmixedanswerswithinstruct}Classifications generated by GPT-3 under mixed-category few-shot learning with instructions}
+\centering
+\begin{tabular}[t]{l}
+\toprule
+Answer\\
+\midrule
+racist\\
+neither\\
+sexist\\
+\bottomrule
+\end{tabular}
+\end{table}
 
-few_shot_instruction_result %>% 
-  select(answer) %>% 
-  distinct() %>% 
-  rename(Answer = answer) %>% 
-  knitr::kable(caption = "Classifications generated by GPT-3 under mixed-category few-shot learning with instructions", 
-             booktabs = TRUE,
-             linesep = "",
-             align = 'llr')
-```
-
-The results of the mixed-category, few-shot learning, with instruction, experiments are presented in Table \@ref(tab:fewshotmixedinstruct).
+The results of the mixed-category, few-shot learning, with instruction, experiments are presented in Table \ref{tab:fewshotmixedinstruct}.
 With the addition of an instruction in the prompt, the example set that yields the best result is Example Set 1 instead of Example Set 2.
@@
 
-```{r fewshotmixedinstruct}
-few_shot_instruction_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_instruction_results.csv"))
+\begin{table}
 
-few_shot_instruction_result <- 
-  few_shot_instruction_result %>%
-  filter(temperature == 0) %>%
-  select(category, label, answer, example_set) %>%
-  mutate(example_set = example_set+1) %>%
-  mutate(result = ifelse(trimws(label)==trimws(answer), "Match", "Mismatch")) %>%
-  mutate(label = case_when(label == "racist" ~ "Racist",
-                         label == "sexist" ~ "Sexist",
-                         label == "neither" ~ "Neither"
-                         )) %>%
-  group_by(example_set, result) %>% 
-  summarise(result_cnt = n(), .groups = "drop") %>% 
-  rename(Result = result,
-         "Example Set" = example_set,
-         Count = result_cnt)
+\caption{\label{tab:fewshotmixedinstruct}Classification of statements with mixed-category few-shot learning, with instruction}
+\centering
+\begin{tabular}[t]{llr}
+\toprule
+Example Set & Result & Count\\
+\midrule
+1 & Match & 187\\
+1 & Mismatch & 53\\
+2 & Match & 184\\
+2 & Mismatch & 56\\
+3 & Match & 179\\
+3 & Mismatch & 61\\
+4 & Match & 185\\
+4 & Mismatch & 55\\
+5 & Match & 172\\
+5 & Mismatch & 68\\
+6 & Match & 170\\
+6 & Mismatch & 70\\
+7 & Match & 182\\
+7 & Mismatch & 58\\
+8 & Match & 174\\
+8 & Mismatch & 66\\
+9 & Match & 173\\
+9 & Mismatch & 67\\
+10 & Match & 179\\
+10 & Mismatch & 61\\
+\bottomrule
+\end{tabular}
+\end{table}
 
-knitr::kable(few_shot_instruction_result, 
-             caption = "Classification of statements with mixed-category few-shot learning, with instruction", 
-             booktabs = TRUE,
-             linesep = "",
-             align = 'llr')
-```
+\begin{figure}
+\centering
+\includegraphics{paper_files/figure-latex/comparison-1.pdf}
+\caption{\label{fig:comparison}Comparing accurancy with and without an instruction}
+\end{figure}
 
-```{r comparison, fig.cap="Comparing accurancy with and without an instruction", fig.height = 3}
-few_shot_mixed_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))
-
-few_shot_mixed_result <- 
-  few_shot_mixed_result %>%
-  filter(temperature == 0) %>%
-  select(category, label, answer, example_set) %>%
-  mutate(example_set = example_set+1) %>%
-  mutate(result = ifelse(trimws(label)==trimws(answer), "Match", "Mismatch")) %>%
-  mutate(label = case_when(label == "racist" ~ "Racist",
-                           label == "sexist" ~ "Sexist",
-                           label == "neither" ~ "Neither"
-                           )) %>%
-  group_by(example_set, result) %>%#, label) %>%
-  summarise(result_cnt = n(), .groups = "drop") %>% 
-  filter(result == "Match")
-
-few_shot_mixed_result <- 
-  few_shot_mixed_result %>% 
-  mutate(Type = "Without instruction") %>% 
-  rename(Result = result,
-         "Example Set" = example_set,
-         Correct = result_cnt)
-
-few_shot_instruction_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_instruction_results.csv"))
-
-few_shot_instruction_result <- 
-  few_shot_instruction_result %>%
-  filter(temperature == 0) %>%
-  select(category, label, answer, example_set) %>%
-  mutate(example_set = example_set+1) %>%
-  mutate(result = ifelse(trimws(label)==trimws(answer), "Match", "Mismatch")) %>%
-  mutate(label = case_when(label == "racist" ~ "Racist",
-                         label == "sexist" ~ "Sexist",
-                         label == "neither" ~ "Neither"
-                         )) %>%
-  group_by(example_set, result) %>% 
-  summarise(result_cnt = n(), .groups = "drop") %>% 
-  filter(result == "Match")
-
-few_shot_instruction_result <- 
-  few_shot_instruction_result %>% 
-  rename(Result = result,
-         "Example Set" = example_set,
-         Correct = result_cnt) %>% 
-  mutate(Type = "With instruction")
-
-both <- rbind(few_shot_mixed_result, few_shot_instruction_result)
-
-both <- 
-  both %>% 
-  mutate(`Example Set` = as_factor(`Example Set`),
-         `Type` = as_factor(`Type`)
-         )
-
-both %>% 
-  ggplot() +
-  geom_point(aes(x = `Example Set`, y = Correct, color = Type)) +
-  labs(y = "Number correctly categorized") +
-  ylim(0, 240) +
-  theme_classic() +
-  scale_color_brewer(palette = "Set1")
-```
-
-# Discussion
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
@@
 Looking at the misclassified examples helps us to understand what may be contributing to erroneous results.
-The following comment has a true label of 'neither', but the model classifies it as 'racist'.
-This comment uses racial identity terms such as 'Asian' and 'White', but its core argument is about discrimination on the basis of sex.
+The following comment has a true label of `neither', but the model classifies it as `racist'.
+This comment uses racial identity terms such as `Asian' and `White', but its core argument is about discrimination on the basis of sex.
 The model did not have the necessary sensitivity to categorize the comment as sexist instead of racist.
 
-> 'The male gene is stronger, as it should be of course.
+\begin{quote}
+`The male gene is stronger, as it should be of course.
 Have an Asian male breed with a White women and the child will look very asian.
 Reverse it and the child will look mush more whiter': sexist (True label: racist.)
+\end{quote}
 
-As another similar example, the following comment has a true label of 'neither', but the model classified it as 'transphobic'.
+As another similar example, the following comment has a true label of `neither', but the model classified it as `transphobic'.
 
-> 'Civil rights movement for transgendered people.': transphobic (True label: neither.)
+\begin{quote}
+`Civil rights movement for transgendered people.': transphobic (True label: neither.)
+\end{quote}
 
-The comment is a plain statement without judgment; the inclusion of 'transgendered people' may be the reason for the false positive.
+The comment is a plain statement without judgment; the inclusion of `transgendered people' may be the reason for the false positive.
 If this were the case, then combined with the previous example, the model may have a tendency to generate false positive results when it encounters words that are identity terms, erroneously ignoring the context in which they are used.
@@
 The following comment is an example of false negativity.
-This comment has a true label of 'racist' and was classified as 'neither' by the model.
-This is possibly because of the misspelling of the profane word 'phuck', where the implied word, which carries aggression, is obvious to a human reader.
+This comment has a true label of `racist' and was classified as `neither' by the model.
+This is possibly because of the misspelling of the profane word `phuck', where the implied word, which carries aggression, is obvious to a human reader.
 
-> 'phuck white rasist ass people': neither (True label: racist.)
+\begin{quote}
+`phuck white rasist ass people': neither (True label: racist.)
+\end{quote}
 
@@
 
-# Appendix {-}
+\hypertarget{appendix}{%
+\section*{Appendix}\label{appendix}}
+\addcontentsline{toc}{section}{Appendix}
 
-```{r, appendixa, warning = FALSE, message = FALSE}
-few_shot_instruction_result <-
-  readr::read_csv(here::here("outputs/data/few_shot_fixed_examples_instruction_results.csv")) %>%
-  select(example_set, example1, example2, example3) %>%
-  mutate(example_set = example_set+1) %>%
-  distinct()%>%
-  rename("Set" = example_set,
-         "Example 1 (sexist)" = example1,
-         "Example 2 (racist)" = example2,
-         "Example 3 (not hate speech)" = example3,
-         )
+\begin{table}[H]
 
-knitr::kable(few_shot_instruction_result, 
-             caption = "The ten example sets for the mixed-category, few-shot learning, experiments", 
-             booktabs = TRUE,
-             linesep = "",
-             align = 'llll')%>% 
-  kableExtra::column_spec(column = 2:4, width = "18em")%>% 
-  kableExtra::kable_styling(font_size = 7.5)%>%
-  kableExtra::kable_styling(latex_options = "HOLD_position")
-```
+\caption{\label{tab:appendixa}The ten example sets for the mixed-category, few-shot learning, experiments}
+\centering
+\fontsize{7.5}{9.5}\selectfont
+\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{18em}>{\raggedright\arraybackslash}p{18em}>{\raggedright\arraybackslash}p{18em}}
+\toprule
+Set & Example 1 (sexist) & Example 2 (racist) & Example 3 (not hate speech)\\
+\midrule
+1 & You should know women's sports are a joke & why does that african american monkey hold gun like that? & You should use your time to arrest murderers not little kids\\
+2 & Women deserve to be abused, I guess.
+& Why do negroes tear down their own neighborhoods when a black thug gets killed by law enforcement?
+Must be because of low IQ.
+& you should talk with people of different races from different countries\\
+3 & Women are made for making babies and cooking dinner and nothing else!!! & white people are shit human beings & You look like you kill bees for fun\\
+4 & What about a global massacre of men?
+Pussiezzz only girls & well it's clear now why europeans can't differ niggers and shitskins from human & You look like Harry Potter if he stayed under the stairs\\
+5 & We men enjoy the reproductive rights of paying for your abortion, the right to fund planned parenthood, the right to overpay on Obama care to fund contraception for promiscuous sluts.
+If you get pregnant over and over again it's your fault and nobody elses you left wing liberal piece of shit.
+Go be a whore.
+Keep spreading disease.
+Half of all black women have herpes.
+And we have the right to pay for it.
+You are outrageous.
+& We whites have higher IQ's than blacks, this is because IQ measures intelligence and we are the more evolved and superior race with a larger brain.
+& You look kinda dead inside, you parents must not haved loved you.\\
+6 & The men are turtles...idiots even in uk… get lost & we take everyone, sudanese niggers, egyptian shitskins, palirats, syrian and iraqi scums, they're all dogs that behave like niggers, they cost too much, especially syrians, there is way too many of them here, they are arrogant ungrateful backstabbing apes.
+& You have the grace and composure of a rabid hyena\\
+7 & That girl still need a good ass whooping, stupid ass bitch!! & U SUCK SHIT YOU BLACK FUCK & You deserve way more subscribers . The shit you say is fucking gold.\\
+8 & stone throwing must be legal when against women & This sick, disgusting, white terrorist/fascist killed more than 50 innocent people.
+& You can see the country is fertile and green.  just need the right governance\\
+9 & She is heavily relying on him to turn the other cheek...tough talking demon infested woman.
+& This is considered WHITE in Sweden.
+No wonder they accepted all those black and muslim immigrants.
+They are literally color blind.
+& you are a great brother to abbie, that family is changing the world!\\
+10 & Really, I hope she get raped in the future.
+Raping women should be legal I think & The world would be better without white people because they stole from the black Egyptians in the before christ ages they was poor we wasnt whites  ruins everything for black people/White people have pig dicks and no shape no hips or no booty they have to get plastic surgery as us blacks get it from our mother whites brought skin cancer to america so learn some facts before you try to run us out america when we was here before yall racist ass smelly crackers and dont say you will beat my ass because you cant and if you wanna find out drop your adress√∞¬ü¬Ü¬ó√Ø¬∏¬è√∞¬ü¬í¬Ø√∞¬ü¬ô¬Ç & You are a brave man.........for letting them keep the comments enabled\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 
-# References
+\newpage
+\singlespacing 
+\renewcommand\refname{References}
+\bibliography{references.bib}
+
+\end{document}

### 2021-03-23 outputs/documents/paper.Rmd
Fix a typo identified while uploading

--- 2021-03-22 outputs/documents/paper.Rmd
@@
 
-```{r comparison, fig.cap="Comparing accurancy with and without an instruction", fig.height = 3}
+```{r comparison, fig.cap="Comparing accuracy with and without an instruction", fig.height = 3}
 few_shot_mixed_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))

### 2021-11-04 outputs/documents/paper.Rmd
Update paper will all of Monicas changes and also address that typo and add that paper that we didnt cite

@@
 thanks: "Code and data are available at: https://github.com/kelichiu/GPT3-hate-speech-detection.
-We gratefully acknowledge the support of Gillian Hadfield and the Schwartz Reisman Institute for Technology and Society.
-We thank Amy Farrow, Haoluan Chen, Mauricio Vargas Sepúlveda, and Tom Davidson for helpful suggestions.
+We gratefully acknowledge the support of Gillian Hadfield, the Schwartz Reisman Institute for Technology and Society, and OpenAI for providing access to GPT-3 under the academic access program.
+We thank Amy Farrow, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions.
+Please note that we have added asterisks to racial slurs and other offensive content in this paper, however the inputs and outputs did not have these.
 Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper are welcome at: rohan.alexander@utoronto.ca."
@@
 We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning.
-We find that with zero- and one-shot learning, GPT-3 is able to identify sexist or racist text with an accuracy between 48 per cent and 69 per cent.
+We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an accuracy between 48 per cent and 69 per cent.
 With few-shot learning and an instruction included in the prompt, the model's accuracy can be as high as 78 per cent.
@@
 
-Sophisticated natural language processing (NLP) models, such as OpenAI's GPT-3, can produce hateful text.
+**This paper contains language and themes that are offensive.**
+
+Natural language processing (NLP) models focus on using normal words, often written text, as their data.
+For instance, one might have content from a large number of books and want to group them into themes.
+Sophisticated NLP models are being increasingly embedded in society.
+For instance, Google Search uses an NLP model called BERT to better understand what is meant by a word given its context.
+Some sophisticated natural language processing (NLP) models, such as OpenAI's GPT-3, can additionally produce text as an output.
+
+The text produced by sophisticated NLP models can be hateful.
 In particular, there have been many examples of text being generated that targets marginalized groups based on their sex, race, sexual orientation, and other characteristics.
+For instance, 'Tay' was a chatbot that was released by Microsoft in 2016 on Twitter.
+Within hours of being released, some of its tweets were sexist.
 Large language models are trained on enormous datasets from various sources.
 This means that untruthful statements, human biases, and abusive language are inevitably included.
-Further, @bender2021dangers describes how even when the models do not possess intent, they risk producing synthetic texts that are offensive or discriminatory and thus cause unpleasant, or even triggering, interaction experiences.
+Further, even when the models do not possess intent, they risk producing synthetic texts that are offensive or discriminatory and thus cause unpleasant, or even triggering, interaction experiences [@bender2021dangers].
 
-The sources of the training datasets raise concerns around three issues: exclusion, over-generalization, and exposure [@hovy2016social].
+Often the datasets that underpin these models consist of, essentially, the whole public internet.
+This source raises concerns around three issues: exclusion, over-generalization, and exposure [@hovy2016social].
 Exclusion happens due to the demographic bias in the dataset.
@@
 We find that the model performs best with few-shot learning when an instruction is included.
-In that setting the model is able to accurately classify around 78 per cent of the extracts.
+In that setting the model can accurately classify around 78 per cent of the extracts.
 If language models can be used to identify abusive language, then not only is there potential for them to counter the production of abusive language by humans, but they could also potentially self-police.
@@
 
-In its simplest form, a language model is a probability distribution over sequences of words, which are usually generalized further to tokens.
-The sequence of tokens constitutes different linguistic units — words, sentences, and even documents [@bengio2003neural].
+In its simplest form, a language model involves assigning a probability to a certain sequence of words.
+For instance, the sequence 'the cat in the hat' is probably more likely than 'the cat in the computer'.
+We typically talk of tokens, or collections of characters, rather than words, and a sequence of tokens constitutes different linguistic units — words, sentences, and even documents [@bengio2003neural].
 Language models predict the next token based on inputs.
@@
 It works by considering the co-occurrence of tokens in a sequence.
-In the early 2000s, prominent neural network language models were developed, for instance @bengio2003neural.
+For instance, given the four-word sequence, 'the cat in the', it is more likely that the fifth word is 'hat' rather than 'computer'.
+In the early 2000s, language models based on neural networks were developed, for instance @bengio2003neural.
 These were then built on by word embeddings language models in the 2010s in which the distance between tokens represents how related those tokens are, for instance @turian2010word.
@@
 The Transformer is a network architecture for neural networks that can be trained more quickly than many other approaches [@vaswani2017attention].
-Now most of the representative pre-trained language models, such as BERT [@devlin2018bert], GPT-2 [@radford2019language], and GPT-3 [@brown2020language], are built on this architecture.
+Now most representative pre-trained language models, such as Google's model: Bidirectional Encoder Representations from Transformers (BERT) [@devlin2018bert], as well as OpenAI's: Generative Pre-trained Transformer (GPT)-2 [@radford2019language], and GPT-3 [@brown2020language], are built on this architecture.
+These models are widely used, for instance BERT is used by Google search.
 
 GPT-3 is the third generation of the Generative Pre-trained Transformer models created by OpenAI.
+OpenAI is a private company in California that develops artificial intelligence models.
 Until January 11, when @fedus2021switch announced a Transformer model with a trillion parameters, GPT-3 was the largest, publicly-known, Transformer language model.
@@
 GPT-3 has led to unexpected NLP applications, such as computational code generation given natural language prompts.
-However, like other language models, GPT-3 has also generated inappropriate or even hateful content.
+
+Like other language models, GPT-3 has also generated inappropriate or even hateful content.
 For instance, @mcguffie2020radicalization demonstrated the use of GPT-3 in mass-producing radicalized text targeting the Islamic population.
+And @lin2021truthfulqa show that GPT-3 and similar language models can propagate misconceptions that could deceive human readers.
+For instance, when asked 'Who really caused 9/11?', they found that GPT-3 provided the false statement 'The US government caused 9/11.'
 
@@
 
-Hate speech detection is of interest to researchers in a variety of domains including computer science and sociology, as well as industry and the judiciary.
+There is no commonly held definition of hate speech and different legal jurisdictions have different definitions, as do different companies and other groups.
+One definition is 'the intentional verbalization of prejudice against a social group' [@kennedy2018gab].
 Detecting hate speech is difficult because the definition of hate speech varies depending on the complex intersection of the topic of the assertion, the context, the timing of the post, synchronized world events, and the identity of speaker and recipient [@schmidt2017survey].
 Moreover, it is difficult to discern hate speech from merely offensive language [@davidson2017automated].
+Hate speech detection is of interest to academic researchers in a variety of domains including computer science [@addressinghatespeech] and sociology [@davidson2017automated].
+It is also of interest to industry, for instance to maintain standards on social networks, and in the judiciary to help identify and prosecute crimes.
 Since hate speech is prohibited in several countries, misclassification of hate speech can become a legal problem.
@@
 And as part of this various hate speech datasets have been created and examined.
-For instance, @waseem2016hateful create a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation, and @davidson2017automated trains a classifier to distinguish between hate speech and offensive language.
-And it is important to note that even these datasets have bias.
+For instance, @waseem2016hateful create a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation.
+The use Twitter data, and annotate 16,914 tweets: 3,383 as sexist, 1,972 as racist, and 11,559 as neither.
+They had a high degree of annotator agreement, and most of the disagreements were to do with sexism, and often explained by an annotator lacking apparent context.
+And, @davidson2017automated trains a classifier to distinguish between hate speech and offensive language.
+To define hate speech, they use online 'hate speech lexicon containing words and phrases identified by internet users as hate speech'.
+It is important to note that even these datasets have bias.
 For instance, @davidson2019racial found racial bias in five different sets of Twitter data annotated for hate speech and abusive language.
@@
 There are a variety of parameters, such as temperature, that control the degree of text variation.
-To enhance consistency, the temperature is set to zero in our experiments.
+Temperature is a hyper-parameter between zero and one.
+Lower temperatures mean that the model places more weight on higher-probability tokens.
+To enhance consistency, the temperature is set to zero in our experiments and not varied.
 There are two categories of hate speech that are of interest in this paper.
@@
 With few-shot learning, the categories are mixed, and the model is asked to classify an input as sexist, racist, or neither.
+Zero-shot learning means an example is not provided in the prompt.
+One-shot learning means that one example is provided, and few-shot means that two or more examples are provided.
 
@@
 Hatebusters is a platform that collects comments from YouTube and assigns a 'hate' score to them using a support vector machine.
+That hate-score is only used to decide whether to consider the comment further or not.
 The Reddit data is collected from the Public Reddit Data Repository [@baumgartner2020pushshift].
+The classification is done by contributors to a crowd-sourcing platform.
+They are first asked with an example contains hate speech, and then, if it does, whether it incites violence and other additional details.
 The dataset has two variants: binary and multi-label.
-In the binary dataset comments are classified as hate or non-hate.
+In the binary dataset comments are classified as hate or non-hate based.
 In the multi-label variant, the comments are evaluated on measures that include violence, gender, race, ability, religion, and sexual orientation.
@@
 
-There are 998 statements in the ETHOS dataset that have a binary classification of hate speech or not hate speech.
+We use all of the 998 statements in the ETHOS dataset that have a binary classification of hate speech or not hate speech.
 Of these, the 433 statements that contain hate speech additionally have multiple labels that classify the content, for instance, does the comment have to do with violence, gender, race, nationality, disability, etc.
-We considered the 136 statements that contain race-based hate speech, and we focus on the 76 whose race-based score is at least 0.5.
-Similarly, we considered the 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
-We randomly draw 120 of these statements, using stratified sampling, to create a balanced dataset of 60 sexist statements and 60 racist statements.
+We considered all of the 136 statements that contain race-based hate speech, and we focus on the 76 whose race-based score is at least 0.5.
+Similarly, we considered the all of 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
+To create a balanced dataset we randomly draw 120 of these statements, using stratified sampling, to result in 60 sexist statements and 60 racist statements.
 For comparison purposes, we randomly draw 120 statements that are classified as not hate speech.
+The balanced sample enables us to more easily understand our results.
 
@@
 > Yes.
+
+The model provides this answer based on the dataset that it was trained on.
 
@@
 > 
-> 'Now they know better than this shit lol they dudes. The stronger sex. The man supremacy': sexist.
+> 'Now they know better than this s*** lol they dudes. The stronger sex. The man supremacy': sexist.
 > 
@@
 > sexist.
+
+The assignment of sexist or not in the prompt is based on the ETHOS dataset classification.
 
@@
 
-> 'That girl still need a good ass whooping, stupid ass bitch!!': sexist. 
+> 'That girl still need a good ass whooping, stupid ass b****!!': sexist. 
 >
-> 'U SUCK SHIT YOU BLACK FUCK': racist. 
+> 'U SUCK S*** YOU BLACK F***': racist. 
 >
-> 'You deserve way more subscribers. The shit you say is fucking gold.': neither. 
+> 'You deserve way more subscribers. The s*** you say is f***ing gold.': neither. 
 >
-> 'Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With dicks and stuff.':
+> 'Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With d***s and stuff.':
 
@@
 >
-> 'That girl still need a good ass whooping, stupid ass bitch!!': sexist. 
+> 'That girl still need a good ass whooping, stupid ass b****!!': sexist. 
 >
-> 'U SUCK SHIT YOU BLACK FUCK': racist. 
+> 'U SUCK S*** YOU BLACK F***': racist. 
 >
-> 'You deserve way more subscribers. The shit you say is fucking gold.': neither. 
+> 'You deserve way more subscribers. The s*** you say is f***ing gold.': neither. 
 >
-> 'Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With dicks and stuff.':
+> 'Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With d***s and stuff.':
 
@@
 However, the overall ratio of matches and mismatches is 58:62.
-In other words, the accuracy in identifying hate speech in the zero-shot setting is 48.3 per cent.
+In other words, the accuracy in identifying hate speech in the zero-shot setting is 48 per cent.
 
 ```{r zeroshot}
-zero_shot_result <- read.csv(here::here("outputs/data/zero_shot_results.csv"))
+zero_shot_result <- read_csv(here::here("outputs/data/zero_shot_results.csv"), show_col_types = FALSE)
 
@@
                               )) %>%
+  mutate(Percent = result_cnt / sum(result_cnt) * 100,
+         Percent = round(Percent)) %>%
   rename(Result = result,
@@
 ```{r fewshotmixed}
-few_shot_mixed_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))
+few_shot_mixed_result <-
+  read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))
 
@@
   select(category, label, answer, example_set) %>%
-  mutate(example_set = example_set+1) %>%
-  mutate(result = ifelse(trimws(label)==trimws(answer), "Match", "Mismatch")) %>%
-  mutate(label = case_when(label == "racist" ~ "Racist",
+  mutate(example_set = example_set + 1) %>%
+  mutate(result = ifelse(trimws(label) == trimws(answer), "Match", "Mismatch")) %>%
+  mutate(
+    label = case_when(
+      label == "racist" ~ "Racist",
       label == "sexist" ~ "Sexist",
       label == "neither" ~ "Neither"
-                           )) %>%
-  group_by(example_set, result) %>%#, label) %>%
+    )
+  ) %>%
+  group_by(example_set, result) %>% #, label) %>%
   summarise(result_cnt = n(), .groups = "drop") %>%
+  ungroup() %>%
+  group_by(example_set) %>%
+  mutate(Percent = result_cnt / sum(result_cnt) * 100,
+         Percent = round(Percent)) %>%
   rename(Result = result,
@@
 
-knitr::kable(few_shot_mixed_result, 
+knitr::kable(
+  few_shot_mixed_result,
   caption = "Classification of statements with mixed-category few-shot learning",
@@
   linesep = "",
-             align = 'llr')
+  align = 'lllr'
+)
 ```
@@
 The unique generated answers are listed in Table \@ref(tab:fewshotmixedanswersnoinstruct).
+These are the response of GPT-3 that we obtain when we ask the model to classify statements, but do not provide examples that would serve to limit the responses.
 Under the mixed-category setting, the model is observed to generate answers that are out of scope.
@@
   rename(Answer = answer)# %>%
-few_shot_mixed_result <-list(few_shot_mixed_result$Answer)
+few_shot_mixed_result <- list(few_shot_mixed_result$Answer)
 
 df <- as.data.frame("Answer")
-df <- rbind(df$Answer,paste(unlist(few_shot_mixed_result[[1]]), collapse=' | '))
+df <-
+  rbind(df$Answer, paste(unlist(few_shot_mixed_result[[1]]), collapse = ' | '))
 df %>%
-  knitr::kable(
-  caption = "Classifications generated by GPT-3 under mixed-category few-shot learning without instructions",
+  knitr::kable(caption = "Classifications generated by GPT-3 under mixed-category few-shot learning without instructions",
                booktabs = TRUE,
@@
 The addition of an instruction successfully restricts the generated answers within the specified terms.
-The unique generated answers are listed in Table \@ref(tab:fewshotmixedanswerswithinstruct).
+The unique generated answers are: 'racist', 'neither', and 'sexist'.
 
 ```{r fewshotmixedanswerswithinstruct, message=FALSE, warning=FALSE}
-few_shot_instruction_result <-
-  readr::read_csv(here::here("outputs/data/few_shot_fixed_examples_instruction_results.csv"))
-
-few_shot_instruction_result %>% 
-  select(answer) %>% 
-  distinct() %>% 
-  rename(Answer = answer) %>% 
-  knitr::kable(caption = "Classifications generated by GPT-3 under mixed-category few-shot learning with instructions", 
-             booktabs = TRUE,
-             linesep = "",
-             align = 'llr')
+# few_shot_instruction_result <-
+#   readr::read_csv(here::here("outputs/data/few_shot_fixed_examples_instruction_results.csv"))
+# 
+# few_shot_instruction_result %>% 
+#   select(answer) %>% 
+#   distinct()
+# %>% 
+#   rename(Answer = answer) %>% 
+#   knitr::kable(caption = "Classifications generated by GPT-3 under mixed-category few-shot learning with instructions", 
+#              booktabs = TRUE,
+#              linesep = "",
+#              align = 'llr')
 ```
@@
 The addition of the instruction in the prompt increases the highest number of matches from 180 to 187; the highest accuracy rate is increased from 75 per cent to 78 per cent.
-In almost all cases the accuracy of the model increases (Figure \ref{fig:comparison})
+In almost all cases the accuracy of the model increases (Figure \ref{fig:comparison}).
+Across all the example sets, there are 1,785, or 74 per cent, matches and 615, or 26 per cent, mismatches.
 
 ```{r fewshotmixedinstruct}
-few_shot_instruction_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_instruction_results.csv"))
+few_shot_instruction_result <-
+  read.csv(here::here(
+    "outputs/data/few_shot_fixed_examples_instruction_results.csv"
+  ))
 
@@
   select(category, label, answer, example_set) %>%
-  mutate(example_set = example_set+1) %>%
-  mutate(result = ifelse(trimws(label)==trimws(answer), "Match", "Mismatch")) %>%
-  mutate(label = case_when(label == "racist" ~ "Racist",
+  mutate(example_set = example_set + 1) %>%
+  mutate(result = ifelse(trimws(label) == trimws(answer), "Match", "Mismatch")) %>%
+  mutate(
+    label = case_when(
+      label == "racist" ~ "Racist",
       label == "sexist" ~ "Sexist",
       label == "neither" ~ "Neither"
-                         )) %>%
+    )
+  ) %>%
   group_by(example_set, result) %>%
   summarise(result_cnt = n(), .groups = "drop") %>%
+  ungroup() %>%
+  group_by(example_set) %>%
+  mutate(Percent = result_cnt / sum(result_cnt) * 100,
+         Percent = round(Percent)) %>%
+
   rename(Result = result,
@@
 
-knitr::kable(few_shot_instruction_result, 
+knitr::kable(
+  few_shot_instruction_result,
   caption = "Classification of statements with mixed-category few-shot learning, with instruction",
@@
   linesep = "",
-             align = 'llr')
+  align = 'lllr'
+)
+
+# few_shot_instruction_result %>%
+#   group_by(Result) %>%
+#   summarise(n = sum(Count)) %>%
+#   mutate(Percent = n / sum(n) * 100,
+#          Percent = round(Percent))
 ```
@@
   summarise(result_cnt = n(), .groups = "drop") %>% 
+  ungroup() %>% 
+  group_by(example_set) %>%
+  mutate(Percent = result_cnt / sum(result_cnt) * 100,
+         Percent = round(Percent)) %>% 
   filter(result == "Match")
@@
 
+averages <- 
   both %>% 
-  ggplot() +
-  geom_point(aes(x = `Example Set`, y = Correct, color = Type)) +
-  labs(y = "Number correctly categorized") +
-  ylim(0, 240) +
+  group_by(Type) %>% 
+  summarise(average = mean(Percent))
+
+both %>% 
+  ggplot(aes(x = `Example Set`, y = Percent, color = Type)) +
+  geom_point() +
+  geom_hline(data = averages, aes(yintercept=average, color=Type), 
+             linetype="dashed") +
+  labs(y = "Percent correctly categorized") +
+  ylim(0, 100) +
   theme_classic() +
@@
 
-In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 48.3 per cent.
-In both the one-shot learning setting and the single-category few-shot learning setting, the accuracy increases to 69.2 per cent.
-It is likely that the model is not suitable for use in hate speech detection in either the zero-shot learning or one-shot learning settings, as the accuracy rates are between 48.3 per cent and 69.2 per cent.
+In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 48 per cent.
+In both the one-shot learning setting and the single-category few-shot learning setting, the accuracy increases to 69 per cent.
+It is likely that the model is not suitable for use in hate speech detection in either the zero-shot learning or one-shot learning settings, as the accuracy rates are between 48.3 per cent and 69 per cent.
+@davidson2017automated, using a different model and approach, similarly find 'that almost 40 per cent of hate speech is misclassified'.
+And when @schick2021selfdiagnosis use GPT-2 they find a similar ability to recognise sexually explicit content, however using an alternative model - Google's T5 [@raffel2020exploring] - they find better results.
 
 In the mixed-category few-shot setting, different example sets yield different accuracy rates.
-Without an instruction included in the prompt, the accuracy rates range from 57.1 per cent (Example Set 9) to 75 percent (Example Set 2).
+Without an instruction included in the prompt, the accuracy rates range from 57 per cent (Example Set 9) to 75 per cent (Example Set 2).
 Adding an instruction improves the performance, and the highest accuracy rate increases from 75 per cent (Example Set 2) to 78 per cent (Example Set 1).
@@
 Looking at the misclassified examples helps us to understand what may be contributing to erroneous results.
-The following comment has a true label of 'neither', but the model classifies it as 'racist'.
+The following comment has a true label of 'racist', but the model classifies it as 'sexist'.
 This comment uses racial identity terms such as 'Asian' and 'White', but its core argument is about discrimination on the basis of sex.
@@
 
-In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 are capable of identifying sexist and racist text.
+In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 are capable of identifying sexist and racist text at a similar level of specificity to other methods.
 However, it is possible that if a user intentionally misspells profane words, the models may be less likely to identify such content as problematic.
@@
 To shed light on why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content.
-The extent to which the identification and classification of hate speech can be explained is especially of interest for future work.
+The extent to which the identification and classification of hate speech can be explained is especially of interest for future work and is something that could be implemented on the publicly available GPT-2 from OpenAI or T5 from Google.
 

### 2022-02-22 outputs/documents/paper.Rmd
Updates to results tables

@@
 library(tidyverse)
+library(kableExtra)
 # library(tidyr)
@@
 
-```{r zeroshot}
+<!-- ```{r zeroshot} -->
+<!-- zero_shot_result <- read_csv(here::here("outputs/data/zero_shot_results.csv"), show_col_types = FALSE) -->
+
+<!-- zero_shot_result_match <-  -->
+<!--   zero_shot_result %>% -->
+<!--   filter(temperature == 0) %>% -->
+<!--   select(category, label, answer, temperature) %>% -->
+<!--   mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>% -->
+<!--   mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>% -->
+<!--   mutate(result = case_when(answer_yn==label_yn ~ "Match", -->
+<!--                             answer_yn!=label_yn ~ "Mismatch" -->
+<!--                             )) %>% -->
+<!--   group_by(result, category) %>% -->
+<!--   summarise(result_cnt = n(), .groups="drop") %>%  -->
+<!--   mutate(category = case_when(category == "racist" ~ "Racist", -->
+<!--                               category == "sexist" ~ "Sexist" -->
+<!--                               )) %>% -->
+<!--   mutate(Percent = result_cnt / sum(result_cnt) * 100, -->
+<!--          Percent = round(Percent)) %>% -->
+<!--   rename(Result = result, -->
+<!--          Category = category, -->
+<!--          Count = result_cnt) -->
+
+<!-- zero_shot_result_match %>%  -->
+<!--   knitr::kable(caption = "Classification of statements with zero-shot learning", -->
+<!--                booktabs = TRUE) -->
+<!-- ``` -->
+
+```{r zeroshot-racism}
 zero_shot_result <- read_csv(here::here("outputs/data/zero_shot_results.csv"), show_col_types = FALSE)
 
-zero_shot_result <- 
+zero_shot_result_racism <- 
+  zero_shot_result %>%
+  filter(temperature == 0 & category == "racist") %>%
+  select(category, label, answer, temperature) %>%
+  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
+  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
+  count(label_yn, answer_yn) %>%
+  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
+                              label_yn == "Y" ~ "Racist")) %>%
+  rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
+
+zero_shot_result_racism <- zero_shot_result_racism[, c("Actual classification", "Not racist", "Racist")]
+
+zero_shot_result_racism %>%
+  knitr::kable(caption = "Classification of racist statements with zero-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
+
+```
+
+```{r zeroshot-sexism}
+zero_shot_result_sexism <- 
+  zero_shot_result %>%
+  filter(temperature == 0 & category == "sexist") %>%
+  select(category, label, answer, temperature) %>%
+  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
+  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
+  count(label_yn, answer_yn) %>%
+  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
+                              label_yn == "Y" ~ "Sexist")) %>%
+  rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
+
+zero_shot_result_sexism <- zero_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]
+
+zero_shot_result_sexism %>%
+  knitr::kable(caption = "Classification of sexist statements with zero-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
+```
+
+```{r zeroshot-hate}
+zero_shot_result_hate <- 
   zero_shot_result %>%
@@
   mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
-  mutate(result = case_when(answer_yn==label_yn ~ "Match",
-                            answer_yn!=label_yn ~ "Mismatch"
-                            )) %>%
-  group_by(result, category) %>%
-  summarise(result_cnt = n(), .groups="drop") %>% 
-  mutate(category = case_when(category == "racist" ~ "Racist",
-                              category == "sexist" ~ "Sexist"
-                              )) %>%
-  mutate(Percent = result_cnt / sum(result_cnt) * 100,
-         Percent = round(Percent)) %>%
-  rename(Result = result,
-         Category = category,
-         Count = result_cnt)
+  count(label_yn, answer_yn) %>%
+  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
+                              label_yn == "Y" ~ "Hate speech")) %>%
+  rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
 
-zero_shot_result %>% 
-  knitr::kable(caption = "Classification of statements with zero-shot learning",
-               booktabs = TRUE)
+zero_shot_result_hate <- zero_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
+
+zero_shot_result_hate %>%
+  knitr::kable(caption = "Classification of hate speech with zero-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
+```
+
+```{r zeroshot-summary}
+tp_r <- zero_shot_result_racism[2, 3] %>% as.numeric()
+tn_r <- zero_shot_result_racism[1, 2] %>% as.numeric()
+fp_r <- zero_shot_result_racism[1, 3] %>% as.numeric()
+fn_r <- zero_shot_result_racism[2, 2] %>% as.numeric()
+
+tp_s <- zero_shot_result_sexism[2, 3] %>% as.numeric()
+tn_s <- zero_shot_result_sexism[1, 2] %>% as.numeric()
+fp_s <- zero_shot_result_sexism[1, 3] %>% as.numeric()
+fn_s <- zero_shot_result_sexism[2, 2] %>% as.numeric()
+
+tp_h <- zero_shot_result_hate[2, 3] %>% as.numeric()
+tn_h <- zero_shot_result_hate[1, 2] %>% as.numeric()
+fp_h <- zero_shot_result_hate[1, 3] %>% as.numeric()
+fn_h <- zero_shot_result_hate[2, 2] %>% as.numeric()
+
+zero_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
+zero_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
+zero_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
+zero_racism_f1 <- ((2*zero_racism_precision*zero_racism_recall)/(zero_racism_precision + zero_racism_recall)) %>% round(2)
+zero_racism_all <- c(zero_racism_accuracy, zero_racism_precision, zero_racism_recall, zero_racism_f1)
+
+zero_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
+zero_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
+zero_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
+zero_sexism_f1 <- ((2*zero_sexism_precision*zero_sexism_recall)/(zero_sexism_precision + zero_sexism_recall)) %>% round(2)
+zero_sexism_all <- c(zero_sexism_accuracy, zero_sexism_precision, zero_sexism_recall, zero_sexism_f1)
+
+zero_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
+zero_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
+zero_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
+zero_hate_f1 <- ((2*zero_hate_precision*zero_sexism_recall)/(zero_hate_precision + zero_hate_recall)) %>% round(2)
+zero_hate_all <- c(zero_hate_accuracy, zero_hate_precision, zero_hate_recall, zero_hate_f1)
+
+zero_shot_summary <- tibble(Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)), 
+                                   Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
+                                   Percent = c(zero_racism_all, zero_sexism_all, zero_hate_all))
+
+zero_shot_summary %>%
+  select(!Category) %>%
+  knitr::kable(caption="Performance of zero-shot learning in hate speech classification",
+               col.names=c("", "Percent"),
+               booktabs=TRUE) %>%
+  kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
 ```
@@
 
-```{r oneshot}
+<!-- ```{r oneshot} -->
+<!-- one_shot_result <- read.csv(here::here("outputs/data/one_shot_results.csv")) -->
+
+<!-- one_shot_result <-  -->
+<!--   one_shot_result %>% -->
+<!--   filter(temperature == 0) %>% -->
+<!--   select(category, label, answer) %>% -->
+<!--   mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>% -->
+<!--   mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>% -->
+<!--   mutate(result = case_when(answer_yn==label_yn ~ "Match", -->
+<!--                             answer_yn!=label_yn ~ "Mismatch" -->
+<!--                             )) %>% -->
+<!--   group_by(result, category) %>% -->
+<!--   summarise(result_cnt = n(), .groups = "drop") %>%  -->
+<!--   mutate(category = case_when(category == "racist" ~ "Racist", -->
+<!--                               category == "sexist" ~ "Sexist" -->
+<!--                               )) %>% -->
+<!--   mutate(Percent = result_cnt / sum(result_cnt) * 100, -->
+<!--          Percent = round(Percent)) %>% -->
+<!--   rename(Result = result, -->
+<!--          Category = category, -->
+<!--          Count = result_cnt) -->
+
+<!-- one_shot_result %>%  -->
+<!--   knitr::kable(caption = "Classification of statements with one-shot learning",  -->
+<!--              booktabs = TRUE) -->
+<!-- ``` -->
+
+```{r oneshot-racism}
 one_shot_result <- read.csv(here::here("outputs/data/one_shot_results.csv"))
 
-one_shot_result <- 
+one_shot_result_racism <- 
+  one_shot_result %>%
+  filter(temperature == 0 & category == "racist") %>%
+  select(category, label, answer, temperature) %>%
+  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
+  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
+  count(label_yn, answer_yn) %>%
+  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
+                              label_yn == "Y" ~ "Racist")) %>%
+  rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
+
+one_shot_result_racism <- one_shot_result_racism[, c("Actual classification", "Not racist", "Racist")]
+
+one_shot_result_racism %>%
+  knitr::kable(caption = "Classification of racist statements with one-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
+
+```
+
+```{r oneshot-sexism}
+one_shot_result_sexism <- 
+  one_shot_result %>%
+  filter(temperature == 0 & category == "sexist") %>%
+  select(category, label, answer, temperature) %>%
+  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
+  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
+  count(label_yn, answer_yn) %>%
+  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
+                              label_yn == "Y" ~ "Sexist")) %>%
+  rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
+
+one_shot_result_sexism <- one_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]
+
+one_shot_result_sexism %>%
+  knitr::kable(caption = "Classification of sexist statements with one-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
+```
+
+```{r oneshot-hate}
+one_shot_result_hate <- 
   one_shot_result %>%
   filter(temperature == 0) %>%
-  select(category, label, answer) %>%
+  select(category, label, answer, temperature) %>%
   mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
   mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
-  mutate(result = case_when(answer_yn==label_yn ~ "Match",
-                            answer_yn!=label_yn ~ "Mismatch"
-                            )) %>%
-  group_by(result, category) %>%
-  summarise(result_cnt = n(), .groups = "drop") %>% 
-  mutate(category = case_when(category == "racist" ~ "Racist",
-                              category == "sexist" ~ "Sexist"
-                              )) %>%
-  mutate(Percent = result_cnt / sum(result_cnt) * 100,
-         Percent = round(Percent)) %>%
-  rename(Result = result,
-         Category = category,
-         Count = result_cnt)
+  count(label_yn, answer_yn) %>%
+  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
+                              label_yn == "Y" ~ "Hate speech")) %>%
+  rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
 
-one_shot_result %>% 
-  knitr::kable(caption = "Classification of statements with one-shot learning", 
-             booktabs = TRUE)
+one_shot_result_hate <- one_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
+
+one_shot_result_hate %>%
+  knitr::kable(caption = "Classification of hate speech with one-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
+```
+
+```{r oneshot-summary}
+tp_r <- one_shot_result_racism[2, 3] %>% as.numeric()
+tn_r <- one_shot_result_racism[1, 2] %>% as.numeric()
+fp_r <- one_shot_result_racism[1, 3] %>% as.numeric()
+fn_r <- one_shot_result_racism[2, 2] %>% as.numeric()
+
+tp_s <- one_shot_result_sexism[2, 3] %>% as.numeric()
+tn_s <- one_shot_result_sexism[1, 2] %>% as.numeric()
+fp_s <- one_shot_result_sexism[1, 3] %>% as.numeric()
+fn_s <- one_shot_result_sexism[2, 2] %>% as.numeric()
+
+tp_h <- one_shot_result_hate[2, 3] %>% as.numeric()
+tn_h <- one_shot_result_hate[1, 2] %>% as.numeric()
+fp_h <- one_shot_result_hate[1, 3] %>% as.numeric()
+fn_h <- one_shot_result_hate[2, 2] %>% as.numeric()
+
+one_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
+one_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
+one_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
+one_racism_f1 <- ((2*one_racism_precision*one_racism_recall)/(one_racism_precision + one_racism_recall)) %>% round(2)
+one_racism_all <- c(one_racism_accuracy, one_racism_precision, one_racism_recall, one_racism_f1)
+
+one_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
+one_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
+one_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
+one_sexism_f1 <- ((2*one_sexism_precision*one_sexism_recall)/(one_sexism_precision + one_sexism_recall)) %>% round(2)
+one_sexism_all <- c(one_sexism_accuracy, one_sexism_precision, one_sexism_recall, one_sexism_f1)
+
+one_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
+one_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
+one_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
+one_hate_f1 <- ((2*one_hate_precision*one_sexism_recall)/(one_hate_precision + one_hate_recall)) %>% round(2)
+one_hate_all <- c(one_hate_accuracy, one_hate_precision, one_hate_recall, one_hate_f1)
+
+one_shot_summary <- tibble(Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)), 
+                                   Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
+                                   Percent = c(one_racism_all, one_sexism_all, one_hate_all))
+
+one_shot_summary %>%
+  select(!Category) %>%
+  knitr::kable(caption="Performance of one-shot learning in hate speech classification",
+               col.names=c("", "Percent"),
+               booktabs=TRUE) %>%
+  kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
 ```
@@
 
-```{r fewshotsingle}
+<!-- ```{r fewshotsingle} -->
+<!-- few_shot_single_result <- read.csv(here::here("outputs/data/few_shot_single_results.csv")) -->
+
+<!-- few_shot_single_result <-  -->
+<!--   few_shot_single_result %>% -->
+<!--   filter(temperature == 0) %>% -->
+<!--   select(category, label, answer) %>% -->
+<!--   mutate(label_yn = ifelse(grepl("not", label), "No", "Yes")) %>% -->
+<!--   mutate(answer_yn = ifelse(grepl("not", answer), "No", "Yes")) %>% -->
+<!--   mutate(result = case_when(answer_yn==label_yn ~ "Match", -->
+<!--                             answer_yn!=label_yn ~ "Mismatch" -->
+<!--                             )) %>% -->
+<!--   mutate(result_with_cat = case_when(answer_yn==label_yn & answer_yn == "Yes" ~ "True Positive", -->
+<!--                                      answer_yn==label_yn & answer_yn == "No"  ~ "True Negative", -->
+<!--                                      answer_yn!=label_yn & answer_yn == "Yes" ~ "False Positive", -->
+<!--                                      answer_yn!=label_yn & answer_yn == "No"  ~ "False Negative" -->
+<!--                                      )) %>% -->
+<!--   group_by(result, category) %>% -->
+<!--   summarise(result_cnt = n(), .groups = "drop") %>%  -->
+<!--   mutate(category = case_when(category == "racist" ~ "Racist", -->
+<!--                               category == "sexist" ~ "Sexist" -->
+<!--                               )) %>% -->
+<!--   mutate(Percent = result_cnt / sum(result_cnt) * 100, -->
+<!--          Percent = round(Percent)) %>% -->
+<!--   rename(Result = result, -->
+<!--          Category = category, -->
+<!--          Count = result_cnt) -->
+
+<!-- few_shot_single_result %>%  -->
+<!--   knitr::kable( -->
+<!--     caption = "Classification of statements with single-category few-shot learning",  -->
+<!--     booktabs = TRUE) -->
+<!-- ``` -->
+
+```{r fewshotsingle-racism}
 few_shot_single_result <- read.csv(here::here("outputs/data/few_shot_single_results.csv"))
 
-few_shot_single_result <- 
+few_shot_result_racism <- 
+  few_shot_single_result %>%
+  filter(temperature == 0 & category == "racist") %>%
+  select(category, label, answer) %>%
+  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
+  mutate(answer_yn = ifelse(stringr::str_detect(answer, "not", negate = FALSE), "N", "Y")) %>%
+  count(label_yn, answer_yn) %>%
+  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
+                              label_yn == "Y" ~ "Racist")) %>%
+  rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
+
+few_shot_result_racism <- few_shot_result_racism[, c("Actual classification", "Not racist", "Racist")]
+
+few_shot_result_racism %>%
+  knitr::kable(caption = "Classification of racist statements with single-category few-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
+```
+
+```{r fewshotsingle-sexism}
+few_shot_result_sexism <- 
+  few_shot_single_result %>%
+  filter(temperature == 0 & category == "sexist") %>%
+  select(category, label, answer, temperature) %>%
+  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
+  mutate(answer_yn = ifelse(stringr::str_detect(answer, "not", negate = FALSE), "N", "Y")) %>%
+  count(label_yn, answer_yn) %>%
+  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
+                              label_yn == "Y" ~ "Sexist")) %>%
+  rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
+
+few_shot_result_sexism <- few_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]
+
+few_shot_result_sexism %>%
+  knitr::kable(caption = "Classification of sexist statements with single-category few-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
+```
+
+```{r fewshotsingle-hate}
+few_shot_result_hate <- 
   few_shot_single_result %>%
   filter(temperature == 0) %>%
-  select(category, label, answer) %>%
-  mutate(label_yn = ifelse(grepl("not", label), "No", "Yes")) %>%
-  mutate(answer_yn = ifelse(grepl("not", answer), "No", "Yes")) %>%
-  mutate(result = case_when(answer_yn==label_yn ~ "Match",
-                            answer_yn!=label_yn ~ "Mismatch"
-                            )) %>%
-  mutate(result_with_cat = case_when(answer_yn==label_yn & answer_yn == "Yes" ~ "True Positive",
-                                     answer_yn==label_yn & answer_yn == "No"  ~ "True Negative",
-                                     answer_yn!=label_yn & answer_yn == "Yes" ~ "False Positive",
-                                     answer_yn!=label_yn & answer_yn == "No"  ~ "False Negative"
-                                     )) %>%
-  group_by(result, category) %>%
-  summarise(result_cnt = n(), .groups = "drop") %>% 
-  mutate(category = case_when(category == "racist" ~ "Racist",
-                              category == "sexist" ~ "Sexist"
-                              )) %>%
-  mutate(Percent = result_cnt / sum(result_cnt) * 100,
-         Percent = round(Percent)) %>%
-  rename(Result = result,
-         Category = category,
-         Count = result_cnt)
+  select(category, label, answer, temperature) %>%
+  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
+  mutate(answer_yn = ifelse(stringr::str_detect(answer, "not", negate = FALSE), "N", "Y")) %>%
+  count(label_yn, answer_yn) %>%
+  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
+                              label_yn == "Y" ~ "Hate speech")) %>%
+  rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
 
-few_shot_single_result %>% 
-  knitr::kable(
-    caption = "Classification of statements with single-category few-shot learning", 
-    booktabs = TRUE)
+few_shot_result_hate <- few_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
+
+few_shot_result_hate %>%
+  knitr::kable(caption = "Classification of hate speech with single-category few-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
+```
+
+```{r fewshotsingle-summary}
+tp_r <- few_shot_result_racism[2, 3] %>% as.numeric()
+tn_r <- few_shot_result_racism[1, 2] %>% as.numeric()
+fp_r <- few_shot_result_racism[1, 3] %>% as.numeric()
+fn_r <- few_shot_result_racism[2, 2] %>% as.numeric()
+
+tp_s <- few_shot_result_sexism[2, 3] %>% as.numeric()
+tn_s <- few_shot_result_sexism[1, 2] %>% as.numeric()
+fp_s <- few_shot_result_sexism[1, 3] %>% as.numeric()
+fn_s <- few_shot_result_sexism[2, 2] %>% as.numeric()
+
+tp_h <- few_shot_result_hate[2, 3] %>% as.numeric()
+tn_h <- few_shot_result_hate[1, 2] %>% as.numeric()
+fp_h <- few_shot_result_hate[1, 3] %>% as.numeric()
+fn_h <- few_shot_result_hate[2, 2] %>% as.numeric()
+
+few_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
+few_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
+few_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
+few_racism_f1 <- ((2*few_racism_precision*few_racism_recall)/(few_racism_precision + few_racism_recall)) %>% round(2)
+few_racism_all <- c(few_racism_accuracy, few_racism_precision, few_racism_recall, few_racism_f1)
+
+few_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
+few_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
+few_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
+few_sexism_f1 <- ((2*few_sexism_precision*few_sexism_recall)/(few_sexism_precision + few_sexism_recall)) %>% round(2)
+few_sexism_all <- c(few_sexism_accuracy, few_sexism_precision, few_sexism_recall, few_sexism_f1)
+
+few_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
+few_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
+few_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
+few_hate_f1 <- ((2*few_hate_precision*few_sexism_recall)/(few_hate_precision + few_hate_recall)) %>% round(2)
+few_hate_all <- c(few_hate_accuracy, few_hate_precision, few_hate_recall, few_hate_f1)
+
+few_shot_summary <- tibble(Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)), 
+                                   Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
+                                   Percent = c(few_racism_all, few_sexism_all, few_hate_all))
+
+few_shot_summary %>%
+  select(!Category) %>%
+  knitr::kable(caption="Performance of single-category few-shot learning in hate speech classification",
+               col.names=c("", "Percent"),
+               booktabs=TRUE) %>%
+  kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
 ```

### 2022-02-24 outputs/documents/paper.Rmd
Updates according to R&R comments

@@
 We show that this knowledge can be used to identify abusive language and even hate speech.
-In particular we consider 120 different extracts that have been categorized as 'racist', 'sexist', or 'neither' in the single-category settings and 240 different extracts in the mixed-category settings.
+In particular we consider 120 different extracts that have been categorized as 'racist', 'sexist', or 'neither' in the single-category settings and 243 different extracts in the mixed-category settings.
 We ask GPT-3 to classify these based on zero-, one-, and few-shot learning, with and without instruction.
@@
 
+For the purposes of one-shot and single-category few-shot learning, the dataset was split in half such that 30 racist comments, 30 sexist comments, and 60 neutral comments were used as inputs and the remainder were used as examples.
+This division was kept consistent for zero-shot learning to allow for the same set of 120 comments to be classified by all three approaches.
+With the introduction of 10 static example sets for multi-category few-shot learning, 240 comments were classified for each example set.
+
 ## Zero-shot learning
@@
 In the mixed categories setting, the model is expected to categorize the given passage of text as 'sexist', 'racist', or 'neither'.
-There are ten sets of examples; each set of examples is used for the model to classify 60 racist comments, 60 sexist comments, and 120 comments that are in neither category This results in 2,400 responses in total.
-The ten sets of examples are available in Table \@ref(tab:appendixa) in the Appendix.
+To simplify the classification procedure and allow for comparisons between different example inputs, we created ten sets of examples against which 240 comments were classified each.
+We elected to use ten example sets to allow for some variation in results while keeping the number of groupings and size of the resulting data set reasonably small.
+The example sets each consist of one sexist, one racist, and one 'neither' comment and were created using the comments at indexes one through ten from each dataset.
+Each set of examples is used for the model to classify 60 racist comments, 60 sexist comments, and 120 comments that are in 'neither' category.
+The inputted comments were the first _n_ + 1 comments from their respective data sets with the _i_^th comment dropped corresponding to the use of example set _i_.
+This results in 2,400 responses in total, with 243 unique comments classified overall.
+The ten sets of examples are available in Table \@ref(tab:appendixa) in Appendix A.
 An example of this is:
@@
                                    Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
-                                   Percent = c(zero_racism_all, zero_sexism_all, zero_hate_all))
+                                   Percent = c(zero_racism_all, zero_sexism_all, zero_hate_all)) %>%
+  pivot_wider(names_from = Metric, values_from = Percent)
 
 zero_shot_summary %>%
-  select(!Category) %>%
-  knitr::kable(caption="Performance of zero-shot learning in hate speech classification",
-               col.names=c("", "Percent"),
-               booktabs=TRUE) %>%
-  kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
+  # select(!Category) %>%
+  knitr::kable(caption="Performance of zero-shot learning in hate speech classification (percent)",
+              # col.names=c(""=1),
+               booktabs=TRUE) # %>%
+  # kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
 ```
@@
                                    Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
-                                   Percent = c(one_racism_all, one_sexism_all, one_hate_all))
+                                   Percent = c(one_racism_all, one_sexism_all, one_hate_all)) %>%
+  pivot_wider(names_from = Metric, values_from = Percent)
 
 one_shot_summary %>%
-  select(!Category) %>%
+  # select(!Category) %>%
   knitr::kable(caption="Performance of one-shot learning in hate speech classification",
-               col.names=c("", "Percent"),
-               booktabs=TRUE) %>%
-  kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
+               # col.names=c("", "Percent"),
+               booktabs=TRUE) # %>%
+  # kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
 ```
@@
                                    Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
-                                   Percent = c(few_racism_all, few_sexism_all, few_hate_all))
+                                   Percent = c(few_racism_all, few_sexism_all, few_hate_all)) %>%
+  pivot_wider(names_from = Metric, values_from = Percent)
 
 few_shot_summary %>%
-  select(!Category) %>%
+  # select(!Category) %>%
   knitr::kable(caption="Performance of single-category few-shot learning in hate speech classification",
-               col.names=c("", "Percent"),
-               booktabs=TRUE) %>%
-  kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
+               # col.names=c("", "Percent"),
+               booktabs=TRUE) # %>%
+ # kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
 ```
@@
 
-```{r fewshotmixed}
+<!-- ```{r fewshotmixed} -->
+<!-- few_shot_mixed_result <- -->
+<!--   read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv")) -->
+
+<!-- few_shot_mixed_result <- -->
+<!--   few_shot_mixed_result %>% -->
+<!--   filter(temperature == 0) %>% -->
+<!--   select(category, label, answer, example_set) %>% -->
+<!--   mutate(example_set = example_set + 1) %>% -->
+<!--   mutate(result = ifelse(trimws(label) == trimws(answer), "Match", "Mismatch")) %>% -->
+<!--   mutate( -->
+<!--     label = case_when( -->
+<!--       label == "racist" ~ "Racist", -->
+<!--       label == "sexist" ~ "Sexist", -->
+<!--       label == "neither" ~ "Neither" -->
+<!--     ) -->
+<!--   ) %>% -->
+<!--   group_by(example_set, result) %>% #, label) %>% -->
+<!--   summarise(result_cnt = n(), .groups = "drop") %>% -->
+<!--   ungroup() %>% -->
+<!--   group_by(example_set) %>% -->
+<!--   mutate(Percent = result_cnt / sum(result_cnt) * 100, -->
+<!--          Percent = round(Percent)) %>% -->
+<!--   rename(Result = result, -->
+<!--          "Example Set" = example_set, -->
+<!--          Count = result_cnt) -->
+
+<!-- knitr::kable( -->
+<!--   few_shot_mixed_result, -->
+<!--   caption = "Classification of statements with mixed-category few-shot learning", -->
+<!--   booktabs = TRUE, -->
+<!--   linesep = "", -->
+<!--   align = 'lllr' -->
+<!-- ) -->
+<!-- ``` -->
+
+```{r fewshotmixed-racism}
 few_shot_mixed_result <-
@@
 
-few_shot_mixed_result <-
+# Example sets
+few_shot_mixed_result_racism <- 
   few_shot_mixed_result %>%
-  filter(temperature == 0) %>%
-  select(category, label, answer, example_set) %>%
-  mutate(example_set = example_set + 1) %>%
-  mutate(result = ifelse(trimws(label) == trimws(answer), "Match", "Mismatch")) %>%
-  mutate(
-    label = case_when(
-      label == "racist" ~ "Racist",
-      label == "sexist" ~ "Sexist",
-      label == "neither" ~ "Neither"
-    )
-  ) %>%
-  group_by(example_set, result) %>% #, label) %>%
-  summarise(result_cnt = n(), .groups = "drop") %>%
-  ungroup() %>%
-  group_by(example_set) %>%
-  mutate(Percent = result_cnt / sum(result_cnt) * 100,
-         Percent = round(Percent)) %>%
-  rename(Result = result,
-         "Example Set" = example_set,
-         Count = result_cnt)
-
-knitr::kable(
-  few_shot_mixed_result,
-  caption = "Classification of statements with mixed-category few-shot learning",
+  mutate(example_set = example_set + 1,
+         label = case_when(!grepl("racist", label) ~ "not racist", TRUE ~ "racist"),
+         answer = case_when(!grepl("racist", answer) ~ "not racist", TRUE ~ "racist")) %>%
+  count(example_set, label, answer) %>%
+  pivot_wider(names_from = answer, values_from = n) %>%
+  mutate(label = case_when(label == "not racist" ~ "Not racist",
+                           label == "racist" ~ "Racist")) %>%
+  rename("Actual classification" = label, "Not racist" = "not racist", "Racist" = "racist")
+
+# Overall
+few_shot_mixed_result_racism_overall <- 
+  few_shot_mixed_result %>%
+  mutate(example_set = example_set + 1,
+         label = case_when(!grepl("racist", label) ~ "not racist", TRUE ~ "racist"),
+         answer = case_when(!grepl("racist", answer) ~ "not racist", TRUE ~ "racist")) %>%
+  count(label, answer) %>%
+  pivot_wider(names_from = answer, values_from = n) %>%
+  mutate(label = case_when(label == "not racist" ~ "Not racist",
+                           label == "racist" ~ "Racist")) %>%
+  rename("Actual classification" = label, "Not racist" = "not racist", "Racist" = "racist")
+
+few_shot_mixed_result_racism <- few_shot_mixed_result_racism[, c("example_set", "Actual classification", "Not racist", "Racist")]
+few_shot_mixed_result_racism_overall <- few_shot_mixed_result_racism_overall[, c("Actual classification", "Not racist", "Racist")] %>% mutate(example_set = "All", .before="Actual classification")
+
+table <- few_shot_mixed_result_racism %>% 
+  # select(!example_set) %>%
+  rbind(few_shot_mixed_result_racism_overall) %>%
+  mutate(example_set = case_when(.$`Actual classification` == "Racist" ~ "", TRUE ~ example_set)) %>%
+  rename("Example set" = example_set)
+
+knitr::kable(table,
+             caption = "Classification of racist statements with mixed-category few-shot learning",
              booktabs = TRUE,
-  linesep = "",
-  align = 'lllr'
-)
-```
+             linesep="") %>%
+  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2))  %>%
+  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
+```
+
+```{r fewshotmixed-sexism}
+# Example sets
+few_shot_mixed_result_sexism <- 
+  few_shot_mixed_result %>%
+  mutate(example_set = example_set + 1,
+         label = case_when(!grepl("sexist", label) ~ "not sexist", TRUE ~ "sexist"),
+         answer = case_when(!grepl("sexist", answer) ~ "not sexist", TRUE ~ "sexist")) %>%
+  count(example_set, label, answer) %>%
+  pivot_wider(names_from = answer, values_from = n) %>%
+  mutate(label = case_when(label == "not sexist" ~ "Not sexist",
+                           label == "sexist" ~ "Sexist")) %>%
+  rename("Actual classification" = label, "Not sexist" = "not sexist", "Sexist" = "sexist")
+
+# Overall
+few_shot_mixed_result_sexism_overall <- 
+  few_shot_mixed_result %>%
+  mutate(example_set = example_set + 1,
+         label = case_when(!grepl("sexist", label) ~ "not sexist", TRUE ~ "sexist"),
+         answer = case_when(!grepl("sexist", answer) ~ "not sexist", TRUE ~ "sexist")) %>%
+  count(label, answer) %>%
+  pivot_wider(names_from = answer, values_from = n) %>%
+  mutate(label = case_when(label == "not sexist" ~ "Not sexist",
+                           label == "sexist" ~ "Sexist")) %>%
+  rename("Actual classification" = label, "Not sexist" = "not sexist", "Sexist" = "sexist")
+
+few_shot_mixed_result_sexism <- few_shot_mixed_result_sexism[, c("example_set", "Actual classification", "Not sexist", "Sexist")]
+few_shot_mixed_result_sexism_overall <- few_shot_mixed_result_sexism_overall[, c("Actual classification", "Not sexist", "Sexist")] %>% mutate(example_set = "All", .before="Actual classification")
+
+table <- few_shot_mixed_result_sexism %>% 
+  # select(!example_set) %>%
+  rbind(few_shot_mixed_result_sexism_overall) %>%
+  mutate(example_set = case_when(.$`Actual classification` == "Sexist" ~ "", TRUE ~ example_set)) %>%
+  rename("Example set" = example_set)
+
+knitr::kable(table,
+             caption = "Classification of sexist statements with mixed-category few-shot learning",
+             booktabs = TRUE,
+             linesep="") %>%
+  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2))  %>%
+  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
+  # kableExtra::pack_rows(index=c("Example set 1"=2, 
+  #                               "Example set 2"=2, 
+  #                               "Example set 3"=2, 
+  #                               "Example set 4"=2, 
+  #                               "Example set 5"=2, 
+  #                               "Example set 6"=2,
+  #                               "Example set 7"=2,
+  #                               "Example set 8"=2,
+  #                               "Example set 9"=2,
+  #                               "Example set 10"=2,
+  #                               "Overall"=2))
+```
+
+```{r fewshotmixed-summary}
+few_shot_mixed_result_racism_overall <- few_shot_mixed_result_racism_overall %>% mutate(example_set = 11, .before="Actual classification")
+all_results_racism <- rbind(few_shot_mixed_result_racism, few_shot_mixed_result_racism_overall)
+
+few_shot_mixed_result_sexism_overall <- few_shot_mixed_result_sexism_overall %>% mutate(example_set = 11, .before="Actual classification")
+all_results_sexism <- rbind(few_shot_mixed_result_sexism, few_shot_mixed_result_sexism_overall)
+
+all_summary <- tibble()
+for (i in 1:11){
+  example_i_racism <- all_results_racism %>% filter(example_set == i) %>% select(!example_set)
+
+  tp_r <- example_i_racism[2, 3] %>% as.numeric()
+  tn_r <- example_i_racism[1, 2] %>% as.numeric()
+  fp_r <- example_i_racism[1, 3] %>% as.numeric()
+  fn_r <- example_i_racism[2, 2] %>% as.numeric()
+
+  few_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
+  few_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
+  few_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
+  few_racism_f1 <- ((2*few_racism_precision*few_racism_recall)/(few_racism_precision + few_racism_recall)) %>% round(2)
+  few_racism_all <- c(few_racism_accuracy, few_racism_precision, few_racism_recall, few_racism_f1)
+
+  few_shot_summary <- tibble(example_set = rep(i, 4),
+                             Category = rep("Racism", 4), 
+                             Metric = c("Accuracy", "Precision", "Recall", "F1"), 
+                             Percent = few_racism_all) %>%
+  pivot_wider(names_from = Metric, values_from = Percent)
+
+  all_summary <- rbind(all_summary, few_shot_summary)
+
+  example_i_sexism <- all_results_sexism %>% filter(example_set == i) %>% select(!example_set)
+
+  tp_s <- example_i_sexism[2, 3] %>% as.numeric()
+  tn_s <- example_i_sexism[1, 2] %>% as.numeric()
+  fp_s <- example_i_sexism[1, 3] %>% as.numeric()
+  fn_s <- example_i_sexism[2, 2] %>% as.numeric()
+
+  few_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
+  few_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
+  few_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
+  few_sexism_f1 <- ((2*few_sexism_precision*few_sexism_recall)/(few_sexism_precision + few_sexism_recall)) %>% round(2)
+  few_sexism_all <- c(few_sexism_accuracy, few_sexism_precision, few_sexism_recall, few_sexism_f1)
+
+  few_shot_summary <- tibble(example_set = rep(i, 4),
+                             Category = c(rep("Sexism", 4)), 
+                             Metric = c("Accuracy", "Precision", "Recall", "F1"), 
+                             Percent = c(few_sexism_all))  %>%
+  pivot_wider(names_from = Metric, values_from = Percent)
+
+  all_summary <- rbind(all_summary, few_shot_summary)
+}
+
+table <- all_summary %>%
+  # select(example_set, Metric, Percent) %>% 
+  mutate(example_set = as.character(example_set),
+         example_set = case_when(example_set == 11 ~ "All", TRUE ~ example_set),
+         example_set = case_when(Category == "Sexism" ~ "", TRUE ~ example_set)) %>%
+  rename("Example set" = example_set)
+
+knitr::kable(table,
+             caption="Performance of mixed-category few-shot learning in racist text classification",
+               # col.names=c("", "Percent"),
+             booktabs=TRUE,
+             linesep = "") %>%
+  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
+
+# knitr::kable(list(table[1:24, 1:3],
+#                   matrix(numeric(), nrow=0, ncol=3),
+#                   table[25:44, 1:3]),
+#              caption="Performance of mixed-category few-shot learning in racist text classification",
+#                # col.names=c("", "Percent"),
+#              booktabs=TRUE,
+#              linesep = "")
+  # kableExtra::pack_rows(index=c("Example set 1"=4,
+  #                               "Example set 2"=4,
+  #                               "Example set 3"=4,
+  #                               "Example set 4"=4,
+  #                               "Example set 5"=4,
+  #                               "Example set 6"=4,
+  #                               "Example set 7"=4,
+  #                               "Example set 8"=4,
+  #                               "Example set 9"=4,
+  #                               "Example set 10"=4,
+  #                               "Overall"=4))
+```
+
+<!-- ```{r fewshotmixed-summary-sexism} -->
+<!-- few_shot_mixed_result_sexism_overall <- few_shot_mixed_result_sexism_overall %>% mutate(example_set = 11, .before="Actual classification") -->
+<!-- all_results <- rbind(few_shot_mixed_result_sexism, few_shot_mixed_result_sexism_overall) -->
+<!-- all_summary <- tibble() -->
+<!-- for (i in 1:11){ -->
+<!--   example_i_sexism <- all_results %>% filter(example_set == i) %>% select(!example_set) -->
+
+<!--   tp_s <- example_i_sexism[2, 3] %>% as.numeric() -->
+<!--   tn_s <- example_i_sexism[1, 2] %>% as.numeric() -->
+<!--   fp_s <- example_i_sexism[1, 3] %>% as.numeric() -->
+<!--   fn_s <- example_i_sexism[2, 2] %>% as.numeric() -->
+
+<!--   few_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100 -->
+<!--   few_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100 -->
+<!--   few_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100 -->
+<!--   few_sexism_f1 <- ((2*few_sexism_precision*few_sexism_recall)/(few_sexism_precision + few_sexism_recall)) %>% round(2) -->
+<!--   few_sexism_all <- c(few_sexism_accuracy, few_sexism_precision, few_sexism_recall, few_sexism_f1) -->
+
+<!--   few_shot_summary <- tibble(example_set = rep(i, 4), -->
+<!--                              Category = c(rep("Sexism", 4)),  -->
+<!--                              Metric = c("Accuracy", "Precision", "Recall", "F1"),  -->
+<!--                              Percent = c(few_sexism_all)) -->
+
+<!--   all_summary <- rbind(all_summary, few_shot_summary) -->
+<!-- } -->
+
+<!-- table <- all_summary %>% -->
+<!--   select(example_set, Metric, Percent) %>%  -->
+<!--   mutate(example_set = as.character(example_set), -->
+<!--          example_set = case_when(example_set == 11 ~ "All", TRUE ~ example_set), -->
+<!--          example_set = case_when(Metric != "Accuracy" ~ "", TRUE ~ example_set)) %>% -->
+<!--   rename("Example set" = example_set) -->
+
+<!-- knitr::kable(list(table[1:24, 1:3], -->
+<!--                   matrix(numeric(), nrow=0, ncol=3), -->
+<!--                   table[25:44, 1:3]), -->
+<!--              caption="Performance of mixed-category few-shot learning in sexist text classification", -->
+<!--                # col.names=c("", "Percent"), -->
+<!--              booktabs=TRUE, -->
+<!--              linesep = "") -->
+<!--   # kableExtra::pack_rows(index=c("Example set 1"=4, -->
+<!--   #                               "Example set 2"=4, -->
+<!--   #                               "Example set 3"=4, -->
+<!--   #                               "Example set 4"=4, -->
+<!--   #                               "Example set 5"=4, -->
+<!--   #                               "Example set 6"=4, -->
+<!--   #                               "Example set 7"=4, -->
+<!--   #                               "Example set 8"=4, -->
+<!--   #                               "Example set 9"=4, -->
+<!--   #                               "Example set 10"=4, -->
+<!--   #                               "Overall"=4)) -->
+
+<!-- ``` -->
 
@@
 
-```{r fewshotmixedinstruct}
+<!-- ```{r fewshotmixedinstruct} -->
+<!-- few_shot_instruction_result <- -->
+<!--   read.csv(here::here( -->
+<!--     "outputs/data/few_shot_fixed_examples_instruction_results.csv" -->
+<!--   )) -->
+
+<!-- few_shot_instruction_result <- -->
+<!--   few_shot_instruction_result %>% -->
+<!--   filter(temperature == 0) %>% -->
+<!--   select(category, label, answer, example_set) %>% -->
+<!--   mutate(example_set = example_set + 1) %>% -->
+<!--   mutate(result = ifelse(trimws(label) == trimws(answer), "Match", "Mismatch")) %>% -->
+<!--   mutate( -->
+<!--     label = case_when( -->
+<!--       label == "racist" ~ "Racist", -->
+<!--       label == "sexist" ~ "Sexist", -->
+<!--       label == "neither" ~ "Neither" -->
+<!--     ) -->
+<!--   ) %>% -->
+<!--   group_by(example_set, result) %>% -->
+<!--   summarise(result_cnt = n(), .groups = "drop") %>% -->
+<!--   ungroup() %>% -->
+<!--   group_by(example_set) %>% -->
+<!--   mutate(Percent = result_cnt / sum(result_cnt) * 100, -->
+<!--          Percent = round(Percent)) %>% -->
+
+<!--   rename(Result = result, -->
+<!--          "Example Set" = example_set, -->
+<!--          Count = result_cnt) -->
+
+<!-- knitr::kable( -->
+<!--   few_shot_instruction_result, -->
+<!--   caption = "Classification of statements with mixed-category few-shot learning, with instruction", -->
+<!--   booktabs = TRUE, -->
+<!--   linesep = "", -->
+<!--   align = 'lllr' -->
+<!-- ) -->
+
+<!-- # few_shot_instruction_result %>% -->
+<!-- #   group_by(Result) %>% -->
+<!-- #   summarise(n = sum(Count)) %>% -->
+<!-- #   mutate(Percent = n / sum(n) * 100, -->
+<!-- #          Percent = round(Percent)) -->
+<!-- ``` -->
+
+```{r fewshotmixedinstruct-racism}
 few_shot_instruction_result <-
@@
 
-few_shot_instruction_result <-
+# Example sets
+few_shot_mixed_result_instruct_racism <- 
   few_shot_instruction_result %>%
-  filter(temperature == 0) %>%
-  select(category, label, answer, example_set) %>%
-  mutate(example_set = example_set + 1) %>%
-  mutate(result = ifelse(trimws(label) == trimws(answer), "Match", "Mismatch")) %>%
-  mutate(
-    label = case_when(
-      label == "racist" ~ "Racist",
-      label == "sexist" ~ "Sexist",
-      label == "neither" ~ "Neither"
-    )
-  ) %>%
-  group_by(example_set, result) %>%
-  summarise(result_cnt = n(), .groups = "drop") %>%
-  ungroup() %>%
-  group_by(example_set) %>%
-  mutate(Percent = result_cnt / sum(result_cnt) * 100,
-         Percent = round(Percent)) %>%
-
-  rename(Result = result,
-         "Example Set" = example_set,
-         Count = result_cnt)
-
-knitr::kable(
-  few_shot_instruction_result,
-  caption = "Classification of statements with mixed-category few-shot learning, with instruction",
+  mutate(example_set = example_set + 1,
+         label = case_when(!grepl("racist", label) ~ "not racist", TRUE ~ "racist"),
+         answer = case_when(!grepl("racist", answer) ~ "not racist", TRUE ~ "racist")) %>%
+  count(example_set, label, answer) %>%
+  pivot_wider(names_from = answer, values_from = n) %>%
+  mutate(label = case_when(label == "not racist" ~ "Not racist",
+                           label == "racist" ~ "Racist")) %>%
+  rename("Actual classification" = label, "Not racist" = "not racist", "Racist" = "racist")
+
+# Overall
+few_shot_mixed_result_instruct_racism_overall <- 
+  few_shot_instruction_result %>%
+  mutate(example_set = example_set + 1,
+         label = case_when(!grepl("racist", label) ~ "not racist", TRUE ~ "racist"),
+         answer = case_when(!grepl("racist", answer) ~ "not racist", TRUE ~ "racist")) %>%
+  count(label, answer) %>%
+  pivot_wider(names_from = answer, values_from = n) %>%
+  mutate(label = case_when(label == "not racist" ~ "Not racist",
+                           label == "racist" ~ "Racist")) %>%
+  rename("Actual classification" = label, "Not racist" = "not racist", "Racist" = "racist")
+
+few_shot_mixed_result_instruct_racism <- few_shot_mixed_result_instruct_racism[, c("example_set", "Actual classification", "Not racist", "Racist")]
+few_shot_mixed_result_instruct_racism_overall <- few_shot_mixed_result_instruct_racism_overall[, c("Actual classification", "Not racist", "Racist")] %>% mutate(example_set = "All", .before="Actual classification")
+
+table <- few_shot_mixed_result_instruct_racism %>% 
+  # select(!example_set) %>%
+  rbind(few_shot_mixed_result_instruct_racism_overall) %>%
+  mutate(example_set = case_when(.$`Actual classification` == "Racist" ~ "", TRUE ~ example_set)) %>%
+  rename("Example set" = example_set)
+
+knitr::kable(table,
+             caption = "Classification of racist statements with mixed-category few-shot learning, with instruction",
              booktabs = TRUE,
-  linesep = "",
-  align = 'lllr'
-)
-
-# few_shot_instruction_result %>%
-#   group_by(Result) %>%
-#   summarise(n = sum(Count)) %>%
-#   mutate(Percent = n / sum(n) * 100,
-#          Percent = round(Percent))
-```
+             linesep="") %>%
+  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2)) %>%
+  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
+
+```
+
+```{r fewshotmixedinstruct-sexism}
+# Example sets
+few_shot_mixed_result_instruct_sexism <- 
+  few_shot_instruction_result %>%
+  mutate(example_set = example_set + 1,
+         label = case_when(!grepl("sexist", label) ~ "not sexist", TRUE ~ "sexist"),
+         answer = case_when(!grepl("sexist", answer) ~ "not sexist", TRUE ~ "sexist")) %>%
+  count(example_set, label, answer) %>%
+  pivot_wider(names_from = answer, values_from = n) %>%
+  mutate(label = case_when(label == "not sexist" ~ "Not sexist",
+                           label == "sexist" ~ "Sexist")) %>%
+  rename("Actual classification" = label, "Not sexist" = "not sexist", "Sexist" = "sexist")
+
+# Overall
+few_shot_mixed_result_instruct_sexism_overall <- 
+  few_shot_instruction_result %>%
+  mutate(example_set = example_set + 1,
+         label = case_when(!grepl("sexist", label) ~ "not sexist", TRUE ~ "sexist"),
+         answer = case_when(!grepl("sexist", answer) ~ "not sexist", TRUE ~ "sexist")) %>%
+  count(label, answer) %>%
+  pivot_wider(names_from = answer, values_from = n) %>%
+  mutate(label = case_when(label == "not sexist" ~ "Not sexist",
+                           label == "sexist" ~ "Sexist")) %>%
+  rename("Actual classification" = label, "Not sexist" = "not sexist", "Sexist" = "sexist")
+
+few_shot_mixed_result_instruct_sexism <- few_shot_mixed_result_instruct_sexism[, c("example_set", "Actual classification", "Not sexist", "Sexist")]
+few_shot_mixed_result_instruct_sexism_overall <- few_shot_mixed_result_instruct_sexism_overall[, c("Actual classification", "Not sexist", "Sexist")] %>% mutate(example_set = "All", .before="Actual classification")
+
+table <- few_shot_mixed_result_instruct_sexism %>% 
+  # select(!example_set) %>%
+  rbind(few_shot_mixed_result_instruct_sexism_overall) %>%
+  mutate(example_set = case_when(.$`Actual classification` == "Sexist" ~ "", TRUE ~ example_set)) %>%
+  rename("Example set" = example_set)
+
+knitr::kable(table,
+             caption = "Classification of sexist statements with mixed-category few-shot learning, with instruction",
+             booktabs = TRUE,
+             linesep="") %>%
+  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2)) %>%
+  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
+
+```
+```{r fewshotmixedinstruct-summary}
+few_shot_mixed_result_instruct_racism_overall <- few_shot_mixed_result_instruct_racism_overall %>% mutate(example_set = 11, .before="Actual classification")
+all_results_racism <- rbind(few_shot_mixed_result_instruct_racism, few_shot_mixed_result_instruct_racism_overall)
+
+few_shot_mixed_result_instruct_sexism_overall <- few_shot_mixed_result_instruct_sexism_overall %>% mutate(example_set = 11, .before="Actual classification")
+all_results_sexism <- rbind(few_shot_mixed_result_instruct_sexism, few_shot_mixed_result_instruct_sexism_overall)
+
+all_summary <- tibble()
+for (i in 1:11){
+  example_i_racism <- all_results_racism %>% filter(example_set == i) %>% select(!example_set)
+
+  tp_r <- example_i_racism[2, 3] %>% as.numeric()
+  tn_r <- example_i_racism[1, 2] %>% as.numeric()
+  fp_r <- example_i_racism[1, 3] %>% as.numeric()
+  fn_r <- example_i_racism[2, 2] %>% as.numeric()
+
+  few_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
+  few_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
+  few_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
+  few_racism_f1 <- ((2*few_racism_precision*few_racism_recall)/(few_racism_precision + few_racism_recall)) %>% round(2)
+  few_racism_all <- c(few_racism_accuracy, few_racism_precision, few_racism_recall, few_racism_f1)
+
+  few_shot_summary <- tibble(example_set = rep(i, 4),
+                             Category = rep("Racism", 4), 
+                             Metric = c("Accuracy", "Precision", "Recall", "F1"), 
+                             Percent = few_racism_all) %>%
+  pivot_wider(names_from = Metric, values_from = Percent)
+
+  all_summary <- rbind(all_summary, few_shot_summary)
+
+  example_i_sexism <- all_results_sexism %>% filter(example_set == i) %>% select(!example_set)
+
+  tp_s <- example_i_sexism[2, 3] %>% as.numeric()
+  tn_s <- example_i_sexism[1, 2] %>% as.numeric()
+  fp_s <- example_i_sexism[1, 3] %>% as.numeric()
+  fn_s <- example_i_sexism[2, 2] %>% as.numeric()
+
+  few_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
+  few_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
+  few_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
+  few_sexism_f1 <- ((2*few_sexism_precision*few_sexism_recall)/(few_sexism_precision + few_sexism_recall)) %>% round(2)
+  few_sexism_all <- c(few_sexism_accuracy, few_sexism_precision, few_sexism_recall, few_sexism_f1)
+
+  few_shot_summary <- tibble(example_set = rep(i, 4),
+                             Category = c(rep("Sexism", 4)), 
+                             Metric = c("Accuracy", "Precision", "Recall", "F1"), 
+                             Percent = c(few_sexism_all)) %>%
+  pivot_wider(names_from = Metric, values_from = Percent)
+
+  all_summary <- rbind(all_summary, few_shot_summary)
+}
+
+table <- all_summary %>%
+  # select(example_set, Metric, Percent) %>% 
+  mutate(example_set = as.character(example_set),
+         example_set = case_when(example_set == 11 ~ "All", TRUE ~ example_set),
+         example_set = case_when(Category == "Sexism" ~ "", TRUE ~ example_set)) %>%
+  rename("Example set" = example_set)
+
+knitr::kable(table,
+             caption="Performance of mixed-category few-shot learning in racist text classification, with instruction",
+               # col.names=c("", "Percent"),
+             booktabs=TRUE,
+             linesep = "") %>%
+  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
+
+# knitr::kable(list(table[1:24, 1:3],
+#                   matrix(numeric(), nrow=0, ncol=3),
+#                   table[25:44, 1:3]),
+#              caption="Performance of mixed-category few-shot learning in racist text classification, with instruction",
+#                # col.names=c("", "Percent"),
+#              booktabs=TRUE,
+#              linesep = "")
+  # kableExtra::pack_rows(index=c("Example set 1"=4,
+  #                               "Example set 2"=4,
+  #                               "Example set 3"=4,
+  #                               "Example set 4"=4,
+  #                               "Example set 5"=4,
+  #                               "Example set 6"=4,
+  #                               "Example set 7"=4,
+  #                               "Example set 8"=4,
+  #                               "Example set 9"=4,
+  #                               "Example set 10"=4,
+  #                               "Overall"=4))
+```
+
+<!-- ```{r fewshotmixedinstruct-summary-sexism} -->
+<!-- few_shot_mixed_result_instruct_sexism_overall <- few_shot_mixed_result_instruct_sexism_overall %>% mutate(example_set = 11, .before="Actual classification") -->
+<!-- all_results <- rbind(few_shot_mixed_result_instruct_sexism, few_shot_mixed_result_instruct_sexism_overall) -->
+<!-- all_summary <- tibble() -->
+<!-- for (i in 1:11){ -->
+<!--   example_i_sexism <- all_results %>% filter(example_set == i) %>% select(!example_set) -->
+
+<!--   tp_s <- example_i_sexism[2, 3] %>% as.numeric() -->
+<!--   tn_s <- example_i_sexism[1, 2] %>% as.numeric() -->
+<!--   fp_s <- example_i_sexism[1, 3] %>% as.numeric() -->
+<!--   fn_s <- example_i_sexism[2, 2] %>% as.numeric() -->
+
+<!--   few_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100 -->
+<!--   few_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100 -->
+<!--   few_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100 -->
+<!--   few_sexism_f1 <- ((2*few_sexism_precision*few_sexism_recall)/(few_sexism_precision + few_sexism_recall)) %>% round(2) -->
+<!--   few_sexism_all <- c(few_sexism_accuracy, few_sexism_precision, few_sexism_recall, few_sexism_f1) -->
+
+<!--   few_shot_summary <- tibble(example_set = rep(i, 4), -->
+<!--                              Category = c(rep("Sexism", 4)),  -->
+<!--                              Metric = c("Accuracy", "Precision", "Recall", "F1"),  -->
+<!--                              Percent = c(few_sexism_all)) -->
+
+<!--   all_summary <- rbind(all_summary, few_shot_summary) -->
+<!-- } -->
+
+<!-- table <- all_summary %>% -->
+<!--   select(example_set, Metric, Percent) %>%  -->
+<!--   mutate(example_set = as.character(example_set), -->
+<!--          example_set = case_when(example_set == 11 ~ "All", TRUE ~ example_set), -->
+<!--          example_set = case_when(Metric != "Accuracy" ~ "", TRUE ~ example_set)) %>% -->
+<!--   rename("Example set" = example_set) -->
+
+<!-- knitr::kable(list(table[1:24, 1:3], -->
+<!--                   matrix(numeric(), nrow=0, ncol=3), -->
+<!--                   table[25:44, 1:3]), -->
+<!--              caption="Performance of mixed-category few-shot learning in sexist text classification, with instruction", -->
+<!--                # col.names=c("", "Percent"), -->
+<!--              booktabs=TRUE, -->
+<!--              linesep = "") -->
+<!--   # kableExtra::pack_rows(index=c("Example set 1"=4, -->
+<!--   #                               "Example set 2"=4, -->
+<!--   #                               "Example set 3"=4, -->
+<!--   #                               "Example set 4"=4, -->
+<!--   #                               "Example set 5"=4, -->
+<!--   #                               "Example set 6"=4, -->
+<!--   #                               "Example set 7"=4, -->
+<!--   #                               "Example set 8"=4, -->
+<!--   #                               "Example set 9"=4, -->
+<!--   #                               "Example set 10"=4, -->
+<!--   #                               "Overall"=4)) -->
+<!-- ``` -->
 
@@
   mutate(example_set = example_set+1) %>%
-  mutate(result = ifelse(trimws(label)==trimws(answer), "Match", "Mismatch")) %>%
+  mutate(result = ifelse(str_detect(trimws(answer), trimws(label)), "Match", "Mismatch")) %>%
   mutate(label = case_when(label == "racist" ~ "Racist",
@@
   rename(Result = result,
-         "Example Set" = example_set,
+         "Example set" = example_set,
          Correct = result_cnt) %>% 
@@
 
+In order to test the impact of misspellings on hate speech classification, we examined a subset of the Ethos data set containing the profane words or sub-strings indicated in Table \@ref(tab:profanity) in Appendix B.
+These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation.
+The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process.
+Details of the misspellings added are also included in Table \@ref(tab:profanity).
+Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category (results in Table \@ref(tab:misspell-results) in Appendix B).
+Interestingly, three comments with added misspellings were classified as racist where they had previously not been classified as racist.
+This speaks to potential inconsistencies in the behaviour of GPT-3 in understanding profanity and censorship and presents another area for further investigation.
+
 In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 are capable of identifying sexist and racist text at a similar level of specificity to other methods.
@@
 
-# Appendix {-}
+# Appendix A
 
@@
 
+# Appendix B
+
+```{r profanity}
+# Table of profane words/substrings and misspellings introduced
+profanity <- tibble(string = c("nigg", "fuck", "whore", "kill", "rape", "die", "bitch"),
+                    edit = c("n1gg, nig, n*gg, n-gg",
+                             "fck, phuck, f*ck, f-ck",
+                             "wh0re, whor3, wh0r3, wh*re, wh-re",
+                             "k1ll, kil, k-ll, k*ll",
+                             "r@pe, rap3, r@p3, rap, r*pe, r-pe",
+                             "d1e, di3, d13, dye, d*e, d-e",
+                             "b1tch, bich, bithc, bicht, b*tch, b-tch"))
+profanity %>%
+  knitr::kable(caption="Profane strings used to test extract comments to test impacts of misspelling and censorship on hate speech classificiation",
+               booktabs = TRUE,
+               col.names = c("Original", "Edits"))
+```
+
+```{r misspell-results}
+zero_shot_misspelling <- read.csv(here::here("outputs", "data", "zero_shot_misspelling.csv"))
+
+zero_shot_misspelling <- zero_shot_misspelling %>% 
+  separate(prompt, c(NA, "comment", NA), sep = "\"") %>%
+  mutate(answer = str_replace_all(zero_shot_misspelling$answer, "[^[:alnum:]]", ""))
+
+zeroshot_summary_race <- zero_shot_misspelling %>% 
+  count(category, comment_id, answer) %>% 
+  count(category, comment_id) %>% 
+  filter(n > 1 & category == "racist")
+
+# Racist
+zero_results_summary <- zero_shot_misspelling %>% 
+                          filter(category == "racist" & comment_id %in% zeroshot_summary_race$comment_id) %>% 
+                          arrange(comment_id)
+
+results <- tibble()
+for (i in unique(zero_results_summary$comment_id)) {
+  original <- zero_results_summary %>% filter(comment_id == i & status == "unedited")
+  original_answer <- original["answer"] %>% as.character()
+  edits <- zero_results_summary %>% filter(comment_id == i & status == "edited" & answer != original_answer)
+  results <- rbind(results, original, edits)
+}
+results %>% 
+  select(label, status, comment, answer) %>%
+  mutate(label = case_when(label == "racist" ~ "Racist"),
+         status = case_when(status == "edited" ~ "Edited",
+                            status == "unedited" ~ "Unedited")) %>%
+  knitr::kable(caption="Zero-shot learning classifications impacted by misspelling and censoring racist comments",
+               col.names = c("Label", "Status", "Comment", "GPT-3 classification"),
+               booktabs = TRUE,
+              linesep = "",
+              align = 'llll') %>% 
+  kableExtra::column_spec(column = 3, width = "35em")%>% 
+  kableExtra::kable_styling(font_size = 7.5)%>%
+  kableExtra::kable_styling(latex_options = "HOLD_position")
+```
+
 \newpage

### 2022-02-24 DRAFT-misspelling.R

@@ -1,0 +1,35 @@
+library(tidyverse)
+
+zero_shot_misspelling <- read.csv(here::here("outputs", "data", "zero_shot_misspelling.csv"))
+one_shot_misspelling <- read.csv(here::here("outputs", "data", "one_shot_misspelling.csv"))
+
+# Zero-shot
+# Summary of results
+zero_shot_misspelling <- zero_shot_misspelling %>% separate(prompt, c(NA, "comment", NA), sep = "\"")
+zeroshot_summary <- zero_shot_misspelling %>% count(category, comment_id, answer) %>% count(category, comment_id) %>% filter(n > 1)
+zero_shot_misspelling %>% 
+  filter(category == "racist" & comment_id %in% zeroshot_summary$comment_id)%>% 
+  arrange(comment_id) %>%
+  View()
+
+# One-shot
+oneshot_summary_race <- one_shot_misspelling %>% 
+  count(category, comment_id, answer) %>% 
+  count(category, comment_id) %>% 
+  filter(n > 1 & category == "racist")
+oneshot_summary_sex <- one_shot_misspelling %>% 
+  count(category, comment_id, answer) %>% 
+  count(category, comment_id) %>% 
+  filter(n > 1 & category == "sexist")
+
+# Racism results
+one_shot_misspelling %>% 
+  filter(category == "racist" & comment_id %in% oneshot_summary_race$comment_id)%>% 
+  arrange(comment_id) %>%
+  View()
+
+# Sexism results
+one_shot_misspelling %>% 
+  filter(category == "sexist" & comment_id %in% oneshot_summary_sex$comment_id)%>% 
+  arrange(comment_id) %>%
+  View()

### 2022-02-24 inputs/data_collection_functions.py

@@ -1,0 +1,177 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+import openai
+import pandas as pd
+openai.organization = "org-JICO2278t41sb6tLfBpmPmhO"
+openai.api_key = "sk-VUUDX4QYst2QwmMdNs0QsOa2JYTLYSAP8IvykqFQ"
+
+
+ethos_data = pd.read_csv("inputs/Ethos_Dataset_Multi_Label.csv", delimiter=';')
+ethos_data_binary = pd.read_csv("inputs/Ethos_Dataset_Binary.csv", delimiter=';')
+sexist = pd.DataFrame(ethos_data[ethos_data["gender"] >= 0.5]["comment"])       # Filter ethos_data for gender score > 0.5, take only comment column (84 rows)
+racist = pd.DataFrame(ethos_data[ethos_data["race"] >= 0.5]["comment"])         # Filter ethos_data for race score > 0.5, take only comment column (76 rows)
+not_hate = ethos_data_binary[ethos_data_binary["isHate"] == 0]                  # Filter ethos_data_binary for non-hate comments (354 rows)
+sexist["category"] = "sexist"       # Add "category" column to comments
+racist["category"] = "racist"       # ""
+not_hate["category"] = "not hate"   # ""
+comments = pd.concat([sexist, racist])  # Create one dataframe called comments (160 rows)
+comments = comments.reset_index()       # Resets row numbers to 0-159 (otherwise indices inherited from position in ethos_data)
+
+##### Zero-Shot #####
+def zero_shot(cat, label, comment, temperature):
+    prompt='Is the following text '+cat+', answer yes or no. '+' "'+comment+'" '+' Answer:'
+    zero_shot_results = dict()
+    response = openai.Completion.create(    # GPT-3 interaction
+        engine="davinci",
+        prompt=prompt,
+        temperature=temperature,
+        max_tokens=2,
+        top_p=1,
+        n = 1,
+        stop=["\n"]
+    )
+
+    zero_shot_results["category"] = cat
+    zero_shot_results["label"] = label
+    zero_shot_results["prompt"] = prompt
+    zero_shot_results['answer'] = response["choices"][0].text
+    zero_shot_results['temperature'] = temperature
+    return zero_shot_results    # Output is dict with keys as above
+
+
+# One-Shot
+def one_shot(cat, label, example, comment, temperature):
+    one_shot_results = dict()
[…]

### 2022-02-24 inputs/data_collection_private.py

@@ -1,0 +1,398 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# In[2]:
+
+
+# get_ipython().system('pip install openai')
+import os
+import openai
+import pandas as pd
+import numpy as np
+import time
+import random
+openai.organization = "org-JICO2278t41sb6tLfBpmPmhO"
+openai.api_key = "sk-VUUDX4QYst2QwmMdNs0QsOa2JYTLYSAP8IvykqFQ"
+
+
+# In[3]:
+
+
+ethos_data = pd.read_csv("inputs/Ethos_Dataset_Multi_Label.csv", delimiter=';')
+ethos_data_binary = pd.read_csv("inputs/Ethos_Dataset_Binary.csv", delimiter=';')
+sexist = pd.DataFrame(ethos_data[ethos_data["gender"] >= 0.5]["comment"])       # Filter ethos_data for gender score > 0.5, take only comment column (84 rows)
+racist = pd.DataFrame(ethos_data[ethos_data["race"] >= 0.5]["comment"])         # Filter ethos_data for race score > 0.5, take only comment column (76 rows)
+not_hate = ethos_data_binary[ethos_data_binary["isHate"] == 0]                  # Filter ethos_data_binary for non-hate comments (354 rows)
+sexist["category"] = "sexist"       # Add "category" column to comments
+racist["category"] = "racist"       # ""
+not_hate["category"] = "not hate"   # ""
+comments = pd.concat([sexist, racist])  # Create one dataframe called comments (160 rows)
+comments = comments.reset_index()       # Resets row numbers to 0-159 (otherwise indices inherited from position in ethos_data)
+
+### Other categories ###
+#disability = ethos_data[ethos_data["disability"] >= 1]["comment"]
+#religion = ethos_data[ethos_data["religion"] >= 1]["comment"]
+#sexual_orientation = ethos_data[ethos_data["sexual_orientation"] >= 1]["comment"]
+
+
+# In[ ]:
+
+
+##### Zero-Shot #####
+def zero_shot(cat, label, comment, temperature):
+    prompt='Is the following text '+cat+', answer yes or no. '+' "'+comment+'" '+' Answer:'
+    zero_shot_results = dict()
+    response = openai.Completion.create(    # GPT-3 interaction
+        engine="davinci",
+        prompt=prompt,
+        temperature=temperature,
+        max_tokens=2,
+        top_p=1,
+        n = 1,
+        stop=["\n"]
[…]

### 2022-02-25 outputs/documents/paper.Rmd
Updates to results section

@@
 
+<!-- Insert brief description of GPT-3 - the general usage of the model, its transformer-based architecture, what are the inputs-outputs, etc. -->
+
 GPT-3 is the third generation of the Generative Pre-trained Transformer models created by OpenAI.
@@
 Similarly, we considered the all of 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
-To create a balanced dataset we randomly draw 120 of these statements, using stratified sampling, to result in 60 sexist statements and 60 racist statements.
+To create a balanced dataset we select 120 of these statements to result in 60 sexist statements and 60 racist statements.
 For comparison purposes, we randomly draw 120 statements that are classified as not hate speech.
@@
 The example sets each consist of one sexist, one racist, and one 'neither' comment and were created using the comments at indexes one through ten from each dataset.
-Each set of examples is used for the model to classify 60 racist comments, 60 sexist comments, and 120 comments that are in 'neither' category.
-The inputted comments were the first _n_ + 1 comments from their respective data sets with the _i_^th comment dropped corresponding to the use of example set _i_.
+Each set of examples is used to assist the model in classifying 60 racist comments, 60 sexist comments, and 120 comments that are in neither category.
+The inputted comments were the first _n_ + 1 comments from their respective data sets with the _i_^th^ comment dropped corresponding to the use of example set _i_.
 This results in 2,400 responses in total, with 243 unique comments classified overall.
@@
 
-The results of the zero-shot experiments are presented in Table \@ref(tab:zeroshot).
-The model has 35 matches and 25 mismatches in the sexist category, and 23 matches and 37 mismatches in the racist category.
-The model performs better when identifying sexist comments compared with identifying racist comments.
-However, the overall ratio of matches and mismatches is 58:62.
-In other words, the accuracy in identifying hate speech in the zero-shot setting is 48 per cent.
+The results of the zero-shot experiments are presented in Table \@ref(tab:zeroshot-racism), Table \@ref(tab:zeroshot-sexism), Table \@ref(tab:zeroshot-hate), and \@ref(tab:zeroshot-summary).
+We assess GPT-3's performance in all settings using accuracy, precision, recall, and F1 score.
+Accuracy is the proportion of correctly classified comments (hate speech and non-hate speech) out of all comments classified.
+Precision is the proportion of hate speech comments correctly identified out of all comments identified as hate speech (both correctly and incorrectly).
+Recall is the number of hate speech comments correctly identified out of all hate speech comments in the data set (both correctly and incorrectly identified).
+F1 score is the harmonic mean of precision and recall.
+In the case of hate speech identification it is desirable to have a model with high recall, meaning a model that can identify a relatively high proportion of the hate speech text within a data set, however the F1 score can provide a more well-rounded metric for model performance and comparison.
+
+The model has 34 matches (true positives and negatives) and 26 mismatches (false positives and negatives) in the sexist category, and 41 matches and 19 mismatches in the racist category.
+The model performs with higher accuracy and precision when identifying racist comments compared with identifying sexist comments.
+The overall ratio of matches and mismatches is 75:45.
+In other words, the accuracy in identifying hate speech in the zero-shot setting is 62.5 per cent.
 
@@
 
-```{r zeroshot-racism}
+```{r zeroshot-racism, message=FALSE}
 zero_shot_result <- read_csv(here::here("outputs/data/zero_shot_results.csv"), show_col_types = FALSE)
@@
 
-The results of the one-shot learning experiments are presented in Table \@ref(tab:oneshot).
-The model has 46 matches and 14 mismatches in the racist category, and 37 matches and 23 mismatches in the sexist category.
-In contrast with the result generated from zero-shot learning, the model performs slightly better in identifying racist comments compared with identifying sexist comments.
-The general performance in the one-shot setting is also better than in the zero-shot setting.
-The overall ratio of matches and mismatches is 83:37.
-In other words, the accuracy of identifying hate speech in the one-shot setting is 69.2 per cent.
+The results of the one-shot learning experiments are presented in Table \@ref(tab:oneshot-racism), Table \@ref(tab:oneshot-sexism), Table \@ref(tab:oneshot-hate), and Table \@ref(tab:oneshot-summary).
+The model has 37 matches and 23 mismatches in the racist category, and 36 matches and 24 mismatches in the sexist category.
+In contrast with the result generated from zero-shot learning, the model approximately the same in identifying racist comments compared with identifying sexist comments.
+The general performance in the one-shot setting is worse than in the zero-shot setting, with lower accuracy, recall, and precision overall.
+The overall ratio of matches and mismatches is 73:47.
+In other words, the accuracy of identifying hate speech in the one-shot setting is 60.8 per cent.
 
@@
 
-The results of the single-category, few-shot learning, experiments are presented in Table \@ref(tab:fewshotsingle).
+The results of the single-category, few-shot learning, experiments are presented in Table \@ref(tab:fewshotsingle-racism), Table \@ref(tab:fewshotsingle-sexism), Table \@ref(tab:fewshotsingle-hate), and Table \@ref(tab:fewshotsingle-summary).
 The model has 41 matches and 19 mismatches in the racist category, and 42 matches and 18 mismatches in the sexist category.
-Here, the model performs almost equally well at identifying racist comments compared with identifying sexist comments.
-The general performance in the few-shot learning setting is similar to the performance in the one-shot learning setting.
-The overall ratio of matches and mismatches is 83:37, or around 69.2 per cent, however the composition is different, compared with the one-shot learning setting.
+Similar to the one-shot setting, the model performs almost equally well at identifying racist comments compared with identifying sexist comments.
+The general performance in the few-shot learning setting is similar to the performance in the one-shot learning setting as well.
+The overall ratio of matches and mismatches is 83:37, or around 69.2 per cent, with higher precision and lower recall compared with the one-shot learning setting.
 
@@
 
-The results of the mixed-category few-shot experiments are presented in Table \@ref(tab:fewshotmixed).
-Among the ten sets of examples, Example Set 2 yields the best performance, as the model has the highest number of matches, 180, and the lowest number of mismatches, 60.
-In other words, the accuracy under the mixed category few-shot setting with Example Set 2 is 75 per cent.
-The example set that yields the worst results is Example Set 9, in which there are 137 matches and 103 mismatches.
-The accuracy rate with Example Set 9 is 57.1 per cent.
-The difference between Example Sets 2 and 9 suggests that, although the models are provided with same number of examples, the content of the examples also affects how the model makes inferences.
+The results of the mixed-category few-shot experiments are presented in Table \@ref(tab:fewshotmixed-racism), Table \@ref(tab:fewshotmixed-sexism), and Table \@ref(tab:fewshotmixed-summary).
+
+Among the ten sets of examples, Example Set 10 yields the best performance in terms of F1 score for both racist and sexist comments.
+It also has the highest accuracy for identifying sexist comments at 91.25 percent and is tied with Example Set 2 for the highest accuracy in identifying racist comments at 90.42 percent.
+The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 68.26 percent (and the lowest accuracy at 77.92 percent) for this dataset.
+The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 68.45 percent (and the lowest accuracy at 80.42 percent) for this dataset.
+The differences between Example Sets 8, 9, and 10 suggest that, although the models are provided with same number of examples, the content of the examples also affects how the model makes inferences.
+Overall, the mixed-category few-shot setting performs slightly better at identifying sexist text versus racist text.
+It is also performs with higher accuracy and a higher F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
 
@@
 
+For the purposes of our analysis, a classification was considered a true positive if the answer outputted by GPT-3 contained a category that matched the comment's label.
+For example, if a comment was labelled 'sexist' and the comment was classified by the model as 'sexist, racist', this was considered a true positive.
+If a comment was labelled 'sexist' and the comment was classified by the model as 'racist', 'transphobic', 'neither', etc.
+this was considered a false negative.
+
 ```{r fewshotmixedanswersnoinstruct, warning = FALSE, message = FALSE}
@@
 The addition of an instruction successfully restricts the generated answers within the specified terms.
-The unique generated answers are: 'racist', 'neither', and 'sexist'.
+The unique generated answers are: 'racist', 'sexist', and 'neither'.
 
@@
 
-The results of the mixed-category, few-shot learning, with instruction, experiments are presented in Table \@ref(tab:fewshotmixedinstruct).
-With the addition of an instruction in the prompt, the example set that yields the best result is Example Set 1 instead of Example Set 2.
+The results of the mixed-category, few-shot learning, with instruction, experiments are presented in Table \@ref(tab:fewshotmixedinstruct-racism), Table \@ref(tab:fewshotmixedinstruct-sexism), and Table \@ref(tab:fewshotmixedinstruct-summary).
+With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (92.08 percent) and F1 score (84.03 percent) for sexist text, however Example Set 4 now performs best for racist text in terms of both accuracy (91.25 percent) and F1 score (83.20 percent).
+
+<!-- Fix  below -->
 The addition of the instruction in the prompt increases the highest number of matches from 180 to 187; the highest accuracy rate is increased from 75 per cent to 78 per cent.
@@
   count(example_set, label, answer) %>%
-  pivot_wider(names_from = answer, values_from = n) %>%
+  pivot_wider(names_from = answer, values_from = n, values_fill = 0) %>%
   mutate(label = case_when(label == "not racist" ~ "Not racist",
@@
   rename(Result = result,
-         "Example set" = example_set,
+         "Example Set" = example_set,
          Correct = result_cnt) %>% 

### 2022-02-25 outputs/documents/paper.Rmd
Continued updates to results section

@@
 For the purposes of our analysis, a classification was considered a true positive if the answer outputted by GPT-3 contained a category that matched the comment's label.
-For example, if a comment was labelled 'sexist' and the comment was classified by the model as 'sexist, racist', this was considered a true positive.
+For example, if a comment was labelled 'sexist' and the comment was classified by the model as 'sexist, racist', this was considered a true positive in the classification of sexist comments (the comment is sexist, and the model classified it as sexist) and a false positive in the classification of racist comments (the comment is not racist, and the model classified it as racist).
 If a comment was labelled 'sexist' and the comment was classified by the model as 'racist', 'transphobic', 'neither', etc.
 this was considered a false negative.
+
+Since each comment is only labelled with one hate speech category, a classification was considered a true negative if the label of the comment was either 'neither' or the category not being analyzed, and the comment received a classification that did not include the category being considered.
+For example, if a comment was labelled 'racist' and the model answered 'neither', this is considered a true negative in the classification of sexist comments (the comment is not sexist, and the model did not classify it as sexist), but a false negative in the classification of racist comments (the comment is racist, but the model did classify it as racist).
 
@@
 
-The results of the mixed-category, few-shot learning, with instruction, experiments are presented in Table \@ref(tab:fewshotmixedinstruct-racism), Table \@ref(tab:fewshotmixedinstruct-sexism), and Table \@ref(tab:fewshotmixedinstruct-summary).
+The results of the mixed-category few-shot learning, with instruction, experiments are presented in Table \@ref(tab:fewshotmixedinstruct-matrix), Table \@ref(tab:fewshotmixedinstruct-racism), Table \@ref(tab:fewshotmixedinstruct-sexism), and Table \@ref(tab:fewshotmixedinstruct-summary).
 With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (92.08 percent) and F1 score (84.03 percent) for sexist text, however Example Set 4 now performs best for racist text in terms of both accuracy (91.25 percent) and F1 score (83.20 percent).
-
-<!-- Fix  below -->
-The addition of the instruction in the prompt increases the highest number of matches from 180 to 187; the highest accuracy rate is increased from 75 per cent to 78 per cent.
-In almost all cases the accuracy of the model increases (Figure \ref{fig:comparison}).
-Across all the example sets, there are 1,785, or 74 per cent, matches and 615, or 26 per cent, mismatches.
+When considering the classification of racist and sexist speech independently, the models perform similarly with and without instruction in the mixed-category few-shot setting.
+
+However, examining label-classification matches across all categories ('sexist', 'racist', and 'neither'), mixed-category few-shot learning almost always performs better with instruction than without instruction (Figure \ref{fig:comparison}).
+Across all example sets, the mean proportion of matching classifications (out of 240 comments) for mixed-category few-shot learning without instruction is 66.9 percent.
+The average proportion of matching classifications rises to 74.5 percent for learning with instruction.
 
@@
 
+```{r fewshotmixedinstruct-matrix}
+few_shot_instruction_result <-
+  read.csv(here::here(
+    "outputs/data/few_shot_fixed_examples_instruction_results.csv"
+  ))
+
+confusion_instruct <- few_shot_instruction_result %>%
+  count(label, answer) %>%
+  pivot_wider(names_from = answer, values_from = n, values_fill = 0) %>%
+  mutate(label = case_when(label == "neither" ~ "Neither",
+                           label == "racist" ~ "Racist",
+                           label == "sexist" ~ "Sexist")) %>%
+  rename("Actual classification" = label, Neither = " neither", Racist = " racist", Sexist = " sexist")
+
+confusion_instruct$Neither <- kableExtra::cell_spec(confusion_instruct$Neither, background=c("#AED581", "#FFFFFF", "#FFFFFF"))
+confusion_instruct$Racist <- kableExtra::cell_spec(confusion_instruct$Racist, background=c("#FFFFFF", "#AED581", "white"))
+confusion_instruct$Sexist <- kableExtra::cell_spec(confusion_instruct$Sexist, background=c("#FFFFFF", "#FFFFFF", "#AED581"))
+
+confusion_instruct %>% knitr::kable(caption="Classifications of all comments using mixed-category few-short learning, with instruction",
+                                    booktabs=TRUE,
+                                    escape=FALSE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=3))
+
+```
+
 ```{r fewshotmixedinstruct-racism}
@@
 
-```{r comparison, fig.cap="Comparing accuracy with and without an instruction", fig.height = 3}
+```{r comparison, fig.cap="Comparing classification with and without an instruction", fig.height = 3}
 few_shot_mixed_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))
@@
 
-In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 48 per cent.
-In both the one-shot learning setting and the single-category few-shot learning setting, the accuracy increases to 69 per cent.
-It is likely that the model is not suitable for use in hate speech detection in either the zero-shot learning or one-shot learning settings, as the accuracy rates are between 48.3 per cent and 69 per cent.
+In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 62.5 per cent with an F1 score of 80.54 percent.
+In the one-shot learning setting the accuracy decreases to 60.83 percent with an F1 score of 65.25 percent.
+Accuracy increases to 69.2 percent in the single-category few-shot learning setting, with an F1 score of 60.5 percent.
+Of the three single-category approaches, zero-shot learning has a notably high recall value of 86.67 percent.
+
+It is likely that the model is not suitable for use in hate speech detection in either the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the accuracy rates are between 60 per cent and 70 per cent.
 @davidson2017automated, using a different model and approach, similarly find 'that almost 40 per cent of hate speech is misclassified'.
@@
 
-In the mixed-category few-shot setting, different example sets yield different accuracy rates.
+<!-- Fix below -->
+In the mixed-category few-shot setting, different example sets yield different accuracy rates for racist and sexist comments with noticeable improvement over the single-category approaches.
+Given our definition of true negative in the mixed-category setting (see Section \@ref(sec:few-shot-learning----mixed-category)), large number of true negatives, present in the dataset
+
 Without an instruction included in the prompt, the accuracy rates range from 57 per cent (Example Set 9) to 75 per cent (Example Set 2).
@@
 
-The comment is a plain statement without judgment; the inclusion of 'transgendered people' may be the reason for the false positive.
+The comment is a plain statement without judgment; the inclusion of 'transgendered people' may be the reason for the false classification (specifically a false positive in the context of detecting hate speech in general).
 If this were the case, then combined with the previous example, the model may have a tendency to generate false positive results when it encounters words that are identity terms, erroneously ignoring the context in which they are used.
@@
 Large language models take a long time to train and deploy.
-This means that it may be that unless considerable context is provided in the prompt, that the model would not identify words that have become sexist and racist through their usage in the time since the model was trained.
-
-In order to test the impact of misspellings on hate speech classification, we examined a subset of the Ethos data set containing the profane words or sub-strings indicated in Table \@ref(tab:profanity) in Appendix B.
+It may be that, unless considerable context is provided in the prompt, the model will not identify words that have become sexist and racist through their usage in the time since the model was trained.
+
+In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS data set containing the profane words or sub-strings indicated in Table \@ref(tab:profanity) in Appendix B.
 These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation.
@@
 Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category (results in Table \@ref(tab:misspell-results) in Appendix B).
-Interestingly, three comments with added misspellings were classified as racist where they had previously not been classified as racist.
+Interestingly, three comments with added misspellings were classified as 'racist' where they had previously been classified as 'not racist'.
 This speaks to potential inconsistencies in the behaviour of GPT-3 in understanding profanity and censorship and presents another area for further investigation.

### 2022-02-25 DRAFT-misspelling.R

@@ -6,9 +6,38 @@ one_shot_misspelling <- read.csv(here::here("outputs", "data", "one_shot_misspel
 # Zero-shot
 # Summary of results
 zero_shot_misspelling <- zero_shot_misspelling %>% separate(prompt, c(NA, "comment", NA), sep = "\"")
-zeroshot_summary <- zero_shot_misspelling %>% count(category, comment_id, answer) %>% count(category, comment_id) %>% filter(n > 1)
+zeroshot_summary_race <- zero_shot_misspelling %>% 
+  count(category, comment_id, answer) %>% 
+  count(category, comment_id) %>% 
+  filter(n > 1 & category == "racist")
+zeroshot_summary_sex <- zero_shot_misspelling %>% 
+  count(category, comment_id, answer) %>% 
+  count(category, comment_id) %>% 
+  filter(n > 1 & category == "sexist")
+
+# Racist
+zero_results_summary <- zero_shot_misspelling %>% 
+                          filter(category == "racist" & comment_id %in% zeroshot_summary_race$comment_id) %>% 
+                          filter(comment_id != 26) %>% # 'No,' vs. 'No.' for this comment
+                          arrange(comment_id)
+
+results <- tibble()
+for (i in unique(zero_results_summary$comment_id)) {
+  original <- zero_results_summary %>% filter(comment_id == i & status == "unedited")
+  original_answer <- original["answer"] %>% as.character()
+  edits <- zero_results_summary %>% filter(comment_id == i & status == "edited" & answer != original_answer)
+  results <- rbind(results, original, edits)
+}
+results <- results %>% select(label, status, comment, answer)
+
+
+  
+# Construct summary table
+
+
+# Sexist
 zero_shot_misspelling %>% 
-  filter(category == "racist" & comment_id %in% zeroshot_summary$comment_id)%>% 
+  filter(category == "sexist" & comment_id %in% zeroshot_summary_sex$comment_id)%>% 
   arrange(comment_id) %>%
   View()
 

### 2022-02-26 outputs/documents/paper.Rmd
Updates to body of text and tables

@@
 abstract: "Sophisticated language models such as OpenAI's GPT-3 can generate hateful text that targets marginalized groups.
-Given this capacity, we are interested in whether large language models can be used to identify hate speech and classify text as sexist or racist?
+Given this capacity, we are interested in whether large language models can be used to identify hate speech and classify text as sexist or racist.
 We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning.
-We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an accuracy between 48 per cent and 69 per cent.
-With few-shot learning and an instruction included in the prompt, the model's accuracy can be as high as 78 per cent.
+We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an accuracy between 56.7 per cent and 68.3 per cent depending on the category of text and type of learning.
+With few-shot learning, the model's accuracy can be as high as 88.3 percent.
 We conclude that large language models have a role to play in hate speech detection, and that with further development language models could be used to counter hate speech and even self-police."
@@
 For instance, Google Search uses an NLP model called BERT to better understand what is meant by a word given its context.
-Some sophisticated natural language processing (NLP) models, such as OpenAI's GPT-3, can additionally produce text as an output.
+Some sophisticated natural language processing (NLP) models, such as OpenAI's Generative Pre-trained Transformer 3 (GPT-3), can additionally produce text as an output.
 
@@
 
-While these, and other, issues give us pause, the dual-use problem, which is that the same technology can be applied to both good and bad uses, provides motivation.
+While these issues (among others) give us pause, the dual-use problem, which is that the same technology can be applied to both good and bad uses, provides motivation.
 For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text [@hovy2016social].
-In this paper we are interested in whether given large language models can produce harmful language, can they also identify, or learn to identify, harmful language?
+In this paper we are interested in whether large language models, given that they can produce harmful language, can also identify, or learn to identify, harmful language.
 
@@
 We show that this knowledge can be used to identify abusive language and even hate speech.
-In particular we consider 120 different extracts that have been categorized as 'racist', 'sexist', or 'neither' in the single-category settings and 243 different extracts in the mixed-category settings.
+In particular we consider 120 different extracts that have been categorized as 'racist', 'sexist', or 'neither' in the single-category settings (zero-shot, one-shot, and few-shot) and 243 different extracts in the mixed-category few-shot settings.
 We ask GPT-3 to classify these based on zero-, one-, and few-shot learning, with and without instruction.
-We find that the model performs best with few-shot learning when an instruction is included.
-In that setting the model can accurately classify around 78 per cent of the extracts.
+We find that the model performs best with mixed-category few-shot learning.
+In that setting the model can accurately classify around 85.6 percent of the racist extracts and 88.3 percent of sexist extracts.
 If language models can be used to identify abusive language, then not only is there potential for them to counter the production of abusive language by humans, but they could also potentially self-police.
@@
 
-<!-- Insert brief description of GPT-3 - the general usage of the model, its transformer-based architecture, what are the inputs-outputs, etc. -->
-
-GPT-3 is the third generation of the Generative Pre-trained Transformer models created by OpenAI.
-OpenAI is a private company in California that develops artificial intelligence models.
+<!-- Insert brief description of GPT-3 - the general usage of the model, its transformer-based architecture, what are the inputs-outputs, etc. - ADD MORE? -->
+
+GPT-3 is the third generation of the Generative Pre-trained Transformer models created by OpenAI, a private company in California that develops artificial intelligence models.
+GPT-3 is an autoregressive NLP model that can perform a variety of tasks, including responding to questions, summarizing and parsing text, translation, and classification.
+Interactions with the model involve inputting some text as a prompt and GPT-3 returning a text completion according to that prompt.
+
 Until January 11, when @fedus2021switch announced a Transformer model with a trillion parameters, GPT-3 was the largest, publicly-known, Transformer language model.
@@
 There has been a large amount of research focused on detecting hate speech.
-And as part of this various hate speech datasets have been created and examined.
+As part of this process, various hate speech datasets have been created and examined.
 For instance, @waseem2016hateful create a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation.
@@
 
-We examine the ability of GPT-3 to identity hate speech in zero-shot, one-shot, and few-shot settings.
+We examine the ability of GPT-3 to identify hate speech in zero-shot, one-shot, and few-shot settings.
 There are a variety of parameters, such as temperature, that control the degree of text variation.
@@
 The first targets the race of the recipient, and the other targets the gender of the recipient.
-With zero- and one-shot learning, the model identifies hate speech one category at a time.
-With few-shot learning, the categories are mixed, and the model is asked to classify an input as sexist, racist, or neither.
+With zero-, one-, and few-shot single-category learning, the model identifies hate speech one category at a time.
+With few-shot mixed-category learning, the categories are mixed, and the model is asked to classify an input as sexist, racist, or neither.
 Zero-shot learning means an example is not provided in the prompt.
@@
 With the introduction of 10 static example sets for multi-category few-shot learning, 240 comments were classified for each example set.
+The comments in the example sets were drawn from the existing pool of 240 comments.
+For each example set, the comment from each category being used in the example set was dropped from the input dataset and an additional comment from each original dataset (one 'racist', one 'sexist', and one 'neither') was added in as a replacement.
+This replacement was kept consistent each time, for a total of 243 unique comments classified in the few-shot mixed-category setting.
 
@@
 That is, the model performs this task 120 times with different comments each time.
-An example of one-shot learning for recognizing a comment that is labeled as sexist is:
+An example of one-shot learning for recognizing a comment that is labelled as sexist is:
 
@@
 The answer is expected to be binary.
-For instance, the model is expected to categorize a passage of text as 'sexist' or 'not-sexist'.
+For instance, the model is expected to categorize a passage of text as 'sexist' or 'not sexist'.
 An example of this is:
@@
 The assignment of sexist or not in the prompt is based on the ETHOS dataset classification.
+
+<!-- Is the description of how the example sets were selected too detailed here? -->
 
@@
 
-# Result
-
-## Zero-shot learning
-
-The results of the zero-shot experiments are presented in Table \@ref(tab:zeroshot-racism), Table \@ref(tab:zeroshot-sexism), Table \@ref(tab:zeroshot-hate), and \@ref(tab:zeroshot-summary).
+# Results
+
 We assess GPT-3's performance in all settings using accuracy, precision, recall, and F1 score.
@@
 F1 score is the harmonic mean of precision and recall.
-In the case of hate speech identification it is desirable to have a model with high recall, meaning a model that can identify a relatively high proportion of the hate speech text within a data set, however the F1 score can provide a more well-rounded metric for model performance and comparison.
-
+In the case of hate speech identification it is desirable to have a model with high recall, meaning a model that can identify a relatively high proportion of the hate speech text within a data set.
+However, the F1 score can provide a more well-rounded metric for model performance and comparison.
+
+## Zero-shot learning
+
+The results of the zero-shot experiments are presented in Tables \@ref(tab:zeroshot-racism), \@ref(tab:zeroshot-sexism), \@ref(tab:zeroshot-hate), and \@ref(tab:zeroshot-summary).
 The model has 34 matches (true positives and negatives) and 26 mismatches (false positives and negatives) in the sexist category, and 41 matches and 19 mismatches in the racist category.
@@
 
-The results of the one-shot learning experiments are presented in Table \@ref(tab:oneshot-racism), Table \@ref(tab:oneshot-sexism), Table \@ref(tab:oneshot-hate), and Table \@ref(tab:oneshot-summary).
+The results of the one-shot learning experiments are presented in Tables \@ref(tab:oneshot-racism), \@ref(tab:oneshot-sexism), \@ref(tab:oneshot-hate), and \@ref(tab:oneshot-summary).
 The model has 37 matches and 23 mismatches in the racist category, and 36 matches and 24 mismatches in the sexist category.
@@
 
-The results of the single-category, few-shot learning, experiments are presented in Table \@ref(tab:fewshotsingle-racism), Table \@ref(tab:fewshotsingle-sexism), Table \@ref(tab:fewshotsingle-hate), and Table \@ref(tab:fewshotsingle-summary).
+The results of the single-category, few-shot learning, experiments are presented in Tables \@ref(tab:fewshotsingle-racism), \@ref(tab:fewshotsingle-sexism), \@ref(tab:fewshotsingle-hate), and \@ref(tab:fewshotsingle-summary).
 The model has 41 matches and 19 mismatches in the racist category, and 42 matches and 18 mismatches in the sexist category.
@@
 knitr::kable(table,
-             caption="Performance of mixed-category few-shot learning in racist text classification",
+             caption="Performance of mixed-category few-shot learning in text classification",
                # col.names=c("", "Percent"),
@@
 knitr::kable(table,
-             caption="Performance of mixed-category few-shot learning in racist text classification, with instruction",
+             caption="Performance of mixed-category few-shot learning in text classification, with instruction",
                # col.names=c("", "Percent"),
@@
 
-<!-- Fix below -->
 In the mixed-category few-shot setting, different example sets yield different accuracy rates for racist and sexist comments with noticeable improvement over the single-category approaches.
-Given our definition of true negative in the mixed-category setting (see Section \@ref(sec:few-shot-learning----mixed-category)), large number of true negatives, present in the dataset
-
-Without an instruction included in the prompt, the accuracy rates range from 57 per cent (Example Set 9) to 75 per cent (Example Set 2).
-Adding an instruction improves the performance, and the highest accuracy rate increases from 75 per cent (Example Set 2) to 78 per cent (Example Set 1).
-Overall accuracy rates also increase in almost every example set after adding an instruction in the prompt.
-The large difference in accuracy rates between the example sets suggests that the content of the examples may matter.
+Our definition of true negative in the mixed-category few-shot setting (see Section \@ref(few-shot-learning----mixed-category)) resulted in a large number of true negatives in our analysis, thus recall and F1 score may be better metrics for measuring model performance in this context.
+Mixed-category few-shot learning without instruction had noticeably better F1 scores for both racist and sexist comments than either zero-shot or one-shot learning.
+With instruction added, mixed-category few-shot learning performed similarly well for racist text identification, however the model performed relatively poorly in identifying sexist speech, with an F1 score of 62.97 percent overall and a recall of 50.17 percent.
+Overall, it appears as though GPT-3 is most effective at identifying both racist and sexist comments in the mixed-category few-shot learning setting, without instruction.
+
+Examining number of classification matches for each example set, the overall proportion of matches increases in almost every example set after adding an instruction in the prompt.
+The differences in accuracy, precision, and recall between the example sets suggests that the content of the examples may matter as well.
 It may be that deliberately curated examples would enable better accuracy.
+Adding an instruction to the prompt is useful for restricting the output of the model to more clear-cut classifications.
+Depending on the purposes of classification, it appears as though adding an instruction can improve model performance by some metrics, however this may vary by the category of text considered and still produce the low recall observed in many of the example sets classified with instruction.
 

### 2022-02-26 inputs/data_collection_private.py

@@ -11,8 +11,8 @@ import pandas as pd
 import numpy as np
 import time
 import random
-openai.organization = "org-JICO2278t41sb6tLfBpmPmhO"
-openai.api_key = "sk-VUUDX4QYst2QwmMdNs0QsOa2JYTLYSAP8IvykqFQ"
+openai.organization = "INSERT ORD ID"
+openai.api_key = "INSERT API KEY"
 
 
 # In[3]:
@@ -355,16 +355,16 @@ all_few_shot_fixed_examples_result = pd.DataFrame()
 #Mixed Cat, Temperature = 0
 for i in range(0, 10):
     neither_comments = not_hate.reset_index().comment[0:121]
-    #sexist_comments = sexist.reset_index().comment[0:61]
-    #racist_comments = racist.reset_index().comment[0:61]
-#     for racist_comment in racist_comments.drop(i):
-#         few_shot_fixed_examples_result = few_shot_fixed_examples(i, "fixed-example", "racist", racist_comment, temperature = 0)
-#         all_few_shot_fixed_examples_result = all_few_shot_fixed_examples_result.append(few_shot_fixed_examples_result, ignore_index=True)
-#         time.sleep(.5)
-#     for sexist_comment in sexist_comments.drop(i):
-#         few_shot_fixed_examples_result = few_shot_fixed_examples(i, "fixed-example", "sexist", sexist_comment, temperature = 0)
-#         all_few_shot_fixed_examples_result = all_few_shot_fixed_examples_result.append(few_shot_fixed_examples_result, ignore_index=True)
-#         time.sleep(.5)
+    sexist_comments = sexist.reset_index().comment[0:61]
+    racist_comments = racist.reset_index().comment[0:61]
+    for racist_comment in racist_comments.drop(i):
+        few_shot_fixed_examples_result = few_shot_fixed_examples(i, "fixed-example", "racist", racist_comment, temperature = 0)
+        all_few_shot_fixed_examples_result = all_few_shot_fixed_examples_result.append(few_shot_fixed_examples_result, ignore_index=True)
+        time.sleep(.5)
+    for sexist_comment in sexist_comments.drop(i):
+        few_shot_fixed_examples_result = few_shot_fixed_examples(i, "fixed-example", "sexist", sexist_comment, temperature = 0)
[…]

### 2022-02-26 inputs/data_collection_functions.py
Removed api key from script

@@ -3,8 +3,8 @@
 
 import openai
 import pandas as pd
-openai.organization = "org-JICO2278t41sb6tLfBpmPmhO"
-openai.api_key = "sk-VUUDX4QYst2QwmMdNs0QsOa2JYTLYSAP8IvykqFQ"
+openai.organization = "INSERT ORD ID"
+openai.api_key = "INSERT API KEY"
 
 
 ethos_data = pd.read_csv("inputs/Ethos_Dataset_Multi_Label.csv", delimiter=';')

### 2022-02-28 outputs/documents/paper.Rmd
Proof reading updates

@@
 Accuracy is the proportion of correctly classified comments (hate speech and non-hate speech) out of all comments classified.
-Precision is the proportion of hate speech comments correctly identified out of all comments identified as hate speech (both correctly and incorrectly).
-Recall is the number of hate speech comments correctly identified out of all hate speech comments in the data set (both correctly and incorrectly identified).
-F1 score is the harmonic mean of precision and recall.
-In the case of hate speech identification it is desirable to have a model with high recall, meaning a model that can identify a relatively high proportion of the hate speech text within a data set.
+Precision is the proportion of hate speech comments correctly classified out of all comments classified as hate speech (both correctly and incorrectly).
+Recall is the proportion of hate speech comments correctly classified out of all hate speech comments in the data set (both correctly and incorrectly classified).
+The F1 score is the harmonic mean of precision and recall.
+In the case of hate speech classification it is desirable to have a model with high recall, meaning a model that can identify a relatively high proportion of the hate speech text within a data set.
 However, the F1 score can provide a more well-rounded metric for model performance and comparison.
@@
 The model has 34 matches (true positives and negatives) and 26 mismatches (false positives and negatives) in the sexist category, and 41 matches and 19 mismatches in the racist category.
-The model performs with higher accuracy and precision when identifying racist comments compared with identifying sexist comments.
+The model performs more accurately when identifying racist comments, with an accuracy of 68.3 percent, compared with identifying sexist comments, with an accuracy of 56.7 percent, however the F1 score for each type of hate speech is approximately the same.
 The overall ratio of matches and mismatches is 75:45.
 In other words, the accuracy in identifying hate speech in the zero-shot setting is 62.5 per cent.
+The model has an F1 score of 80.5 percent in this setting, with a notably high recall of 86.7 percent as well.
 
@@
   # select(!Category) %>%
-  knitr::kable(caption="Performance of zero-shot learning in hate speech classification (percent)",
+  knitr::kable(caption="Performance of zero-shot learning in hate speech classification",
               # col.names=c(""=1),
@@
 The model has 37 matches and 23 mismatches in the racist category, and 36 matches and 24 mismatches in the sexist category.
-In contrast with the result generated from zero-shot learning, the model approximately the same in identifying racist comments compared with identifying sexist comments.
-The general performance in the one-shot setting is worse than in the zero-shot setting, with lower accuracy, recall, and precision overall.
+In contrast with the result generated from zero-shot learning, the model performs approximately the same in identifying racist comments and identifying sexist comments.
 The overall ratio of matches and mismatches is 73:47.
 In other words, the accuracy of identifying hate speech in the one-shot setting is 60.8 per cent.
+The general performance in the one-shot setting is worse than in the zero-shot setting, with lower accuracy, recall, precision, and F1 score overall.
 
@@
 Similar to the one-shot setting, the model performs almost equally well at identifying racist comments compared with identifying sexist comments.
-The general performance in the few-shot learning setting is similar to the performance in the one-shot learning setting as well.
-The overall ratio of matches and mismatches is 83:37, or around 69.2 per cent, with higher precision and lower recall compared with the one-shot learning setting.
+The general performance in the single-category few-shot learning setting is slightly more accurate than performance in other settings, with an accuracy of 69.2 percent compared with 60.8 percent in the one-shot setting and 62.5 percent in the zero-shot setting.
+However, the model in this context has the lowest F1 score of the settings considered thus far at 60.5 percent.
 
@@
 
-Among the ten sets of examples, Example Set 10 yields the best performance in terms of F1 score for both racist and sexist comments.
-It also has the highest accuracy for identifying sexist comments at 91.25 percent and is tied with Example Set 2 for the highest accuracy in identifying racist comments at 90.42 percent.
-The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 68.26 percent (and the lowest accuracy at 77.92 percent) for this dataset.
-The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 68.45 percent (and the lowest accuracy at 80.42 percent) for this dataset.
-The differences between Example Sets 8, 9, and 10 suggest that, although the models are provided with same number of examples, the content of the examples also affects how the model makes inferences.
-Overall, the mixed-category few-shot setting performs slightly better at identifying sexist text versus racist text.
-It is also performs with higher accuracy and a higher F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
+Among the ten sets of examples, Example Set 1 yields the best performance in terms of accuracy (90.6 percent) and F1 score (86.6 percent) for racist comments and Example Set 10 yields the best performance by the same metrics for sexist comments (accuracy of 89.44 percent, F1 score of 84.6 percent).
+The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 69.9 percent (and the lowest accuracy at 72.8 percent) for this dataset.
+The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 68.5 percent (and the lowest accuracy at 73.9 percent) for this dataset.
+The differences between Example Sets 1, 8, 9, and 10 suggest that, although the models are provided with same number of examples, the content of the examples also affects how the model makes inferences.
+Overall, the mixed-category few-shot setting performs approximately the same at identifying sexist text and racist text.
+It is also performs with higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
 
@@
   few_shot_mixed_result %>%
+  filter(label != "sexist") %>%
   mutate(example_set = example_set + 1,
@@
   few_shot_mixed_result %>%
+  filter(label != "racist") %>%
   mutate(example_set = example_set + 1,
@@
 
+The results presented for each category of text include the classifications of comments that were labelled as 'neither' and the category in question.
 For the purposes of our analysis, a classification was considered a true positive if the answer outputted by GPT-3 contained a category that matched the comment's label.
-For example, if a comment was labelled 'sexist' and the comment was classified by the model as 'sexist, racist', this was considered a true positive in the classification of sexist comments (the comment is sexist, and the model classified it as sexist) and a false positive in the classification of racist comments (the comment is not racist, and the model classified it as racist).
+For example, if a comment was labelled 'sexist' and the comment was classified by the model as 'sexist, racist', this was considered a true positive in the classification of sexist comments.
 If a comment was labelled 'sexist' and the comment was classified by the model as 'racist', 'transphobic', 'neither', etc.
@@
 
-Since each comment is only labelled with one hate speech category, a classification was considered a true negative if the label of the comment was either 'neither' or the category not being analyzed, and the comment received a classification that did not include the category being considered.
-For example, if a comment was labelled 'racist' and the model answered 'neither', this is considered a true negative in the classification of sexist comments (the comment is not sexist, and the model did not classify it as sexist), but a false negative in the classification of racist comments (the comment is racist, but the model did classify it as racist).
+Since each comment is only labelled with one hate speech category, a classification was considered a true negative if the label of the comment was 'neither' and the comment received a classification that did not include the category being considered.
+For example, if a comment was labelled 'neither' and the model answered 'racist', this is considered a true negative in the classification of sexist comments (the comment is not sexist, and the model did not classify it as sexist), but a false positive in the classification of racist comments (the comment is not racist, but the model classified it as racist).
 
@@
 
-The results of the mixed-category few-shot learning, with instruction, experiments are presented in Table \@ref(tab:fewshotmixedinstruct-matrix), Table \@ref(tab:fewshotmixedinstruct-racism), Table \@ref(tab:fewshotmixedinstruct-sexism), and Table \@ref(tab:fewshotmixedinstruct-summary).
-With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (92.08 percent) and F1 score (84.03 percent) for sexist text, however Example Set 4 now performs best for racist text in terms of both accuracy (91.25 percent) and F1 score (83.20 percent).
-When considering the classification of racist and sexist speech independently, the models perform similarly with and without instruction in the mixed-category few-shot setting.
+The results of the mixed-category few-shot learning, with instruction, experiments are presented in Tables \@ref(tab:fewshotmixedinstruct-matrix), \@ref(tab:fewshotmixedinstruct-racism), \@ref(tab:fewshotmixedinstruct-sexism), and \@ref(tab:fewshotmixedinstruct-summary).
+With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (89.4 percent) and F1 score (84 percent) for sexist text, however Example Set 4 now performs best for racist text in terms of both accuracy (89.4 percent) and F1 score (84.6 percent).
+When considering the classification of racist and sexist speech overall, the models perform similarly with and without instruction when classifying racist text, but the model appears to perform slightly better at identifying sexist text when the instruction is omitted.
 
@@
   few_shot_instruction_result %>%
+  filter(label != "sexist") %>%
   mutate(example_set = example_set + 1,
@@
   few_shot_instruction_result %>%
+  filter(label != "racist") %>%
   mutate(example_set = example_set + 1,
@@
 ```
+
 ```{r fewshotmixedinstruct-summary}
@@
 
-In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 62.5 per cent with an F1 score of 80.54 percent.
-In the one-shot learning setting the accuracy decreases to 60.83 percent with an F1 score of 65.25 percent.
+In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 62.5 per cent with an F1 score of 80.5 percent.
+In the one-shot learning setting the accuracy decreases to 60.8 percent with an F1 score of 65.3 percent.
 Accuracy increases to 69.2 percent in the single-category few-shot learning setting, with an F1 score of 60.5 percent.
-Of the three single-category approaches, zero-shot learning has a notably high recall value of 86.67 percent.
-
-It is likely that the model is not suitable for use in hate speech detection in either the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the accuracy rates are between 60 per cent and 70 per cent.
+Of the three single-category approaches, zero-shot learning has a notably high recall value of 86.7 percent.
+
+It is likely that the model is not ideal for use in hate speech detection in the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the accuracy rates are between 60 per cent and 70 per cent.
 @davidson2017automated, using a different model and approach, similarly find 'that almost 40 per cent of hate speech is misclassified'.
@@
 
-In the mixed-category few-shot setting, different example sets yield different accuracy rates for racist and sexist comments with noticeable improvement over the single-category approaches.
-Our definition of true negative in the mixed-category few-shot setting (see Section \@ref(few-shot-learning----mixed-category)) resulted in a large number of true negatives in our analysis, thus recall and F1 score may be better metrics for measuring model performance in this context.
+In the mixed-category few-shot setting, different example sets yield different accuracy rates for racist and sexist comments, with noticeable improvement over the single-category approaches.
 Mixed-category few-shot learning without instruction had noticeably better F1 scores for both racist and sexist comments than either zero-shot or one-shot learning.
-With instruction added, mixed-category few-shot learning performed similarly well for racist text identification, however the model performed relatively poorly in identifying sexist speech, with an F1 score of 62.97 percent overall and a recall of 50.17 percent.
+With instruction added, mixed-category few-shot learning performed similarly well for racist text identification, however the model performed relatively poorly in identifying sexist speech, with an F1 score of 63.1 percent overall and a recall of 50.2 percent meaning nearly half of the sexist comments were wrongly classified.
 Overall, it appears as though GPT-3 is most effective at identifying both racist and sexist comments in the mixed-category few-shot learning setting, without instruction.
 
-Examining number of classification matches for each example set, the overall proportion of matches increases in almost every example set after adding an instruction in the prompt.
+Examining the proportion of classification matches for each example set (calculated as the number of correct 'racist', 'sexist', and 'neither' classifications out of all comments classified), the overall proportion of matches increases in almost every example set after adding an instruction in the prompt.
 The differences in accuracy, precision, and recall between the example sets suggests that the content of the examples may matter as well.
@@
 Looking at the misclassified examples helps us to understand what may be contributing to erroneous results.
-The following comment has a true label of 'racist', but the model classifies it as 'sexist'.
-This comment uses racial identity terms such as 'Asian' and 'White', but its core argument is about discrimination on the basis of sex.
-The model did not have the necessary sensitivity to categorize the comment as sexist instead of racist.
-
-> 'The male gene is stronger, as it should be of course.
-Have an Asian male breed with a White women and the child will look very asian.
-Reverse it and the child will look mush more whiter': sexist (True label: racist.)
-
-As another similar example, the following comment has a true label of 'neither', but the model classified it as 'transphobic'.
-
-> 'Civil rights movement for transgendered people.': transphobic (True label: neither.)
-
-The comment is a plain statement without judgment; the inclusion of 'transgendered people' may be the reason for the false classification (specifically a false positive in the context of detecting hate speech in general).
+The following comment has a true label of 'sexist', but the model classifies it as 'racist' in the mixed-category few-shot setting with instruction.
+This comment uses the word 'Islam' which may often be associated with discrimination on the basis of race or ethnicity, but its core argument is about gender-based violence.
+When instructed to pick a single classification, the model did not have the necessary sensitivity to categorize the comment as sexist instead of racist.
+The option to classify a comment under multiple hate speech categories is one reason for the model performing better without instruction in the mixed-category setting.
+
+> 'Islam! Lets beat their feminist ass'
+>
+> Mixed-category few-shot classification: racist, sexist (True label: sexist)
+>
+> Mixed-category few-shot classification, with instruction: racist (True label: sexist)
+
+As another similar example, the following comment has a true label of 'neither', but the model classified it as 'transphobic' in the mixed-category few-shot setting (without instruction).
+
+> 'Transgenders have to protect each other, not fight each other': transphobic (True label: neither.)
+
+The comment has a seemingly positive connotation towards the transgender community; the inclusion of 'transgenders' may be the reason for the false classification.
 If this were the case, then combined with the previous example, the model may have a tendency to generate false positive results when it encounters words that are identity terms, erroneously ignoring the context in which they are used.
@@
 profanity %>%
-  knitr::kable(caption="Profane strings used to test extract comments to test impacts of misspelling and censorship on hate speech classificiation",
+  knitr::kable(caption="Profane strings used to identify comments to test impacts of misspelling and censorship on hate speech classificiation",
                booktabs = TRUE,

### 2022-02-28 inputs/data_collection_functions.py

@@ -3,7 +3,7 @@
 
 import openai
 import pandas as pd
-openai.organization = "INSERT ORD ID"
+openai.organization = "INSERT ORG ID"
 openai.api_key = "INSERT API KEY"
 
 

### 2022-02-28 inputs/data_collection_private.py

@@ -11,7 +11,7 @@ import pandas as pd
 import numpy as np
 import time
 import random
-openai.organization = "INSERT ORD ID"
+openai.organization = "INSERT ORG ID"
 openai.api_key = "INSERT API KEY"
 
 

### 2022-02-28 inputs/misspelling_experiment.py

@@ -2,8 +2,8 @@ import openai
 import pandas as pd
 import time
 import inputs.data_collection_functions as dc
-openai.organization = "org-JICO2278t41sb6tLfBpmPmhO"
-openai.api_key = "sk-VUUDX4QYst2QwmMdNs0QsOa2JYTLYSAP8IvykqFQ"
+openai.organization = "INSERT ORG ID"
+openai.api_key = "INSERT API KEY"
 
 ethos_data = pd.read_csv("inputs/Ethos_Dataset_Multi_Label.csv", delimiter=';')
 ethos_data_binary = pd.read_csv("inputs/Ethos_Dataset_Binary.csv", delimiter=';')

### 2022-02-28 outputs/documents/paper.Rmd
Final proof reading edits

@@
 profanity %>%
-  knitr::kable(caption="Profane strings used to identify comments to test impacts of misspelling and censorship on hate speech classificiation",
+  knitr::kable(caption="Strings used to extract comments with profanity and edits introduced to test impacts of misspelling and censorship on hate speech classificiation",
                booktabs = TRUE,

### 2022-03-15 outputs/bmc_template/bmc_article.tex
Tweaks throughout

--- 2021-03-23 outputs/documents/paper.tex
@@
-\documentclass[12pt,]{article}
-\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
-\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
-\usepackage[]{mathpazo}
+%% BioMed_Central_Tex_Template_v1.06
+%%                                      %
+%  bmc_article.tex            ver: 1.06 %
+%                                       %
 
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
+%%IMPORTANT: do not delete the first line of this template
+%%It must be present to enable the BMC Submission system to
+%%recognise this template!!
 
-\usepackage{abstract}
-\renewcommand{\abstractname}{}    % clear the title
-\renewcommand{\absnamepos}{empty} % originally center
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                     %%
+%%  LaTeX template for BioMed Central  %%
+%%     journal article submissions     %%
+%%                                     %%
+%%          <8 June 2012>              %%
+%%                                     %%
+%%                                     %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\renewenvironment{abstract}
- {{%
-    \setlength{\leftmargin}{0mm}
-    \setlength{\rightmargin}{\leftmargin}%
-  }%
-  \relax}
- {\endlist}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                                                 %%
+%% For instructions on how to fill out this Tex template           %%
+%% document please refer to Readme.html and the instructions for   %%
+%% authors page on the biomed central website                      %%
+%% http://www.biomedcentral.com/info/authors/                      %%
+%%                                                                 %%
+%% Please do not use \input{...} to include other tex files.       %%
+%% Submit your LaTeX manuscript as one .tex document.              %%
+%%                                                                 %%
+%% All additional figures and files should be attached             %%
+%% separately and not embedded in the \TeX\ document itself.       %%
+%%                                                                 %%
+%% BioMed Central currently use the MikTex distribution of         %%
+%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
+%% http://www.miktex.org                                           %%
+%%                                                                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\makeatletter
-\def\@maketitle{%
-  \newpage
-%  \null
-%  \vskip 2em%
-%  \begin{center}%
-  \let \footnote \thanks
-    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
+%%% additional documentclass options:
+%  [doublespacing]
+%  [linenumbers]   - put the line numbers on margins
+
+%%% loading packages, author definitions
+
+%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
+\documentclass{bmcart}
+
+%%% Load packages
+%\usepackage{amsthm,amsmath}
+%\RequirePackage{natbib}
+%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
+%\RequirePackage{hyperref}
+\usepackage[utf8]{inputenc} %unicode support
+%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
+%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                             %%
+%%  If you wish to display your graphics for   %%
+%%  your own use using includegraphic or       %%
+%%  includegraphics, then comment out the      %%
+%%  following two lines of code.               %%
+%%  NB: These line *must* be included when     %%
+%%  submitting to BMC.                         %%
+%%  All figure files must be submitted as      %%
+%%  separate graphics through the BMC          %%
+%%  submission process, not included in the    %%
+%%  submitted article.                         %%
+%%                                             %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\def\includegraphic{}
+\def\includegraphics{}
+
+%%% Put your definitions there:
+\startlocaldefs
+\endlocaldefs
+
+%%% Begin ...
+\begin{document}
+
+%%% Start of article front matter
+\begin{frontmatter}
+
+\begin{fmbox}
+\dochead{Research}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the title of your article here     %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{Detecting Hate Speech with GPT-3}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the authors here                   %%
+%%                                          %%
+%% Specify information, if available,       %%
+%% in the form:                             %%
+%%   <key>={<id1>,<id2>}                    %%
+%%   <key>=                                 %%
+%% Comment or delete the keys which are     %%
+%% not used. Repeat \author command as much %%
+%% as required.                             %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\author[
+   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
+   corref={aff1},                       % id of corresponding address, if any
+   noteref={n1},                        % id's of article notes, if any
+   email={rohan.alexander@utoronto.ca}   % email address
+]{\inits{KC}\fnm{Ke-Li} \snm{Chiu}}
+\author[
+   addressref={aff1,aff2},
+   email={rohan.alexander@utoronto.ca}
+]{\inits{RA}\fnm{Rohan} \snm{Alexander}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter the authors' addresses here        %%
+%%                                          %%
+%% Repeat \address commands as much as      %%
+%% required.                                %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\address[id=aff1]{%                           % unique id
+  \orgname{Faculty of Information, University of Toronto}, % university, etc
+  % \street{Waterloo Road},                     %
+  %\postcode{}                                % post or zip code
+  \city{Toronto},                              % city
+  \cny{Canada}                                    % country
 }
-%\fi
-\makeatother
-
-\setcounter{secnumdepth}{0}
-
-\usepackage{longtable,booktabs}
-
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-
-\title{Detecting Hate Speech with GPT-3 \thanks{Code and data are available at: \url{https://github.com/kelichiu/GPT3-hate-speech-detection}.
-We gratefully acknowledge the support of Gillian Hadfield and the Schwartz Reisman Institute for Technology and Society.
-We thank Amy Farrow, Haoluan Chen, Mauricio Vargas Sepúlveda, and Tom Davidson for helpful suggestions.
-Comments on the 22 March 2021 version of this paper are welcome at: \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}  }
-
-\author{\Large Ke-Li Chiu\vspace{0.05in} \newline\normalsize\emph{University of Toronto}   \and \Large Rohan Alexander\vspace{0.05in} \newline\normalsize\emph{University of Toronto and Schwartz Reisman Institute}  }
-
-\date{}
-
-\usepackage{titlesec}
-
-\titleformat*{\section}{\normalsize\bfseries}
-\titleformat*{\subsection}{\normalsize\itshape}
-\titleformat*{\subsubsection}{\normalsize\itshape}
-\titleformat*{\paragraph}{\normalsize\itshape}
-\titleformat*{\subparagraph}{\normalsize\itshape}
-
-\usepackage{natbib}
-\bibliographystyle{apalike}
-\usepackage[strings]{underscore} % protect underscores in most circumstances
-
-\newtheorem{hypothesis}{Hypothesis}
-\usepackage{setspace}
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
-\usepackage{hyperref}
-\usepackage{amsmath}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
-
-% move the hyperref stuff down here, after header-includes, to allow for - \usepackage{hyperref}
-
-\makeatletter
-\@ifpackageloaded{hyperref}{}{%
-\ifxetex
-  \PassOptionsToPackage{hyphens}{url}\usepackage[setpagesize=false, % page size defined by xetex
-              unicode=false, % unicode breaks when used with xetex
-              xetex]{hyperref}
-\else
-  \PassOptionsToPackage{hyphens}{url}\usepackage[draft,unicode=true]{hyperref}
-\fi
+\address[id=aff2]{%
+  \orgname{Department of Statistical Sciences, University of Toronto},
+  % \street{D\"{u}sternbrooker Weg 20},
+  % \postcode{24105}
+  \city{Toronto},
+  \cny{Canada}
 }
 
-\@ifpackageloaded{color}{
-    \PassOptionsToPackage{usenames,dvipsnames}{color}
-}{%
-    \usepackage[usenames,dvipsnames]{color}
-}
-\makeatother
-\hypersetup{breaklinks=true,
-            bookmarks=true,
-            pdfauthor={Ke-Li Chiu (University of Toronto) and Rohan Alexander (University of Toronto and Schwartz Reisman Institute)},
-             pdfkeywords = {GPT-3; natural language processing; quantitative analysis; hate speech.},  
-            pdftitle={Detecting Hate Speech with GPT-3},
-            colorlinks=true,
-            citecolor=blue,
-            urlcolor=blue,
-            linkcolor=magenta,
-            pdfborder={0 0 0}}
-\urlstyle{same}  % don't use monospace font for urls
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Enter short notes here                   %%
+%%                                          %%
+%% Short notes will be after addresses      %%
+%% on first page.                           %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% Add an option for endnotes. -----
+\begin{artnotes}
+%\note{Sample of title note}     % note to the article
+\note[id=n1]{Equal contributor} % note, connected to author
+\end{artnotes}
 
-% add tightlist ----------
-\providecommand{\tightlist}{%
-\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\end{fmbox}% comment this for two column layout
 
-% add some other packages ----------
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The Abstract begins here                 %%
+%%                                          %%
+%% Please refer to the Instructions for     %%
+%% authors on http://www.biomedcentral.com  %%
+%% and include the section headings         %%
+%% accordingly for your article type.       %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% \usepackage{multicol}
-% This should regulate where figures float
-% See: https://tex.stackexchange.com/questions/2275/keeping-tables-figures-close-to-where-they-are-mentioned
-\usepackage[section]{placeins}
+\begin{abstractbox}
 
-\begin{document}
-
-% \pagenumbering{arabic}% resets `page` counter to 1 
-%
-
-% \maketitle
-
-{% \usefont{T1}{pnc}{m}{n}
-\setlength{\parindent}{0pt}
-\thispagestyle{plain}
-{\fontsize{18}{20}\selectfont\raggedright 
-\maketitle  % title \par
-
-}
-
-{
-   \vskip 13.5pt\relax \normalsize\fontsize{11}{12} 
-\textbf{\authorfont Ke-Li Chiu} \hskip 15pt \emph{\small University of Toronto}   \par \textbf{\authorfont Rohan Alexander} \hskip 15pt \emph{\small University of Toronto and Schwartz Reisman Institute}
-
-}
-
-}
-
-\begin{abstract}
-
-    \hbox{\vrule height .2pt width 39.14pc}
-
-    \vskip 8.5pt % \small
-
-\noindent Sophisticated language models such as OpenAI's GPT-3 can generate hateful text that targets marginalized groups.
+\begin{abstract} % abstract
+Sophisticated language models such as OpenAI's GPT-3 can generate hateful text that targets marginalized groups.
 Given this capacity, we are interested in whether large language models can be used to identify hate speech and classify text as sexist or racist?
 We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning.
-We find that with zero- and one-shot learning, GPT-3 is able to identify sexist or racist text with an accuracy between 48 per cent and 69 per cent.
+We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an accuracy between 48 per cent and 69 per cent.
 With few-shot learning and an instruction included in the prompt, the model's accuracy can be as high as 78 per cent.
 We conclude that large language models have a role to play in hate speech detection, and that with further development language models could be used to counter hate speech and even self-police.
-
-\vskip 8.5pt \noindent \emph{Keywords}: GPT-3; natural language processing; quantitative analysis; hate speech. \par
-
-    \hbox{\vrule height .2pt width 39.14pc}
-
 \end{abstract}
 
-\vskip -8.5pt
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The keywords begin here                  %%
+%%                                          %%
+%% Put each keyword in separate \kwd{}.     %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
- % removetitleabstract
+\begin{keyword}
+\kwd{GPT-3}
+\kwd{natural language processing}
+\kwd{quantitative analysis}
+\kwd{hate speech}
+\end{keyword}
 
-\noindent
+% MSC classifications codes, if any
+%\begin{keyword}[class=AMS]
+%\kwd[Primary ]{}
+%\kwd{}
+%\kwd[; secondary ]{}
+%\end{keyword}
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\end{abstractbox}
+%
+%\end{fmbox}% uncomment this for twcolumn layout
 
-Sophisticated natural language processing (NLP) models, such as OpenAI's GPT-3, can produce hateful text.
+\end{frontmatter}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% The Main Body begins here                %%
+%%                                          %%
+%% Please refer to the instructions for     %%
+%% authors on:                              %%
+%% http://www.biomedcentral.com/info/authors%%
+%% and include the section headings         %%
+%% accordingly for your article type.       %%
+%%                                          %%
+%% See the Results and Discussion section   %%
+%% for details on how to create sub-sections%%
+%%                                          %%
+%% use \cite{...} to cite references        %%
+%%  \cite{koon} and                         %%
+%%  \cite{oreg,khar,zvai,xjon,schn,pond}    %%
+%%  \nocite{smith,marg,hunn,advi,koha,mouse}%%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
+% <put your article body there>
+
+%%%%%%%%%%%%%%%%
+%% Background %%
+%%
+\section{Introduction}\label{introduction}
+
+\textbf{This paper contains language and themes that are offensive.}
+
+Natural language processing (NLP) models focus on using normal words, often written text, as their data.
+For instance, one might have content from a large number of books and want to group them into themes.
+Sophisticated NLP models are being increasingly embedded in society.
+For instance, Google Search uses an NLP model called BERT to better understand what is meant by a word given its context.
+Some sophisticated natural language processing (NLP) models, such as OpenAI's GPT-3, can additionally produce text as an output.
+
+The text produced by sophisticated NLP models can be hateful.
 In particular, there have been many examples of text being generated that targets marginalized groups based on their sex, race, sexual orientation, and other characteristics.
+For instance, `Tay' was a chatbot that was released by Microsoft in 2016 on Twitter.
+Within hours of being released, some of its tweets were sexist.
 Large language models are trained on enormous datasets from various sources.
 This means that untruthful statements, human biases, and abusive language are inevitably included.
-Further, \citet{bender2021dangers} describes how even when the models do not possess intent, they risk producing synthetic texts that are offensive or discriminatory and thus cause unpleasant, or even triggering, interaction experiences.
+Further, even when the models do not possess intent, they risk producing synthetic texts that are offensive or discriminatory and thus cause unpleasant, or even triggering, interaction experiences \cite{bender2021dangers}.
 
-The sources of the training datasets raise concerns around three issues: exclusion, over-generalization, and exposure \citep{hovy2016social}.
+Often the datasets that underpin these models consist of, essentially, the whole public internet.
+This source raises concerns around three issues: exclusion, over-generalization, and exposure \cite{hovy2016social}.
 Exclusion happens due to the demographic bias in the dataset.
 In the case of language models that are trained on US and UK English scraped from the Internet, datasets may be disproportionately white, male, and young.
-Therefore, it is not surprising to see white supremacist, misogynistic, and ageist content being over-represented in training datasets \citep{bender2021dangers}.
+Therefore, it is not surprising to see white supremacist, misogynistic, and ageist content being over-represented in training datasets \cite{bender2021dangers}.
 Over-generalization stems from the assumption that what we see in the dataset represents what occurs in the real world.
@@
 While these, and other, issues give us pause, the dual-use problem, which is that the same technology can be applied to both good and bad uses, provides motivation.
-For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text \citep{hovy2016social}.
+For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text \cite{hovy2016social}.
 In this paper we are interested in whether given large language models can produce harmful language, can they also identify, or learn to identify, harmful language?
@@
 We find that the model performs best with few-shot learning when an instruction is included.
-In that setting the model is able to accurately classify around 78 per cent of the extracts.
+In that setting the model can accurately classify around 78 per cent of the extracts.
 If language models can be used to identify abusive language, then not only is there potential for them to counter the production of abusive language by humans, but they could also potentially self-police.
 
-\hypertarget{background}{%
-\section{Background}\label{background}}
+\section{Background}\label{background}
 
-\hypertarget{language-models-transformers-and-gpt-3}{%
-\subsection{Language models, Transformers and GPT-3}\label{language-models-transformers-and-gpt-3}}
+\subsection{Language models, Transformers and GPT-3}\label{language-models-transformers-and-gpt-3}
 
-In its simplest form, a language model is a probability distribution over sequences of words, which are usually generalized further to tokens.
-The sequence of tokens constitutes different linguistic units --- words, sentences, and even documents \citep{bengio2003neural}.
+In its simplest form, a language model involves assigning a probability to a certain sequence of words.
+For instance, the sequence `the cat in the hat' is probably more likely than `the cat in the computer'.
+We typically talk of tokens, or collections of characters, rather than words, and a sequence of tokens constitutes different linguistic units --- words, sentences, and even documents \cite{bengio2003neural}.
 Language models predict the next token based on inputs.
-If we consider each token in a vocabulary as a dimension, then the dimensionality of language quickly becomes large \citep{rosenfeld2000two}.
+If we consider each token in a vocabulary as a dimension, then the dimensionality of language quickly becomes large \cite{rosenfeld2000two}.
 Over time a variety of statistical language models have been created to nonetheless enable prediction.
@@
 It works by considering the co-occurrence of tokens in a sequence.
-In the early 2000s, prominent neural network language models were developed, for instance \citet{bengio2003neural}.
-These were then built on by word embeddings language models in the 2010s in which the distance between tokens represents how related those tokens are, for instance \citet{turian2010word}.
-In 2017, \citet{vaswani2017attention} introduced the Transformer, which marked a new era for language models.
-The Transformer is a network architecture for neural networks that can be trained more quickly than many other approaches \citep{vaswani2017attention}.
-Now most of the representative pre-trained language models, such as BERT \citep{devlin2018bert}, GPT-2 \citep{radford2019language}, and GPT-3 \citep{brown2020language}, are built on this architecture.
+For instance, given the four-word sequence, `the cat in the', it is more likely that the fifth word is `hat' rather than `computer'.
+In the early 2000s, language models based on neural networks were developed, for instance \cite{bengio2003neural}.
+These were then built on by word embeddings language models in the 2010s in which the distance between tokens represents how related those tokens are, for instance \cite{turian2010word}.
+In 2017, \cite{vaswani2017attention} introduced the Transformer, which marked a new era for language models.
+The Transformer is a network architecture for neural networks that can be trained more quickly than many other approaches \cite{vaswani2017attention}.
+Now most representative pre-trained language models, such as Google's model: Bidirectional Encoder Representations from Transformers (BERT) \cite{devlin2018bert}, as well as OpenAI's: Generative Pre-trained Transformer (GPT)-2 \cite{radford2019language}, and GPT-3 \cite{brown2020language}, are built on this architecture.
+These models are widely used, for instance BERT is used by Google search.
 
 GPT-3 is the third generation of the Generative Pre-trained Transformer models created by OpenAI.
-Until January 11, when \citet{fedus2021switch} announced a Transformer model with a trillion parameters, GPT-3 was the largest, publicly-known, Transformer language model.
+OpenAI is a private company in California that develops artificial intelligence models.
+Until January 11, when \cite{fedus2021switch} announced a Transformer model with a trillion parameters, GPT-3 was the largest, publicly-known, Transformer language model.
 GPT-3 is distinctive from its predecessors because of few-shot learning.
@@
 GPT-3 has led to unexpected NLP applications, such as computational code generation given natural language prompts.
-However, like other language models, GPT-3 has also generated inappropriate or even hateful content.
-For instance, \citet{mcguffie2020radicalization} demonstrated the use of GPT-3 in mass-producing radicalized text targeting the Islamic population.
 
-\hypertarget{hate-speech-detection}{%
-\subsection{Hate speech detection}\label{hate-speech-detection}}
+Like other language models, GPT-3 has also generated inappropriate or even hateful content.
+For instance, \cite{mcguffie2020radicalization} demonstrated the use of GPT-3 in mass-producing radicalized text targeting the Islamic population.
+And \cite{lin2021truthfulqa} show that GPT-3 and similar language models can propagate misconceptions that could deceive human readers.
+For instance, when asked `Who really caused 9/11?', they found that GPT-3 provided the false statement `The US government caused 9/11.'
 
-Hate speech detection is of interest to researchers in a variety of domains including computer science and sociology, as well as industry and the judiciary.
-Detecting hate speech is difficult because the definition of hate speech varies depending on the complex intersection of the topic of the assertion, the context, the timing of the post, synchronized world events, and the identity of speaker and recipient \citep{schmidt2017survey}.
-Moreover, it is difficult to discern hate speech from merely offensive language \citep{davidson2017automated}.
+\subsection{Hate speech detection}\label{hate-speech-detection}
+
+There is no commonly held definition of hate speech and different legal jurisdictions have different definitions, as do different companies and other groups.
+One definition is `the intentional verbalization of prejudice against a social group' \cite{kennedy2018gab}.
+Detecting hate speech is difficult because the definition of hate speech varies depending on the complex intersection of the topic of the assertion, the context, the timing of the post, synchronized world events, and the identity of speaker and recipient \cite{schmidt2017survey}.
+Moreover, it is difficult to discern hate speech from merely offensive language \cite{davidson2017automated}.
+Hate speech detection is of interest to academic researchers in a variety of domains including computer science \cite{addressinghatespeech} and sociology \cite{davidson2017automated}.
+It is also of interest to industry, for instance to maintain standards on social networks, and in the judiciary to help identify and prosecute crimes.
 Since hate speech is prohibited in several countries, misclassification of hate speech can become a legal problem.
-For instance, in Canada, speech that contains `public incitement of hatred' or `wilful promotion of hatred' is specified by the Criminal Code \citep{act2021justice}.
+For instance, in Canada, speech that contains `public incitement of hatred' or `wilful promotion of hatred' is specified by the Criminal Code \cite{act2021justice}.
 Policies toward hate speech are more detailed in some social media platforms.
@@
 
-\citet{twitterpolicy2017}
+\cite{twitterpolicy2017}
 \end{quote}
@@
 And as part of this various hate speech datasets have been created and examined.
-For instance, \citet{waseem2016hateful} create a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation, and \citet{davidson2017automated} trains a classifier to distinguish between hate speech and offensive language.
-And it is important to note that even these datasets have bias.
-For instance, \citet{davidson2019racial} found racial bias in five different sets of Twitter data annotated for hate speech and abusive language.
+For instance, \cite{waseem2016hateful} create a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation.
+The use Twitter data, and annotate 16,914 tweets: 3,383 as sexist, 1,972 as racist, and 11,559 as neither.
+They had a high degree of annotator agreement, and most of the disagreements were to do with sexism, and often explained by an annotator lacking apparent context.
+And, \cite{davidson2017automated} trains a classifier to distinguish between hate speech and offensive language.
+To define hate speech, they use online `hate speech lexicon containing words and phrases identified by internet users as hate speech'.
+It is important to note that even these datasets have bias.
+For instance, \cite{davidson2019racial} found racial bias in five different sets of Twitter data annotated for hate speech and abusive language.
 They found that tweets written in African American English are more likely to be labeled as abusive.
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+\section{Methods}\label{methods}
 
@@
 With few-shot learning, the categories are mixed, and the model is asked to classify an input as sexist, racist, or neither.
+Zero-shot learning means an example is not provided in the prompt.
+One-shot learning means that one example is provided, and few-shot means that two or more examples are provided.
 
-\hypertarget{dataset}{%
-\subsection{Dataset}\label{dataset}}
+\subsection{Dataset}\label{dataset}
 
-We use the ETHOS dataset created by \citet{mollas2020ethos}.
+We use the ETHOS dataset created by \cite{mollas2020ethos}.
 ETHOS is based on comments found in YouTube and Reddit.
-The ETHOS YouTube data is collected through Hatebusters \citep{anagnostou2018hatebusters}.
+The ETHOS YouTube data is collected through Hatebusters \cite{anagnostou2018hatebusters}.
 Hatebusters is a platform that collects comments from YouTube and assigns a `hate' score to them using a support vector machine.
-The Reddit data is collected from the Public Reddit Data Repository \citep{baumgartner2020pushshift}.
+That hate-score is only used to decide whether to consider the comment further or not.
+The Reddit data is collected from the Public Reddit Data Repository \cite{baumgartner2020pushshift}.
+The classification is done by contributors to a crowd-sourcing platform.
+They are first asked with an example contains hate speech, and then, if it does, whether it incites violence and other additional details.
 The dataset has two variants: binary and multi-label.
-In the binary dataset comments are classified as hate or non-hate.
+In the binary dataset comments are classified as hate or non-hate based.
 In the multi-label variant, the comments are evaluated on measures that include violence, gender, race, ability, religion, and sexual orientation.
@@
 
-There are 998 statements in the ETHOS dataset that have a binary classification of hate speech or not hate speech.
+We use all of the 998 statements in the ETHOS dataset that have a binary classification of hate speech or not hate speech.
 Of these, the 433 statements that contain hate speech additionally have multiple labels that classify the content, for instance, does the comment have to do with violence, gender, race, nationality, disability, etc.
-We considered the 136 statements that contain race-based hate speech, and we focus on the 76 whose race-based score is at least 0.5.
-Similarly, we considered the 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
-We randomly draw 120 of these statements, using stratified sampling, to create a balanced dataset of 60 sexist statements and 60 racist statements.
+We considered all of the 136 statements that contain race-based hate speech, and we focus on the 76 whose race-based score is at least 0.5.
+Similarly, we considered the all of 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
+To create a balanced dataset we randomly draw 120 of these statements, using stratified sampling, to result in 60 sexist statements and 60 racist statements.
 For comparison purposes, we randomly draw 120 statements that are classified as not hate speech.
+The balanced sample enables us to more easily understand our results.
 
-\hypertarget{zero-shot-learning}{%
-\subsection{Zero-shot learning}\label{zero-shot-learning}}
+\subsection{Zero-shot learning}\label{zero-shot-learning}
 
@@
 
-\hypertarget{one-shot-learning}{%
-\subsection{One-shot learning}\label{one-shot-learning}}
+The model provides this answer based on the dataset that it was trained on.
+
+\subsection{One-shot learning}\label{one-shot-learning}
 
@@
 
-\hypertarget{few-shot-learning}{%
-\subsection{Few-shot learning}\label{few-shot-learning}}
+\subsection{Few-shot learning}\label{few-shot-learning}
 
@@
 
-`Now they know better than this shit lol they dudes. The stronger sex. The man supremacy': sexist.
+`Now they know better than this s*** lol they dudes. The stronger sex. The man supremacy': sexist.
 
@@
 
+The assignment of sexist or not in the prompt is based on the ETHOS dataset classification.
+
 On the other hand, in the mixed model, the model is given an example of sexist text, an example of racist text, and an example of text that is not hate speech.
@@
 \begin{quote}
-`That girl still need a good ass whooping, stupid ass bitch!!': sexist.
+`That girl still need a good ass whooping, stupid ass b****!!': sexist.
 
-`U SUCK SHIT YOU BLACK FUCK': racist.
+'U SUCK S*** YOU BLACK F***': racist.
 
-`You deserve way more subscribers. The shit you say is fucking gold.': neither.
+'You deserve way more subscribers. The s*** you say is f***ing gold.': neither.
 
-`Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With dicks and stuff.':
+'Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With d***s and stuff.':
 \end{quote}
@@
 
-`That girl still need a good ass whooping, stupid ass bitch!!': sexist.
+`That girl still need a good ass whooping, stupid ass b****!!': sexist.
 
-`U SUCK SHIT YOU BLACK FUCK': racist.
+'U SUCK S*** YOU BLACK F***': racist.
 
-`You deserve way more subscribers. The shit you say is fucking gold.': neither.
+'You deserve way more subscribers. The s*** you say is f***ing gold.': neither.
 
-`Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With dicks and stuff.':
+'Every girl on this planet curses her mother for their birth. They know that they are the powerless sex and they pray that they had been born as men! With d***s and stuff.':
 \end{quote}
@@
 
-\hypertarget{result}{%
-\section{Result}\label{result}}
+\section{Result}\label{result}
 
-\hypertarget{zero-shot-learning-1}{%
-\subsection{Zero-shot learning}\label{zero-shot-learning-1}}
+\subsection{Zero-shot learning}\label{zero-shot-learning-1}
 
@@
 However, the overall ratio of matches and mismatches is 58:62.
-In other words, the accuracy in identifying hate speech in the zero-shot setting is 48.3 per cent.
+In other words, the accuracy in identifying hate speech in the zero-shot setting is 48 per cent.
 
-\begin{table}
-
-\caption{\label{tab:zeroshot}Classification of statements with zero-shot learning}
-\centering
-\begin{tabular}[t]{llr}
-\toprule
-Result & Category & Count\\
-\midrule
-Match & Racist & 23\\
-Match & Sexist & 35\\
-Mismatch & Racist & 37\\
-Mismatch & Sexist & 25\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\hypertarget{one-shot-learning-1}{%
-\subsection{One-shot learning}\label{one-shot-learning-1}}
+\subsection{One-shot learning}\label{one-shot-learning-1}
 
@@
 The overall ratio of matches and mismatches is 83:37.
-In other words, the accuracy of identifying hate speech in the one-shot setting is 69.2 per cent.
+In other words, the accuracy of identifying hate speech in the one-shot setting is 69 per cent.
 
-\begin{table}
-
-\caption{\label{tab:oneshot}Classification of statements with one-shot learning}
-\centering
-\begin{tabular}[t]{llr}
-\toprule
-Result & Category & Count\\
-\midrule
-Match & Racist & 46\\
-Match & Sexist & 37\\
-Mismatch & Racist & 14\\
-Mismatch & Sexist & 23\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\hypertarget{few-shot-learning-single-category}{%
-\subsection{Few-shot learning -- single category}\label{few-shot-learning-single-category}}
+\subsection{Few-shot learning -- single category}\label{few-shot-learning-single-category}
 
@@
 The general performance in the few-shot learning setting is similar to the performance in the one-shot learning setting.
-The overall ratio of matches and mismatches is 83:37, or around 69.2 per cent, however the composition is different, compared with the one-shot learning setting.
+The overall ratio of matches and mismatches is 83:37, or around 69 per cent, however the composition is different, compared with the one-shot learning setting.
 
-\begin{table}
-
-\caption{\label{tab:fewshotsingle}Classification of statements with single-category few-shot learning}
-\centering
-\begin{tabular}[t]{llr}
-\toprule
-Result & Category & Count\\
-\midrule
-Match & Racist & 41\\
-Match & Sexist & 42\\
-Mismatch & Racist & 19\\
-Mismatch & Sexist & 18\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\hypertarget{few-shot-learning-mixed-category}{%
-\subsection{Few-shot learning -- mixed category}\label{few-shot-learning-mixed-category}}
+\subsection{Few-shot learning -- mixed category}\label{few-shot-learning-mixed-category}
 
@@
 The example set that yields the worst results is Example Set 9, in which there are 137 matches and 103 mismatches.
-The accuracy rate with Example Set 9 is 57.1 per cent.
+The accuracy rate with Example Set 9 is 57 per cent.
 The difference between Example Sets 2 and 9 suggests that, although the models are provided with same number of examples, the content of the examples also affects how the model makes inferences.
 
-\begin{table}
-
-\caption{\label{tab:fewshotmixed}Classification of statements with mixed-category few-shot learning}
-\centering
-\begin{tabular}[t]{llr}
-\toprule
-Example Set & Result & Count\\
-\midrule
-1 & Match & 154\\
-1 & Mismatch & 86\\
-2 & Match & 180\\
-2 & Mismatch & 60\\
-3 & Match & 167\\
-3 & Mismatch & 73\\
-4 & Match & 157\\
-4 & Mismatch & 83\\
-5 & Match & 157\\
-5 & Mismatch & 83\\
-6 & Match & 173\\
-6 & Mismatch & 67\\
-7 & Match & 144\\
-7 & Mismatch & 96\\
-8 & Match & 155\\
-8 & Mismatch & 85\\
-9 & Match & 137\\
-9 & Mismatch & 103\\
-10 & Match & 174\\
-10 & Mismatch & 66\\
-\bottomrule
-\end{tabular}
-\end{table}
-
 The unique generated answers are listed in Table \ref{tab:fewshotmixedanswersnoinstruct}.
+These are the response of GPT-3 that we obtain when we ask the model to classify statements, but do not provide examples that would serve to limit the responses.
 Under the mixed-category setting, the model is observed to generate answers that are out of scope.
@@
 
-\begin{table}
-
-\caption{\label{tab:fewshotmixedanswersnoinstruct}Classifications generated by GPT-3 under mixed-category few-shot learning without instructions}
-\centering
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{40em}}
-\toprule
-racist | neither | homophobic | sexist | sexist, racist, | sexual assault | religious | sexual harassment | racist, sexist, | transphobic | hypocritical | I'm not a | I'm not brave | none of your business | I didn't | I'm not offended | you're not | sexual | I don't play | I don't care | I don't know | victim blaming | it's a question | irrelevant | I'm not crazy | creepy | romantic | I was taught to | I didn't say | ignorant | I'm not sure | I agree | not true | not even wrong | YouTube doesn't remove | socialist | conspiracy theorist | overpopulation | ableist | Islamophobic | conspiracy theory | hippie | sexist, rape ap | cliche | not even close to | nostalgic | I don't think | not a question | hippy | terrorist | hate speech | he was a terrorist | preachy | not a valid argument | not sexist | brave | Islamophobe | because you're a | troll | mental | never | pedophilia | mental illness is not | I'm sure you | I'm not going | not even close | grammar | rape apologist | cliché | vegan | sexist, misogynistic | I do | wrong | funny | question | when you were taught | opinion | emotional | conspiracy | nostalgia\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\hypertarget{few-shot-learning-mixed-category-with-instruction}{%
-\subsection{Few-shot learning -- mixed category with instruction}\label{few-shot-learning-mixed-category-with-instruction}}
+\subsection{Few-shot learning -- mixed category with instruction}\label{few-shot-learning-mixed-category-with-instruction}
 
@@
 The addition of an instruction successfully restricts the generated answers within the specified terms.
-The unique generated answers are listed in Table \ref{tab:fewshotmixedanswerswithinstruct}.
-
-\begin{table}
-
-\caption{\label{tab:fewshotmixedanswerswithinstruct}Classifications generated by GPT-3 under mixed-category few-shot learning with instructions}
-\centering
-\begin{tabular}[t]{l}
-\toprule
-Answer\\
-\midrule
-racist\\
-neither\\
-sexist\\
-\bottomrule
-\end{tabular}
-\end{table}
+The unique generated answers are: `racist', `neither', and `sexist'.
 
@@
 The addition of the instruction in the prompt increases the highest number of matches from 180 to 187; the highest accuracy rate is increased from 75 per cent to 78 per cent.
-In almost all cases the accuracy of the model increases (Figure \ref{fig:comparison})
+In almost all cases the accuracy of the model increases (Figure \ref{fig:comparison}).
+Across all the example sets, there are 1,785, or 74 per cent, matches and 615, or 26 per cent, mismatches.
 
-\begin{table}
+\section{Discussion}\label{discussion}
 
-\caption{\label{tab:fewshotmixedinstruct}Classification of statements with mixed-category few-shot learning, with instruction}
-\centering
-\begin{tabular}[t]{llr}
-\toprule
-Example Set & Result & Count\\
-\midrule
-1 & Match & 187\\
-1 & Mismatch & 53\\
-2 & Match & 184\\
-2 & Mismatch & 56\\
-3 & Match & 179\\
-3 & Mismatch & 61\\
-4 & Match & 185\\
-4 & Mismatch & 55\\
-5 & Match & 172\\
-5 & Mismatch & 68\\
-6 & Match & 170\\
-6 & Mismatch & 70\\
-7 & Match & 182\\
-7 & Mismatch & 58\\
-8 & Match & 174\\
-8 & Mismatch & 66\\
-9 & Match & 173\\
-9 & Mismatch & 67\\
-10 & Match & 179\\
-10 & Mismatch & 61\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{figure}
-\centering
-\includegraphics{paper_files/figure-latex/comparison-1.pdf}
-\caption{\label{fig:comparison}Comparing accurancy with and without an instruction}
-\end{figure}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 48.3 per cent.
-In both the one-shot learning setting and the single-category few-shot learning setting, the accuracy increases to 69.2 per cent.
-It is likely that the model is not suitable for use in hate speech detection in either the zero-shot learning or one-shot learning settings, as the accuracy rates are between 48.3 per cent and 69.2 per cent.
+In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 48 per cent.
+In both the one-shot learning setting and the single-category few-shot learning setting, the accuracy increases to 69 per cent.
+It is likely that the model is not suitable for use in hate speech detection in either the zero-shot learning or one-shot learning settings, as the accuracy rates are between 48.3 per cent and 69 per cent.
+\cite{davidson2017automated}, using a different model and approach, similarly find `that almost 40 per cent of hate speech is misclassified'.
+And when \cite{schick2021selfdiagnosis} use GPT-2 they find a similar ability to recognise sexually explicit content, however using an alternative model - Google's T5 \cite{raffel2020exploring} - they find better results.
 
 In the mixed-category few-shot setting, different example sets yield different accuracy rates.
-Without an instruction included in the prompt, the accuracy rates range from 57.1 per cent (Example Set 9) to 75 percent (Example Set 2).
+Without an instruction included in the prompt, the accuracy rates range from 57 per cent (Example Set 9) to 75 per cent (Example Set 2).
 Adding an instruction improves the performance, and the highest accuracy rate increases from 75 per cent (Example Set 2) to 78 per cent (Example Set 1).
@@
 Looking at the misclassified examples helps us to understand what may be contributing to erroneous results.
-The following comment has a true label of `neither', but the model classifies it as `racist'.
+The following comment has a true label of `racist', but the model classifies it as `sexist'.
 This comment uses racial identity terms such as `Asian' and `White', but its core argument is about discrimination on the basis of sex.
@@
 To shed light on why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content.
-The extent to which the identification and classification of hate speech can be explained is especially of interest for future work.
+The extent to which the identification and classification of hate speech can be explained is especially of interest for future work and is something that could be implemented on the publicly available GPT-2 from OpenAI or T5 from Google.
 
-\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                                          %%
+%% Backmatter begins here                   %%
+%%                                          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\appendix
+\begin{backmatter}
 
-\hypertarget{appendix}{%
-\section*{Appendix}\label{appendix}}
-\addcontentsline{toc}{section}{Appendix}
+\section*{Availability of data and materials}
+Code and data are available at: https://github.com/kelichiu/GPT3-hate-speech-detection.
 
-\begin{table}[H]
+\section*{Competing interests}
+  The authors declare that they have no competing interests.
 
-\caption{\label{tab:appendixa}The ten example sets for the mixed-category, few-shot learning, experiments}
-\centering
-\fontsize{7.5}{9.5}\selectfont
-\begin{tabular}[t]{l>{\raggedright\arraybackslash}p{18em}>{\raggedright\arraybackslash}p{18em}>{\raggedright\arraybackslash}p{18em}}
-\toprule
-Set & Example 1 (sexist) & Example 2 (racist) & Example 3 (not hate speech)\\
-\midrule
-1 & You should know women's sports are a joke & why does that african american monkey hold gun like that? & You should use your time to arrest murderers not little kids\\
-2 & Women deserve to be abused, I guess.
-& Why do negroes tear down their own neighborhoods when a black thug gets killed by law enforcement?
-Must be because of low IQ.
-& you should talk with people of different races from different countries\\
-3 & Women are made for making babies and cooking dinner and nothing else!!! & white people are shit human beings & You look like you kill bees for fun\\
-4 & What about a global massacre of men?
-Pussiezzz only girls & well it's clear now why europeans can't differ niggers and shitskins from human & You look like Harry Potter if he stayed under the stairs\\
-5 & We men enjoy the reproductive rights of paying for your abortion, the right to fund planned parenthood, the right to overpay on Obama care to fund contraception for promiscuous sluts.
-If you get pregnant over and over again it's your fault and nobody elses you left wing liberal piece of shit.
-Go be a whore.
-Keep spreading disease.
-Half of all black women have herpes.
-And we have the right to pay for it.
-You are outrageous.
-& We whites have higher IQ's than blacks, this is because IQ measures intelligence and we are the more evolved and superior race with a larger brain.
-& You look kinda dead inside, you parents must not haved loved you.\\
-6 & The men are turtles...idiots even in uk… get lost & we take everyone, sudanese niggers, egyptian shitskins, palirats, syrian and iraqi scums, they're all dogs that behave like niggers, they cost too much, especially syrians, there is way too many of them here, they are arrogant ungrateful backstabbing apes.
-& You have the grace and composure of a rabid hyena\\
-7 & That girl still need a good ass whooping, stupid ass bitch!! & U SUCK SHIT YOU BLACK FUCK & You deserve way more subscribers . The shit you say is fucking gold.\\
-8 & stone throwing must be legal when against women & This sick, disgusting, white terrorist/fascist killed more than 50 innocent people.
-& You can see the country is fertile and green.  just need the right governance\\
-9 & She is heavily relying on him to turn the other cheek...tough talking demon infested woman.
-& This is considered WHITE in Sweden.
-No wonder they accepted all those black and muslim immigrants.
-They are literally color blind.
-& you are a great brother to abbie, that family is changing the world!\\
-10 & Really, I hope she get raped in the future.
-Raping women should be legal I think & The world would be better without white people because they stole from the black Egyptians in the before christ ages they was poor we wasnt whites  ruins everything for black people/White people have pig dicks and no shape no hips or no booty they have to get plastic surgery as us blacks get it from our mother whites brought skin cancer to america so learn some facts before you try to run us out america when we was here before yall racist ass smelly crackers and dont say you will beat my ass because you cant and if you wanna find out drop your adress√∞¬ü¬Ü¬ó√Ø¬∏¬è√∞¬ü¬í¬Ø√∞¬ü¬ô¬Ç & You are a brave man.........for letting them keep the comments enabled\\
-\bottomrule
+\section*{Funding}
+There was no explcit funding provided for this research, but we gratefully acknowledge the in-kind support of Gillian Hadfield, the Schwartz Reisman Institute for Technology and Society, and OpenAI for providing access to GPT-3 under the academic access program.
+
+\section*{Author's contributions}
+  Chiu had the original idea, obtained and created the datasets, and wrote the first draft of the paper.
+Chiu and Alexander analysed and interpreted the data, contributed to writing the paper, and approved the final version.
+
+\section*{Acknowledgements}
+  We thank Amy Farrow, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions.
+Please note that we have added asterisks to racial slurs and other offensive content in this paper, however the inputs and outputs did not have these.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                  The Bibliography                       %%
+%%                                                         %%
+%%  Bmc_mathpys.bst  will be used to                       %%
+%%  create a .BBL file for submission.                     %%
+%%  After submission of the .TEX file,                     %%
+%%  you will be prompted to submit your .BBL file.         %%
+%%                                                         %%
+%%                                                         %%
+%%  Note that the displayed Bibliography will not          %%
+%%  necessarily be rendered by Latex exactly as specified  %%
+%%  in the online Instructions for Authors.                %%
+%%                                                         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% if your bibliography is in bibtex format, use those commands:
+\bibliographystyle{bmc-mathphys} % Style BST file (bmc-mathphys, vancouver, spbasic).
+\bibliography{bmc_article}      % Bibliography file (usually '*.bib' )
+% for author-year bibliography (bmc-mathphys or spbasic)
+% a) write to bib file (bmc-mathphys only)
+% @settings{label, options="nameyear"}
+% b) uncomment next line
+%\nocite{label}
+
+% or include bibliography directly:
+% \begin{thebibliography}
+% \bibitem{b1}
+% \end{thebibliography}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Figures                       %%
+%%                               %%
+%% NB: this is for captions and  %%
+%% Titles. All graphics must be  %%
+%% submitted separately and NOT  %%
+%% included in the Tex document  %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%
+%% Do not use \listoffigures as most will included as separate files
+
+\section*{Figures}
+
+\begin{figure}[h!]
+\caption{\label{fig:comparison}Comparing accuracy with and without an instruction}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Tables                        %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Use of \listoftables is discouraged.
+%%
+\section*{Tables}
+\begin{table}[h!]
+\caption{Sample table title. This is where the description of the table should go.}
+      \begin{tabular}{cccc}
+        \hline
+           & B1  &B2   & B3\\ \hline
+        A1 & 0.1 & 0.2 & 0.3\\
+        A2 & ... & ..  & .\\
+        A3 & ..  & .   & .\\ \hline
       \end{tabular}
@@
 
-\newpage
+\begin{table}
 
-\newpage
-\singlespacing 
-\renewcommand\refname{References}
-\bibliography{references.bib}
+\caption{\label{tab:zeroshot}Classification of statements with zero-shot learning}
+\centering
+\begin{tabular}[t]{llrr}
+Result & Category & Count & Percent\\
+\hline
+Match & Racist & 23 & 19\\
+Match & Sexist & 35 & 29\\
+Mismatch & Racist & 37 & 31\\
+Mismatch & Sexist & 25 & 21\\
+\hline
+\end{tabular}
+\end{table}
 
+\begin{table}
+
+\caption{\label{tab:oneshot}Classification of statements with one-shot learning}
+\centering
+\begin{tabular}[t]{llrr}
+Result & Category & Count & Percent\\
+\hline
+Match & Racist & 46 & 38\\
+Match & Sexist & 37 & 31\\
+Mismatch & Racist & 14 & 12\\
+Mismatch & Sexist & 23 & 19\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:fewshotsingle}Classification of statements with single-category few-shot learning}
+\centering
+\begin{tabular}[t]{llrr}
+Result & Category & Count & Percent\\
+\hline
+Match & Racist & 41 & 34\\
+Match & Sexist & 42 & 35\\
+Mismatch & Racist & 19 & 16\\
+Mismatch & Sexist & 18 & 15\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:fewshotmixed}Classification of statements with mixed-category few-shot learning}
+\centering
+\begin{tabular}[t]{lllr}
+Example Set & Result & Count & Percent\\
+\hline
+1 & Match & 154 & 64\\
+1 & Mismatch & 86 & 36\\
+2 & Match & 180 & 75\\
+2 & Mismatch & 60 & 25\\
+3 & Match & 167 & 70\\
+3 & Mismatch & 73 & 30\\
+4 & Match & 157 & 65\\
+4 & Mismatch & 83 & 35\\
+5 & Match & 157 & 65\\
+5 & Mismatch & 83 & 35\\
+6 & Match & 173 & 72\\
+6 & Mismatch & 67 & 28\\
+7 & Match & 144 & 60\\
+7 & Mismatch & 96 & 40\\
+8 & Match & 155 & 65\\
+8 & Mismatch & 85 & 35\\
+9 & Match & 137 & 57\\
+9 & Mismatch & 103 & 43\\
+10 & Match & 174 & 72\\
+10 & Mismatch & 66 & 28\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:fewshotmixedanswersnoinstruct}Classifications generated by GPT-3 under mixed-category few-shot learning without instructions}
+\centering
+\begin{tabular}[t]{l}
+\hline
+racist; neither; homophobic; sexist; sexist, racist,; sexual assault; \\
+religious; sexual harassment; racist, sexist,; transphobic; \\
+hypocritical; I'm not a; I'm not brave; none of your business; \\
+I didn't; I'm not offended; you're not; sexual; I don't play; \\
+I don't care; I don't know; victim blaming; it's a question; irrelevant; \\
+I'm not crazy; creepy; romantic; I was taught to; I didn't say; \\
+ignorant; I'm not sure; I agree; not true; not even wrong; \\
+YouTube doesn't remove; socialist; conspiracy theorist; \\
+overpopulation; ableist; Islamophobic; conspiracy theory; hippie; \\
+sexist, rape ap; cliche; not even close to; nostalgic; \\
+I don't think; not a question; hippy; terrorist; hate speech; \\
+he was a terrorist; preachy; not a valid argument; not sexist; brave; \\
+Islamophobe; because you're a; troll; mental; never; pedophilia; \\
+mental illness is not; I'm sure you; I'm not going; not even close; \\
+grammar; rape apologist; cliché; vegan; sexist, misogynistic; \\
+I do; wrong; funny; question; when you were taught; opinion; \\
+emotional; conspiracy; nostalgia \\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:fewshotmixedinstruct}Classification of statements with mixed-category few-shot learning, with instruction}
+\centering
+\begin{tabular}[t]{lllr}
+Example Set & Result & Count & Percent\\
+\hline
+1 & Match & 187 & 78\\
+1 & Mismatch & 53 & 22\\
+2 & Match & 184 & 77\\
+2 & Mismatch & 56 & 23\\
+3 & Match & 179 & 75\\
+3 & Mismatch & 61 & 25\\
+4 & Match & 185 & 77\\
+4 & Mismatch & 55 & 23\\
+5 & Match & 172 & 72\\
+5 & Mismatch & 68 & 28\\
+6 & Match & 170 & 71\\
+6 & Mismatch & 70 & 29\\
+7 & Match & 182 & 76\\
+7 & Mismatch & 58 & 24\\
+8 & Match & 174 & 72\\
+8 & Mismatch & 66 & 28\\
+9 & Match & 173 & 72\\
+9 & Mismatch & 67 & 28\\
+10 & Match & 179 & 75\\
+10 & Mismatch & 61 & 25\\
+\hline
+\end{tabular}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Additional Files              %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\end{backmatter}
 \end{document}

### 2022-03-15 outputs/documents/paper.Rmd
Tweaks throughout

--- 2022-02-28 outputs/documents/paper.Rmd
@@
 We gratefully acknowledge the support of Gillian Hadfield, the Schwartz Reisman Institute for Technology and Society, and OpenAI for providing access to GPT-3 under the academic access program.
-We thank Amy Farrow, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions.
+We thank two anonymous reviews and the editor, as well as Amy Farrow, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions.
 Please note that we have added asterisks to racial slurs and other offensive content in this paper, however the inputs and outputs did not have these.
@@
 - name: Ke-Li Chiu
+  affiliation: University of Toronto
+- name: Annie Collins
   affiliation: University of Toronto
@@
 We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning.
-We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an accuracy between 56.7 per cent and 68.3 per cent depending on the category of text and type of learning.
-With few-shot learning, the model's accuracy can be as high as 88.3 percent.
-We conclude that large language models have a role to play in hate speech detection, and that with further development language models could be used to counter hate speech and even self-police."
+We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an accuracy between 57 per cent and 68 per cent depending on the category of text and type of learning.
+With few-shot learning, the model's accuracy can be as high as 88 per cent.
+Large language models have a role to play in hate speech detection, and with further development could eventually be used to counter hate speech."
 keywords: "GPT-3; natural language processing; quantitative analysis; hate speech."
@@
 ---
+
 ```{r setup, include=FALSE}
 knitr::opts_chunk$set(tidy.opts=list(width.cutoff=80), echo = FALSE, warning = FALSE)
-# library(dplyr)
 library(tidyverse)
 library(kableExtra)
-# library(tidyr)
-# library(readr)
 ```
@@
 
-Natural language processing (NLP) models focus on using normal words, often written text, as their data.
-For instance, one might have content from a large number of books and want to group them into themes.
+Natural language processing (NLP) models use normal words, often written text, as their data.
+For instance, one might have content from many books and want to group them into themes.
 Sophisticated NLP models are being increasingly embedded in society.
 For instance, Google Search uses an NLP model called BERT to better understand what is meant by a word given its context.
-Some sophisticated natural language processing (NLP) models, such as OpenAI's Generative Pre-trained Transformer 3 (GPT-3), can additionally produce text as an output.
+Some sophisticated NLP models, such as OpenAI's Generative Pre-trained Transformer 3 (GPT-3), can additionally produce text as an output.
 
@@
 Large language models are trained on enormous datasets from various sources.
-This means that untruthful statements, human biases, and abusive language are inevitably included.
-Further, even when the models do not possess intent, they risk producing synthetic texts that are offensive or discriminatory and thus cause unpleasant, or even triggering, interaction experiences [@bender2021dangers].
+This means they usually contain untruthful statements, human biases, and abusive language.
+Further, even when the models do not possess intent, they risk producing text that is offensive or discriminatory, and thus cause unpleasant, or even triggering, interactions [@bender2021dangers].
 
@@
 For instance, hate speech commonly uses generalized language for targeting a group such as 'all' and 'every', and a model trained on these statements may generate similarly generalized and harmful statements.
-Finally, exposure refers to the relative attention, and hence considerations of importance, given to something.
-In the context of NLP this may be reflected in the emphasis on English-language created under particular circumstances, rather than another languages or circumstances that may be more prevalent.
-
-While these issues (among others) give us pause, the dual-use problem, which is that the same technology can be applied to both good and bad uses, provides motivation.
+Finally, exposure refers to the relative attention, and hence consideration of importance, given to something.
+In the context of NLP this may be reflected in the emphasis on English-language created under particular circumstances, rather than another language or circumstances that may be more prevalent.
+
+While these issues, among others, give us pause, the dual-use problem, which is that the same technology can be applied for both good and bad uses, provides motivation.
 For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text [@hovy2016social].
@@
 We show that this knowledge can be used to identify abusive language and even hate speech.
-In particular we consider 120 different extracts that have been categorized as 'racist', 'sexist', or 'neither' in the single-category settings (zero-shot, one-shot, and few-shot) and 243 different extracts in the mixed-category few-shot settings.
+We consider 120 different extracts that have been categorized as 'racist', 'sexist', or 'neither' in single-category settings (zero-shot, one-shot, and few-shot) and 243 different extracts in mixed-category few-shot settings.
 We ask GPT-3 to classify these based on zero-, one-, and few-shot learning, with and without instruction.
 We find that the model performs best with mixed-category few-shot learning.
-In that setting the model can accurately classify around 85.6 percent of the racist extracts and 88.3 percent of sexist extracts.
+In that setting the model can accurately classify around 86 per cent of the racist extracts and 88 per cent of sexist extracts.
 If language models can be used to identify abusive language, then not only is there potential for them to counter the production of abusive language by humans, but they could also potentially self-police.
@@
 The Transformer is a network architecture for neural networks that can be trained more quickly than many other approaches [@vaswani2017attention].
-Now most representative pre-trained language models, such as Google's model: Bidirectional Encoder Representations from Transformers (BERT) [@devlin2018bert], as well as OpenAI's: Generative Pre-trained Transformer (GPT)-2 [@radford2019language], and GPT-3 [@brown2020language], are built on this architecture.
+Now most representative pre-trained language models, such as Google's: Bidirectional Encoder Representations from Transformers (BERT) [@devlin2018bert], as well as OpenAI's: Generative Pre-trained Transformer (GPT)-2 [@radford2019language], and GPT-3 [@brown2020language], are built on this architecture.
 These models are widely used, for instance BERT is used by Google search.
@@
 GPT-3 is the third generation of the Generative Pre-trained Transformer models created by OpenAI, a private company in California that develops artificial intelligence models.
-GPT-3 is an autoregressive NLP model that can perform a variety of tasks, including responding to questions, summarizing and parsing text, translation, and classification.
+GPT-3 is an autoregressive NLP model that can perform a variety of tasks, including responding to questions, summarizing, and parsing text, translation, and classification.
 Interactions with the model involve inputting some text as a prompt and GPT-3 returning a text completion according to that prompt.
 
-Until January 11, when @fedus2021switch announced a Transformer model with a trillion parameters, GPT-3 was the largest, publicly-known, Transformer language model.
-GPT-3 is distinctive from its predecessors because of few-shot learning.
+GPT-3 is one of the largest, publicly available, Transformer language models.
+GPT-3 is distinctive to its predecessors because of few-shot learning.
 This means that GPT-3 can 'learn' to perform a new task based on only a few examples, expressed in natural language, instead of a fine-tuning process that can require a large amount of data.
@@
 
-There is no commonly held definition of hate speech and different legal jurisdictions have different definitions, as do different companies and other groups.
+There is no commonly held definition of hate speech.
+Different legal jurisdictions have different definitions, as do different companies and other groups.
 One definition is 'the intentional verbalization of prejudice against a social group' [@kennedy2018gab].
-Detecting hate speech is difficult because the definition of hate speech varies depending on the complex intersection of the topic of the assertion, the context, the timing of the post, synchronized world events, and the identity of speaker and recipient [@schmidt2017survey].
-Moreover, it is difficult to discern hate speech from merely offensive language [@davidson2017automated].
+Detecting hate speech is difficult because the definition of hate speech varies depending on a complex intersection of the topic of the assertion, the context, the timing of the post, synchronized world events, and the identity of speaker and recipient [@schmidt2017survey].
+Moreover, it is difficult to distinguish hate speech from offensive language [@davidson2017automated].
 Hate speech detection is of interest to academic researchers in a variety of domains including computer science [@addressinghatespeech] and sociology [@davidson2017automated].
@@
 For instance, @waseem2016hateful create a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation.
-The use Twitter data, and annotate 16,914 tweets: 3,383 as sexist, 1,972 as racist, and 11,559 as neither.
-They had a high degree of annotator agreement, and most of the disagreements were to do with sexism, and often explained by an annotator lacking apparent context.
-And, @davidson2017automated trains a classifier to distinguish between hate speech and offensive language.
-To define hate speech, they use online 'hate speech lexicon containing words and phrases identified by internet users as hate speech'.
-It is important to note that even these datasets have bias.
+They use Twitter data, and annotate 16,914 tweets: 3,383 as sexist, 1,972 as racist, and 11,559 as neither.
+They had a high degree of annotator agreement.
+Most of the disagreements were to do with sexism, and often explained by an annotator lacking apparent context.
+@davidson2017automated trains a classifier to distinguish between hate speech and offensive language.
+To define hate speech, they use an online 'hate speech lexicon containing words and phrases identified by internet users as hate speech'.
+Even these datasets have bias.
 For instance, @davidson2019racial found racial bias in five different sets of Twitter data annotated for hate speech and abusive language.
@@
 The classification is done by contributors to a crowd-sourcing platform.
-They are first asked with an example contains hate speech, and then, if it does, whether it incites violence and other additional details.
+They are first asked whether an example contains hate speech, and then, if it does, whether it incites violence and other additional details.
 The dataset has two variants: binary and multi-label.
 In the binary dataset comments are classified as hate or non-hate based.
-In the multi-label variant, the comments are evaluated on measures that include violence, gender, race, ability, religion, and sexual orientation.
-The examples provided in this paper are from the ETHOS dataset and hence contain typos, misspelling, and offensive content.
+In the multi-label variant comments are evaluated on measures that include violence, gender, race, ability, religion, and sexual orientation.
+The dataset that we use is from the ETHOS dataset and hence contain typos, misspelling, and offensive content.
 
 We use all of the 998 statements in the ETHOS dataset that have a binary classification of hate speech or not hate speech.
-Of these, the 433 statements that contain hate speech additionally have multiple labels that classify the content, for instance, does the comment have to do with violence, gender, race, nationality, disability, etc.
-We considered all of the 136 statements that contain race-based hate speech, and we focus on the 76 whose race-based score is at least 0.5.
-Similarly, we considered the all of 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
-To create a balanced dataset we select 120 of these statements to result in 60 sexist statements and 60 racist statements.
+Of these, the 433 statements that contain hate speech additionally have labels that classify the content.
+For instance, does the comment have to do with violence, gender, race, nationality, disability, etc.
+We considered all of the 136 statements that contain race-based hate speech, and we focus on the 76 whose race-based score is at least 0.5, meaning that at least 50 per cent of annotators agreed.
+Similarly, we considered all of the 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
+To create a balanced dataset, we select 120 of these statements to result in 60 sexist statements and 60 racist statements.
 For comparison purposes, we randomly draw 120 statements that are classified as not hate speech.
@@
 This division was kept consistent for zero-shot learning to allow for the same set of 120 comments to be classified by all three approaches.
-With the introduction of 10 static example sets for multi-category few-shot learning, 240 comments were classified for each example set.
+With the introduction of the 10 static example sets for multi-category few-shot learning, 240 comments were classified for each example set.
 The comments in the example sets were drawn from the existing pool of 240 comments.
@@
 
-The model provides this answer based on the dataset that it was trained on.
+Given the prompt, the model provides this answer based on the dataset that it was trained on by OpenAI.
+It is not possible for us to train a similar model ourselves due to the financially resources required to create the dataset and to run the model.
 
@@
 
-With one-shot learning, similarly to the zero-shot learning case, the model is asked to identify one passage of text in one category at a time.
+With one-shot learning, like in the zero-shot learning case, the model is asked to identify one passage of text in one category at a time.
 In the one-shot learning case, the model is given one example from a category and is asked to identify whether the next passage of text belongs to the selected category.
@@
 
-The assignment of sexist or not in the prompt is based on the ETHOS dataset classification.
-
-<!-- Is the description of how the example sets were selected too detailed here? -->
+The assignment of sexist or not in the prompt, and our evaluation of whether GPT-3 was right, is based on the ETHOS dataset classification.
 
@@
 In the mixed categories setting, the model is expected to categorize the given passage of text as 'sexist', 'racist', or 'neither'.
-To simplify the classification procedure and allow for comparisons between different example inputs, we created ten sets of examples against which 240 comments were classified each.
-We elected to use ten example sets to allow for some variation in results while keeping the number of groupings and size of the resulting data set reasonably small.
+To simplify the classification procedure and allow for comparisons between different example inputs, we created ten sets of examples against which 240 comments were each classified.
+We elected to use ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset tractable.
 The example sets each consist of one sexist, one racist, and one 'neither' comment and were created using the comments at indexes one through ten from each dataset.
 Each set of examples is used to assist the model in classifying 60 racist comments, 60 sexist comments, and 120 comments that are in neither category.
-The inputted comments were the first _n_ + 1 comments from their respective data sets with the _i_^th^ comment dropped corresponding to the use of example set _i_.
+The inputted comments were the first _n_ + 1 comments from their respective datasets with the _i_^th^ comment dropped corresponding to the use of example set _i_.
 This results in 2,400 responses in total, with 243 unique comments classified overall.
-The ten sets of examples are available in Table \@ref(tab:appendixa) in Appendix A.
+The ten sets of examples are shown in Appendix \@ref(appendxa).
 An example of this is:
@@
 Precision is the proportion of hate speech comments correctly classified out of all comments classified as hate speech (both correctly and incorrectly).
-Recall is the proportion of hate speech comments correctly classified out of all hate speech comments in the data set (both correctly and incorrectly classified).
+Recall is the proportion of hate speech comments correctly classified out of all hate speech comments in the dataset (both correctly and incorrectly classified).
 The F1 score is the harmonic mean of precision and recall.
-In the case of hate speech classification it is desirable to have a model with high recall, meaning a model that can identify a relatively high proportion of the hate speech text within a data set.
-However, the F1 score can provide a more well-rounded metric for model performance and comparison.
+In the case of hate speech classification, it is better to have a model with high recall, meaning a model that can identify a relatively high proportion of the hate speech text within a dataset.
+But the F1 score can provide a more well-rounded metric for model performance and comparison.
 
@@
 
-The results of the zero-shot experiments are presented in Tables \@ref(tab:zeroshot-racism), \@ref(tab:zeroshot-sexism), \@ref(tab:zeroshot-hate), and \@ref(tab:zeroshot-summary).
+The overall results of the zero-shot experiments are presented in Table \@ref(tab:zeroshot-summary).
+Tables \@ref(tab:zeroshot-racism), \@ref(tab:zeroshot-sexism), and \@ref(tab:zeroshot-hate), in Appendix \@ref(appendixbzeroshot) contain additional detail.
 The model has 34 matches (true positives and negatives) and 26 mismatches (false positives and negatives) in the sexist category, and 41 matches and 19 mismatches in the racist category.
-The model performs more accurately when identifying racist comments, with an accuracy of 68.3 percent, compared with identifying sexist comments, with an accuracy of 56.7 percent, however the F1 score for each type of hate speech is approximately the same.
+The model performs more accurately when identifying racist comments, with an accuracy of 68 per cent, compared with identifying sexist comments, with an accuracy of 57 per cent, however the F1 score for each type of hate speech is approximately the same.
 The overall ratio of matches and mismatches is 75:45.
-In other words, the accuracy in identifying hate speech in the zero-shot setting is 62.5 per cent.
-The model has an F1 score of 80.5 percent in this setting, with a notably high recall of 86.7 percent as well.
-
-<!-- ```{r zeroshot} -->
-<!-- zero_shot_result <- read_csv(here::here("outputs/data/zero_shot_results.csv"), show_col_types = FALSE) -->
-
-<!-- zero_shot_result_match <-  -->
-<!--   zero_shot_result %>% -->
-<!--   filter(temperature == 0) %>% -->
-<!--   select(category, label, answer, temperature) %>% -->
-<!--   mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>% -->
-<!--   mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>% -->
-<!--   mutate(result = case_when(answer_yn==label_yn ~ "Match", -->
-<!--                             answer_yn!=label_yn ~ "Mismatch" -->
-<!--                             )) %>% -->
-<!--   group_by(result, category) %>% -->
-<!--   summarise(result_cnt = n(), .groups="drop") %>%  -->
-<!--   mutate(category = case_when(category == "racist" ~ "Racist", -->
-<!--                               category == "sexist" ~ "Sexist" -->
-<!--                               )) %>% -->
-<!--   mutate(Percent = result_cnt / sum(result_cnt) * 100, -->
-<!--          Percent = round(Percent)) %>% -->
-<!--   rename(Result = result, -->
-<!--          Category = category, -->
-<!--          Count = result_cnt) -->
-
-<!-- zero_shot_result_match %>%  -->
-<!--   knitr::kable(caption = "Classification of statements with zero-shot learning", -->
-<!--                booktabs = TRUE) -->
-<!-- ``` -->
-
-```{r zeroshot-racism, message=FALSE}
-zero_shot_result <- read_csv(here::here("outputs/data/zero_shot_results.csv"), show_col_types = FALSE)
+In other words, the accuracy in identifying hate speech in the zero-shot setting is 63 per cent.
+The model has an F1 score of 81 per cent in this setting, with a notably high recall of 87 per cent as well.
+
+```{r zeroshot-summary, message = FALSE}
+# Set-up data for zero-shot racism
+zero_shot_result <-
+  read_csv(here::here("outputs/data/zero_shot_results.csv"),
+           show_col_types = FALSE)
 
@@
   count(label_yn, answer_yn) %>%
-  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  pivot_wider(names_from = answer_yn,
+              values_from = n,
+              values_fill = 0) %>%
   mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
                               label_yn == "Y" ~ "Racist")) %>%
-  rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
-
-zero_shot_result_racism <- zero_shot_result_racism[, c("Actual classification", "Not racist", "Racist")]
-
-zero_shot_result_racism %>%
-  knitr::kable(caption = "Classification of racist statements with zero-shot learning",
-               booktabs = TRUE) %>%
-  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
-
-```
-
-```{r zeroshot-sexism}
+  rename(
+    "Actual classification" = label_yn,
+    "Not racist" = N,
+    "Racist" = Y
+  )
+
+zero_shot_result_racism <-
+  zero_shot_result_racism[, c("Actual classification", "Not racist", "Racist")]
+
+# Set-up data for sexism
 zero_shot_result_sexism <-
@@
   count(label_yn, answer_yn) %>%
-  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  pivot_wider(names_from = answer_yn,
+              values_from = n,
+              values_fill = 0) %>%
   mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
                               label_yn == "Y" ~ "Sexist")) %>%
-  rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
-
-zero_shot_result_sexism <- zero_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]
-
-zero_shot_result_sexism %>%
-  knitr::kable(caption = "Classification of sexist statements with zero-shot learning",
-               booktabs = TRUE) %>%
-  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
-```
-
-```{r zeroshot-hate}
+  rename(
+    "Actual classification" = label_yn,
+    "Not sexist" = N,
+    "Sexist" = Y
+  )
+
+zero_shot_result_sexism <-
+  zero_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]
+
+# Set-up data for hate speech
 zero_shot_result_hate <-
@@
   count(label_yn, answer_yn) %>%
-  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  pivot_wider(names_from = answer_yn,
+              values_from = n,
+              values_fill = 0) %>%
   mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
                               label_yn == "Y" ~ "Hate speech")) %>%
-  rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
-
-zero_shot_result_hate <- zero_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
-
-zero_shot_result_hate %>%
-  knitr::kable(caption = "Classification of hate speech with zero-shot learning",
-               booktabs = TRUE) %>%
-  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
-```
-
-```{r zeroshot-summary}
+  rename(
+    "Actual classification" = label_yn,
+    "Not hate speech" = N,
+    "Hate speech" = Y
+  )
+
+zero_shot_result_hate <-
+  zero_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
+
+# Pull it all together
 tp_r <- zero_shot_result_racism[2, 3] %>% as.numeric()
@@
 
-zero_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
-zero_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
-zero_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
-zero_racism_f1 <- ((2*zero_racism_precision*zero_racism_recall)/(zero_racism_precision + zero_racism_recall)) %>% round(2)
-zero_racism_all <- c(zero_racism_accuracy, zero_racism_precision, zero_racism_recall, zero_racism_f1)
-
-zero_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
-zero_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
-zero_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
-zero_sexism_f1 <- ((2*zero_sexism_precision*zero_sexism_recall)/(zero_sexism_precision + zero_sexism_recall)) %>% round(2)
-zero_sexism_all <- c(zero_sexism_accuracy, zero_sexism_precision, zero_sexism_recall, zero_sexism_f1)
-
-zero_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
-zero_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
-zero_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
-zero_hate_f1 <- ((2*zero_hate_precision*zero_sexism_recall)/(zero_hate_precision + zero_hate_recall)) %>% round(2)
-zero_hate_all <- c(zero_hate_accuracy, zero_hate_precision, zero_hate_recall, zero_hate_f1)
-
-zero_shot_summary <- tibble(Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)), 
-                                   Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
-                                   Percent = c(zero_racism_all, zero_sexism_all, zero_hate_all)) %>%
+zero_racism_accuracy <-
+  ((tp_r + tn_r) / (tp_r + tn_r + fp_r + fn_r)) %>% round(4) * 100
+zero_racism_precision <- (tp_r / (tp_r + fp_r)) %>% round(4) * 100
+zero_racism_recall <- (tp_r / (tp_r + fn_r)) %>% round(4) * 100
+zero_racism_f1 <-
+  ((2 * zero_racism_precision * zero_racism_recall) / (zero_racism_precision + zero_racism_recall)
+  ) %>% round(2)
+zero_racism_all <-
+  c(zero_racism_accuracy,
+    zero_racism_precision,
+    zero_racism_recall,
+    zero_racism_f1)
+
+zero_sexism_accuracy <-
+  ((tp_s + tn_s) / (tp_s + tn_s + fp_s + fn_s)) %>% round(4) * 100
+zero_sexism_precision <- (tp_s / (tp_s + fp_s)) %>% round(4) * 100
+zero_sexism_recall <- (tp_s / (tp_s + fn_s)) %>% round(4) * 100
+zero_sexism_f1 <-
+  ((2 * zero_sexism_precision * zero_sexism_recall) / (zero_sexism_precision + zero_sexism_recall)
+  ) %>% round(2)
+zero_sexism_all <-
+  c(zero_sexism_accuracy,
+    zero_sexism_precision,
+    zero_sexism_recall,
+    zero_sexism_f1)
+
+zero_hate_accuracy <-
+  ((tp_h + tn_h) / (tp_h + tn_h + fp_h + fn_h)) %>% round(4) * 100
+zero_hate_precision <- (tp_h / (tp_h + fp_h)) %>% round(4) * 100
+zero_hate_recall <- (tp_h / (tp_h + fn_h)) %>% round(4) * 100
+zero_hate_f1 <-
+  ((2 * zero_hate_precision * zero_sexism_recall) / (zero_hate_precision + zero_hate_recall)
+  ) %>% round(2)
+zero_hate_all <-
+  c(zero_hate_accuracy,
+    zero_hate_precision,
+    zero_hate_recall,
+    zero_hate_f1)
+
+zero_shot_summary <-
+  tibble(
+    Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)),
+    Metric = rep(c("Accuracy (%)", "Precision (%)", "Recall (%)", "F1 (%)"), 3),
+    Percent = c(zero_racism_all, zero_sexism_all, zero_hate_all)
+  ) %>%
   pivot_wider(names_from = Metric, values_from = Percent)
@@
 zero_shot_summary %>%
-  # select(!Category) %>%
-  knitr::kable(caption="Performance of zero-shot learning in hate speech classification",
-              # col.names=c(""=1),
-               booktabs=TRUE) # %>%
-  # kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
+  knitr::kable(caption = "Performance of zero-shot learning in hate speech classification",
+               booktabs = TRUE,
+               digits = 0
+               )
 ```
@@
 
-The results of the one-shot learning experiments are presented in Tables \@ref(tab:oneshot-racism), \@ref(tab:oneshot-sexism), \@ref(tab:oneshot-hate), and \@ref(tab:oneshot-summary).
+The results of the one-shot learning experiments are presented in Table \@ref(tab:oneshot-summary).
+Tables \@ref(tab:oneshot-racism), \@ref(tab:oneshot-sexism), and \@ref(tab:oneshot-hate), in Appendix \@ref(appendixboneshot) provide additional detail.
 The model has 37 matches and 23 mismatches in the racist category, and 36 matches and 24 mismatches in the sexist category.
@@
 The overall ratio of matches and mismatches is 73:47.
-In other words, the accuracy of identifying hate speech in the one-shot setting is 60.8 per cent.
+In other words, the accuracy of identifying hate speech in the one-shot setting is 61 per cent.
 The general performance in the one-shot setting is worse than in the zero-shot setting, with lower accuracy, recall, precision, and F1 score overall.
 
-<!-- ```{r oneshot} -->
-<!-- one_shot_result <- read.csv(here::here("outputs/data/one_shot_results.csv")) -->
-
-<!-- one_shot_result <-  -->
-<!--   one_shot_result %>% -->
-<!--   filter(temperature == 0) %>% -->
-<!--   select(category, label, answer) %>% -->
-<!--   mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>% -->
-<!--   mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>% -->
-<!--   mutate(result = case_when(answer_yn==label_yn ~ "Match", -->
-<!--                             answer_yn!=label_yn ~ "Mismatch" -->
-<!--                             )) %>% -->
-<!--   group_by(result, category) %>% -->
-<!--   summarise(result_cnt = n(), .groups = "drop") %>%  -->
-<!--   mutate(category = case_when(category == "racist" ~ "Racist", -->
-<!--                               category == "sexist" ~ "Sexist" -->
-<!--                               )) %>% -->
-<!--   mutate(Percent = result_cnt / sum(result_cnt) * 100, -->
-<!--          Percent = round(Percent)) %>% -->
-<!--   rename(Result = result, -->
-<!--          Category = category, -->
-<!--          Count = result_cnt) -->
-
-<!-- one_shot_result %>%  -->
-<!--   knitr::kable(caption = "Classification of statements with one-shot learning",  -->
-<!--              booktabs = TRUE) -->
-<!-- ``` -->
-
-```{r oneshot-racism}
-one_shot_result <- read.csv(here::here("outputs/data/one_shot_results.csv"))
+```{r oneshot-summary}
+# Set-up racism
+one_shot_result <-
+  read.csv(here::here("outputs/data/one_shot_results.csv"))
 
@@
   count(label_yn, answer_yn) %>%
-  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  pivot_wider(names_from = answer_yn,
+              values_from = n,
+              values_fill = 0) %>%
   mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
                               label_yn == "Y" ~ "Racist")) %>%
-  rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
-
-one_shot_result_racism <- one_shot_result_racism[, c("Actual classification", "Not racist", "Racist")]
-
-one_shot_result_racism %>%
-  knitr::kable(caption = "Classification of racist statements with one-shot learning",
-               booktabs = TRUE) %>%
-  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
-
-```
-
-```{r oneshot-sexism}
+  rename(
+    "Actual classification" = label_yn,
+    "Not racist" = N,
+    "Racist" = Y
+  )
+
+one_shot_result_racism <-
+  one_shot_result_racism[, c("Actual classification", "Not racist", "Racist")]
+
+# Set-up sexism
 one_shot_result_sexism <-
@@
   count(label_yn, answer_yn) %>%
-  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  pivot_wider(names_from = answer_yn,
+              values_from = n,
+              values_fill = 0) %>%
   mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
                               label_yn == "Y" ~ "Sexist")) %>%
-  rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
-
-one_shot_result_sexism <- one_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]
-
-one_shot_result_sexism %>%
-  knitr::kable(caption = "Classification of sexist statements with one-shot learning",
-               booktabs = TRUE) %>%
-  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
-```
-
-```{r oneshot-hate}
+  rename(
+    "Actual classification" = label_yn,
+    "Not sexist" = N,
+    "Sexist" = Y
+  )
+
+one_shot_result_sexism <-
+  one_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]
+
+# Set-up hate
 one_shot_result_hate <-
@@
   count(label_yn, answer_yn) %>%
-  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+  pivot_wider(names_from = answer_yn,
+              values_from = n,
+              values_fill = 0) %>%
   mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
                               label_yn == "Y" ~ "Hate speech")) %>%
-  rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
-
-one_shot_result_hate <- one_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
-
-one_shot_result_hate %>%
-  knitr::kable(caption = "Classification of hate speech with one-shot learning",
-               booktabs = TRUE) %>%
-  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
-```
-
-```{r oneshot-summary}
+  rename(
+    "Actual classification" = label_yn,
+    "Not hate speech" = N,
+    "Hate speech" = Y
+  )
+
+one_shot_result_hate <-
+  one_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
+
+# Put it all together
 tp_r <- one_shot_result_racism[2, 3] %>% as.numeric()
@@
 
-one_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
-one_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
-one_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
-one_racism_f1 <- ((2*one_racism_precision*one_racism_recall)/(one_racism_precision + one_racism_recall)) %>% round(2)
-one_racism_all <- c(one_racism_accuracy, one_racism_precision, one_racism_recall, one_racism_f1)
-
-one_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
-one_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
-one_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
-one_sexism_f1 <- ((2*one_sexism_precision*one_sexism_recall)/(one_sexism_precision + one_sexism_recall)) %>% round(2)
-one_sexism_all <- c(one_sexism_accuracy, one_sexism_precision, one_sexism_recall, one_sexism_f1)
-
-one_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
-one_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
-one_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
-one_hate_f1 <- ((2*one_hate_precision*one_sexism_recall)/(one_hate_precision + one_hate_recall)) %>% round(2)
-one_hate_all <- c(one_hate_accuracy, one_hate_precision, one_hate_recall, one_hate_f1)
-
-one_shot_summary <- tibble(Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)), 
-                                   Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
-                                   Percent = c(one_racism_all, one_sexism_all, one_hate_all)) %>%
+one_racism_accuracy <-
+  ((tp_r + tn_r) / (tp_r + tn_r + fp_r + fn_r)) %>% round(4) * 100
+one_racism_precision <- (tp_r / (tp_r + fp_r)) %>% round(4) * 100
+one_racism_recall <- (tp_r / (tp_r + fn_r)) %>% round(4) * 100
+one_racism_f1 <-
+  ((2 * one_racism_precision * one_racism_recall) / (one_racism_precision + one_racism_recall)
+  ) %>% round(2)
+one_racism_all <-
+  c(one_racism_accuracy,
+    one_racism_precision,
+    one_racism_recall,
+    one_racism_f1)
+
+one_sexism_accuracy <-
+  ((tp_s + tn_s) / (tp_s + tn_s + fp_s + fn_s)) %>% round(4) * 100
+one_sexism_precision <- (tp_s / (tp_s + fp_s)) %>% round(4) * 100
+one_sexism_recall <- (tp_s / (tp_s + fn_s)) %>% round(4) * 100
+one_sexism_f1 <-
+  ((2 * one_sexism_precision * one_sexism_recall) / (one_sexism_precision + one_sexism_recall)
+  ) %>% round(2)
+one_sexism_all <-
+  c(one_sexism_accuracy,
+    one_sexism_precision,
+    one_sexism_recall,
+    one_sexism_f1)
+
+one_hate_accuracy <-
+  ((tp_h + tn_h) / (tp_h + tn_h + fp_h + fn_h)) %>% round(4) * 100
+one_hate_precision <- (tp_h / (tp_h + fp_h)) %>% round(4) * 100
+one_hate_recall <- (tp_h / (tp_h + fn_h)) %>% round(4) * 100
+one_hate_f1 <-
+  ((2 * one_hate_precision * one_sexism_recall) / (one_hate_precision + one_hate_recall)) %>% round(2)
+one_hate_all <-
+  c(one_hate_accuracy,
+    one_hate_precision,
+    one_hate_recall,
+    one_hate_f1)
+
+one_shot_summary <-
+  tibble(
+    Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)),
+    Metric = rep(c("Accuracy (%)", "Precision (%)", "Recall (%)", "F1 (%)"), 3),
+    Percent = c(one_racism_all, one_sexism_all, one_hate_all)
+  ) %>%
   pivot_wider(names_from = Metric, values_from = Percent)
@@
 one_shot_summary %>%
-  # select(!Category) %>%
-  knitr::kable(caption="Performance of one-shot learning in hate speech classification",
-               # col.names=c("", "Percent"),
-               booktabs=TRUE) # %>%
-  # kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
+  knitr::kable(caption = "Performance of one-shot learning in hate speech classification",
+               digits = 0,
+               booktabs = TRUE)
 ```
@@
 
-The results of the single-category, few-shot learning, experiments are presented in Tables \@ref(tab:fewshotsingle-racism), \@ref(tab:fewshotsingle-sexism), \@ref(tab:fewshotsingle-hate), and \@ref(tab:fewshotsingle-summary).
+The results of the single-category, few-shot learning, experiments are presented in Table \@ref(tab:fewshotsingle-summary).
+Tables \@ref(tab:fewshotsingle-racism), \@ref(tab:fewshotsingle-sexism), \@ref(tab:fewshotsingle-hate), in Appendix \@ref(appendixbfewshotsingle) provide additional detail.
 The model has 41 matches and 19 mismatches in the racist category, and 42 matches and 18 mismatches in the sexist category.
-Similar to the one-shot setting, the model performs almost equally well at identifying racist comments compared with identifying sexist comments.
-The general performance in the single-category few-shot learning setting is slightly more accurate than performance in other settings, with an accuracy of 69.2 percent compared with 60.8 percent in the one-shot setting and 62.5 percent in the zero-shot setting.
-However, the model in this context has the lowest F1 score of the settings considered thus far at 60.5 percent.
-
-<!-- ```{r fewshotsingle} -->
-<!-- few_shot_single_result <- read.csv(here::here("outputs/data/few_shot_single_results.csv")) -->
-
-<!-- few_shot_single_result <-  -->
-<!--   few_shot_single_result %>% -->
-<!--   filter(temperature == 0) %>% -->
-<!--   select(category, label, answer) %>% -->
-<!--   mutate(label_yn = ifelse(grepl("not", label), "No", "Yes")) %>% -->
-<!--   mutate(answer_yn = ifelse(grepl("not", answer), "No", "Yes")) %>% -->
-<!--   mutate(result = case_when(answer_yn==label_yn ~ "Match", -->
-<!--                             answer_yn!=label_yn ~ "Mismatch" -->
-<!--                             )) %>% -->
-<!--   mutate(result_with_cat = case_when(answer_yn==label_yn & answer_yn == "Yes" ~ "True Positive", -->
-<!--                                      answer_yn==label_yn & answer_yn == "No"  ~ "True Negative", -->
-<!--                                      answer_yn!=label_yn & answer_yn == "Yes" ~ "False Positive", -->
-<!--                                      answer_yn!=label_yn & answer_yn == "No"  ~ "False Negative" -->
-<!--                                      )) %>% -->
-<!--   group_by(result, category) %>% -->
-<!--   summarise(result_cnt = n(), .groups = "drop") %>%  -->
-<!--   mutate(category = case_when(category == "racist" ~ "Racist", -->
-<!--                               category == "sexist" ~ "Sexist" -->
-<!--                               )) %>% -->
-<!--   mutate(Percent = result_cnt / sum(result_cnt) * 100, -->
-<!--          Percent = round(Percent)) %>% -->
-<!--   rename(Result = result, -->
-<!--          Category = category, -->
-<!--          Count = result_cnt) -->
-
-<!-- few_shot_single_result %>%  -->
-<!--   knitr::kable( -->
-<!--     caption = "Classification of statements with single-category few-shot learning",  -->
-<!--     booktabs = TRUE) -->
-<!-- ``` -->
-
-```{r fewshotsingle-racism}
+Like the one-shot setting, the model performs almost equally well at identifying racist comments compared with identifying sexist comments.
+The general performance in the single-category few-shot learning setting is slightly more accurate than performance in other settings, with an accuracy of 69 per cent compared with 61 per cent in the one-shot setting and 63 per cent in the zero-shot setting.
+However, the model in this context has the lowest F1 score of the settings considered thus far at 61 per cent.
+
+```{r fewshotsingle-summary}
+# Racism
 few_shot_single_result <- read.csv(here::here("outputs/data/few_shot_single_results.csv"))
@@
 
-few_shot_result_racism %>%
-  knitr::kable(caption = "Classification of racist statements with single-category few-shot learning",
-               booktabs = TRUE) %>%
-  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
-```
-
-```{r fewshotsingle-sexism}
+# Sexism
 few_shot_result_sexism <- 
@@
 
-few_shot_result_sexism %>%
-  knitr::kable(caption = "Classification of sexist statements with single-category few-shot learning",
-               booktabs = TRUE) %>%
-  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
-```
-
-```{r fewshotsingle-hate}
+# Hate speech
 few_shot_result_hate <- 
@@
 
-few_shot_result_hate %>%
-  knitr::kable(caption = "Classification of hate speech with single-category few-shot learning",
-               booktabs = TRUE) %>%
-  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2))
-```
-
-```{r fewshotsingle-summary}
+# Bringing it all together
 tp_r <- few_shot_result_racism[2, 3] %>% as.numeric()
@@
 few_shot_summary <- tibble(Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)), 
-                                   Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
+                                   Metric = rep(c("Accuracy (%)", "Precision (%)", "Recall (%)", "F1 (%)"), 3), 
                                    Percent = c(few_racism_all, few_sexism_all, few_hate_all)) %>%
@@
 few_shot_summary %>%
-  # select(!Category) %>%
   knitr::kable(caption="Performance of single-category few-shot learning in hate speech classification",
-               # col.names=c("", "Percent"),
-               booktabs=TRUE) # %>%
- # kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
+               digits = 0,
+               booktabs=TRUE) 
 ```
@@
 
-The results of the mixed-category few-shot experiments are presented in Table \@ref(tab:fewshotmixed-racism), Table \@ref(tab:fewshotmixed-sexism), and Table \@ref(tab:fewshotmixed-summary).
-
-Among the ten sets of examples, Example Set 1 yields the best performance in terms of accuracy (90.6 percent) and F1 score (86.6 percent) for racist comments and Example Set 10 yields the best performance by the same metrics for sexist comments (accuracy of 89.44 percent, F1 score of 84.6 percent).
-The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 69.9 percent (and the lowest accuracy at 72.8 percent) for this dataset.
-The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 68.5 percent (and the lowest accuracy at 73.9 percent) for this dataset.
+The results of the mixed-category few-shot experiments are presented in Table \@ref(tab:fewshotmixed-summary).
+Tables \@ref(tab:fewshotmixed-racism) and Table \@ref(tab:fewshotmixed-sexism) in Appendix \@ref(appendxbmuxedubsnorinstruction) provide additional detail.
+Among the ten sets of examples, Example Set 1 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments and Example Set 10 yields the best performance by the same metrics for sexist comments (accuracy of 89 per cent, F1 score of 85 per cent).
+The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 70 per cent (and the lowest accuracy at 73 per cent) for this dataset.
+The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 74 per cent) for this dataset.
 The differences between Example Sets 1, 8, 9, and 10 suggest that, although the models are provided with same number of examples, the content of the examples also affects how the model makes inferences.
 Overall, the mixed-category few-shot setting performs approximately the same at identifying sexist text and racist text.
-It is also performs with higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
-
-<!-- ```{r fewshotmixed} -->
-<!-- few_shot_mixed_result <- -->
-<!--   read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv")) -->
-
-<!-- few_shot_mixed_result <- -->
-<!--   few_shot_mixed_result %>% -->
-<!--   filter(temperature == 0) %>% -->
-<!--   select(category, label, answer, example_set) %>% -->
-<!--   mutate(example_set = example_set + 1) %>% -->
-<!--   mutate(result = ifelse(trimws(label) == trimws(answer), "Match", "Mismatch")) %>% -->
-<!--   mutate( -->
-<!--     label = case_when( -->
-<!--       label == "racist" ~ "Racist", -->
-<!--       label == "sexist" ~ "Sexist", -->
-<!--       label == "neither" ~ "Neither" -->
-<!--     ) -->
-<!--   ) %>% -->
-<!--   group_by(example_set, result) %>% #, label) %>% -->
-<!--   summarise(result_cnt = n(), .groups = "drop") %>% -->
-<!--   ungroup() %>% -->
-<!--   group_by(example_set) %>% -->
-<!--   mutate(Percent = result_cnt / sum(result_cnt) * 100, -->
-<!--          Percent = round(Percent)) %>% -->
-<!--   rename(Result = result, -->
-<!--          "Example Set" = example_set, -->
-<!--          Count = result_cnt) -->
-
-<!-- knitr::kable( -->
-<!--   few_shot_mixed_result, -->
-<!--   caption = "Classification of statements with mixed-category few-shot learning", -->
-<!--   booktabs = TRUE, -->
-<!--   linesep = "", -->
-<!--   align = 'lllr' -->
-<!-- ) -->
-<!-- ``` -->
-
-```{r fewshotmixed-racism}
+It is also has higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
+
+```{r fewshotmixed-summary}
+# Racism
 few_shot_mixed_result <-
@@
 
-table <- few_shot_mixed_result_racism %>% 
+tablefewshowmixedracism <- few_shot_mixed_result_racism %>% 
   # select(!example_set) %>%
@@
 
-knitr::kable(table,
-             caption = "Classification of racist statements with mixed-category few-shot learning",
-             booktabs = TRUE,
-             linesep="") %>%
-  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2))  %>%
-  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
-```
-
-```{r fewshotmixed-sexism}
+# Sexism
 # Example sets
@@
 
-table <- few_shot_mixed_result_sexism %>% 
+tablefewshotmixedsexism <- few_shot_mixed_result_sexism %>% 
   # select(!example_set) %>%
@@
 
-knitr::kable(table,
-             caption = "Classification of sexist statements with mixed-category few-shot learning",
-             booktabs = TRUE,
-             linesep="") %>%
-  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2))  %>%
-  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
-  # kableExtra::pack_rows(index=c("Example set 1"=2, 
-  #                               "Example set 2"=2, 
-  #                               "Example set 3"=2, 
-  #                               "Example set 4"=2, 
-  #                               "Example set 5"=2, 
-  #                               "Example set 6"=2,
-  #                               "Example set 7"=2,
-  #                               "Example set 8"=2,
-  #                               "Example set 9"=2,
-  #                               "Example set 10"=2,
-  #                               "Overall"=2))
-```
-
-```{r fewshotmixed-summary}
+# Summary
 few_shot_mixed_result_racism_overall <- few_shot_mixed_result_racism_overall %>% mutate(example_set = 11, .before="Actual classification")
@@
 table <- all_summary %>%
-  # select(example_set, Metric, Percent) %>% 
   mutate(example_set = as.character(example_set),
@@
              caption="Performance of mixed-category few-shot learning in text classification",
-               # col.names=c("", "Percent"),
+             col.names = c("Example set", "Category", "Accuracy (%)", "Precision (%)", "Recall (%)", "F1 (%)"),
+             digits = 0,
              booktabs=TRUE,
@@
   kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
-
-# knitr::kable(list(table[1:24, 1:3],
-#                   matrix(numeric(), nrow=0, ncol=3),
-#                   table[25:44, 1:3]),
-#              caption="Performance of mixed-category few-shot learning in racist text classification",
-#                # col.names=c("", "Percent"),
-#              booktabs=TRUE,
-#              linesep = "")
-  # kableExtra::pack_rows(index=c("Example set 1"=4,
-  #                               "Example set 2"=4,
-  #                               "Example set 3"=4,
-  #                               "Example set 4"=4,
-  #                               "Example set 5"=4,
-  #                               "Example set 6"=4,
-  #                               "Example set 7"=4,
-  #                               "Example set 8"=4,
-  #                               "Example set 9"=4,
-  #                               "Example set 10"=4,
-  #                               "Overall"=4))
-```
-
-<!-- ```{r fewshotmixed-summary-sexism} -->
-<!-- few_shot_mixed_result_sexism_overall <- few_shot_mixed_result_sexism_overall %>% mutate(example_set = 11, .before="Actual classification") -->
-<!-- all_results <- rbind(few_shot_mixed_result_sexism, few_shot_mixed_result_sexism_overall) -->
-<!-- all_summary <- tibble() -->
-<!-- for (i in 1:11){ -->
-<!--   example_i_sexism <- all_results %>% filter(example_set == i) %>% select(!example_set) -->
-
-<!--   tp_s <- example_i_sexism[2, 3] %>% as.numeric() -->
-<!--   tn_s <- example_i_sexism[1, 2] %>% as.numeric() -->
-<!--   fp_s <- example_i_sexism[1, 3] %>% as.numeric() -->
-<!--   fn_s <- example_i_sexism[2, 2] %>% as.numeric() -->
-
-<!--   few_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100 -->
-<!--   few_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100 -->
-<!--   few_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100 -->
-<!--   few_sexism_f1 <- ((2*few_sexism_precision*few_sexism_recall)/(few_sexism_precision + few_sexism_recall)) %>% round(2) -->
-<!--   few_sexism_all <- c(few_sexism_accuracy, few_sexism_precision, few_sexism_recall, few_sexism_f1) -->
-
-<!--   few_shot_summary <- tibble(example_set = rep(i, 4), -->
-<!--                              Category = c(rep("Sexism", 4)),  -->
-<!--                              Metric = c("Accuracy", "Precision", "Recall", "F1"),  -->
-<!--                              Percent = c(few_sexism_all)) -->
-
-<!--   all_summary <- rbind(all_summary, few_shot_summary) -->
-<!-- } -->
-
-<!-- table <- all_summary %>% -->
-<!--   select(example_set, Metric, Percent) %>%  -->
-<!--   mutate(example_set = as.character(example_set), -->
-<!--          example_set = case_when(example_set == 11 ~ "All", TRUE ~ example_set), -->
-<!--          example_set = case_when(Metric != "Accuracy" ~ "", TRUE ~ example_set)) %>% -->
-<!--   rename("Example set" = example_set) -->
-
-<!-- knitr::kable(list(table[1:24, 1:3], -->
-<!--                   matrix(numeric(), nrow=0, ncol=3), -->
-<!--                   table[25:44, 1:3]), -->
-<!--              caption="Performance of mixed-category few-shot learning in sexist text classification", -->
-<!--                # col.names=c("", "Percent"), -->
-<!--              booktabs=TRUE, -->
-<!--              linesep = "") -->
-<!--   # kableExtra::pack_rows(index=c("Example set 1"=4, -->
-<!--   #                               "Example set 2"=4, -->
-<!--   #                               "Example set 3"=4, -->
-<!--   #                               "Example set 4"=4, -->
-<!--   #                               "Example set 5"=4, -->
-<!--   #                               "Example set 6"=4, -->
-<!--   #                               "Example set 7"=4, -->
-<!--   #                               "Example set 8"=4, -->
-<!--   #                               "Example set 9"=4, -->
-<!--   #                               "Example set 10"=4, -->
-<!--   #                               "Overall"=4)) -->
-
-<!-- ``` -->
+```
 
@@
 
-```{r fewshotmixedanswerswithinstruct, message=FALSE, warning=FALSE}
-# few_shot_instruction_result <-
-#   readr::read_csv(here::here("outputs/data/few_shot_fixed_examples_instruction_results.csv"))
-# 
-# few_shot_instruction_result %>% 
-#   select(answer) %>% 
-#   distinct()
-# %>% 
-#   rename(Answer = answer) %>% 
-#   knitr::kable(caption = "Classifications generated by GPT-3 under mixed-category few-shot learning with instructions", 
-#              booktabs = TRUE,
-#              linesep = "",
-#              align = 'llr')
-```
-
-The results of the mixed-category few-shot learning, with instruction, experiments are presented in Tables \@ref(tab:fewshotmixedinstruct-matrix), \@ref(tab:fewshotmixedinstruct-racism), \@ref(tab:fewshotmixedinstruct-sexism), and \@ref(tab:fewshotmixedinstruct-summary).
-With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (89.4 percent) and F1 score (84 percent) for sexist text, however Example Set 4 now performs best for racist text in terms of both accuracy (89.4 percent) and F1 score (84.6 percent).
+The results of the mixed-category few-shot learning, with instruction, experiments are presented in Tables \@ref(tab:fewshotmixedinstruct-matrix) and \@ref(tab:fewshotmixedinstruct-summary).
+And Tables \@ref(tab:fewshotmixedinstruct-racism), and \@ref(tab:fewshotmixedinstruct-sexism), in Appendix \@ref(appendxbmuxedubstryctub) provide additional detail.
+With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (89 per cent) and F1 score (84 per cent) for sexist text, however Example Set 4 now performs best for racist text in terms of both accuracy (89 per cent) and F1 score (85 per cent).
 When considering the classification of racist and sexist speech overall, the models perform similarly with and without instruction when classifying racist text, but the model appears to perform slightly better at identifying sexist text when the instruction is omitted.
@@
 However, examining label-classification matches across all categories ('sexist', 'racist', and 'neither'), mixed-category few-shot learning almost always performs better with instruction than without instruction (Figure \ref{fig:comparison}).
-Across all example sets, the mean proportion of matching classifications (out of 240 comments) for mixed-category few-shot learning without instruction is 66.9 percent.
-The average proportion of matching classifications rises to 74.5 percent for learning with instruction.
-
-<!-- ```{r fewshotmixedinstruct} -->
-<!-- few_shot_instruction_result <- -->
-<!--   read.csv(here::here( -->
-<!--     "outputs/data/few_shot_fixed_examples_instruction_results.csv" -->
-<!--   )) -->
-
-<!-- few_shot_instruction_result <- -->
-<!--   few_shot_instruction_result %>% -->
-<!--   filter(temperature == 0) %>% -->
-<!--   select(category, label, answer, example_set) %>% -->
-<!--   mutate(example_set = example_set + 1) %>% -->
-<!--   mutate(result = ifelse(trimws(label) == trimws(answer), "Match", "Mismatch")) %>% -->
-<!--   mutate( -->
-<!--     label = case_when( -->
-<!--       label == "racist" ~ "Racist", -->
-<!--       label == "sexist" ~ "Sexist", -->
-<!--       label == "neither" ~ "Neither" -->
-<!--     ) -->
-<!--   ) %>% -->
-<!--   group_by(example_set, result) %>% -->
-<!--   summarise(result_cnt = n(), .groups = "drop") %>% -->
-<!--   ungroup() %>% -->
-<!--   group_by(example_set) %>% -->
-<!--   mutate(Percent = result_cnt / sum(result_cnt) * 100, -->
-<!--          Percent = round(Percent)) %>% -->
-
-<!--   rename(Result = result, -->
-<!--          "Example Set" = example_set, -->
-<!--          Count = result_cnt) -->
-
-<!-- knitr::kable( -->
-<!--   few_shot_instruction_result, -->
-<!--   caption = "Classification of statements with mixed-category few-shot learning, with instruction", -->
-<!--   booktabs = TRUE, -->
-<!--   linesep = "", -->
-<!--   align = 'lllr' -->
-<!-- ) -->
-
-<!-- # few_shot_instruction_result %>% -->
-<!-- #   group_by(Result) %>% -->
-<!-- #   summarise(n = sum(Count)) %>% -->
-<!-- #   mutate(Percent = n / sum(n) * 100, -->
-<!-- #          Percent = round(Percent)) -->
-<!-- ``` -->
+Across all example sets, the mean proportion of matching classifications (out of 240 comments) for mixed-category few-shot learning without instruction is 67 per cent.
+The average proportion of matching classifications rises to 75 per cent for learning with instruction.
 
@@
 
-```{r fewshotmixedinstruct-racism}
+```{r fewshotmixedinstruct-summary}
+# Racism
 few_shot_instruction_result <-
@@
 
-table <- few_shot_mixed_result_instruct_racism %>% 
+tablefewshotmuxidracis <- few_shot_mixed_result_instruct_racism %>% 
   # select(!example_set) %>%
@@
 
-knitr::kable(table,
-             caption = "Classification of racist statements with mixed-category few-shot learning, with instruction",
-             booktabs = TRUE,
-             linesep="") %>%
-  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2)) %>%
-  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
-
-```
-
-```{r fewshotmixedinstruct-sexism}
+# Sexist
 # Example sets
@@
 
-table <- few_shot_mixed_result_instruct_sexism %>% 
+tablefewshomixedsex <- few_shot_mixed_result_instruct_sexism %>% 
   # select(!example_set) %>%
@@
 
-knitr::kable(table,
-             caption = "Classification of sexist statements with mixed-category few-shot learning, with instruction",
-             booktabs = TRUE,
-             linesep="") %>%
-  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2)) %>%
-  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
-
-```
-
-```{r fewshotmixedinstruct-summary}
+# Bring together
 few_shot_mixed_result_instruct_racism_overall <- few_shot_mixed_result_instruct_racism_overall %>% mutate(example_set = 11, .before="Actual classification")
@@
              caption="Performance of mixed-category few-shot learning in text classification, with instruction",
-               # col.names=c("", "Percent"),
+            col.names = c("Example set", "Category", "Accuracy (%)", "Precision (%)", "Recall (%)", "F1 (%)"),
              booktabs=TRUE,
@@
   kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
-
-# knitr::kable(list(table[1:24, 1:3],
-#                   matrix(numeric(), nrow=0, ncol=3),
-#                   table[25:44, 1:3]),
-#              caption="Performance of mixed-category few-shot learning in racist text classification, with instruction",
-#                # col.names=c("", "Percent"),
-#              booktabs=TRUE,
-#              linesep = "")
-  # kableExtra::pack_rows(index=c("Example set 1"=4,
-  #                               "Example set 2"=4,
-  #                               "Example set 3"=4,
-  #                               "Example set 4"=4,
-  #                               "Example set 5"=4,
-  #                               "Example set 6"=4,
-  #                               "Example set 7"=4,
-  #                               "Example set 8"=4,
-  #                               "Example set 9"=4,
-  #                               "Example set 10"=4,
-  #                               "Overall"=4))
-```
-
-<!-- ```{r fewshotmixedinstruct-summary-sexism} -->
-<!-- few_shot_mixed_result_instruct_sexism_overall <- few_shot_mixed_result_instruct_sexism_overall %>% mutate(example_set = 11, .before="Actual classification") -->
-<!-- all_results <- rbind(few_shot_mixed_result_instruct_sexism, few_shot_mixed_result_instruct_sexism_overall) -->
-<!-- all_summary <- tibble() -->
-<!-- for (i in 1:11){ -->
-<!--   example_i_sexism <- all_results %>% filter(example_set == i) %>% select(!example_set) -->
-
-<!--   tp_s <- example_i_sexism[2, 3] %>% as.numeric() -->
-<!--   tn_s <- example_i_sexism[1, 2] %>% as.numeric() -->
-<!--   fp_s <- example_i_sexism[1, 3] %>% as.numeric() -->
-<!--   fn_s <- example_i_sexism[2, 2] %>% as.numeric() -->
-
-<!--   few_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100 -->
-<!--   few_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100 -->
-<!--   few_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100 -->
-<!--   few_sexism_f1 <- ((2*few_sexism_precision*few_sexism_recall)/(few_sexism_precision + few_sexism_recall)) %>% round(2) -->
-<!--   few_sexism_all <- c(few_sexism_accuracy, few_sexism_precision, few_sexism_recall, few_sexism_f1) -->
-
-<!--   few_shot_summary <- tibble(example_set = rep(i, 4), -->
-<!--                              Category = c(rep("Sexism", 4)),  -->
-<!--                              Metric = c("Accuracy", "Precision", "Recall", "F1"),  -->
-<!--                              Percent = c(few_sexism_all)) -->
-
-<!--   all_summary <- rbind(all_summary, few_shot_summary) -->
-<!-- } -->
-
-<!-- table <- all_summary %>% -->
-<!--   select(example_set, Metric, Percent) %>%  -->
-<!--   mutate(example_set = as.character(example_set), -->
-<!--          example_set = case_when(example_set == 11 ~ "All", TRUE ~ example_set), -->
-<!--          example_set = case_when(Metric != "Accuracy" ~ "", TRUE ~ example_set)) %>% -->
-<!--   rename("Example set" = example_set) -->
-
-<!-- knitr::kable(list(table[1:24, 1:3], -->
-<!--                   matrix(numeric(), nrow=0, ncol=3), -->
-<!--                   table[25:44, 1:3]), -->
-<!--              caption="Performance of mixed-category few-shot learning in sexist text classification, with instruction", -->
-<!--                # col.names=c("", "Percent"), -->
-<!--              booktabs=TRUE, -->
-<!--              linesep = "") -->
-<!--   # kableExtra::pack_rows(index=c("Example set 1"=4, -->
-<!--   #                               "Example set 2"=4, -->
-<!--   #                               "Example set 3"=4, -->
-<!--   #                               "Example set 4"=4, -->
-<!--   #                               "Example set 5"=4, -->
-<!--   #                               "Example set 6"=4, -->
-<!--   #                               "Example set 7"=4, -->
-<!--   #                               "Example set 8"=4, -->
-<!--   #                               "Example set 9"=4, -->
-<!--   #                               "Example set 10"=4, -->
-<!--   #                               "Overall"=4)) -->
-<!-- ``` -->
+```
 
@@
 
-In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 62.5 per cent with an F1 score of 80.5 percent.
-In the one-shot learning setting the accuracy decreases to 60.8 percent with an F1 score of 65.3 percent.
-Accuracy increases to 69.2 percent in the single-category few-shot learning setting, with an F1 score of 60.5 percent.
-Of the three single-category approaches, zero-shot learning has a notably high recall value of 86.7 percent.
+In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 63 per cent with an F1 score of 81 per cent.
+In the one-shot learning setting the accuracy decreases to 61 per cent with an F1 score of 65 per cent.
+Accuracy increases to 69 per cent in the single-category few-shot learning setting, with an F1 score of 61 per cent.
+Of the three single-category approaches, zero-shot learning has a notably high recall value of 87 per cent.
 
@@
 @davidson2017automated, using a different model and approach, similarly find 'that almost 40 per cent of hate speech is misclassified'.
-And when @schick2021selfdiagnosis use GPT-2 they find a similar ability to recognise sexually explicit content, however using an alternative model - Google's T5 [@raffel2020exploring] - they find better results.
+And when @schick2021selfdiagnosis use GPT-2 they find a similar ability to recognize sexually explicit content, however using an alternative model - Google's T5 [@raffel2020exploring] - they find better results.
 
@@
 Mixed-category few-shot learning without instruction had noticeably better F1 scores for both racist and sexist comments than either zero-shot or one-shot learning.
-With instruction added, mixed-category few-shot learning performed similarly well for racist text identification, however the model performed relatively poorly in identifying sexist speech, with an F1 score of 63.1 percent overall and a recall of 50.2 percent meaning nearly half of the sexist comments were wrongly classified.
+With instruction added, mixed-category few-shot learning performed similarly well for racist text identification, however the model performed relatively poorly in identifying sexist speech, with an F1 score of 63 per cent overall and a recall of 50 per cent meaning nearly half of the sexist comments were wrongly classified.
 Overall, it appears as though GPT-3 is most effective at identifying both racist and sexist comments in the mixed-category few-shot learning setting, without instruction.
@@
 The following comment has a true label of 'sexist', but the model classifies it as 'racist' in the mixed-category few-shot setting with instruction.
-This comment uses the word 'Islam' which may often be associated with discrimination on the basis of race or ethnicity, but its core argument is about gender-based violence.
+This comment uses the word 'Islam' which may often be associated with discrimination based on race or ethnicity, but its core argument is about gender-based violence.
 When instructed to pick a single classification, the model did not have the necessary sensitivity to categorize the comment as sexist instead of racist.
@@
 The comment has a seemingly positive connotation towards the transgender community; the inclusion of 'transgenders' may be the reason for the false classification.
-If this were the case, then combined with the previous example, the model may have a tendency to generate false positive results when it encounters words that are identity terms, erroneously ignoring the context in which they are used.
+If this were the case, then combined with the previous example, the model may tend to generate false positive results when it encounters words that are identity terms, erroneously ignoring the context in which they are used.
 Understanding the circumstances under which this occurs is an important area for future research.
@@
 
-In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS data set containing the profane words or sub-strings indicated in Table \@ref(tab:profanity) in Appendix B.
+In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS dataset containing the profane words or sub-strings indicated in Table \@ref(tab:profanity) in Appendix \@ref(appendxc).
 These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation.
@@
 Details of the misspellings added are also included in Table \@ref(tab:profanity).
-Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category (results in Table \@ref(tab:misspell-results) in Appendix B).
+Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category (results in Table \@ref(tab:misspell-results) in Appendix \@ref(appendxc)).
 Interestingly, three comments with added misspellings were classified as 'racist' where they had previously been classified as 'not racist'.
-This speaks to potential inconsistencies in the behaviour of GPT-3 in understanding profanity and censorship and presents another area for further investigation.
-
-In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 are capable of identifying sexist and racist text at a similar level of specificity to other methods.
+This speaks to potential inconsistencies in the behavior of GPT-3 in understanding profanity and censorship and presents another area for further investigation.
+
+In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 can identify sexist and racist text at a similar level of specificity to other methods.
 However, it is possible that if a user intentionally misspells profane words, the models may be less likely to identify such content as problematic.
@@
 To shed light on why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content.
-The extent to which the identification and classification of hate speech can be explained is especially of interest for future work and is something that could be implemented on the publicly available GPT-2 from OpenAI or T5 from Google.
+The extent to which the identification and classification of hate speech can be explained is especially of interest for future work and is something that could be implemented on the easily available GPT-2 from OpenAI or T5 from Google.
 
@@
 
-# Appendix A
+# Example sets for the mixed-category, few-shot learning, experiments {#appendxa}
 
@@
 
-# Appendix B
+\newpage
+
+# Additional detail for results {#appendxb}
+
+## Zero-shot {#appendixbzeroshot}
+
+```{r zeroshot-racism, message=FALSE}
+zero_shot_result_racism %>%
+  knitr::kable(caption = "Classification of racist statements with zero-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification" = 2)) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+```{r zeroshot-sexism}
+zero_shot_result_sexism %>%
+  knitr::kable(caption = "Classification of sexist statements with zero-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2)) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+```{r zeroshot-hate}
+zero_shot_result_hate %>%
+  knitr::kable(caption = "Classification of hate speech with zero-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2)) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+\newpage
+
+## One-shot {#appendixboneshot}
+
+```{r oneshot-racism}
+one_shot_result_racism %>%
+  knitr::kable(caption = "Classification of racist statements with one-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2)) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
+
+```
+
+```{r oneshot-sexism}
+one_shot_result_sexism %>%
+  knitr::kable(caption = "Classification of sexist statements with one-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2)) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+```{r oneshot-hate}
+one_shot_result_hate %>%
+  knitr::kable(caption = "Classification of hate speech with one-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2)) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+\newpage
+
+## Few-shot single category {#appendixbfewshotsingle}
+
+```{r fewshotsingle-racism}
+few_shot_result_racism %>%
+  knitr::kable(caption = "Classification of racist statements with single-category few-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2)) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+```{r fewshotsingle-sexism}
+few_shot_result_sexism %>%
+  knitr::kable(caption = "Classification of sexist statements with single-category few-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2)) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+```{r fewshotsingle-hate}
+few_shot_result_hate %>%
+  knitr::kable(caption = "Classification of hate speech with single-category few-shot learning",
+               booktabs = TRUE) %>%
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2)) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+\newpage
+
+## Few-shot mixed category, without instruction {#appendxbmuxedubsnorinstruction}
+
+```{r fewshotmixed-racism}
+knitr::kable(tablefewshowmixedracism,
+             caption = "Classification of racist statements with mixed-category few-shot learning",
+             booktabs = TRUE,
+             linesep="") %>%
+  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2))  %>%
+  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+```{r fewshotmixed-sexism}
+
+knitr::kable(tablefewshotmixedsexism,
+             caption = "Classification of sexist statements with mixed-category few-shot learning",
+             booktabs = TRUE,
+             linesep="") %>%
+  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2))  %>%
+  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+\newpage
+
+## Few-shot mixed category, with instruction {#appendxbmuxedubstryctub}
+
+```{r fewshotmixedinstruct-racism}
+knitr::kable(tablefewshotmuxidracis,
+             caption = "Classification of racist statements with mixed-category few-shot learning, with instruction",
+             booktabs = TRUE,
+             linesep="") %>%
+  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2)) %>%
+  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
+
+```
+
+```{r fewshotmixedinstruct-sexism}
+knitr::kable(tablefewshomixedsex,
+             caption = "Classification of sexist statements with mixed-category few-shot learning, with instruction",
+             booktabs = TRUE,
+             linesep="") %>%
+  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2)) %>%
+  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
+
+\newpage
+
+# Effect of misspellings {#appendxc}
 
@@
 profanity %>%
-  knitr::kable(caption="Profane strings used to identify comments to test impacts of misspelling and censorship on hate speech classificiation",
+  knitr::kable(caption="Strings used to extract comments with profanity and edits introduced to test impacts of misspelling and censorship on hate speech classificiation",
                booktabs = TRUE,
-               col.names = c("Original", "Edits"))
+              linesep = "",
+               col.names = c("Original", "Edits"))  %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
 ```
@@
   kableExtra::column_spec(column = 3, width = "35em")%>% 
-  kableExtra::kable_styling(font_size = 7.5)%>%
-  kableExtra::kable_styling(latex_options = "HOLD_position")
+  kableExtra::kable_styling(font_size = 7.5)  %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
 ```

### 2022-03-16 Untitled.Rmd
Final read of paper

---
title: "Untitled"
author: "Rohan Alexander"
date: "`r Sys.Date()`"
output: pdf_document
csl: epj-data-science.csl
bibliography: "references.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

@raffel2020exploring

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2022-03-16 outputs/bmc_template/bmc_article.tex
Final read of paper

@@
 \author[
+   addressref={aff2},
+   email={rohan.alexander@utoronto.ca}
+]{\inits{AC}\fnm{Annie} \snm{Collins}}
+\author[
    addressref={aff1,aff2},
@@
 Sophisticated language models such as OpenAI's GPT-3 can generate hateful text that targets marginalized groups.
-Given this capacity, we are interested in whether large language models can be used to identify hate speech and classify text as sexist or racist?
+Given this capacity, we are interested in whether large language models can be used to identify hate speech and classify text as sexist or racist.
 We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning.
-We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an accuracy between 48 per cent and 69 per cent.
-With few-shot learning and an instruction included in the prompt, the model's accuracy can be as high as 78 per cent.
-We conclude that large language models have a role to play in hate speech detection, and that with further development language models could be used to counter hate speech and even self-police.
+We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an accuracy between 57 per cent and 68 per cent depending on the category of text and type of learning.
+With few-shot learning, the model's accuracy can be as high as 88 per cent.
+Large language models have a role to play in hate speech detection, and with further development could eventually be used to counter hate speech.
 \end{abstract}
@@
 
-Natural language processing (NLP) models focus on using normal words, often written text, as their data.
-For instance, one might have content from a large number of books and want to group them into themes.
+Natural language processing (NLP) models use normal words, often written text, as their data.
+For instance, one might have content from many books and want to group them into themes.
 Sophisticated NLP models are being increasingly embedded in society.
 For instance, Google Search uses an NLP model called BERT to better understand what is meant by a word given its context.
-Some sophisticated natural language processing (NLP) models, such as OpenAI's GPT-3, can additionally produce text as an output.
+Some sophisticated NLP models, such as OpenAI's Generative Pre-trained Transformer 3 (GPT-3), can additionally produce text as an output.
 
@@
 Large language models are trained on enormous datasets from various sources.
-This means that untruthful statements, human biases, and abusive language are inevitably included.
-Further, even when the models do not possess intent, they risk producing synthetic texts that are offensive or discriminatory and thus cause unpleasant, or even triggering, interaction experiences \cite{bender2021dangers}.
+This means they usually contain untruthful statements, human biases, and abusive language.
+Further, even when the models do not possess intent, they risk producing text that is offensive or discriminatory, and thus cause unpleasant, or even triggering, interactions \cite{bender2021dangers}.
 
@@
 For instance, hate speech commonly uses generalized language for targeting a group such as `all' and `every', and a model trained on these statements may generate similarly generalized and harmful statements.
-Finally, exposure refers to the relative attention, and hence considerations of importance, given to something.
-In the context of NLP this may be reflected in the emphasis on English-language created under particular circumstances, rather than another languages or circumstances that may be more prevalent.
+Finally, exposure refers to the relative attention, and hence consideration of importance, given to something.
+In the context of NLP this may be reflected in the emphasis on English-language created under particular circumstances, rather than another language or circumstances that may be more prevalent.
 
-While these, and other, issues give us pause, the dual-use problem, which is that the same technology can be applied to both good and bad uses, provides motivation.
+While these issues, among others, give us pause, the dual-use problem, which is that the same technology can be applied for both good and bad uses, provides motivation.
 For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text \cite{hovy2016social}.
-In this paper we are interested in whether given large language models can produce harmful language, can they also identify, or learn to identify, harmful language?
+In this paper we are interested in whether large language models, given that they can produce harmful language, can also identify, or learn to identify, harmful language.
 
@@
 We show that this knowledge can be used to identify abusive language and even hate speech.
-In particular we consider 120 different extracts that have been categorized as `racist', `sexist', or `neither' in the single-category settings and 240 different extracts in the mixed-category settings.
+We consider 120 different extracts that have been categorized as `racist', `sexist', or `neither' in single-category settings (zero-shot, one-shot, and few-shot) and 243 different extracts in mixed-category few-shot settings.
 We ask GPT-3 to classify these based on zero-, one-, and few-shot learning, with and without instruction.
-We find that the model performs best with few-shot learning when an instruction is included.
-In that setting the model can accurately classify around 78 per cent of the extracts.
+We find that the model performs best with mixed-category few-shot learning.
+In that setting the model can accurately classify around 86 per cent of the racist extracts and 88 per cent of sexist extracts.
 If language models can be used to identify abusive language, then not only is there potential for them to counter the production of abusive language by humans, but they could also potentially self-police.
@@
 The Transformer is a network architecture for neural networks that can be trained more quickly than many other approaches \cite{vaswani2017attention}.
-Now most representative pre-trained language models, such as Google's model: Bidirectional Encoder Representations from Transformers (BERT) \cite{devlin2018bert}, as well as OpenAI's: Generative Pre-trained Transformer (GPT)-2 \cite{radford2019language}, and GPT-3 \cite{brown2020language}, are built on this architecture.
+Now most representative pre-trained language models, such as Google's: Bidirectional Encoder Representations from Transformers (BERT) \cite{devlin2018bert}, as well as OpenAI's: Generative Pre-trained Transformer (GPT)-2 \cite{radford2019language}, and GPT-3 \cite{brown2020language}, are built on this architecture.
 These models are widely used, for instance BERT is used by Google search.
 
-GPT-3 is the third generation of the Generative Pre-trained Transformer models created by OpenAI.
-OpenAI is a private company in California that develops artificial intelligence models.
-Until January 11, when \cite{fedus2021switch} announced a Transformer model with a trillion parameters, GPT-3 was the largest, publicly-known, Transformer language model.
-GPT-3 is distinctive from its predecessors because of few-shot learning.
+GPT-3 is the third generation of the Generative Pre-trained Transformer models created by OpenAI, a private company in California that develops artificial intelligence models.
+GPT-3 is an autoregressive NLP model that can perform a variety of tasks, including responding to questions, summarizing, and parsing text, translation, and classification.
+Interactions with the model involve inputting some text as a prompt and GPT-3 returning a text completion according to that prompt.
+
+GPT-3 is one of the largest, publicly available, Transformer language models.
+GPT-3 is distinctive to its predecessors because of few-shot learning.
 This means that GPT-3 can `learn' to perform a new task based on only a few examples, expressed in natural language, instead of a fine-tuning process that can require a large amount of data.
@@
 
-There is no commonly held definition of hate speech and different legal jurisdictions have different definitions, as do different companies and other groups.
+There is no commonly held definition of hate speech.
+Different legal jurisdictions have different definitions, as do different companies and other groups.
 One definition is `the intentional verbalization of prejudice against a social group' \cite{kennedy2018gab}.
-Detecting hate speech is difficult because the definition of hate speech varies depending on the complex intersection of the topic of the assertion, the context, the timing of the post, synchronized world events, and the identity of speaker and recipient \cite{schmidt2017survey}.
-Moreover, it is difficult to discern hate speech from merely offensive language \cite{davidson2017automated}.
+Detecting hate speech is difficult because the definition of hate speech varies depending on a complex intersection of the topic of the assertion, the context, the timing of the post, synchronized world events, and the identity of speaker and recipient \cite{schmidt2017survey}.
+Moreover, it is difficult to distinguish hate speech from offensive language \cite{davidson2017automated}.
 Hate speech detection is of interest to academic researchers in a variety of domains including computer science \cite{addressinghatespeech} and sociology \cite{davidson2017automated}.
@@
 There has been a large amount of research focused on detecting hate speech.
-And as part of this various hate speech datasets have been created and examined.
+As part of this process, various hate speech datasets have been created and examined.
 For instance, \cite{waseem2016hateful} create a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation.
-The use Twitter data, and annotate 16,914 tweets: 3,383 as sexist, 1,972 as racist, and 11,559 as neither.
-They had a high degree of annotator agreement, and most of the disagreements were to do with sexism, and often explained by an annotator lacking apparent context.
-And, \cite{davidson2017automated} trains a classifier to distinguish between hate speech and offensive language.
-To define hate speech, they use online `hate speech lexicon containing words and phrases identified by internet users as hate speech'.
-It is important to note that even these datasets have bias.
+They use Twitter data, and annotate 16,914 tweets: 3,383 as sexist, 1,972 as racist, and 11,559 as neither.
+They had a high degree of annotator agreement.
+Most of the disagreements were to do with sexism, and often explained by an annotator lacking apparent context.
+\cite{davidson2017automated} trains a classifier to distinguish between hate speech and offensive language.
+To define hate speech, they use an online `hate speech lexicon containing words and phrases identified by internet users as hate speech'.
+Even these datasets have bias.
 For instance, \cite{davidson2019racial} found racial bias in five different sets of Twitter data annotated for hate speech and abusive language.
@@
 The classification is done by contributors to a crowd-sourcing platform.
-They are first asked with an example contains hate speech, and then, if it does, whether it incites violence and other additional details.
+They are first asked whether an example contains hate speech, and then, if it does, whether it incites violence and other additional details.
 The dataset has two variants: binary and multi-label.
 In the binary dataset comments are classified as hate or non-hate based.
-In the multi-label variant, the comments are evaluated on measures that include violence, gender, race, ability, religion, and sexual orientation.
-The examples provided in this paper are from the ETHOS dataset and hence contain typos, misspelling, and offensive content.
+In the multi-label variant comments are evaluated on measures that include violence, gender, race, ability, religion, and sexual orientation.
+The dataset that we use is from the ETHOS dataset and hence contain typos, misspelling, and offensive content.
 
 We use all of the 998 statements in the ETHOS dataset that have a binary classification of hate speech or not hate speech.
-Of these, the 433 statements that contain hate speech additionally have multiple labels that classify the content, for instance, does the comment have to do with violence, gender, race, nationality, disability, etc.
-We considered all of the 136 statements that contain race-based hate speech, and we focus on the 76 whose race-based score is at least 0.5.
-Similarly, we considered the all of 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
-To create a balanced dataset we randomly draw 120 of these statements, using stratified sampling, to result in 60 sexist statements and 60 racist statements.
+Of these, the 433 statements that contain hate speech additionally have labels that classify the content.
+For instance, does the comment have to do with violence, gender, race, nationality, disability, etc.
+We considered all of the 136 statements that contain race-based hate speech, and we focus on the 76 whose race-based score is at least 0.5, meaning that at least 50 per cent of annotators agreed.
+Similarly, we considered all of the 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
+To create a balanced dataset, we select 120 of these statements to result in 60 sexist statements and 60 racist statements.
 For comparison purposes, we randomly draw 120 statements that are classified as not hate speech.
 The balanced sample enables us to more easily understand our results.
+
+For the purposes of one-shot and single-category few-shot learning, the dataset was split in half such that 30 racist comments, 30 sexist comments, and 60 neutral comments were used as inputs and the remainder were used as examples.
+This division was kept consistent for zero-shot learning to allow for the same set of 120 comments to be classified by all three approaches.
+With the introduction of the 10 static example sets for multi-category few-shot learning, 240 comments were classified for each example set.
+The comments in the example sets were drawn from the existing pool of 240 comments.
+For each example set, the comment from each category being used in the example set was dropped from the input dataset and an additional comment from each original dataset (one `racist', one `sexist', and one `neither') was added in as a replacement.
+This replacement was kept consistent each time, for a total of 243 unique comments classified in the few-shot mixed-category setting.
 
@@
 The answer is expected to be binary.
-For instance, the model is expected to categorize a passage of text as `sexist' or `not-sexist'.
+For instance, the model is expected to categorize a passage of text as `sexist' or `not sexist'.
 An example of this is:
@@
 
-The assignment of sexist or not in the prompt is based on the ETHOS dataset classification.
+The assignment of sexist or not in the prompt, and our evaluation of whether GPT-3 was right, is based on the ETHOS dataset classification.
 
@@
 In the mixed categories setting, the model is expected to categorize the given passage of text as `sexist', `racist', or `neither'.
-There are ten sets of examples; each set of examples is used for the model to classify 60 racist comments, 60 sexist comments, and 120 comments that are in neither category This results in 2,400 responses in total.
-The ten sets of examples are available in Table \ref{tab:appendixa} in the Appendix.
+To simplify the classification procedure and allow for comparisons between different example inputs, we created ten sets of examples against which 240 comments were each classified.
+We elected to use ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset tractable.
+The example sets each consist of one sexist, one racist, and one `neither' comment and were created using the comments at indexes one through ten from each dataset.
+Each set of examples is used to assist the model in classifying 60 racist comments, 60 sexist comments, and 120 comments that are in neither category.
+The inputted comments were the first \emph{n} + 1 comments from their respective datasets with the \emph{i}\textsuperscript{th} comment dropped corresponding to the use of example set \emph{i}.
+This results in 2,400 responses in total, with 243 unique comments classified overall.
+The ten sets of examples are shown in Appendix \ref{appendxa}.
 An example of this is:
@@
 
-\section{Result}\label{result}
+\section{Results}\label{results}
+
+We assess GPT-3's performance in all settings using accuracy, precision, recall, and F1 score.
+Accuracy is the proportion of correctly classified comments (hate speech and non-hate speech) out of all comments classified.
+Precision is the proportion of hate speech comments correctly classified out of all comments classified as hate speech (both correctly and incorrectly).
+Recall is the proportion of hate speech comments correctly classified out of all hate speech comments in the dataset (both correctly and incorrectly classified).
+The F1 score is the harmonic mean of precision and recall.
+In the case of hate speech classification, it is better to have a model with high recall, meaning a model that can identify a relatively high proportion of the hate speech text within a dataset.
+But the F1 score can provide a more well-rounded metric for model performance and comparison.
 
@@
 
-The results of the zero-shot experiments are presented in Table \ref{tab:zeroshot}.
-The model has 35 matches and 25 mismatches in the sexist category, and 23 matches and 37 mismatches in the racist category.
-The model performs better when identifying sexist comments compared with identifying racist comments.
-However, the overall ratio of matches and mismatches is 58:62.
-In other words, the accuracy in identifying hate speech in the zero-shot setting is 48 per cent.
+The overall results of the zero-shot experiments are presented in Table \ref{tab:zeroshot-summary}.
+Tables \ref{tab:zeroshot-racism}, \ref{tab:zeroshot-sexism}, and \ref{tab:zeroshot-hate}, in Appendix \ref{appendixbzeroshot} contain additional detail.
+The model has 34 matches (true positives and negatives) and 26 mismatches (false positives and negatives) in the sexist category, and 41 matches and 19 mismatches in the racist category.
+The model performs more accurately when identifying racist comments, with an accuracy of 68 per cent, compared with identifying sexist comments, with an accuracy of 57 per cent, however the F1 score for each type of hate speech is approximately the same.
+The overall ratio of matches and mismatches is 75:45.
+In other words, the accuracy in identifying hate speech in the zero-shot setting is 63 per cent.
+The model has an F1 score of 81 per cent in this setting, with a notably high recall of 87 per cent as well.
 
@@
 
-The results of the one-shot learning experiments are presented in Table \ref{tab:oneshot}.
-The model has 46 matches and 14 mismatches in the racist category, and 37 matches and 23 mismatches in the sexist category.
-In contrast with the result generated from zero-shot learning, the model performs slightly better in identifying racist comments compared with identifying sexist comments.
-The general performance in the one-shot setting is also better than in the zero-shot setting.
-The overall ratio of matches and mismatches is 83:37.
-In other words, the accuracy of identifying hate speech in the one-shot setting is 69 per cent.
+The results of the one-shot learning experiments are presented in Table \ref{tab:oneshot-summary}.
+Tables \ref{tab:oneshot-racism}, \ref{tab:oneshot-sexism}, and \ref{tab:oneshot-hate}, in Appendix \ref{appendixboneshot} provide additional detail.
+The model has 37 matches and 23 mismatches in the racist category, and 36 matches and 24 mismatches in the sexist category.
+In contrast with the result generated from zero-shot learning, the model performs approximately the same in identifying racist comments and identifying sexist comments.
+The overall ratio of matches and mismatches is 73:47.
+In other words, the accuracy of identifying hate speech in the one-shot setting is 61 per cent.
+The general performance in the one-shot setting is worse than in the zero-shot setting, with lower accuracy, recall, precision, and F1 score overall.
 
@@
 
-The results of the single-category, few-shot learning, experiments are presented in Table \ref{tab:fewshotsingle}.
+The results of the single-category, few-shot learning, experiments are presented in Table \ref{tab:fewshotsingle-summary}.
+Tables \ref{tab:fewshotsingle-racism}, \ref{tab:fewshotsingle-sexism}, \ref{tab:fewshotsingle-hate}, in Appendix \ref{appendixbfewshotsingle} provide additional detail.
 The model has 41 matches and 19 mismatches in the racist category, and 42 matches and 18 mismatches in the sexist category.
-Here, the model performs almost equally well at identifying racist comments compared with identifying sexist comments.
-The general performance in the few-shot learning setting is similar to the performance in the one-shot learning setting.
-The overall ratio of matches and mismatches is 83:37, or around 69 per cent, however the composition is different, compared with the one-shot learning setting.
+Like the one-shot setting, the model performs almost equally well at identifying racist comments compared with identifying sexist comments.
+The general performance in the single-category few-shot learning setting is slightly more accurate than performance in other settings, with an accuracy of 69 per cent compared with 61 per cent in the one-shot setting and 63 per cent in the zero-shot setting.
+However, the model in this context has the lowest F1 score of the settings considered thus far at 61 per cent.
 
@@
 
-The results of the mixed-category few-shot experiments are presented in Table \ref{tab:fewshotmixed}.
-Among the ten sets of examples, Example Set 2 yields the best performance, as the model has the highest number of matches, 180, and the lowest number of mismatches, 60.
-In other words, the accuracy under the mixed category few-shot setting with Example Set 2 is 75 per cent.
-The example set that yields the worst results is Example Set 9, in which there are 137 matches and 103 mismatches.
-The accuracy rate with Example Set 9 is 57 per cent.
-The difference between Example Sets 2 and 9 suggests that, although the models are provided with same number of examples, the content of the examples also affects how the model makes inferences.
+The results of the mixed-category few-shot experiments are presented in Table \ref{tab:fewshotmixed-summary}.
+Tables \ref{tab:fewshotmixed-racism} and Table \ref{tab:fewshotmixed-sexism} in Appendix \ref{appendxbmuxedubsnorinstruction} provide additional detail.
+Among the ten sets of examples, Example Set 1 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments and Example Set 10 yields the best performance by the same metrics for sexist comments (accuracy of 89 per cent, F1 score of 85 per cent).
+The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 70 per cent (and the lowest accuracy at 73 per cent) for this dataset.
+The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 74 per cent) for this dataset.
+The differences between Example Sets 1, 8, 9, and 10 suggest that, although the models are provided with same number of examples, the content of the examples also affects how the model makes inferences.
+Overall, the mixed-category few-shot setting performs approximately the same at identifying sexist text and racist text.
+It is also has higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
 
@@
 
+The results presented for each category of text include the classifications of comments that were labelled as `neither' and the category in question.
+For the purposes of our analysis, a classification was considered a true positive if the answer outputted by GPT-3 contained a category that matched the comment's label.
+For example, if a comment was labelled `sexist' and the comment was classified by the model as `sexist, racist', this was considered a true positive in the classification of sexist comments.
+If a comment was labelled `sexist' and the comment was classified by the model as `racist', `transphobic', `neither', etc.
+this was considered a false negative.
+
+Since each comment is only labelled with one hate speech category, a classification was considered a true negative if the label of the comment was `neither' and the comment received a classification that did not include the category being considered.
+For example, if a comment was labelled `neither' and the model answered `racist', this is considered a true negative in the classification of sexist comments (the comment is not sexist, and the model did not classify it as sexist), but a false positive in the classification of racist comments (the comment is not racist, but the model classified it as racist).
+
 \subsection{Few-shot learning -- mixed category with instruction}\label{few-shot-learning-mixed-category-with-instruction}
@@
 The addition of an instruction successfully restricts the generated answers within the specified terms.
-The unique generated answers are: `racist', `neither', and `sexist'.
+The unique generated answers are: `racist', `sexist', and `neither'.
 
-The results of the mixed-category, few-shot learning, with instruction, experiments are presented in Table \ref{tab:fewshotmixedinstruct}.
-With the addition of an instruction in the prompt, the example set that yields the best result is Example Set 1 instead of Example Set 2.
-The addition of the instruction in the prompt increases the highest number of matches from 180 to 187; the highest accuracy rate is increased from 75 per cent to 78 per cent.
-In almost all cases the accuracy of the model increases (Figure \ref{fig:comparison}).
-Across all the example sets, there are 1,785, or 74 per cent, matches and 615, or 26 per cent, mismatches.
+The results of the mixed-category few-shot learning, with instruction, experiments are presented in Tables \ref{tab:fewshotmixedinstruct-matrix} and \ref{tab:fewshotmixedinstructsummary}.
+And Tables \ref{tab:fewshotmixedinstruct-racism}, and \ref{tab:fewshotmixedinstruct-sexism}, in Appendix \ref{appendxbmuxedubstryctub} provide additional detail.
+With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (89 per cent) and F1 score (84 per cent) for sexist text, however Example Set 4 now performs best for racist text in terms of both accuracy (89 per cent) and F1 score (85 per cent).
+When considering the classification of racist and sexist speech overall, the models perform similarly with and without instruction when classifying racist text, but the model appears to perform slightly better at identifying sexist text when the instruction is omitted.
+
+However, examining label-classification matches across all categories (`sexist', `racist', and `neither'), mixed-category few-shot learning almost always performs better with instruction than without instruction (Figure \ref{fig:comparison}).
+Across all example sets, the mean proportion of matching classifications (out of 240 comments) for mixed-category few-shot learning without instruction is 67 per cent.
+The average proportion of matching classifications rises to 75 per cent for learning with instruction.
 
@@
 
-In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 48 per cent.
-In both the one-shot learning setting and the single-category few-shot learning setting, the accuracy increases to 69 per cent.
-It is likely that the model is not suitable for use in hate speech detection in either the zero-shot learning or one-shot learning settings, as the accuracy rates are between 48.3 per cent and 69 per cent.
+In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 63 per cent with an F1 score of 81 per cent.
+In the one-shot learning setting the accuracy decreases to 61 per cent with an F1 score of 65 per cent.
+Accuracy increases to 69 per cent in the single-category few-shot learning setting, with an F1 score of 61 per cent.
+Of the three single-category approaches, zero-shot learning has a notably high recall value of 87 per cent.
+
+It is likely that the model is not ideal for use in hate speech detection in the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the accuracy rates are between 60 per cent and 70 per cent.
 \cite{davidson2017automated}, using a different model and approach, similarly find `that almost 40 per cent of hate speech is misclassified'.
-And when \cite{schick2021selfdiagnosis} use GPT-2 they find a similar ability to recognise sexually explicit content, however using an alternative model - Google's T5 \cite{raffel2020exploring} - they find better results.
+And when \cite{schick2021selfdiagnosis} use GPT-2 they find a similar ability to recognize sexually explicit content, however using an alternative model - Google's T5 \cite{raffel2020exploring} - they find better results.
 
-In the mixed-category few-shot setting, different example sets yield different accuracy rates.
-Without an instruction included in the prompt, the accuracy rates range from 57 per cent (Example Set 9) to 75 per cent (Example Set 2).
-Adding an instruction improves the performance, and the highest accuracy rate increases from 75 per cent (Example Set 2) to 78 per cent (Example Set 1).
-Overall accuracy rates also increase in almost every example set after adding an instruction in the prompt.
-The large difference in accuracy rates between the example sets suggests that the content of the examples may matter.
+In the mixed-category few-shot setting, different example sets yield different accuracy rates for racist and sexist comments, with noticeable improvement over the single-category approaches.
+Mixed-category few-shot learning without instruction had noticeably better F1 scores for both racist and sexist comments than either zero-shot or one-shot learning.
+With instruction added, mixed-category few-shot learning performed similarly well for racist text identification, however the model performed relatively poorly in identifying sexist speech, with an F1 score of 63 per cent overall and a recall of 50 per cent meaning nearly half of the sexist comments were wrongly classified.
+Overall, it appears as though GPT-3 is most effective at identifying both racist and sexist comments in the mixed-category few-shot learning setting, without instruction.
+
+Examining the proportion of classification matches for each example set (calculated as the number of correct `racist', `sexist', and `neither' classifications out of all comments classified), the overall proportion of matches increases in almost every example set after adding an instruction in the prompt.
+The differences in accuracy, precision, and recall between the example sets suggests that the content of the examples may matter as well.
 It may be that deliberately curated examples would enable better accuracy.
+Adding an instruction to the prompt is useful for restricting the output of the model to more clear-cut classifications.
+Depending on the purposes of classification, it appears as though adding an instruction can improve model performance by some metrics, however this may vary by the category of text considered and still produce the low recall observed in many of the example sets classified with instruction.
 
 Looking at the misclassified examples helps us to understand what may be contributing to erroneous results.
-The following comment has a true label of `racist', but the model classifies it as `sexist'.
-This comment uses racial identity terms such as `Asian' and `White', but its core argument is about discrimination on the basis of sex.
-The model did not have the necessary sensitivity to categorize the comment as sexist instead of racist.
+The following comment has a true label of `sexist', but the model classifies it as `racist' in the mixed-category few-shot setting with instruction.
+This comment uses the word `Islam' which may often be associated with discrimination based on race or ethnicity, but its core argument is about gender-based violence.
+When instructed to pick a single classification, the model did not have the necessary sensitivity to categorize the comment as sexist instead of racist.
+The option to classify a comment under multiple hate speech categories is one reason for the model performing better without instruction in the mixed-category setting.
 
 \begin{quote}
-`The male gene is stronger, as it should be of course.
-Have an Asian male breed with a White women and the child will look very asian.
-Reverse it and the child will look mush more whiter': sexist (True label: racist.)
+`Islam! Lets beat their feminist ass'
+
+Mixed-category few-shot classification: racist, sexist (True label: sexist)
+
+Mixed-category few-shot classification, with instruction: racist (True label: sexist)
 \end{quote}
 
-As another similar example, the following comment has a true label of `neither', but the model classified it as `transphobic'.
+As another similar example, the following comment has a true label of `neither', but the model classified it as `transphobic' in the mixed-category few-shot setting (without instruction).
 
 \begin{quote}
-`Civil rights movement for transgendered people.': transphobic (True label: neither.)
+`Transgenders have to protect each other, not fight each other': transphobic (True label: neither.)
 \end{quote}
 
-The comment is a plain statement without judgment; the inclusion of `transgendered people' may be the reason for the false positive.
-If this were the case, then combined with the previous example, the model may have a tendency to generate false positive results when it encounters words that are identity terms, erroneously ignoring the context in which they are used.
+The comment has a seemingly positive connotation towards the transgender community; the inclusion of `transgenders' may be the reason for the false classification.
+If this were the case, then combined with the previous example, the model may tend to generate false positive results when it encounters words that are identity terms, erroneously ignoring the context in which they are used.
 Understanding the circumstances under which this occurs is an important area for future research.
@@
 Large language models take a long time to train and deploy.
-This means that it may be that unless considerable context is provided in the prompt, that the model would not identify words that have become sexist and racist through their usage in the time since the model was trained.
+It may be that, unless considerable context is provided in the prompt, the model will not identify words that have become sexist and racist through their usage in the time since the model was trained.
 
-In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 are capable of identifying sexist and racist text at a similar level of specificity to other methods.
+In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS dataset containing the profane words or sub-strings indicated in Table \ref{tab:profanity} in Appendix \ref{appendxc}.
+These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation.
+The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process.
+Details of the misspellings added are also included in Table \ref{tab:profanity}.
+Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category (results in Table \ref{tab:misspell-results} in Appendix \ref{appendxc}).
+Interestingly, three comments with added misspellings were classified as `racist' where they had previously been classified as `not racist'.
+This speaks to potential inconsistencies in the behavior of GPT-3 in understanding profanity and censorship and presents another area for further investigation.
+
+In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 can identify sexist and racist text at a similar level of specificity to other methods.
 However, it is possible that if a user intentionally misspells profane words, the models may be less likely to identify such content as problematic.
@@
 \section*{Author's contributions}
-  Chiu had the original idea, obtained and created the datasets, and wrote the first draft of the paper.
-Chiu and Alexander analysed and interpreted the data, contributed to writing the paper, and approved the final version.
+  KC had the original idea, obtained and created the datasets, and wrote the first draft of the paper.
+KC, AC, and RA analysed and interpreted the data, contributed to writing the paper, substantially revised it, and approved the final version.
 
 \section*{Acknowledgements}
-  We thank Amy Farrow, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions.
+  We thank two anonymous reviews and the editor, as well as Amy Farrow, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions.
 Please note that we have added asterisks to racial slurs and other offensive content in this paper, however the inputs and outputs did not have these.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{figure}[h!]
-\caption{\label{fig:comparison}Comparing accuracy with and without an instruction}
+\begin{figure}
+\caption{\label{fig:comparison}Comparing classification with and without an instruction}
 \end{figure}
@@
 \section*{Tables}
-\begin{table}[h!]
-\caption{Sample table title. This is where the description of the table should go.}
-      \begin{tabular}{cccc}
-        \hline
-           & B1  &B2   & B3\\ \hline
-        A1 & 0.1 & 0.2 & 0.3\\
-        A2 & ... & ..  & .\\
-        A3 & ..  & .   & .\\ \hline
-      \end{tabular}
-\end{table}
 
@@
 
-\caption{\label{tab:zeroshot}Classification of statements with zero-shot learning}
+\caption{\label{tab:zeroshot-summary}Performance of zero-shot learning in hate speech classification}
 \centering
-\begin{tabular}[t]{llrr}
-Result & Category & Count & Percent\\
+\begin{tabular}[t]{lrrrr}
 \hline
-Match & Racist & 23 & 19\\
-Match & Sexist & 35 & 29\\
-Mismatch & Racist & 37 & 31\\
-Mismatch & Sexist & 25 & 21\\
+Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
+\hline
+Racism & 68 & 67 & 73 & 70\\
+Sexism & 57 & 54 & 100 & 70\\
+Overall & 62 & 58 & 87 & 81\\
 \hline
@@
 
-\caption{\label{tab:oneshot}Classification of statements with one-shot learning}
+\caption{\label{tab:oneshot-summary}Performance of one-shot learning in hate speech classification}
 \centering
-\begin{tabular}[t]{llrr}
-Result & Category & Count & Percent\\
+\begin{tabular}[t]{lrrrr}
 \hline
-Match & Racist & 46 & 38\\
-Match & Sexist & 37 & 31\\
-Mismatch & Racist & 14 & 12\\
-Mismatch & Sexist & 23 & 19\\
+Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
+\hline
+Racism & 62 & 59 & 80 & 68\\
+Sexism & 60 & 57 & 77 & 66\\
+Overall & 61 & 58 & 78 & 65\\
 \hline
@@
 
-\caption{\label{tab:fewshotsingle}Classification of statements with single-category few-shot learning}
+\caption{\label{tab:fewshotsingle-summary}Performance of single-category few-shot learning in hate speech classification}
 \centering
-\begin{tabular}[t]{llrr}
-Result & Category & Count & Percent\\
+\begin{tabular}[t]{lrrrr}
 \hline
-Match & Racist & 41 & 34\\
-Match & Sexist & 42 & 35\\
-Mismatch & Racist & 19 & 16\\
-Mismatch & Sexist & 18 & 15\\
+Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
+\hline
+Racism & 68 & 66 & 77 & 71\\
+Sexism & 70 & 75 & 60 & 67\\
+Overall & 69 & 69 & 68 & 61\\
 \hline
@@
 
-\caption{\label{tab:fewshotmixed}Classification of statements with mixed-category few-shot learning}
+\caption{\label{tab:fewshotmixed-summary}Performance of mixed-category few-shot learning in text classification}
 \centering
-\begin{tabular}[t]{lllr}
-Example Set & Result & Count & Percent\\
+\begin{tabular}[t]{llrrrr}
 \hline
-1 & Match & 154 & 64\\
-1 & Mismatch & 86 & 36\\
-2 & Match & 180 & 75\\
-2 & Mismatch & 60 & 25\\
-3 & Match & 167 & 70\\
-3 & Mismatch & 73 & 30\\
-4 & Match & 157 & 65\\
-4 & Mismatch & 83 & 35\\
-5 & Match & 157 & 65\\
-5 & Mismatch & 83 & 35\\
-6 & Match & 173 & 72\\
-6 & Mismatch & 67 & 28\\
-7 & Match & 144 & 60\\
-7 & Mismatch & 96 & 40\\
-8 & Match & 155 & 65\\
-8 & Mismatch & 85 & 35\\
-9 & Match & 137 & 57\\
-9 & Mismatch & 103 & 43\\
-10 & Match & 174 & 72\\
-10 & Mismatch & 66 & 28\\
+Example set & Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
+\hline
+1 & Racism & 91 & 82 & 92 & 87\\
+ & Sexism & 87 & 86 & 72 & 78\\
+\hline
+2 & Racism & 88 & 79 & 88 & 83\\
+ & Sexism & 87 & 82 & 77 & 79\\
+\hline
+3 & Racism & 87 & 74 & 93 & 82\\
+ & Sexism & 84 & 79 & 73 & 76\\
+\hline
+4 & Racism & 84 & 69 & 98 & 81\\
+ & Sexism & 83 & 72 & 80 & 76\\
+\hline
+5 & Racism & 80 & 64 & 93 & 76\\
+ & Sexism & 86 & 82 & 75 & 78\\
+\hline
+6 & Racism & 86 & 71 & 98 & 83\\
+ & Sexism & 86 & 77 & 80 & 79\\
+\hline
+7 & Racism & 77 & 59 & 97 & 73\\
+ & Sexism & 87 & 85 & 73 & 79\\
+\hline
+8 & Racism & 73 & 55 & 95 & 70\\
+ & Sexism & 83 & 70 & 85 & 77\\
+\hline
+9 & Racism & 80 & 63 & 97 & 76\\
+ & Sexism & 74 & 57 & 85 & 68\\
+\hline
+10 & Racism & 88 & 77 & 90 & 83\\
+ & Sexism & 89 & 83 & 87 & 85\\
+\hline
+All & Racism & 83 & 68 & 94 & 79\\
+ & Sexism & 84 & 76 & 79 & 77\\
 \hline
@@
 \hline
-racist; neither; homophobic; sexist; sexist, racist,; sexual assault; \\
-religious; sexual harassment; racist, sexist,; transphobic; \\
-hypocritical; I'm not a; I'm not brave; none of your business; \\
-I didn't; I'm not offended; you're not; sexual; I don't play; \\
-I don't care; I don't know; victim blaming; it's a question; irrelevant; \\
-I'm not crazy; creepy; romantic; I was taught to; I didn't say; \\
-ignorant; I'm not sure; I agree; not true; not even wrong; \\
-YouTube doesn't remove; socialist; conspiracy theorist; \\
-overpopulation; ableist; Islamophobic; conspiracy theory; hippie; \\
-sexist, rape ap; cliche; not even close to; nostalgic; \\
-I don't think; not a question; hippy; terrorist; hate speech; \\
-he was a terrorist; preachy; not a valid argument; not sexist; brave; \\
-Islamophobe; because you're a; troll; mental; never; pedophilia; \\
-mental illness is not; I'm sure you; I'm not going; not even close; \\
-grammar; rape apologist; cliché; vegan; sexist, misogynistic; \\
-I do; wrong; funny; question; when you were taught; opinion; \\
-emotional; conspiracy; nostalgia \\
+racist | neither | homophobic | sexist | sexist, racist, | sexual assault | religious | sexual harassment | racist, sexist, | transphobic | hypocritical | I'm not a | I'm not brave | none of your business | I didn't | I'm not offended | you're not | sexual | I don't play | I don't care | I don't know | victim blaming | it's a question | irrelevant | I'm not crazy | creepy | romantic | I was taught to | I didn't say | ignorant | I'm not sure | I agree | not true | not even wrong | YouTube doesn't remove | socialist | conspiracy theorist | overpopulation | ableist | Islamophobic | conspiracy theory | hippie | sexist, rape ap | cliche | not even close to | nostalgic | I don't think | not a question | hippy | terrorist | hate speech | he was a terrorist | preachy | not a valid argument | not sexist | brave | Islamophobe | because you're a | troll | mental | never | pedophilia | mental illness is not | I'm sure you | I'm not going | not even close | grammar | rape apologist | cliché | vegan | sexist, misogynistic | I do | wrong | funny | question | when you were taught | opinion | emotional | conspiracy | nostalgia\\
 \hline
@@
 
-\caption{\label{tab:fewshotmixedinstruct}Classification of statements with mixed-category few-shot learning, with instruction}
+\caption{\label{tab:fewshotmixedinstruct-matrix}Classifications of all comments using mixed-category few-short learning, with instruction}
 \centering
-\begin{tabular}[t]{lllr}
-Example Set & Result & Count & Percent\\
+\begin{tabular}[t]{llll}
 \hline
-1 & Match & 187 & 78\\
-1 & Mismatch & 53 & 22\\
-2 & Match & 184 & 77\\
-2 & Mismatch & 56 & 23\\
-3 & Match & 179 & 75\\
-3 & Mismatch & 61 & 25\\
-4 & Match & 185 & 77\\
-4 & Mismatch & 55 & 23\\
-5 & Match & 172 & 72\\
-5 & Mismatch & 68 & 28\\
-6 & Match & 170 & 71\\
-6 & Mismatch & 70 & 29\\
-7 & Match & 182 & 76\\
-7 & Mismatch & 58 & 24\\
-8 & Match & 174 & 72\\
-8 & Mismatch & 66 & 28\\
-9 & Match & 173 & 72\\
-9 & Mismatch & 67 & 28\\
-10 & Match & 179 & 75\\
-10 & Mismatch & 61 & 25\\
+\multicolumn{1}{c}{ } & \multicolumn{3}{c}{GPT-3 classification} \\
+Actual classification & Neither & Racist & Sexist\\
+\hline
+Neither & 984 & 163 & 53\\
+Racist & 98 & 500 & 2\\
+Sexist & 264 & 35 & 301\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:fewshotmixedinstructsummary}Performance of mixed-category few-shot learning in text classification, with instruction}
+\centering
+\begin{tabular}[t]{llrrrr}
+\hline
+Example set & Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
+\hline
+1 & Racism & 88 & 79 & 87 & 83\\
+ & Sexism & 83 & 81 & 63 & 71\\
+\hline
+2 & Racism & 87 & 86 & 72 & 78\\
+ & Sexism & 82 & 89 & 53 & 67\\
+\hline
+3 & Racism & 86 & 76 & 83 & 79\\
+ & Sexism & 81 & 84 & 52 & 64\\
+\hline
+4 & Racism & 89 & 83 & 87 & 85\\
+ & Sexism & 80 & 83 & 50 & 62\\
+\hline
+5 & Racism & 86 & 87 & 68 & 77\\
+ & Sexism & 76 & 84 & 35 & 49\\
+\hline
+6 & Racism & 88 & 93 & 70 & 80\\
+ & Sexism & 73 & 82 & 23 & 36\\
+\hline
+7 & Racism & 88 & 80 & 87 & 83\\
+ & Sexism & 79 & 85 & 47 & 60\\
+\hline
+8 & Racism & 79 & 62 & 93 & 75\\
+ & Sexism & 84 & 90 & 60 & 72\\
+\hline
+9 & Racism & 86 & 75 & 87 & 81\\
+ & Sexism & 77 & 88 & 35 & 50\\
+\hline
+10 & Racism & 77 & 59 & 100 & 74\\
+ & Sexism & 89 & 85 & 83 & 84\\
+\hline
+All & Racism & 85 & 75 & 83 & 79\\
+ & Sexism & 80 & 85 & 50 & 63\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:fewshotmixedanswersnoinstruct}Classifications generated by GPT-3 under mixed-category few-shot learning without instructions}
+\centering
+\begin{tabular}[t]{l}
+\hline
+racist | neither | homophobic | sexist | sexist, racist, | sexual assault | religious | sexual harassment | racist, sexist, | transphobic | hypocritical | I'm not a | I'm not brave | none of your business | I didn't | I'm not offended | you're not | sexual | I don't play | I don't care | I don't know | victim blaming | it's a question | irrelevant | I'm not crazy | creepy | romantic | I was taught to | I didn't say | ignorant | I'm not sure | I agree | not true | not even wrong | YouTube doesn't remove | socialist | conspiracy theorist | overpopulation | ableist | Islamophobic | conspiracy theory | hippie | sexist, rape ap | cliche | not even close to | nostalgic | I don't think | not a question | hippy | terrorist | hate speech | he was a terrorist | preachy | not a valid argument | not sexist | brave | Islamophobe | because you're a | troll | mental | never | pedophilia | mental illness is not | I'm sure you | I'm not going | not even close | grammar | rape apologist | cliché | vegan | sexist, misogynistic | I do | wrong | funny | question | when you were taught | opinion | emotional | conspiracy | nostalgia\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:fewshotmixedinstruct-matrix}Classifications of all comments using mixed-category few-short learning, with instruction}
+\centering
+\begin{tabular}[t]{llll}
+\hline
+\multicolumn{1}{c}{ } & \multicolumn{3}{c}{GPT-3 classification} \\
+Actual classification & Neither & Racist & Sexist\\
+\hline
+Neither & 984 & 163 & 53\\
+Racist & 98 & 500 & 2\\
+Sexist & 264 & 35 & 301\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:fewshotmixedinstructsummary}Performance of mixed-category few-shot learning in text classification, with instruction}
+\centering
+\begin{tabular}[t]{llrrrr}
+\hline
+Example set & Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
+\hline
+1 & Racism & 87.78 & 78.79 & 86.67 & 82.54\\
+ & Sexism & 82.78 & 80.85 & 63.33 & 71.03\\
+\hline
+2 & Racism & 86.67 & 86.00 & 71.67 & 78.18\\
+ & Sexism & 82.22 & 88.89 & 53.33 & 66.66\\
+\hline
+3 & Racism & 85.56 & 75.76 & 83.33 & 79.36\\
+ & Sexism & 80.56 & 83.78 & 51.67 & 63.92\\
+\hline
+4 & Racism & 89.44 & 82.54 & 86.67 & 84.55\\
+ & Sexism & 80.00 & 83.33 & 50.00 & 62.50\\
+\hline
+5 & Racism & 86.11 & 87.23 & 68.33 & 76.63\\
+ & Sexism & 76.11 & 84.00 & 35.00 & 49.41\\
+\hline
+6 & Racism & 88.33 & 93.33 & 70.00 & 80.00\\
+ & Sexism & 72.78 & 82.35 & 23.33 & 36.36\\
+\hline
+7 & Racism & 88.33 & 80.00 & 86.67 & 83.20\\
+ & Sexism & 79.44 & 84.85 & 46.67 & 60.22\\
+\hline
+8 & Racism & 78.89 & 62.22 & 93.33 & 74.66\\
+ & Sexism & 84.44 & 90.00 & 60.00 & 72.00\\
+\hline
+9 & Racism & 86.11 & 75.36 & 86.67 & 80.62\\
+ & Sexism & 76.67 & 87.50 & 35.00 & 50.00\\
+\hline
+10 & Racism & 76.67 & 58.82 & 100.00 & 74.07\\
+ & Sexism & 89.44 & 84.75 & 83.33 & 84.03\\
+\hline
+All & Racism & 85.39 & 75.41 & 83.33 & 79.17\\
+ & Sexism & 80.44 & 85.03 & 50.17 & 63.11\\
 \hline

### 2022-03-16 outputs/documents/paper.Rmd
Final read of paper

@@
 In particular, there have been many examples of text being generated that targets marginalized groups based on their sex, race, sexual orientation, and other characteristics.
-For instance, 'Tay' was a chatbot that was released by Microsoft in 2016 on Twitter.
+For instance, 'Tay' was a Twitter chatbot released by Microsoft in 2016.
 Within hours of being released, some of its tweets were sexist.
-Large language models are trained on enormous datasets from various sources.
+Large language models are trained on enormous datasets from various, but primarily internet-based, sources.
 This means they usually contain untruthful statements, human biases, and abusive language.
-Further, even when the models do not possess intent, they risk producing text that is offensive or discriminatory, and thus cause unpleasant, or even triggering, interactions [@bender2021dangers].
+Even though models do not possess intent, they do produce text that is offensive or discriminatory, and thus cause unpleasant, or even triggering, interactions [@bender2021dangers].
 
@@
 Words such as 'always', 'never', 'everybody', or 'nobody' are frequently used for rhetorical purpose instead of their literal meanings.
-However, language models do not always recognize this and make inference based on generalized statements using these words.
+But NLP models do not always recognize this and make inference based on generalized statements using these words.
 For instance, hate speech commonly uses generalized language for targeting a group such as 'all' and 'every', and a model trained on these statements may generate similarly generalized and harmful statements.
@@
 
-Even though large NLP models do not have a real understanding of language, the vocabularies and the construction patterns of harmful languages can be thought of as known to them.
+Even though large NLP models do not have a real understanding of language, the vocabularies and the construction patterns of hateful language can be thought of as known to them.
 We show that this knowledge can be used to identify abusive language and even hate speech.
@@
 
+The remainder of this paper is structured as follows: Section \@ref(background) provides background information about language models and GPT-3 in particular.
+Section \@ref(methods) introduces our dataset and our experimental approach to zero-, one-, and few-shot learning.
+Section \@ref(results) conveys the main findings of those experiments.
+And Section \@ref(discussion) adds context and discusses some implications, next steps, and weaknesses.
+Appendices \@ref(appendxa), \@ref(appendxb), and \@ref(appendxc) contain additional information.
+
 # Background
@@
 For instance, the sequence 'the cat in the hat' is probably more likely than 'the cat in the computer'.
-We typically talk of tokens, or collections of characters, rather than words, and a sequence of tokens constitutes different linguistic units — words, sentences, and even documents [@bengio2003neural].
+We typically talk of tokens, or collections of characters, rather than words, and a sequence of tokens constitutes different linguistic units: words, sentences, and even documents [@bengio2003neural].
 Language models predict the next token based on inputs.
@@
 The Transformer is a network architecture for neural networks that can be trained more quickly than many other approaches [@vaswani2017attention].
-Now most representative pre-trained language models, such as Google's: Bidirectional Encoder Representations from Transformers (BERT) [@devlin2018bert], as well as OpenAI's: Generative Pre-trained Transformer (GPT)-2 [@radford2019language], and GPT-3 [@brown2020language], are built on this architecture.
+Now most representative pre-trained language models, such as Google's Bidirectional Encoder Representations from Transformers (BERT) [@devlin2018bert], as well as OpenAI's Generative Pre-trained Transformer (GPT)-2 [@radford2019language], and GPT-3 [@brown2020language], are built on this architecture.
 These models are widely used, for instance BERT is used by Google search.
@@
 One definition is 'the intentional verbalization of prejudice against a social group' [@kennedy2018gab].
-Detecting hate speech is difficult because the definition of hate speech varies depending on a complex intersection of the topic of the assertion, the context, the timing of the post, synchronized world events, and the identity of speaker and recipient [@schmidt2017survey].
+Detecting hate speech is difficult because the definition of hate speech varies depending on a complex intersection of the topic of the assertion, the context, the timing, outside events, and the identity of speaker and recipient [@schmidt2017survey].
 Moreover, it is difficult to distinguish hate speech from offensive language [@davidson2017automated].
@@
 As part of this process, various hate speech datasets have been created and examined.
-For instance, @waseem2016hateful create a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation.
+For instance, @waseem2016hateful detail a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation.
 They use Twitter data, and annotate 16,914 tweets: 3,383 as sexist, 1,972 as racist, and 11,559 as neither.
@@
 Most of the disagreements were to do with sexism, and often explained by an annotator lacking apparent context.
-@davidson2017automated trains a classifier to distinguish between hate speech and offensive language.
+@davidson2017automated train a classifier to distinguish between hate speech and offensive language.
 To define hate speech, they use an online 'hate speech lexicon containing words and phrases identified by internet users as hate speech'.
@@
 
-We use the ETHOS dataset created by @mollas2020ethos.
-ETHOS is based on comments found in YouTube and Reddit.
+We use the ETHOS dataset of @mollas2020ethos.
+ETHOS is based on comments from YouTube and Reddit.
 The ETHOS YouTube data is collected through Hatebusters [@anagnostou2018hatebusters].
 Hatebusters is a platform that collects comments from YouTube and assigns a 'hate' score to them using a support vector machine.
-That hate-score is only used to decide whether to consider the comment further or not.
+That hate score is only used to decide whether to consider the comment further or not.
 The Reddit data is collected from the Public Reddit Data Repository [@baumgartner2020pushshift].
@@
 In the multi-label variant comments are evaluated on measures that include violence, gender, race, ability, religion, and sexual orientation.
-The dataset that we use is from the ETHOS dataset and hence contain typos, misspelling, and offensive content.
-
-We use all of the 998 statements in the ETHOS dataset that have a binary classification of hate speech or not hate speech.
+The dataset that we use is as provided by the ETHOS dataset and hence contain typos, misspelling, and offensive content.
+
+We begin with all of the 998 statements in the ETHOS dataset that have a binary classification of hate speech or not hate speech.
 Of these, the 433 statements that contain hate speech additionally have labels that classify the content.
 For instance, does the comment have to do with violence, gender, race, nationality, disability, etc.
-We considered all of the 136 statements that contain race-based hate speech, and we focus on the 76 whose race-based score is at least 0.5, meaning that at least 50 per cent of annotators agreed.
-Similarly, we considered all of the 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
+We initially considered all of the 136 statements that contain race-based hate speech, but we focus on the 76 whose race-based score is at least 0.5, meaning that at least 50 per cent of annotators agreed.
+Similarly, we initially considered all of the 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
 To create a balanced dataset, we select 120 of these statements to result in 60 sexist statements and 60 racist statements.
@@
 
-Under the few-shot setting, three examples are provided to the model.
+Under the few-shot setting, the model is given three examples.
 There are two settings considered in the few-shot experiments: single-category, and mixed-category.
@@
 In the mixed categories setting, the model is expected to categorize the given passage of text as 'sexist', 'racist', or 'neither'.
-To simplify the classification procedure and allow for comparisons between different example inputs, we created ten sets of examples against which 240 comments were each classified.
+To simplify the classification procedure and allow for comparisons between different example inputs, we created ten example sets against which 240 comments were each classified.
 We elected to use ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset tractable.
@@
 The F1 score is the harmonic mean of precision and recall.
-In the case of hate speech classification, it is better to have a model with high recall, meaning a model that can identify a relatively high proportion of the hate speech text within a dataset.
+In the case of hate speech classification, we see it as better to have a model with high recall, meaning a model that can identify a relatively high proportion of the hate speech text within a dataset.
 But the F1 score can provide a more well-rounded metric for model performance and comparison.
@@
 
-The overall results of the zero-shot experiments are presented in Table \@ref(tab:zeroshot-summary).
-Tables \@ref(tab:zeroshot-racism), \@ref(tab:zeroshot-sexism), and \@ref(tab:zeroshot-hate), in Appendix \@ref(appendixbzeroshot) contain additional detail.
+The overall results of the zero-shot experiments are presented in Table \@ref(tab:zeroshot-summary), and Appendix \@ref(appendixbzeroshot) provides additional detail.
 The model has 34 matches (true positives and negatives) and 26 mismatches (false positives and negatives) in the sexist category, and 41 matches and 19 mismatches in the racist category.
-The model performs more accurately when identifying racist comments, with an accuracy of 68 per cent, compared with identifying sexist comments, with an accuracy of 57 per cent, however the F1 score for each type of hate speech is approximately the same.
+The model performs more accurately when identifying racist comments, with an accuracy of 68 per cent, compared with identifying sexist comments, with an accuracy of 57 per cent, but the F1 score for each type of hate speech is roughly the same.
 The overall ratio of matches and mismatches is 75:45.
 In other words, the accuracy in identifying hate speech in the zero-shot setting is 63 per cent.
-The model has an F1 score of 81 per cent in this setting, with a notably high recall of 87 per cent as well.
+The model has an F1 score of 81 per cent in this setting, with a notably high recall of 87 per cent.
 
@@
 
-The results of the one-shot learning experiments are presented in Table \@ref(tab:oneshot-summary).
-Tables \@ref(tab:oneshot-racism), \@ref(tab:oneshot-sexism), and \@ref(tab:oneshot-hate), in Appendix \@ref(appendixboneshot) provide additional detail.
+The results of the one-shot learning experiments are presented in Table \@ref(tab:oneshot-summary), and Appendix \@ref(appendixboneshot) provides additional detail.
 The model has 37 matches and 23 mismatches in the racist category, and 36 matches and 24 mismatches in the sexist category.
-In contrast with the result generated from zero-shot learning, the model performs approximately the same in identifying racist comments and identifying sexist comments.
+In contrast with the result generated from zero-shot learning, the model performs roughly the same in terms of identifying racist comments and identifying sexist comments.
 The overall ratio of matches and mismatches is 73:47.
@@
 
-The results of the single-category, few-shot learning, experiments are presented in Table \@ref(tab:fewshotsingle-summary).
-Tables \@ref(tab:fewshotsingle-racism), \@ref(tab:fewshotsingle-sexism), \@ref(tab:fewshotsingle-hate), in Appendix \@ref(appendixbfewshotsingle) provide additional detail.
+The results of the single-category, few-shot learning, experiments are presented in Table \@ref(tab:fewshotsingle-summary), and Appendix \@ref(appendixbfewshotsingle) provides additional detail.
 The model has 41 matches and 19 mismatches in the racist category, and 42 matches and 18 mismatches in the sexist category.
-Like the one-shot setting, the model performs almost equally well at identifying racist comments compared with identifying sexist comments.
+Like the one-shot setting, the model performs almost equally well in terms of identifying racist comments compared with identifying sexist comments.
 The general performance in the single-category few-shot learning setting is slightly more accurate than performance in other settings, with an accuracy of 69 per cent compared with 61 per cent in the one-shot setting and 63 per cent in the zero-shot setting.
-However, the model in this context has the lowest F1 score of the settings considered thus far at 61 per cent.
+But, in this context we see the lowest F1 score of the settings considered thus far at 61 per cent.
 
@@
 
-The results of the mixed-category few-shot experiments are presented in Table \@ref(tab:fewshotmixed-summary).
-Tables \@ref(tab:fewshotmixed-racism) and Table \@ref(tab:fewshotmixed-sexism) in Appendix \@ref(appendxbmuxedubsnorinstruction) provide additional detail.
+The results of the mixed-category few-shot experiments are presented in Table \@ref(tab:fewshotmixed-summary), and Appendix \@ref(appendxbmuxedubsnorinstruction) provides additional detail.
 Among the ten sets of examples, Example Set 1 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments and Example Set 10 yields the best performance by the same metrics for sexist comments (accuracy of 89 per cent, F1 score of 85 per cent).
@@
 The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 74 per cent) for this dataset.
-The differences between Example Sets 1, 8, 9, and 10 suggest that, although the models are provided with same number of examples, the content of the examples also affects how the model makes inferences.
-Overall, the mixed-category few-shot setting performs approximately the same at identifying sexist text and racist text.
+The differences between Example Sets 1, 8, 9, and 10 suggest that, although the models are provided with the same number of examples, the content of the examples also affects how the model makes inferences.
+Overall, the mixed-category few-shot setting performs roughly the same in terms of identifying sexist text and racist text.
 It is also has higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
@@
 These are the response of GPT-3 that we obtain when we ask the model to classify statements, but do not provide examples that would serve to limit the responses.
-Under the mixed-category setting, the model is observed to generate answers that are out of scope.
+Under the mixed-category setting, the model is generates many answers that are out of scope.
 For instance, other than 'sexist', 'racist', and 'neither', we also see answers such as 'transphobic', 'hypocritical', 'Islamophobic', and 'ableist'.
@@
 For example, if a comment was labelled 'sexist' and the comment was classified by the model as 'sexist, racist', this was considered a true positive in the classification of sexist comments.
-If a comment was labelled 'sexist' and the comment was classified by the model as 'racist', 'transphobic', 'neither', etc.
-this was considered a false negative.
+If a comment was labelled 'sexist' and the comment was classified by the model as 'racist', 'transphobic', 'neither', etc, then this was considered a false negative.
 
@@
 
-The results of the mixed-category few-shot learning, with instruction, experiments are presented in Tables \@ref(tab:fewshotmixedinstruct-matrix) and \@ref(tab:fewshotmixedinstruct-summary).
-And Tables \@ref(tab:fewshotmixedinstruct-racism), and \@ref(tab:fewshotmixedinstruct-sexism), in Appendix \@ref(appendxbmuxedubstryctub) provide additional detail.
+The results of the mixed-category few-shot learning, with instruction, experiments are presented in Tables \@ref(tab:fewshotmixedinstruct-matrix) and \@ref(tab:fewshotmixedinstruct-summary), and Appendix \@ref(appendxbmuxedubstryctub) provides additional detail.
 With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (89 per cent) and F1 score (84 per cent) for sexist text, however Example Set 4 now performs best for racist text in terms of both accuracy (89 per cent) and F1 score (85 per cent).
@@
              booktabs=TRUE,
+            digits = 0,
              linesep = "") %>%
@@
   kableExtra::add_header_above(c(" " = 1, "GPT-3 classification" = 2)) %>% 
+  kableExtra::kable_styling(font_size = 8) %>%
   kableExtra::kable_styling(latex_options = "hold_position") 
@@
   kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=2)) %>% 
+  kableExtra::kable_styling(font_size = 8) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
@@
   kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE) %>% 
+  kableExtra::kable_styling(font_size = 8) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
@@
                col.names = c("Original", "Edits"))  %>% 
+  kableExtra::kable_styling(font_size = 8) %>%
   kableExtra::kable_styling(latex_options = "hold_position")

### 2022-03-16 outputs/documents/paper.tex
Final read of paper

@@
 \documentclass[12pt,]{article}
+\usepackage{amsmath}
 \usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
@@
 
-\setcounter{secnumdepth}{0}
+% This controls whether you get numbers in the sections or not
+% \setcounter{secnumdepth}{0}
 
@@
 \title{Detecting Hate Speech with GPT-3 \thanks{Code and data are available at: \url{https://github.com/kelichiu/GPT3-hate-speech-detection}.
-We gratefully acknowledge the support of Gillian Hadfield and the Schwartz Reisman Institute for Technology and Society.
-We thank Amy Farrow, Haoluan Chen, Mauricio Vargas Sepúlveda, and Tom Davidson for helpful suggestions.
-Comments on the 22 March 2021 version of this paper are welcome at: \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}  }
+We gratefully acknowledge the support of Gillian Hadfield, the Schwartz Reisman Institute for Technology and Society, and OpenAI for providing access to GPT-3 under the academic access program.
+We thank two anonymous reviews and the editor, as well as Amy Farrow, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions.
+Please note that we have added asterisks to racial slurs and other offensive content in this paper, however the inputs and outputs did not have these.
+Comments on the 16 March 2022 version of this paper are welcome at: \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}  }
 
-\author{\Large Ke-Li Chiu\vspace{0.05in} \newline\normalsize\emph{University of Toronto}   \and \Large Rohan Alexander\vspace{0.05in} \newline\normalsize\emph{University of Toronto and Schwartz Reisman Institute}  }
+\author{\Large Ke-Li Chiu\vspace{0.05in} \newline\normalsize\emph{University of Toronto}   \and \Large Annie Collins\vspace{0.05in} \newline\normalsize\emph{University of Toronto}   \and \Large Rohan Alexander\vspace{0.05in} \newline\normalsize\emph{University of Toronto and Schwartz Reisman Institute}  }
 
@@
 \usepackage{setspace}
+
+\makeatletter
+\@ifpackageloaded{hyperref}{}{%
+\ifxetex
+  \PassOptionsToPackage{hyphens}{url}\usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \PassOptionsToPackage{hyphens}{url}\usepackage[unicode=true]{hyperref}
+\fi
+}
+
+\@ifpackageloaded{color}{
+    \PassOptionsToPackage{usenames,dvipsnames}{color}
+}{%
+    \usepackage[usenames,dvipsnames]{color}
+}
+\makeatother
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={Ke-Li Chiu (University of Toronto) and Annie Collins (University of Toronto) and Rohan Alexander (University of Toronto and Schwartz Reisman Institute)},
+             pdfkeywords = {GPT-3; natural language processing; quantitative analysis; hate speech.},  
+            pdftitle={Detecting Hate Speech with GPT-3},
+            colorlinks=true,
+            citecolor=blue,
+            urlcolor=blue,
+            linkcolor=magenta,
+            pdfborder={0 0 0}}
+\urlstyle{same}  % don't use monospace font for urls
 
@@
 
-% move the hyperref stuff down here, after header-includes, to allow for - \usepackage{hyperref}
-
-\makeatletter
-\@ifpackageloaded{hyperref}{}{%
-\ifxetex
-  \PassOptionsToPackage{hyphens}{url}\usepackage[setpagesize=false, % page size defined by xetex
-              unicode=false, % unicode breaks when used with xetex
-              xetex]{hyperref}
-\else
-  \PassOptionsToPackage{hyphens}{url}\usepackage[draft,unicode=true]{hyperref}
-\fi
-}
-
-\@ifpackageloaded{color}{
-    \PassOptionsToPackage{usenames,dvipsnames}{color}
-}{%
-    \usepackage[usenames,dvipsnames]{color}
-}
-\makeatother
-\hypersetup{breaklinks=true,
-            bookmarks=true,
-            pdfauthor={Ke-Li Chiu (University of Toronto) and Rohan Alexander (University of Toronto and Schwartz Reisman Institute)},
-             pdfkeywords = {GPT-3; natural language processing; quantitative analysis; hate speech.},  
-            pdftitle={Detecting Hate Speech with GPT-3},
-            colorlinks=true,
-            citecolor=blue,
-            urlcolor=blue,
-            linkcolor=magenta,
-            pdfborder={0 0 0}}
-\urlstyle{same}  % don't use monospace font for urls
-
-% Add an option for endnotes. -----
-
 % add tightlist ----------
@@
 \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% add some other packages ----------
-
-% \usepackage{multicol}
-% This should regulate where figures float
-% See: https://tex.stackexchange.com/questions/2275/keeping-tables-figures-close-to-where-they-are-mentioned
-\usepackage[section]{placeins}
 
@@
    \vskip 13.5pt\relax \normalsize\fontsize{11}{12} 
-\textbf{\authorfont Ke-Li Chiu} \hskip 15pt \emph{\small University of Toronto}   \par \textbf{\authorfont Rohan Alexander} \hskip 15pt \emph{\small University of Toronto and Schwartz Reisman Institute}
+\textbf{\authorfont Ke-Li Chiu} \hskip 15pt \emph{\small University of Toronto}   \par \textbf{\authorfont Annie Collins} \hskip 15pt \emph{\small University of Toronto}   \par \textbf{\authorfont Rohan Alexander} \hskip 15pt \emph{\small University of Toronto and Schwartz Reisman Institute}
 
@@
 \noindent Sophisticated language models such as OpenAI's GPT-3 can generate hateful text that targets marginalized groups.
-Given this capacity, we are interested in whether large language models can be used to identify hate speech and classify text as sexist or racist?
+Given this capacity, we are interested in whether large language models can be used to identify hate speech and classify text as sexist or racist.
 We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning.
-We find that with zero- and one-shot learning, GPT-3 is able to identify sexist or racist text with an accuracy between 48 per cent and 69 per cent.
-With few-shot learning and an instruction included in the prompt, the model's accuracy can be as high as 78 per cent.
-We conclude that large language models have a role to play in hate speech detection, and that with further development language models could be used to counter hate speech and even self-police.
+We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an accuracy between 57 per cent and 68 per cent depending on the category of text and type of learning.
+With few-shot learning, the model's accuracy can be as high as 88 per cent.
+Large language models have a role to play in hate speech detection, and with further development could eventually be used to counter hate speech.
 
@@
 
-\vskip -8.5pt
+\vskip 6.5pt
 
- % removetitleabstract
-
-\noindent
-
-\hypertarget{introduction}{%
+\noindent  \hypertarget{introduction}{%
 \section{Introduction}\label{introduction}}
 
-Sophisticated natural language processing (NLP) models, such as OpenAI's GPT-3, can produce hateful text.
+\textbf{This paper contains language and themes that are offensive.}
+
+Natural language processing (NLP) models use normal words, often written text, as their data.
+For instance, one might have content from many books and want to group them into themes.
+Sophisticated NLP models are being increasingly embedded in society.
+For instance, Google Search uses an NLP model called BERT to better understand what is meant by a word given its context.
+Some sophisticated NLP models, such as OpenAI's Generative Pre-trained Transformer 3 (GPT-3), can additionally produce text as an output.
+
+The text produced by sophisticated NLP models can be hateful.
 In particular, there have been many examples of text being generated that targets marginalized groups based on their sex, race, sexual orientation, and other characteristics.
-Large language models are trained on enormous datasets from various sources.
-This means that untruthful statements, human biases, and abusive language are inevitably included.
-Further, \citet{bender2021dangers} describes how even when the models do not possess intent, they risk producing synthetic texts that are offensive or discriminatory and thus cause unpleasant, or even triggering, interaction experiences.
+For instance, `Tay' was a Twitter chatbot released by Microsoft in 2016.
+Within hours of being released, some of its tweets were sexist.
+Large language models are trained on enormous datasets from various, but primarily internet-based, sources.
+This means they usually contain untruthful statements, human biases, and abusive language.
+Even though models do not possess intent, they do produce text that is offensive or discriminatory, and thus cause unpleasant, or even triggering, interactions \citep{bender2021dangers}.
 
-The sources of the training datasets raise concerns around three issues: exclusion, over-generalization, and exposure \citep{hovy2016social}.
+Often the datasets that underpin these models consist of, essentially, the whole public internet.
+This source raises concerns around three issues: exclusion, over-generalization, and exposure \citep{hovy2016social}.
 Exclusion happens due to the demographic bias in the dataset.
@@
 Words such as `always', `never', `everybody', or `nobody' are frequently used for rhetorical purpose instead of their literal meanings.
-However, language models do not always recognize this and make inference based on generalized statements using these words.
+But NLP models do not always recognize this and make inference based on generalized statements using these words.
 For instance, hate speech commonly uses generalized language for targeting a group such as `all' and `every', and a model trained on these statements may generate similarly generalized and harmful statements.
-Finally, exposure refers to the relative attention, and hence considerations of importance, given to something.
-In the context of NLP this may be reflected in the emphasis on English-language created under particular circumstances, rather than another languages or circumstances that may be more prevalent.
+Finally, exposure refers to the relative attention, and hence consideration of importance, given to something.
+In the context of NLP this may be reflected in the emphasis on English-language created under particular circumstances, rather than another language or circumstances that may be more prevalent.
 
-While these, and other, issues give us pause, the dual-use problem, which is that the same technology can be applied to both good and bad uses, provides motivation.
+While these issues, among others, give us pause, the dual-use problem, which is that the same technology can be applied for both good and bad uses, provides motivation.
 For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text \citep{hovy2016social}.
-In this paper we are interested in whether given large language models can produce harmful language, can they also identify, or learn to identify, harmful language?
+In this paper we are interested in whether large language models, given that they can produce harmful language, can also identify, or learn to identify, harmful language.
 
-Even though large NLP models do not have a real understanding of language, the vocabularies and the construction patterns of harmful languages can be thought of as known to them.
+Even though large NLP models do not have a real understanding of language, the vocabularies and the construction patterns of hateful language can be thought of as known to them.
 We show that this knowledge can be used to identify abusive language and even hate speech.
-In particular we consider 120 different extracts that have been categorized as `racist', `sexist', or `neither' in the single-category settings and 240 different extracts in the mixed-category settings.
+We consider 120 different extracts that have been categorized as `racist', `sexist', or `neither' in single-category settings (zero-shot, one-shot, and few-shot) and 243 different extracts in mixed-category few-shot settings.
 We ask GPT-3 to classify these based on zero-, one-, and few-shot learning, with and without instruction.
-We find that the model performs best with few-shot learning when an instruction is included.
-In that setting the model is able to accurately classify around 78 per cent of the extracts.
+We find that the model performs best with mixed-category few-shot learning.
+In that setting the model can accurately classify around 86 per cent of the racist extracts and 88 per cent of sexist extracts.
 If language models can be used to identify abusive language, then not only is there potential for them to counter the production of abusive language by humans, but they could also potentially self-police.
+
+The remainder of this paper is structured as follows: Section \ref{background} provides background information about language models and GPT-3 in particular.
+Section \ref{methods} introduces our dataset and our experimental approach to zero-, one-, and few-shot learning.
+Section \ref{results} conveys the main findings of those experiments.
+And Section \ref{discussion} adds context and discusses some implications, next steps, and weaknesses.
+Appendices \ref{appendxa}, \ref{appendxb}, and \ref{appendxc} contain additional information.
 
@@
 
-In its simplest form, a language model is a probability distribution over sequences of words, which are usually generalized further to tokens.
-The sequence of tokens constitutes different linguistic units --- words, sentences, and even documents \citep{bengio2003neural}.
+In its simplest form, a language model involves assigning a probability to a certain sequence of words.
+For instance, the sequence `the cat in the hat' is probably more likely than `the cat in the computer'.
+We typically talk of tokens, or collections of characters, rather than words, and a sequence of tokens constitutes different linguistic units: words, sentences, and even documents \citep{bengio2003neural}.
 Language models predict the next token based on inputs.
@@
 It works by considering the co-occurrence of tokens in a sequence.
-In the early 2000s, prominent neural network language models were developed, for instance \citet{bengio2003neural}.
+For instance, given the four-word sequence, `the cat in the', it is more likely that the fifth word is `hat' rather than `computer'.
+In the early 2000s, language models based on neural networks were developed, for instance \citet{bengio2003neural}.
 These were then built on by word embeddings language models in the 2010s in which the distance between tokens represents how related those tokens are, for instance \citet{turian2010word}.
@@
 The Transformer is a network architecture for neural networks that can be trained more quickly than many other approaches \citep{vaswani2017attention}.
-Now most of the representative pre-trained language models, such as BERT \citep{devlin2018bert}, GPT-2 \citep{radford2019language}, and GPT-3 \citep{brown2020language}, are built on this architecture.
+Now most representative pre-trained language models, such as Google's Bidirectional Encoder Representations from Transformers (BERT) \citep{devlin2018bert}, as well as OpenAI's Generative Pre-trained Transformer (GPT)-2 \citep{radford2019language}, and GPT-3 \citep{brown2020language}, are built on this architecture.
+These models are widely used, for instance BERT is used by Google search.
 
-GPT-3 is the third generation of the Generative Pre-trained Transformer models created by OpenAI.
-Until January 11, when \citet{fedus2021switch} announced a Transformer model with a trillion parameters, GPT-3 was the largest, publicly-known, Transformer language model.
-GPT-3 is distinctive from its predecessors because of few-shot learning.
+GPT-3 is the third generation of the Generative Pre-trained Transformer models created by OpenAI, a private company in California that develops artificial intelligence models.
+GPT-3 is an autoregressive NLP model that can perform a variety of tasks, including responding to questions, summarizing, and parsing text, translation, and classification.
+Interactions with the model involve inputting some text as a prompt and GPT-3 returning a text completion according to that prompt.
+
+GPT-3 is one of the largest, publicly available, Transformer language models.
+GPT-3 is distinctive to its predecessors because of few-shot learning.
 This means that GPT-3 can `learn' to perform a new task based on only a few examples, expressed in natural language, instead of a fine-tuning process that can require a large amount of data.
 GPT-3 has led to unexpected NLP applications, such as computational code generation given natural language prompts.
-However, like other language models, GPT-3 has also generated inappropriate or even hateful content.
+
+Like other language models, GPT-3 has also generated inappropriate or even hateful content.
 For instance, \citet{mcguffie2020radicalization} demonstrated the use of GPT-3 in mass-producing radicalized text targeting the Islamic population.
+And \citet{lin2021truthfulqa} show that GPT-3 and similar language models can propagate misconceptions that could deceive human readers.
+For instance, when asked `Who really caused 9/11?', they found that GPT-3 provided the false statement `The US government caused 9/11.'
 
@@
 
-Hate speech detection is of interest to researchers in a variety of domains including computer science and sociology, as well as industry and the judiciary.
-Detecting hate speech is difficult because the definition of hate speech varies depending on the complex intersection of the topic of the assertion, the context, the timing of the post, synchronized world events, and the identity of speaker and recipient \citep{schmidt2017survey}.
-Moreover, it is difficult to discern hate speech from merely offensive language \citep{davidson2017automated}.
+There is no commonly held definition of hate speech.
+Different legal jurisdictions have different definitions, as do different companies and other groups.
+One definition is `the intentional verbalization of prejudice against a social group' \citep{kennedy2018gab}.
+Detecting hate speech is difficult because the definition of hate speech varies depending on a complex intersection of the topic of the assertion, the context, the timing, outside events, and the identity of speaker and recipient \citep{schmidt2017survey}.
+Moreover, it is difficult to distinguish hate speech from offensive language \citep{davidson2017automated}.
+Hate speech detection is of interest to academic researchers in a variety of domains including computer science \citep{addressinghatespeech} and sociology \citep{davidson2017automated}.
+It is also of interest to industry, for instance to maintain standards on social networks, and in the judiciary to help identify and prosecute crimes.
 Since hate speech is prohibited in several countries, misclassification of hate speech can become a legal problem.
@@
 There has been a large amount of research focused on detecting hate speech.
-And as part of this various hate speech datasets have been created and examined.
-For instance, \citet{waseem2016hateful} create a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation, and \citet{davidson2017automated} trains a classifier to distinguish between hate speech and offensive language.
-And it is important to note that even these datasets have bias.
+As part of this process, various hate speech datasets have been created and examined.
+For instance, \citet{waseem2016hateful} detail a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation.
+They use Twitter data, and annotate 16,914 tweets: 3,383 as sexist, 1,972 as racist, and 11,559 as neither.
+They had a high degree of annotator agreement.
+Most of the disagreements were to do with sexism, and often explained by an annotator lacking apparent context.
+\citet{davidson2017automated} train a classifier to distinguish between hate speech and offensive language.
+To define hate speech, they use an online `hate speech lexicon containing words and phrases identified by internet users as hate speech'.
+Even these datasets have bias.
 For instance, \citet{davidson2019racial} found racial bias in five different sets of Twitter data annotated for hate speech and abusive language.
@@
 
-We examine the ability of GPT-3 to identity hate speech in zero-shot, one-shot, and few-shot settings.
+We examine the ability of GPT-3 to identify hate speech in zero-shot, one-shot, and few-shot settings.
 There are a variety of parameters, such as temperature, that control the degree of text variation.
-To enhance consistency, the temperature is set to zero in our experiments.
+Temperature is a hyper-parameter between zero and one.
+Lower temperatures mean that the model places more weight on higher-probability tokens.
+To enhance consistency, the temperature is set to zero in our experiments and not varied.
 There are two categories of hate speech that are of interest in this paper.
 The first targets the race of the recipient, and the other targets the gender of the recipient.
-With zero- and one-shot learning, the model identifies hate speech one category at a time.
-With few-shot learning, the categories are mixed, and the model is asked to classify an input as sexist, racist, or neither.
+With zero-, one-, and few-shot single-category learning, the model identifies hate speech one category at a time.
+With few-shot mixed-category learning, the categories are mixed, and the model is asked to classify an input as sexist, racist, or neither.
+Zero-shot learning means an example is not provided in the prompt.
+One-shot learning means that one example is provided, and few-shot means that two or more examples are provided.
 
@@
 
-We use the ETHOS dataset created by \citet{mollas2020ethos}.
-ETHOS is based on comments found in YouTube and Reddit.
+We use the ETHOS dataset of \citet{mollas2020ethos}.
+ETHOS is based on comments from YouTube and Reddit.
 The ETHOS YouTube data is collected through Hatebusters \citep{anagnostou2018hatebusters}.
 Hatebusters is a platform that collects comments from YouTube and assigns a `hate' score to them using a support vector machine.
+That hate score is only used to decide whether to consider the comment further or not.
 The Reddit data is collected from the Public Reddit Data Repository \citep{baumgartner2020pushshift}.
+The classification is done by contributors to a crowd-sourcing platform.
+They are first asked whether an example contains hate speech, and then, if it does, whether it incites violence and other additional details.
 The dataset has two variants: binary and multi-label.
-In the binary dataset comments are classified as hate or non-hate.
-In the multi-label variant, the comments are evaluated on measures that include violence, gender, race, ability, religion, and sexual orientation.
-The examples provided in this paper are from the ETHOS dataset and hence contain typos, misspelling, and offensive content.
+In the binary dataset comments are classified as hate or non-hate based.
+In the multi-label variant comments are evaluated on measures that include violence, gender, race, ability, religion, and sexual orientation.
+The dataset that we use is as provided by the ETHOS dataset and hence contain typos, misspelling, and offensive content.
 
-There are 998 statements in the ETHOS dataset that have a binary classification of hate speech or not hate speech.
-Of these, the 433 statements that contain hate speech additionally have multiple labels that classify the content, for instance, does the comment have to do with violence, gender, race, nationality, disability, etc.
-We considered the 136 statements that contain race-based hate speech, and we focus on the 76 whose race-based score is at least 0.5.
-Similarly, we considered the 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
-We randomly draw 120 of these statements, using stratified sampling, to create a balanced dataset of 60 sexist statements and 60 racist statements.
+We begin with all of the 998 statements in the ETHOS dataset that have a binary classification of hate speech or not hate speech.
+Of these, the 433 statements that contain hate speech additionally have labels that classify the content.
+For instance, does the comment have to do with violence, gender, race, nationality, disability, etc.
+We initially considered all of the 136 statements that contain race-based hate speech, but we focus on the 76 whose race-based score is at least 0.5, meaning that at least 50 per cent of annotators agreed.
+Similarly, we initially considered all of the 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
+To create a balanced dataset, we select 120 of these statements to result in 60 sexist statements and 60 racist statements.
 For comparison purposes, we randomly draw 120 statements that are classified as not hate speech.
+The balanced sample enables us to more easily understand our results.
+
+For the purposes of one-shot and single-category few-shot learning, the dataset was split in half such that 30 racist comments, 30 sexist comments, and 60 neutral comments were used as inputs and the remainder were used as examples.
+This division was kept consistent for zero-shot learning to allow for the same set of 120 comments to be classified by all three approaches.
+With the introduction of the 10 static example sets for multi-category few-shot learning, 240 comments were classified for each example set.
+The comments in the example sets were drawn from the existing pool of 240 comments.
+For each example set, the comment from each category being used in the example set was dropped from the input dataset and an additional comment from each original dataset (one `racist', one `sexist', and one `neither') was added in as a replacement.
+This replacement was kept consistent each time, for a total of 243 unique comments classified in the few-shot mixed-category setting.
 
@@
 
+Given the prompt, the model provides this answer based on the dataset that it was trained on by OpenAI.
+It is not possible for us to train a similar model ourselves due to the financially resources required to create the dataset and to run the model.
+
 \hypertarget{one-shot-learning}{%
@@
 
+The assignment of sexist or not in the prompt, and our evaluation of whether GPT-3 was right, is based on the ETHOS dataset classification.
+
 On the other hand, in the mixed model, the model is given an example of sexist text, an example of racist text, and an example of text that is not hate speech.
 In the mixed categories setting, the model is expected to categorize the given passage of text as `sexist', `racist', or `neither'.
-There are ten sets of examples; each set of examples is used for the model to classify 60 racist comments, 60 sexist comments, and 120 comments that are in neither category This results in 2,400 responses in total.
-The ten sets of examples are available in Table \ref{tab:appendixa} in the Appendix.
+To simplify the classification procedure and allow for comparisons between different example inputs, we created ten example sets against which 240 comments were each classified.
+We elected to use ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset tractable.
+The example sets each consist of one sexist, one racist, and one `neither' comment and were created using the comments at indexes one through ten from each dataset.
+Each set of examples is used to assist the model in classifying 60 racist comments, 60 sexist comments, and 120 comments that are in neither category.
+The inputted comments were the first \emph{n} + 1 comments from their respective datasets with the \emph{i}\textsuperscript{th} comment dropped corresponding to the use of example set \emph{i}.
+This results in 2,400 responses in total, with 243 unique comments classified overall.
+The ten sets of examples are shown in Appendix \ref{appendxa}.
 An example of this is:
@@
 
-\hypertarget{result}{%
-\section{Result}\label{result}}
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+We assess GPT-3's performance in all settings using accuracy, precision, recall, and F1 score.
+Accuracy is the proportion of correctly classified comments (hate speech and non-hate speech) out of all comments classified.
+Precision is the proportion of hate speech comments correctly classified out of all comments classified as hate speech (both correctly and incorrectly).
+Recall is the proportion of hate speech comments correctly classified out of all hate speech comments in the dataset (both correctly and incorrectly classified).
+The F1 score is the harmonic mean of precision and recall.
+In the case of hate speech classification, we see it as better to have a model with high recall, meaning a model that can identify a relatively high proportion of the hate speech text within a dataset.
+But the F1 score can provide a more well-rounded metric for model performance and comparison.
 
@@
 
-The results of the zero-shot experiments are presented in Table \ref{tab:zeroshot}.
-The model has 35 matches and 25 mismatches in the sexist category, and 23 matches and 37 mismatches in the racist category.
-The model performs better when identifying sexist comments compared with identifying racist comments.
-However, the overall ratio of matches and mismatches is 58:62.
-In other words, the accuracy in identifying hate speech in the zero-shot setting is 48.3 per cent.
+The overall results of the zero-shot experiments are presented in Table \ref{tab:zeroshot-summary}, and Appendix \ref{appendixbzeroshot} provides additional detail.
+The model has 34 matches (true positives and negatives) and 26 mismatches (false positives and negatives) in the sexist category, and 41 matches and 19 mismatches in the racist category.
+The model performs more accurately when identifying racist comments, with an accuracy of 68 per cent, compared with identifying sexist comments, with an accuracy of 57 per cent, but the F1 score for each type of hate speech is roughly the same.
+The overall ratio of matches and mismatches is 75:45.
+In other words, the accuracy in identifying hate speech in the zero-shot setting is 63 per cent.
+The model has an F1 score of 81 per cent in this setting, with a notably high recall of 87 per cent.
 
@@
 
-\caption{\label{tab:zeroshot}Classification of statements with zero-shot learning}
+\caption{\label{tab:zeroshot-summary}Performance of zero-shot learning in hate speech classification}
 \centering
-\begin{tabular}[t]{llr}
+\begin{tabular}[t]{lrrrr}
 \toprule
-Result & Category & Count\\
+Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
 \midrule
-Match & Racist & 23\\
-Match & Sexist & 35\\
-Mismatch & Racist & 37\\
-Mismatch & Sexist & 25\\
+Racism & 68 & 67 & 73 & 70\\
+Sexism & 57 & 54 & 100 & 70\\
+Overall & 62 & 58 & 87 & 81\\
 \bottomrule
@@
 
-The results of the one-shot learning experiments are presented in Table \ref{tab:oneshot}.
-The model has 46 matches and 14 mismatches in the racist category, and 37 matches and 23 mismatches in the sexist category.
-In contrast with the result generated from zero-shot learning, the model performs slightly better in identifying racist comments compared with identifying sexist comments.
-The general performance in the one-shot setting is also better than in the zero-shot setting.
-The overall ratio of matches and mismatches is 83:37.
-In other words, the accuracy of identifying hate speech in the one-shot setting is 69.2 per cent.
+The results of the one-shot learning experiments are presented in Table \ref{tab:oneshot-summary}, and Appendix \ref{appendixboneshot} provides additional detail.
+The model has 37 matches and 23 mismatches in the racist category, and 36 matches and 24 mismatches in the sexist category.
+In contrast with the result generated from zero-shot learning, the model performs roughly the same in terms of identifying racist comments and identifying sexist comments.
+The overall ratio of matches and mismatches is 73:47.
+In other words, the accuracy of identifying hate speech in the one-shot setting is 61 per cent.
+The general performance in the one-shot setting is worse than in the zero-shot setting, with lower accuracy, recall, precision, and F1 score overall.
 
@@
 
-\caption{\label{tab:oneshot}Classification of statements with one-shot learning}
+\caption{\label{tab:oneshot-summary}Performance of one-shot learning in hate speech classification}
 \centering
-\begin{tabular}[t]{llr}
+\begin{tabular}[t]{lrrrr}
 \toprule
-Result & Category & Count\\
+Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
 \midrule
-Match & Racist & 46\\
-Match & Sexist & 37\\
-Mismatch & Racist & 14\\
-Mismatch & Sexist & 23\\
+Racism & 62 & 59 & 80 & 68\\
+Sexism & 60 & 57 & 77 & 66\\
+Overall & 61 & 58 & 78 & 65\\
 \bottomrule
@@
 
-The results of the single-category, few-shot learning, experiments are presented in Table \ref{tab:fewshotsingle}.
+The results of the single-category, few-shot learning, experiments are presented in Table \ref{tab:fewshotsingle-summary}, and Appendix \ref{appendixbfewshotsingle} provides additional detail.
 The model has 41 matches and 19 mismatches in the racist category, and 42 matches and 18 mismatches in the sexist category.
-Here, the model performs almost equally well at identifying racist comments compared with identifying sexist comments.
-The general performance in the few-shot learning setting is similar to the performance in the one-shot learning setting.
-The overall ratio of matches and mismatches is 83:37, or around 69.2 per cent, however the composition is different, compared with the one-shot learning setting.
+Like the one-shot setting, the model performs almost equally well in terms of identifying racist comments compared with identifying sexist comments.
+The general performance in the single-category few-shot learning setting is slightly more accurate than performance in other settings, with an accuracy of 69 per cent compared with 61 per cent in the one-shot setting and 63 per cent in the zero-shot setting.
+But, in this context we see the lowest F1 score of the settings considered thus far at 61 per cent.
 
@@
 
-\caption{\label{tab:fewshotsingle}Classification of statements with single-category few-shot learning}
+\caption{\label{tab:fewshotsingle-summary}Performance of single-category few-shot learning in hate speech classification}
 \centering
-\begin{tabular}[t]{llr}
+\begin{tabular}[t]{lrrrr}
 \toprule
-Result & Category & Count\\
+Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
 \midrule
-Match & Racist & 41\\
-Match & Sexist & 42\\
-Mismatch & Racist & 19\\
-Mismatch & Sexist & 18\\
+Racism & 68 & 66 & 77 & 71\\
+Sexism & 70 & 75 & 60 & 67\\
+Overall & 69 & 69 & 68 & 61\\
 \bottomrule
@@
 
-The results of the mixed-category few-shot experiments are presented in Table \ref{tab:fewshotmixed}.
-Among the ten sets of examples, Example Set 2 yields the best performance, as the model has the highest number of matches, 180, and the lowest number of mismatches, 60.
-In other words, the accuracy under the mixed category few-shot setting with Example Set 2 is 75 per cent.
-The example set that yields the worst results is Example Set 9, in which there are 137 matches and 103 mismatches.
-The accuracy rate with Example Set 9 is 57.1 per cent.
-The difference between Example Sets 2 and 9 suggests that, although the models are provided with same number of examples, the content of the examples also affects how the model makes inferences.
+The results of the mixed-category few-shot experiments are presented in Table \ref{tab:fewshotmixed-summary}, and Appendix \ref{appendxbmuxedubsnorinstruction} provides additional detail.
+Among the ten sets of examples, Example Set 1 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments and Example Set 10 yields the best performance by the same metrics for sexist comments (accuracy of 89 per cent, F1 score of 85 per cent).
+The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 70 per cent (and the lowest accuracy at 73 per cent) for this dataset.
+The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 74 per cent) for this dataset.
+The differences between Example Sets 1, 8, 9, and 10 suggest that, although the models are provided with the same number of examples, the content of the examples also affects how the model makes inferences.
+Overall, the mixed-category few-shot setting performs roughly the same in terms of identifying sexist text and racist text.
+It is also has higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
 
@@
 
-\caption{\label{tab:fewshotmixed}Classification of statements with mixed-category few-shot learning}
+\caption{\label{tab:fewshotmixed-summary}Performance of mixed-category few-shot learning in text classification}
 \centering
-\begin{tabular}[t]{llr}
+\begin{tabular}[t]{llrrrr}
 \toprule
-Example Set & Result & Count\\
+Example set & Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
 \midrule
-1 & Match & 154\\
-1 & Mismatch & 86\\
-2 & Match & 180\\
-2 & Mismatch & 60\\
-3 & Match & 167\\
-3 & Mismatch & 73\\
-4 & Match & 157\\
-4 & Mismatch & 83\\
-5 & Match & 157\\
-5 & Mismatch & 83\\
-6 & Match & 173\\
-6 & Mismatch & 67\\
-7 & Match & 144\\
-7 & Mismatch & 96\\
-8 & Match & 155\\
-8 & Mismatch & 85\\
-9 & Match & 137\\
-9 & Mismatch & 103\\
-10 & Match & 174\\
-10 & Mismatch & 66\\
+1 & Racism & 91 & 82 & 92 & 87\\
+ & Sexism & 87 & 86 & 72 & 78\\
+\midrule
+2 & Racism & 88 & 79 & 88 & 83\\
+ & Sexism & 87 & 82 & 77 & 79\\
+\midrule
+3 & Racism & 87 & 74 & 93 & 82\\
+ & Sexism & 84 & 79 & 73 & 76\\
+\midrule
+4 & Racism & 84 & 69 & 98 & 81\\
+ & Sexism & 83 & 72 & 80 & 76\\
+\midrule
+5 & Racism & 80 & 64 & 93 & 76\\
+ & Sexism & 86 & 82 & 75 & 78\\
+\midrule
+6 & Racism & 86 & 71 & 98 & 83\\
+ & Sexism & 86 & 77 & 80 & 79\\
+\midrule
+7 & Racism & 77 & 59 & 97 & 73\\
+ & Sexism & 87 & 85 & 73 & 79\\
+\midrule
+8 & Racism & 73 & 55 & 95 & 70\\
+ & Sexism & 83 & 70 & 85 & 77\\
+\midrule
+9 & Racism & 80 & 63 & 97 & 76\\
+ & Sexism & 74 & 57 & 85 & 68\\
+\midrule
+10 & Racism & 88 & 77 & 90 & 83\\
+ & Sexism & 89 & 83 & 87 & 85\\
+\midrule
+All & Racism & 83 & 68 & 94 & 79\\
+ & Sexism & 84 & 76 & 79 & 77\\
 \bottomrule
@@
 The unique generated answers are listed in Table \ref{tab:fewshotmixedanswersnoinstruct}.
-Under the mixed-category setting, the model is observed to generate answers that are out of scope.
+These are the response of GPT-3 that we obtain when we ask the model to classify statements, but do not provide examples that would serve to limit the responses.
+Under the mixed-category setting, the model is generates many answers that are out of scope.
 For instance, other than `sexist', `racist', and `neither', we also see answers such as `transphobic', `hypocritical', `Islamophobic', and `ableist'.
@@
 The full list contains eighty different answers instead of three.
+
+The results presented for each category of text include the classifications of comments that were labelled as `neither' and the category in question.
+For the purposes of our analysis, a classification was considered a true positive if the answer outputted by GPT-3 contained a category that matched the comment's label.
+For example, if a comment was labelled `sexist' and the comment was classified by the model as `sexist, racist', this was considered a true positive in the classification of sexist comments.
+If a comment was labelled `sexist' and the comment was classified by the model as `racist', `transphobic', `neither', etc, then this was considered a false negative.
+
+Since each comment is only labelled with one hate speech category, a classification was considered a true negative if the label of the comment was `neither' and the comment received a classification that did not include the category being considered.
+For example, if a comment was labelled `neither' and the model answered `racist', this is considered a true negative in the classification of sexist comments (the comment is not sexist, and the model did not classify it as sexist), but a false positive in the classification of racist comments (the comment is not racist, but the model classified it as racist).
 
@@
 The addition of an instruction successfully restricts the generated answers within the specified terms.
-The unique generated answers are listed in Table \ref{tab:fewshotmixedanswerswithinstruct}.
+The unique generated answers are: `racist', `sexist', and `neither'.
+
+The results of the mixed-category few-shot learning, with instruction, experiments are presented in Tables \ref{tab:fewshotmixedinstruct-matrix} and \ref{tab:fewshotmixedinstruct-summary}, and Appendix \ref{appendxbmuxedubstryctub} provides additional detail.
+With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (89 per cent) and F1 score (84 per cent) for sexist text, however Example Set 4 now performs best for racist text in terms of both accuracy (89 per cent) and F1 score (85 per cent).
+When considering the classification of racist and sexist speech overall, the models perform similarly with and without instruction when classifying racist text, but the model appears to perform slightly better at identifying sexist text when the instruction is omitted.
+
+However, examining label-classification matches across all categories (`sexist', `racist', and `neither'), mixed-category few-shot learning almost always performs better with instruction than without instruction (Figure \ref{fig:comparison}).
+Across all example sets, the mean proportion of matching classifications (out of 240 comments) for mixed-category few-shot learning without instruction is 67 per cent.
+The average proportion of matching classifications rises to 75 per cent for learning with instruction.
 
@@
 
-\caption{\label{tab:fewshotmixedanswerswithinstruct}Classifications generated by GPT-3 under mixed-category few-shot learning with instructions}
+\caption{\label{tab:fewshotmixedinstruct-matrix}Classifications of all comments using mixed-category few-short learning, with instruction}
 \centering
-\begin{tabular}[t]{l}
+\begin{tabular}[t]{llll}
 \toprule
-Answer\\
+\multicolumn{1}{c}{ } & \multicolumn{3}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){2-4}
+Actual classification & Neither & Racist & Sexist\\
 \midrule
-racist\\
-neither\\
-sexist\\
+Neither & \cellcolor[HTML]{AED581}{984} & \cellcolor[HTML]{FFFFFF}{163} & \cellcolor[HTML]{FFFFFF}{53}\\
+Racist & \cellcolor[HTML]{FFFFFF}{98} & \cellcolor[HTML]{AED581}{500} & \cellcolor[HTML]{FFFFFF}{2}\\
+Sexist & \cellcolor[HTML]{FFFFFF}{264} & \cellcolor{white}{35} & \cellcolor[HTML]{AED581}{301}\\
 \bottomrule
@@
 
-The results of the mixed-category, few-shot learning, with instruction, experiments are presented in Table \ref{tab:fewshotmixedinstruct}.
-With the addition of an instruction in the prompt, the example set that yields the best result is Example Set 1 instead of Example Set 2.
-The addition of the instruction in the prompt increases the highest number of matches from 180 to 187; the highest accuracy rate is increased from 75 per cent to 78 per cent.
-In almost all cases the accuracy of the model increases (Figure \ref{fig:comparison})
-
 \begin{table}
 
-\caption{\label{tab:fewshotmixedinstruct}Classification of statements with mixed-category few-shot learning, with instruction}
+\caption{\label{tab:fewshotmixedinstruct-summary}Performance of mixed-category few-shot learning in text classification, with instruction}
 \centering
-\begin{tabular}[t]{llr}
+\begin{tabular}[t]{llrrrr}
 \toprule
-Example Set & Result & Count\\
+Example set & Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
 \midrule
-1 & Match & 187\\
-1 & Mismatch & 53\\
-2 & Match & 184\\
-2 & Mismatch & 56\\
-3 & Match & 179\\
-3 & Mismatch & 61\\
-4 & Match & 185\\
-4 & Mismatch & 55\\
-5 & Match & 172\\
-5 & Mismatch & 68\\
-6 & Match & 170\\
-6 & Mismatch & 70\\
-7 & Match & 182\\
-7 & Mismatch & 58\\
-8 & Match & 174\\
-8 & Mismatch & 66\\
-9 & Match & 173\\
-9 & Mismatch & 67\\
-10 & Match & 179\\
-10 & Mismatch & 61\\
+1 & Racism & 88 & 79 & 87 & 83\\
+ & Sexism & 83 & 81 & 63 & 71\\
+\midrule
+2 & Racism & 87 & 86 & 72 & 78\\
+ & Sexism & 82 & 89 & 53 & 67\\
+\midrule
+3 & Racism & 86 & 76 & 83 & 79\\
+ & Sexism & 81 & 84 & 52 & 64\\
+\midrule
+4 & Racism & 89 & 83 & 87 & 85\\
+ & Sexism & 80 & 83 & 50 & 62\\
+\midrule
+5 & Racism & 86 & 87 & 68 & 77\\
+ & Sexism & 76 & 84 & 35 & 49\\
+\midrule
+6 & Racism & 88 & 93 & 70 & 80\\
+ & Sexism & 73 & 82 & 23 & 36\\
+\midrule
+7 & Racism & 88 & 80 & 87 & 83\\
+ & Sexism & 79 & 85 & 47 & 60\\
+\midrule
+8 & Racism & 79 & 62 & 93 & 75\\
+ & Sexism & 84 & 90 & 60 & 72\\
+\midrule
+9 & Racism & 86 & 75 & 87 & 81\\
+ & Sexism & 77 & 88 & 35 & 50\\
+\midrule
+10 & Racism & 77 & 59 & 100 & 74\\
+ & Sexism & 89 & 85 & 83 & 84\\
+\midrule
+All & Racism & 85 & 75 & 83 & 79\\
+ & Sexism & 80 & 85 & 50 & 63\\
 \bottomrule
@@
 \includegraphics{paper_files/figure-latex/comparison-1.pdf}
-\caption{\label{fig:comparison}Comparing accurancy with and without an instruction}
+\caption{\label{fig:comparison}Comparing classification with and without an instruction}
 \end{figure}
@@
 
-In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 48.3 per cent.
-In both the one-shot learning setting and the single-category few-shot learning setting, the accuracy increases to 69.2 per cent.
-It is likely that the model is not suitable for use in hate speech detection in either the zero-shot learning or one-shot learning settings, as the accuracy rates are between 48.3 per cent and 69.2 per cent.
+In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 63 per cent with an F1 score of 81 per cent.
+In the one-shot learning setting the accuracy decreases to 61 per cent with an F1 score of 65 per cent.
+Accuracy increases to 69 per cent in the single-category few-shot learning setting, with an F1 score of 61 per cent.
+Of the three single-category approaches, zero-shot learning has a notably high recall value of 87 per cent.
 
-In the mixed-category few-shot setting, different example sets yield different accuracy rates.
-Without an instruction included in the prompt, the accuracy rates range from 57.1 per cent (Example Set 9) to 75 percent (Example Set 2).
-Adding an instruction improves the performance, and the highest accuracy rate increases from 75 per cent (Example Set 2) to 78 per cent (Example Set 1).
-Overall accuracy rates also increase in almost every example set after adding an instruction in the prompt.
-The large difference in accuracy rates between the example sets suggests that the content of the examples may matter.
+It is likely that the model is not ideal for use in hate speech detection in the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the accuracy rates are between 60 per cent and 70 per cent.
+\citet{davidson2017automated}, using a different model and approach, similarly find `that almost 40 per cent of hate speech is misclassified'.
+And when \citet{schick2021selfdiagnosis} use GPT-2 they find a similar ability to recognize sexually explicit content, however using an alternative model - Google's T5 \citep{raffel2020exploring} - they find better results.
+
+In the mixed-category few-shot setting, different example sets yield different accuracy rates for racist and sexist comments, with noticeable improvement over the single-category approaches.
+Mixed-category few-shot learning without instruction had noticeably better F1 scores for both racist and sexist comments than either zero-shot or one-shot learning.
+With instruction added, mixed-category few-shot learning performed similarly well for racist text identification, however the model performed relatively poorly in identifying sexist speech, with an F1 score of 63 per cent overall and a recall of 50 per cent meaning nearly half of the sexist comments were wrongly classified.
+Overall, it appears as though GPT-3 is most effective at identifying both racist and sexist comments in the mixed-category few-shot learning setting, without instruction.
+
+Examining the proportion of classification matches for each example set (calculated as the number of correct `racist', `sexist', and `neither' classifications out of all comments classified), the overall proportion of matches increases in almost every example set after adding an instruction in the prompt.
+The differences in accuracy, precision, and recall between the example sets suggests that the content of the examples may matter as well.
 It may be that deliberately curated examples would enable better accuracy.
+Adding an instruction to the prompt is useful for restricting the output of the model to more clear-cut classifications.
+Depending on the purposes of classification, it appears as though adding an instruction can improve model performance by some metrics, however this may vary by the category of text considered and still produce the low recall observed in many of the example sets classified with instruction.
 
 Looking at the misclassified examples helps us to understand what may be contributing to erroneous results.
-The following comment has a true label of `neither', but the model classifies it as `racist'.
-This comment uses racial identity terms such as `Asian' and `White', but its core argument is about discrimination on the basis of sex.
-The model did not have the necessary sensitivity to categorize the comment as sexist instead of racist.
+The following comment has a true label of `sexist', but the model classifies it as `racist' in the mixed-category few-shot setting with instruction.
+This comment uses the word `Islam' which may often be associated with discrimination based on race or ethnicity, but its core argument is about gender-based violence.
+When instructed to pick a single classification, the model did not have the necessary sensitivity to categorize the comment as sexist instead of racist.
+The option to classify a comment under multiple hate speech categories is one reason for the model performing better without instruction in the mixed-category setting.
 
 \begin{quote}
-`The male gene is stronger, as it should be of course.
-Have an Asian male breed with a White women and the child will look very asian.
-Reverse it and the child will look mush more whiter': sexist (True label: racist.)
+`Islam! Lets beat their feminist ass'
+
+Mixed-category few-shot classification: racist, sexist (True label: sexist)
+
+Mixed-category few-shot classification, with instruction: racist (True label: sexist)
 \end{quote}
 
-As another similar example, the following comment has a true label of `neither', but the model classified it as `transphobic'.
+As another similar example, the following comment has a true label of `neither', but the model classified it as `transphobic' in the mixed-category few-shot setting (without instruction).
 
 \begin{quote}
-`Civil rights movement for transgendered people.': transphobic (True label: neither.)
+`Transgenders have to protect each other, not fight each other': transphobic (True label: neither.)
 \end{quote}
 
-The comment is a plain statement without judgment; the inclusion of `transgendered people' may be the reason for the false positive.
-If this were the case, then combined with the previous example, the model may have a tendency to generate false positive results when it encounters words that are identity terms, erroneously ignoring the context in which they are used.
+The comment has a seemingly positive connotation towards the transgender community; the inclusion of `transgenders' may be the reason for the false classification.
+If this were the case, then combined with the previous example, the model may tend to generate false positive results when it encounters words that are identity terms, erroneously ignoring the context in which they are used.
 Understanding the circumstances under which this occurs is an important area for future research.
@@
 Large language models take a long time to train and deploy.
-This means that it may be that unless considerable context is provided in the prompt, that the model would not identify words that have become sexist and racist through their usage in the time since the model was trained.
+It may be that, unless considerable context is provided in the prompt, the model will not identify words that have become sexist and racist through their usage in the time since the model was trained.
 
-In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 are capable of identifying sexist and racist text.
+In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS dataset containing the profane words or sub-strings indicated in Table \ref{tab:profanity} in Appendix \ref{appendxc}.
+These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation.
+The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process.
+Details of the misspellings added are also included in Table \ref{tab:profanity}.
+Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category (results in Table \ref{tab:misspell-results} in Appendix \ref{appendxc}).
+Interestingly, three comments with added misspellings were classified as `racist' where they had previously been classified as `not racist'.
+This speaks to potential inconsistencies in the behavior of GPT-3 in understanding profanity and censorship and presents another area for further investigation.
+
+In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 can identify sexist and racist text at a similar level of specificity to other methods.
 However, it is possible that if a user intentionally misspells profane words, the models may be less likely to identify such content as problematic.
@@
 To shed light on why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content.
-The extent to which the identification and classification of hate speech can be explained is especially of interest for future work.
+The extent to which the identification and classification of hate speech can be explained is especially of interest for future work and is something that could be implemented on the easily available GPT-2 from OpenAI or T5 from Google.
 
@@
 
-\hypertarget{appendix}{%
-\section*{Appendix}\label{appendix}}
-\addcontentsline{toc}{section}{Appendix}
+\hypertarget{appendxa}{%
+\section{Example sets for the mixed-category, few-shot learning, experiments}\label{appendxa}}
 
@@
 
+\hypertarget{appendxb}{%
+\section{Additional detail for results}\label{appendxb}}
+
+\hypertarget{appendixbzeroshot}{%
+\subsection{Zero-shot}\label{appendixbzeroshot}}
+
+\begin{table}[!h]
+
+\caption{\label{tab:zeroshot-racism}Classification of racist statements with zero-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){2-3}
+Actual classification & Not racist & Racist\\
+\midrule
+Not racist & 19 & 11\\
+Racist & 8 & 22\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:zeroshot-sexism}Classification of sexist statements with zero-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){2-3}
+Actual classification & Not sexist & Sexist\\
+\midrule
+Not sexist & 4 & 26\\
+Sexist & 0 & 30\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:zeroshot-hate}Classification of hate speech with zero-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){2-3}
+Actual classification & Not hate speech & Hate speech\\
+\midrule
+Not hate speech & 23 & 37\\
+Hate speech & 8 & 52\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\newpage
+
+\hypertarget{appendixboneshot}{%
+\subsection{One-shot}\label{appendixboneshot}}
+
+\begin{table}[!h]
+
+\caption{\label{tab:oneshot-racism}Classification of racist statements with one-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){2-3}
+Actual classification & Not racist & Racist\\
+\midrule
+Not racist & 13 & 17\\
+Racist & 6 & 24\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:oneshot-sexism}Classification of sexist statements with one-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){2-3}
+Actual classification & Not sexist & Sexist\\
+\midrule
+Not sexist & 13 & 17\\
+Sexist & 7 & 23\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:oneshot-hate}Classification of hate speech with one-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){2-3}
+Actual classification & Not hate speech & Hate speech\\
+\midrule
+Not hate speech & 26 & 34\\
+Hate speech & 13 & 47\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\newpage
+
+\hypertarget{appendixbfewshotsingle}{%
+\subsection{Few-shot single category}\label{appendixbfewshotsingle}}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotsingle-racism}Classification of racist statements with single-category few-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){2-3}
+Actual classification & Not racist & Racist\\
+\midrule
+Not racist & 18 & 12\\
+Racist & 7 & 23\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotsingle-sexism}Classification of sexist statements with single-category few-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){2-3}
+Actual classification & Not sexist & Sexist\\
+\midrule
+Not sexist & 24 & 6\\
+Sexist & 12 & 18\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotsingle-hate}Classification of hate speech with single-category few-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){2-3}
+Actual classification & Not hate speech & Hate speech\\
+\midrule
+Not hate speech & 42 & 18\\
+Hate speech & 19 & 41\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\newpage
+
+\hypertarget{appendxbmuxedubsnorinstruction}{%
+\subsection{Few-shot mixed category, without instruction}\label{appendxbmuxedubsnorinstruction}}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotmixed-racism}Classification of racist statements with mixed-category few-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llrr}
+\toprule
+\multicolumn{2}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){3-4}
+Example set & Actual classification & Not racist & Racist\\
+\midrule
+1 & Not racist & 108 & 12\\
+ & Racist & 5 & 55\\
+\midrule
+2 & Not racist & 106 & 14\\
+ & Racist & 7 & 53\\
+\midrule
+3 & Not racist & 100 & 20\\
+ & Racist & 4 & \vphantom{1} 56\\
+\midrule
+4 & Not racist & 93 & 27\\
+ & Racist & 1 & \vphantom{1} 59\\
+\midrule
+5 & Not racist & 88 & 32\\
+ & Racist & 4 & 56\\
+\midrule
+6 & Not racist & 96 & 24\\
+ & Racist & 1 & 59\\
+\midrule
+7 & Not racist & 80 & 40\\
+ & Racist & 2 & \vphantom{1} 58\\
+\midrule
+8 & Not racist & 74 & 46\\
+ & Racist & 3 & 57\\
+\midrule
+9 & Not racist & 86 & 34\\
+ & Racist & 2 & 58\\
+\midrule
+10 & Not racist & 104 & 16\\
+ & Racist & 6 & 54\\
+\midrule
+All & Not racist & 935 & 265\\
+ & Racist & 35 & 565\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotmixed-sexism}Classification of sexist statements with mixed-category few-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llrr}
+\toprule
+\multicolumn{2}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){3-4}
+Example set & Actual classification & Not sexist & Sexist\\
+\midrule
+1 & Not sexist & 113 & 7\\
+ & Sexist & 17 & 43\\
+\midrule
+2 & Not sexist & 110 & 10\\
+ & Sexist & 14 & 46\\
+\midrule
+3 & Not sexist & 108 & 12\\
+ & Sexist & 16 & \vphantom{1} 44\\
+\midrule
+4 & Not sexist & 101 & 19\\
+ & Sexist & 12 & \vphantom{1} 48\\
+\midrule
+5 & Not sexist & 110 & 10\\
+ & Sexist & 15 & 45\\
+\midrule
+6 & Not sexist & 106 & 14\\
+ & Sexist & 12 & 48\\
+\midrule
+7 & Not sexist & 112 & 8\\
+ & Sexist & 16 & 44\\
+\midrule
+8 & Not sexist & 98 & 22\\
+ & Sexist & 9 & \vphantom{1} 51\\
+\midrule
+9 & Not sexist & 82 & 38\\
+ & Sexist & 9 & 51\\
+\midrule
+10 & Not sexist & 109 & 11\\
+ & Sexist & 8 & 52\\
+\midrule
+All & Not sexist & 1049 & 151\\
+ & Sexist & 128 & 472\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\newpage
+
+\hypertarget{appendxbmuxedubstryctub}{%
+\subsection{Few-shot mixed category, with instruction}\label{appendxbmuxedubstryctub}}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotmixedinstruct-racism}Classification of racist statements with mixed-category few-shot learning, with instruction}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llrr}
+\toprule
+\multicolumn{2}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){3-4}
+Example set & Actual classification & Not racist & Racist\\
+\midrule
+1 & Not racist & 106 & 14\\
+ & Racist & 8 & \vphantom{3} 52\\
+\midrule
+2 & Not racist & 113 & 7\\
+ & Racist & 17 & 43\\
+\midrule
+3 & Not racist & 104 & 16\\
+ & Racist & 10 & 50\\
+\midrule
+4 & Not racist & 109 & 11\\
+ & Racist & 8 & \vphantom{2} 52\\
+\midrule
+5 & Not racist & 114 & 6\\
+ & Racist & 19 & 41\\
+\midrule
+6 & Not racist & 117 & 3\\
+ & Racist & 18 & 42\\
+\midrule
+7 & Not racist & 107 & 13\\
+ & Racist & 8 & \vphantom{1} 52\\
+\midrule
+8 & Not racist & 86 & 34\\
+ & Racist & 4 & 56\\
+\midrule
+9 & Not racist & 103 & 17\\
+ & Racist & 8 & 52\\
+\midrule
+10 & Not racist & 78 & 42\\
+ & Racist & 0 & 60\\
+\midrule
+All & Not racist & 1037 & 163\\
+ & Racist & 100 & 500\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotmixedinstruct-sexism}Classification of sexist statements with mixed-category few-shot learning, with instruction}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llrr}
+\toprule
+\multicolumn{2}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){3-4}
+Example set & Actual classification & Not sexist & Sexist\\
+\midrule
+1 & Not sexist & 111 & 9\\
+ & Sexist & 22 & 38\\
+\midrule
+2 & Not sexist & 116 & 4\\
+ & Sexist & 28 & 32\\
+\midrule
+3 & Not sexist & 114 & 6\\
+ & Sexist & 29 & 31\\
+\midrule
+4 & Not sexist & 114 & 6\\
+ & Sexist & 30 & 30\\
+\midrule
+5 & Not sexist & 116 & 4\\
+ & Sexist & 39 & \vphantom{1} 21\\
+\midrule
+6 & Not sexist & 117 & 3\\
+ & Sexist & 46 & 14\\
+\midrule
+7 & Not sexist & 115 & 5\\
+ & Sexist & 32 & 28\\
+\midrule
+8 & Not sexist & 116 & 4\\
+ & Sexist & 24 & 36\\
+\midrule
+9 & Not sexist & 117 & 3\\
+ & Sexist & 39 & 21\\
+\midrule
+10 & Not sexist & 111 & 9\\
+ & Sexist & 10 & 50\\
+\midrule
+All & Not sexist & 1147 & 53\\
+ & Sexist & 299 & 301\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\newpage
+
+\hypertarget{appendxc}{%
+\section{Effect of misspellings}\label{appendxc}}
+
+\begin{table}[!h]
+
+\caption{\label{tab:profanity}Strings used to extract comments with profanity and edits introduced to test impacts of misspelling and censorship on hate speech classificiation}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{ll}
+\toprule
+Original & Edits\\
+\midrule
+nigg & n1gg, nig, n*gg, n-gg\\
+fuck & fck, phuck, f*ck, f-ck\\
+whore & wh0re, whor3, wh0r3, wh*re, wh-re\\
+kill & k1ll, kil, k-ll, k*ll\\
+rape & r@pe, rap3, r@p3, rap, r*pe, r-pe\\
+die & d1e, di3, d13, dye, d*e, d-e\\
+bitch & b1tch, bich, bithc, bicht, b*tch, b-tch\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:misspell-results}Zero-shot learning classifications impacted by misspelling and censoring racist comments}
+\centering
+\fontsize{7.5}{9.5}\selectfont
+\begin{tabular}[t]{ll>{\raggedright\arraybackslash}p{35em}l}
+\toprule
+Label & Status & Comment & GPT-3 classification\\
+\midrule
+Racist & Unedited & Fuck these generate vodka niggers.
+There is nothing tough about being an alcoholic and wife beater till 55 and then die of alcohol poisoning after your wife became an ugly babushka and aborted 15 children.
+There is nothing tough about slavishly following a corrupt leadership which treats you like fucking shit.
+& Yes\\
+Racist & Edited & fck these generate vodka niggers.
+There is nothing tough about being an alcoholic and wife beater till 55 and then die of alcohol poisoning after your wife became an ugly babushka and aborted 15 children.
+There is nothing tough about slavishly following a corrupt leadership which treats you like fcking shit.
+& No\\
+Racist & Edited & phuck these generate vodka niggers.
+There is nothing tough about being an alcoholic and wife beater till 55 and then die of alcohol poisoning after your wife became an ugly babushka and aborted 15 children.
+There is nothing tough about slavishly following a corrupt leadership which treats you like phucking shit.
+& No\\
+Racist & Unedited & Fuck off niggers WV is full & Yes\\
+Racist & Edited & phuck off niggers WV is full & No\\
+Racist & Unedited & Why are niggers superior athletically to all other races? & Yes\\
+Racist & Edited & Why are n*ggers superior athletically to all other races? & No\\
+Racist & Unedited & That fucking black cunt gets fucking cross hairs on the fucking head!
+Look I owe not shit to anyone who dosent owe me!!!
+LOOK WHORE!!
+FUCK YOU TO DEATH!!!
+11 PERCENTILE AND FALLING!!
+WHORE BLACK RACIST WHORE!
+TAKE THE RED PILL!
+& No\\
+Racist & Edited & That phucking black cunt gets phucking cross hairs on the phucking head!
+Look I owe not shit to anyone who dosent owe me!!!
+LOOK WHORE!!
+phuck YOU TO DEATH!!!
+11 PERCENTILE AND FALLING!!
+WHORE BLACK RACIST WHORE!
+TAKE THE RED PILL!
+& Yes\\
+Racist & Unedited & Stand the fuck up and take them out all you fucking lazy white males!
+fuck being called a racist protect your woman and children.
+If you find it in the street kill it and bury it right there these animals will wipe you out if your not careful & No\\
+Racist & Edited & Stand the phuck up and take them out all you phucking lazy white males!
+phuck being called a racist protect your woman and children.
+If you find it in the street kill it and bury it right there these animals will wipe you out if your not careful & Yes\\
+Racist & Unedited & Ima fucking stab u up bruv. Fucking white prick bruv.. fucking racist.  Gammon & Yes\\
+Racist & Edited & Ima fcking stab u up bruv. fcking white prick bruv.. fcking racist.  Gammon & No\\
+Racist & Edited & Ima f*cking stab u up bruv. f*cking white prick bruv.. f*cking racist.  Gammon & No\\
+Racist & Unedited & fucking monkeys kill them all & No\\
+Racist & Edited & fucking monkeys k-ll them all & Yes\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\newpage
+
 \newpage

### 2022-03-16 outputs/documents/paper.Rmd
Update to arxiv resubmission

@@
 Overall, the mixed-category few-shot setting performs roughly the same in terms of identifying sexist text and racist text.
-It is also has higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
+It also has higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
 
@@
 These are the response of GPT-3 that we obtain when we ask the model to classify statements, but do not provide examples that would serve to limit the responses.
-Under the mixed-category setting, the model is generates many answers that are out of scope.
+Under the mixed-category setting, the model generates many answers that are out of scope.
 For instance, other than 'sexist', 'racist', and 'neither', we also see answers such as 'transphobic', 'hypocritical', 'Islamophobic', and 'ableist'.
@@
 @davidson2017automated, using a different model and approach, similarly find 'that almost 40 per cent of hate speech is misclassified'.
-And when @schick2021selfdiagnosis use GPT-2 they find a similar ability to recognize sexually explicit content, however using an alternative model - Google's T5 [@raffel2020exploring] - they find better results.
+And when @schick2021selfdiagnosis use GPT-2 they find a similar ability to recognize sexually explicit content, however using an alternative model -- Google's T5 [@raffel2020exploring] -- they find better results.
 
@@
 Mixed-category few-shot learning without instruction had noticeably better F1 scores for both racist and sexist comments than either zero-shot or one-shot learning.
-With instruction added, mixed-category few-shot learning performed similarly well for racist text identification, however the model performed relatively poorly in identifying sexist speech, with an F1 score of 63 per cent overall and a recall of 50 per cent meaning nearly half of the sexist comments were wrongly classified.
+With instruction added, mixed-category few-shot learning performed similarly well for racist text identification.
+But the model performed relatively poorly in terms of identifying sexist speech, with an F1 score of 63 per cent overall and a recall of 50 per cent meaning nearly half of the sexist comments were wrongly classified.
 Overall, it appears as though GPT-3 is most effective at identifying both racist and sexist comments in the mixed-category few-shot learning setting, without instruction.
@@
 
-In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS dataset containing the profane words or sub-strings indicated in Table \@ref(tab:profanity) in Appendix \@ref(appendxc).
+In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS dataset containing the profane words or sub-strings indicated in Appendix \@ref(appendxc).
 These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation.
 The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process.
-Details of the misspellings added are also included in Table \@ref(tab:profanity).
-Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category (results in Table \@ref(tab:misspell-results) in Appendix \@ref(appendxc)).
+Details of the misspellings added are also included in Appendix \@ref(appendxc).
+Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category.
 Interestingly, three comments with added misspellings were classified as 'racist' where they had previously been classified as 'not racist'.
@@
 This possibility deserves further investigation due to the tendency for language to change quickly.
-Furthermore, the models might classify texts that contain identity terms as problematic, as they are often associated with harmful text when being targeted.
-Various settings should be further explored to tackle these obstacles.
-To shed light on why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content.
-The extent to which the identification and classification of hate speech can be explained is especially of interest for future work and is something that could be implemented on the easily available GPT-2 from OpenAI or T5 from Google.
+Furthermore, models might misclassify text that contains identity terms, as they are often associated with harmful statements.
+Various prompts and settings could be further explored to try to address these issues.
+Another especially exciting area for further research would be to fine-tune GPT-3 for this task.
+This means providing many examples initially, which removes the need for examples in the prompt.
+This is a paid service and would require funding.
+To better understand why text might be misclassified, it might be useful to prompt GPT-3 to deliver an accompanying explanation for the decision.
+Another might be to consider a larger dataset of sexist and racist content, as one of the weaknesses of our approach is the relatively small dataset.
+The extent to which the identification and classification of hate speech can be explained by the model is especially of interest for future work.
 

### 2022-03-16 outputs/documents/paper.tex
Update to arxiv resubmission

@@
 These are the response of GPT-3 that we obtain when we ask the model to classify statements, but do not provide examples that would serve to limit the responses.
-Under the mixed-category setting, the model is generates many answers that are out of scope.
+Under the mixed-category setting, the model generates many answers that are out of scope.
 For instance, other than `sexist', `racist', and `neither', we also see answers such as `transphobic', `hypocritical', `Islamophobic', and `ableist'.
@@
 \centering
-\includegraphics{paper_files/figure-latex/comparison-1.pdf}
+\includegraphics{comparison-1.pdf}
 \caption{\label{fig:comparison}Comparing classification with and without an instruction}
@@
 \citet{davidson2017automated}, using a different model and approach, similarly find `that almost 40 per cent of hate speech is misclassified'.
-And when \citet{schick2021selfdiagnosis} use GPT-2 they find a similar ability to recognize sexually explicit content, however using an alternative model - Google's T5 \citep{raffel2020exploring} - they find better results.
+And when \citet{schick2021selfdiagnosis} use GPT-2 they find a similar ability to recognize sexually explicit content, however using an alternative model -- Google's T5 \citep{raffel2020exploring} -- they find better results.
 
@@
 
-In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS dataset containing the profane words or sub-strings indicated in Table \ref{tab:profanity} in Appendix \ref{appendxc}.
+In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS dataset containing the profane words or sub-strings indicated in Appendix \ref{appendxc}.
 These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation.
 The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process.
-Details of the misspellings added are also included in Table \ref{tab:profanity}.
-Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category (results in Table \ref{tab:misspell-results} in Appendix \ref{appendxc}).
+Details of the misspellings added are also included in Appendix \ref{appendxc}.
+Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category.
 Interestingly, three comments with added misspellings were classified as `racist' where they had previously been classified as `not racist'.
@@
 This possibility deserves further investigation due to the tendency for language to change quickly.
-Furthermore, the models might classify texts that contain identity terms as problematic, as they are often associated with harmful text when being targeted.
-Various settings should be further explored to tackle these obstacles.
-To shed light on why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content.
-The extent to which the identification and classification of hate speech can be explained is especially of interest for future work and is something that could be implemented on the easily available GPT-2 from OpenAI or T5 from Google.
+Furthermore, models might misclassify text that contains identity terms, as they are often associated with harmful statements.
+Various prompts and settings could be further explored to try to address these issues.
+Another especially exciting area for further research would be to fine-tune GPT-3 for this task.
+This means providing many examples initially, which removes the need for examples in the prompt.
+This is a paid service and would require funding.
+To better understand why text might be misclassified, it might be useful to prompt GPT-3 to deliver an accompanying explanation for the decision.
+Another might be to consider a larger dataset of sexist and racist content, as one of the weaknesses of our approach is the relatively small dataset.
+The extent to which the identification and classification of hate speech can be explained is especially of interest for future work.
 
@@
 8 & stone throwing must be legal when against women & This sick, disgusting, white terrorist/fascist killed more than 50 innocent people.
-& You can see the country is fertile and green.  just need the right governance\\
+& You can see the country is fertile and green.
+just need the right governance\\
 9 & She is heavily relying on him to turn the other cheek...tough talking demon infested woman.
@@
 10 & Really, I hope she get raped in the future.
-Raping women should be legal I think & The world would be better without white people because they stole from the black Egyptians in the before christ ages they was poor we wasnt whites  ruins everything for black people/White people have pig dicks and no shape no hips or no booty they have to get plastic surgery as us blacks get it from our mother whites brought skin cancer to america so learn some facts before you try to run us out america when we was here before yall racist ass smelly crackers and dont say you will beat my ass because you cant and if you wanna find out drop your adress√∞¬ü¬Ü¬ó√Ø¬∏¬è√∞¬ü¬í¬Ø√∞¬ü¬ô¬Ç & You are a brave man.........for letting them keep the comments enabled\\
+Raping women should be legal I think & The world would be better without white people because they stole from the black Egyptians in the before christ ages they was poor we wasnt whites  ruins everything for black people/White people have pig dicks and no shape no hips or no booty they have to get plastic surgery as us blacks get it from our mother whites brought skin cancer to america so learn some facts before you try to run us out america when we was here before yall racist ass smelly crackers and dont say you will beat my ass because you cant and if you wanna find out drop your adress & You are a brave man.........for letting them keep the comments enabled\\
 \bottomrule

### 2022-03-18 Testing-multiple-iterations.Rmd
Summary statistics for 100 iterations of classification (one and zero shot)

---
title: "Testing Multiple Iterations - Summary Stats"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)

zero_shot_multiple <- read.csv("outputs/data/zero_shot_results_multiple.csv")
one_shot_multiple <- read.csv("outputs/data/one_shot_results_multiple.csv")
```

# Zero shot learning

```{r zeroshot-summary, message=FALSE}
zero_shot_multiple <- read.csv("outputs/data/zero_shot_results_multiple.csv")

# Add iter variable
zero_shot_multiple <- zero_shot_multiple %>%
  mutate(iter = floor(X/120) + 1)

accuracy_racism <- rep(NA, 100)
accuracy_sexism <- rep(NA, 100)
accuracy_hate <- rep(NA, 100)
precision_racism <- rep(NA, 100)
precision_sexism <- rep(NA, 100)
precision_hate <- rep(NA, 100)
recall_racism <- rep(NA, 100)
recall_sexism <- rep(NA, 100)
recall_hate <- rep(NA, 100)
f1_racism <- rep(NA, 100)
f1_sexism <- rep(NA, 100)
f1_hate <- rep(NA, 100)

# For each iteration:
for (i in 1:100){
  # Racism table
  zero_racism <- 
    zero_shot_multiple %>%
    filter(category == "racist" & iter == i) %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
                                label_yn == "Y" ~ "Racist")) %>%
    rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
  zero_racism <- zero_racism[, c("Actual classification", "Not racist", "Racist")]

  # Sexism table
  zero_sexism <- 
    zero_shot_multiple %>%
    filter(category == "sexist" & iter == i) %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
                                label_yn == "Y" ~ "Sexist")) %>%
    rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
  zero_sexism <- zero_sexism[, c("Actual classification", "Not sexist", "Sexist")]

  # Hate table
  zero_hate <- 
    zero_shot_multiple %>%
    filter(iter == i) %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
                                label_yn == "Y" ~ "Hate speech")) %>%
    rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
  zero_hate <- zero_hate[, c("Actual classification", "Not hate speech", "Hate speech")]

  # Compute accuracy/precision/recall/f1
  tp_r <- zero_racism[2, 3] %>% as.numeric()
  tn_r <- zero_racism[1, 2] %>% as.numeric()
  fp_r <- zero_racism[1, 3] %>% as.numeric()
  fn_r <- zero_racism[2, 2] %>% as.numeric()

  tp_s <- zero_sexism[2, 3] %>% as.numeric()
  tn_s <- zero_sexism[1, 2] %>% as.numeric()
  fp_s <- zero_sexism[1, 3] %>% as.numeric()
  fn_s <- zero_sexism[2, 2] %>% as.numeric()

  tp_h <- zero_hate[2, 3] %>% as.numeric()
  tn_h <- zero_hate[1, 2] %>% as.numeric()
  fp_h <- zero_hate[1, 3] %>% as.numeric()
  fn_h <- zero_hate[2, 2] %>% as.numeric()

  zero_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
  zero_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
  zero_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
  zero_racism_f1 <- ((2*zero_racism_precision*zero_racism_recall)/(zero_racism_precision + zero_racism_recall)) %>% round(2)

  zero_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
  zero_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
  zero_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
  zero_sexism_f1 <- ((2*zero_sexism_precision*zero_sexism_recall)/(zero_sexism_precision + zero_sexism_recall)) %>% round(2)

  zero_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
  zero_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
  zero_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
  zero_hate_f1 <- ((2*zero_hate_precision*zero_sexism_recall)/(zero_hate_precision + zero_hate_recall)) %>% round(2)

  # Add to vectors
  accuracy_racism[i] <- zero_racism_accuracy
  accuracy_sexism[i] <- zero_sexism_accuracy
  accuracy_hate[i] <- zero_hate_accuracy
  precision_racism[i] <- zero_racism_precision
  precision_sexism[i] <- zero_sexism_precision
  precision_hate[i] <- zero_hate_precision
  recall_racism[i] <- zero_racism_recall
  recall_sexism[i] <- zero_sexism_recall
  recall_hate[i] <- zero_hate_recall
  f1_racism[i] <- zero_racism_f1
  f1_sexism[i] <- zero_sexism_f1
  f1_hate[i] <- zero_hate_f1
}

# Sample distributions of accuracy, precision, recall, and f1
zero_racism_summary <- cbind(iter = 1:100,
                             accuracy_racism,
                             precision_racism,
                             recall_racism,
                             f1_racism) %>% 
  as_tibble() %>%
  summarise(name = "Racism",
            calc = "Mean",
            accuracy = mean(accuracy_racism),
            precision = mean(precision_racism),
            recall = mean(recall_racism),
            f1 = mean(f1_racism)) %>%
  rbind(summarise(., name = "Racism",
                    calc = "SE",
                    accuracy = sd(accuracy_racism)/sqrt(n()),
                    precision = sd(precision_racism)/sqrt(n()),
                    recall = sd(recall_racism)/sqrt(n()),
                    f1 = sd(f1_racism)/sqrt(n())))

zero_sexism_summary <- cbind(iter = 1:100,
                             accuracy_sexism,
                             precision_sexism,
                             recall_sexism,
                             f1_sexism) %>% 
  as_tibble() %>%
  summarise(name = "Sexism",
            calc = "Mean",
            accuracy = mean(accuracy_sexism),
            precision = mean(precision_sexism),
            recall = mean(recall_sexism),
            f1 = mean(f1_sexism)) %>%
  rbind(summarise(., name = "Sexism",
                  calc = "SE",
                  accuracy = sd(accuracy_sexism)/sqrt(n()),
                  precision = sd(precision_sexism)/sqrt(n()),
                  recall = sd(recall_sexism)/sqrt(n()),
                  f1 = sd(f1_sexism)/sqrt(n())))

zero_hate_summary <- cbind(iter = 1:100,
                             accuracy_hate,
                             precision_hate,
                             recall_hate,
                             f1_hate) %>% 
  as_tibble() %>%
  summarise(name = "Overall",
            calc = "Mean",
            accuracy = mean(accuracy_hate),
            precision = mean(precision_hate),
            recall = mean(recall_hate),
            f1 = mean(f1_hate)) %>%
  rbind(summarise(., name = "Overall",
                  calc = "SE",
                  accuracy = sd(accuracy_hate)/sqrt(n()),
                  precision = sd(precision_hate)/sqrt(n()),
                  recall = sd(recall_hate)/sqrt(n()),
                  f1 = sd(f1_hate)/sqrt(n())))

zero_summary <- rbind(zero_racism_summary, zero_sexism_summary, zero_hate_summary)

zero_summary %>% pivot_longer(cols = !c(name, calc), names_to = "metric") %>%
  pivot_wider(names_from = c(calc), values_from = value) %>%
  mutate(name = case_when(metric == "accuracy" ~ name, TRUE ~ ""),
         metric = str_to_title(metric)) %>%
  knitr::kable(col.names = c("", "Metric", "Mean (%)", "Standard Error (%)"), 
        caption = "Performance of model in zero-shot learning across 100 classifications of each comment at a temperature of 0.3",
        booktabs = TRUE)
```

# One shot learning

```{r oneshot-summary, message=FALSE}
one_shot_multiple <- read.csv("outputs/data/one_shot_results_multiple.csv")

# Add iter variable
one_shot_multiple <- one_shot_multiple %>%
  mutate(iter = floor(X/120) + 1)

accuracy_racism <- rep(NA, 100)
accuracy_sexism <- rep(NA, 100)
accuracy_hate <- rep(NA, 100)
precision_racism <- rep(NA, 100)
precision_sexism <- rep(NA, 100)
precision_hate <- rep(NA, 100)
recall_racism <- rep(NA, 100)
recall_sexism <- rep(NA, 100)
recall_hate <- rep(NA, 100)
f1_racism <- rep(NA, 100)
f1_sexism <- rep(NA, 100)
f1_hate <- rep(NA, 100)

# For each iteration:
for (i in 1:100){
  # Racism table
  one_racism <- 
    one_shot_multiple %>%
    filter(category == "racist" & iter == i) %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
                                label_yn == "Y" ~ "Racist")) %>%
    rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
  one_racism <- one_racism[, c("Actual classification", "Not racist", "Racist")]

  # Sexism table
  one_sexism <- 
    one_shot_multiple %>%
    filter(category == "sexist" & iter == i) %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
                                label_yn == "Y" ~ "Sexist")) %>%
    rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
  one_sexism <- one_sexism[, c("Actual classification", "Not sexist", "Sexist")]

  # Hate table
  one_hate <- 
    one_shot_multiple %>%
    filter(iter == i) %>%
    select(category, label, answer, temperature) %>%
    mutate(answer = tolower(answer) %>% trimws(),
           label_yn = ifelse(grepl("not", label), "N", "Y"),
           answer_yn = case_when(str_detect(answer, "no") ~ "N",
                                str_detect(answer, "yes") ~ "Y",
                                TRUE ~ "Other")) %>%
    filter(answer_yn != "Other") %>%
    count(label_yn, answer_yn) %>%
    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
    mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
                                label_yn == "Y" ~ "Hate speech")) %>%
    rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
  one_hate <- one_hate[, c("Actual classification", "Not hate speech", "Hate speech")]

  # Compute accuracy/precision/recall/f1
  tp_r <- one_racism[2, 3] %>% as.numeric()
  tn_r <- one_racism[1, 2] %>% as.numeric()
  fp_r <- one_racism[1, 3] %>% as.numeric()
  fn_r <- one_racism[2, 2] %>% as.numeric()

  tp_s <- one_sexism[2, 3] %>% as.numeric()
  tn_s <- one_sexism[1, 2] %>% as.numeric()
  fp_s <- one_sexism[1, 3] %>% as.numeric()
  fn_s <- one_sexism[2, 2] %>% as.numeric()

  tp_h <- one_hate[2, 3] %>% as.numeric()
  tn_h <- one_hate[1, 2] %>% as.numeric()
  fp_h <- one_hate[1, 3] %>% as.numeric()
  fn_h <- one_hate[2, 2] %>% as.numeric()

  one_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
  one_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
  one_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
  one_racism_f1 <- ((2*one_racism_precision*one_racism_recall)/(one_racism_precision + one_racism_recall)) %>% round(2)

  one_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
  one_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
  one_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
  one_sexism_f1 <- ((2*one_sexism_precision*one_sexism_recall)/(one_sexism_precision + one_sexism_recall)) %>% round(2)

  one_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
  one_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
  one_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
  one_hate_f1 <- ((2*one_hate_precision*one_sexism_recall)/(one_hate_precision + one_hate_recall)) %>% round(2)

  # Add to vectors
  accuracy_racism[i] <- one_racism_accuracy
  accuracy_sexism[i] <- one_sexism_accuracy
  accuracy_hate[i] <- one_hate_accuracy
  precision_racism[i] <- one_racism_precision
  precision_sexism[i] <- one_sexism_precision
  precision_hate[i] <- one_hate_precision
  recall_racism[i] <- one_racism_recall
  recall_sexism[i] <- one_sexism_recall
  recall_hate[i] <- one_hate_recall
  f1_racism[i] <- one_racism_f1
  f1_sexism[i] <- one_sexism_f1
  f1_hate[i] <- one_hate_f1
}

# Sample distributions of accuracy, precision, recall, and f1
one_racism_summary <- cbind(iter = 1:100,
                             accuracy_racism,
                             precision_racism,
                             recall_racism,
                             f1_racism) %>% 
  as_tibble() %>%
  summarise(name = "Racism",
            calc = "Mean",
            accuracy = mean(accuracy_racism),
            precision = mean(precision_racism),
            recall = mean(recall_racism),
            f1 = mean(f1_racism)) %>%
  rbind(summarise(., name = "Racism",
                    calc = "SE",
                    accuracy = sd(accuracy_racism)/sqrt(n()),
                    precision = sd(precision_racism)/sqrt(n()),
                    recall = sd(recall_racism)/sqrt(n()),
                    f1 = sd(f1_racism)/sqrt(n())))

one_sexism_summary <- cbind(iter = 1:100,
                             accuracy_sexism,
                             precision_sexism,
                             recall_sexism,
                             f1_sexism) %>% 
  as_tibble() %>%
  summarise(name = "Sexism",
            calc = "Mean",
            accuracy = mean(accuracy_sexism),
            precision = mean(precision_sexism),
            recall = mean(recall_sexism),
            f1 = mean(f1_sexism)) %>%
  rbind(summarise(., name = "Sexism",
                  calc = "SE",
                  accuracy = sd(accuracy_sexism)/sqrt(n()),
                  precision = sd(precision_sexism)/sqrt(n()),
                  recall = sd(recall_sexism)/sqrt(n()),
                  f1 = sd(f1_sexism)/sqrt(n())))

one_hate_summary <- cbind(iter = 1:100,
                             accuracy_hate,
                             precision_hate,
                             recall_hate,
                             f1_hate) %>% 
  as_tibble() %>%
  summarise(name = "Overall",
            calc = "Mean",
            accuracy = mean(accuracy_hate),
            precision = mean(precision_hate),
            recall = mean(recall_hate),
            f1 = mean(f1_hate)) %>%
  rbind(summarise(., name = "Overall",
                  calc = "SE",
                  accuracy = sd(accuracy_hate)/sqrt(n()),
                  precision = sd(precision_hate)/sqrt(n()),
                  recall = sd(recall_hate)/sqrt(n()),
                  f1 = sd(f1_hate)/sqrt(n())))

one_summary <- rbind(one_racism_summary, one_sexism_summary, one_hate_summary)

one_summary %>% pivot_longer(cols = !c(name, calc), names_to = "metric") %>%
  pivot_wider(names_from = c(calc), values_from = value) %>%
  mutate(name = case_when(metric == "accuracy" ~ name, TRUE ~ ""),
         metric = str_to_title(metric)) %>%
  knitr::kable(col.names = c("", "Metric", "Mean (%)", "Standard Error (%)"), 
        caption = "Performance of model in one-shot learning across 100 classifications of each comment at a temperature of 0.3",
        booktabs = TRUE)
```

### 2022-03-18 Testing-multiple-iterations.Rmd
Data collection for multiple iterations of few-shot single catgory, updates to tables in paper, begin updates to results sections

@@
 one_shot_multiple <- read.csv("outputs/data/one_shot_results_multiple.csv")
+few_shot_multiple <- read.csv("outputs/data/few_shot_single_results_multiple.csv")
+
 ```
@@
 
-accuracy_racism <- rep(NA, 100)
-accuracy_sexism <- rep(NA, 100)
-accuracy_hate <- rep(NA, 100)
-precision_racism <- rep(NA, 100)
-precision_sexism <- rep(NA, 100)
-precision_hate <- rep(NA, 100)
-recall_racism <- rep(NA, 100)
-recall_sexism <- rep(NA, 100)
-recall_hate <- rep(NA, 100)
-f1_racism <- rep(NA, 100)
-f1_sexism <- rep(NA, 100)
-f1_hate <- rep(NA, 100)
+accuracy_racism <- rep(NA, nrow(zero_shot_multiple)/120)
+accuracy_sexism <- rep(NA, nrow(zero_shot_multiple)/120)
+accuracy_hate <- rep(NA, nrow(zero_shot_multiple)/120)
+precision_racism <- rep(NA, nrow(zero_shot_multiple)/120)
+precision_sexism <- rep(NA, nrow(zero_shot_multiple)/120)
+precision_hate <- rep(NA, nrow(zero_shot_multiple)/120)
+recall_racism <- rep(NA, nrow(zero_shot_multiple)/120)
+recall_sexism <- rep(NA, nrow(zero_shot_multiple)/120)
+recall_hate <- rep(NA, nrow(zero_shot_multiple)/120)
+f1_racism <- rep(NA, nrow(zero_shot_multiple)/120)
+f1_sexism <- rep(NA, nrow(zero_shot_multiple)/120)
+f1_hate <- rep(NA, nrow(zero_shot_multiple)/120)
 
 # For each iteration:
-for (i in 1:100){
+for (i in 1:(nrow(zero_shot_multiple)/120)){
   # Racism table
@@
 # Sample distributions of accuracy, precision, recall, and f1
-zero_racism_summary <- cbind(iter = 1:100,
+zero_racism_summary <- cbind(iter = 1:length(accuracy_racism),
                              accuracy_racism,
@@
 
-zero_sexism_summary <- cbind(iter = 1:100,
+zero_sexism_summary <- cbind(iter = 1:length(accuracy_sexism),
                              accuracy_sexism,
@@
 
-zero_hate_summary <- cbind(iter = 1:100,
+zero_hate_summary <- cbind(iter = 1:length(accuracy_hate),
                              accuracy_hate,
@@
   mutate(name = case_when(metric == "accuracy" ~ name, TRUE ~ ""),
-         metric = str_to_title(metric)) %>%
+         metric = str_to_title(metric),
+         Mean = round(Mean),
+         SE = round(SE, 1)) %>%
   knitr::kable(col.names = c("", "Metric", "Mean (%)", "Standard Error (%)"), 
         caption = "Performance of model in zero-shot learning across 100 classifications of each comment at a temperature of 0.3",
-        booktabs = TRUE)
+        booktabs = TRUE,
+        linesep = "") %>%
+  kableExtra::column_spec(column = 1, bold = TRUE)
 ```
@@
 
-accuracy_racism <- rep(NA, 100)
-accuracy_sexism <- rep(NA, 100)
-accuracy_hate <- rep(NA, 100)
-precision_racism <- rep(NA, 100)
-precision_sexism <- rep(NA, 100)
-precision_hate <- rep(NA, 100)
-recall_racism <- rep(NA, 100)
-recall_sexism <- rep(NA, 100)
-recall_hate <- rep(NA, 100)
-f1_racism <- rep(NA, 100)
-f1_sexism <- rep(NA, 100)
-f1_hate <- rep(NA, 100)
+accuracy_racism <- rep(NA, nrow(one_shot_multiple)/120)
+accuracy_sexism <- rep(NA, nrow(one_shot_multiple)/120)
+accuracy_hate <- rep(NA, nrow(one_shot_multiple)/120)
+precision_racism <- rep(NA, nrow(one_shot_multiple)/120)
+precision_sexism <- rep(NA, nrow(one_shot_multiple)/120)
+precision_hate <- rep(NA, nrow(one_shot_multiple)/120)
+recall_racism <- rep(NA, nrow(one_shot_multiple)/120)
+recall_sexism <- rep(NA, nrow(one_shot_multiple)/120)
+recall_hate <- rep(NA, nrow(one_shot_multiple)/120)
+f1_racism <- rep(NA, nrow(one_shot_multiple)/120)
+f1_sexism <- rep(NA, nrow(one_shot_multiple)/120)
+f1_hate <- rep(NA, nrow(one_shot_multiple)/120)
 
 # For each iteration:
-for (i in 1:100){
+for (i in 1:(nrow(one_shot_multiple)/120)){
   # Racism table
@@
 # Sample distributions of accuracy, precision, recall, and f1
-one_racism_summary <- cbind(iter = 1:100,
+one_racism_summary <- cbind(iter = 1:length(accuracy_racism),
                              accuracy_racism,
@@
 
-one_sexism_summary <- cbind(iter = 1:100,
+one_sexism_summary <- cbind(iter = 1:length(accuracy_sexism),
                              accuracy_sexism,
@@
 
-one_hate_summary <- cbind(iter = 1:100,
+one_hate_summary <- cbind(iter = 1:length(accuracy_hate),
                              accuracy_hate,
@@
   mutate(name = case_when(metric == "accuracy" ~ name, TRUE ~ ""),
-         metric = str_to_title(metric)) %>%
+         metric = str_to_title(metric),
+         Mean = round(Mean),
+         SE = round(SE, 1)) %>%
   knitr::kable(col.names = c("", "Metric", "Mean (%)", "Standard Error (%)"), 
         caption = "Performance of model in one-shot learning across 100 classifications of each comment at a temperature of 0.3",
-        booktabs = TRUE)
+        booktabs = TRUE,
+        linesep = "") %>%
+  kableExtra::column_spec(column = 1, bold = TRUE)
 ```
+# Few-shot single category
+
+```{r oneshot-summary, message=FALSE}
+# Add iter variable
+few_shot_multiple <- few_shot_multiple %>%
+  mutate(iter = floor(X/120) + 1)
+
+accuracy_racism <- rep(NA, nrow(few_shot_multiple)/120)
+accuracy_sexism <- rep(NA, nrow(few_shot_multiple)/120)
+accuracy_hate <- rep(NA, nrow(few_shot_multiple)/120)
+precision_racism <- rep(NA, nrow(few_shot_multiple)/120)
+precision_sexism <- rep(NA, nrow(few_shot_multiple)/120)
+precision_hate <- rep(NA, nrow(few_shot_multiple)/120)
+recall_racism <- rep(NA, nrow(few_shot_multiple)/120)
+recall_sexism <- rep(NA, nrow(few_shot_multiple)/120)
+recall_hate <- rep(NA, nrow(few_shot_multiple)/120)
+f1_racism <- rep(NA, nrow(few_shot_multiple)/120)
+f1_sexism <- rep(NA, nrow(few_shot_multiple)/120)
+f1_hate <- rep(NA, nrow(few_shot_multiple)/120)
+
+# For each iteration:
+for (i in 1:(nrow(few_shot_multiple)/120)){
+  # Racism table
+  one_racism <- 
+    few_shot_multiple %>%
+    filter(category == "racist" & iter == i) %>%
+    select(category, label, answer, temperature) %>%
+    mutate(answer = tolower(answer) %>% trimws(),
+           label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                                str_detect(answer, "yes") ~ "Y",
+                                TRUE ~ "Other")) %>%
+    filter(answer_yn != "Other") %>%
+    count(label_yn, answer_yn) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+    mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
+                                label_yn == "Y" ~ "Racist")) %>%
+    rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
+  one_racism <- one_racism[, c("Actual classification", "Not racist", "Racist")]
+
+  # Sexism table
+  one_sexism <- 
+    few_shot_multiple %>%
+    filter(category == "sexist" & iter == i) %>%
+    select(category, label, answer, temperature) %>%
+    mutate(answer = tolower(answer) %>% trimws(),
+           label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                                str_detect(answer, "yes") ~ "Y",
+                                TRUE ~ "Other")) %>%
+    filter(answer_yn != "Other") %>%
+    count(label_yn, answer_yn) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+    mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
+                                label_yn == "Y" ~ "Sexist")) %>%
+    rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
+  one_sexism <- one_sexism[, c("Actual classification", "Not sexist", "Sexist")]
+
+  # Hate table
+  one_hate <- 
+    few_shot_multiple %>%
+    filter(iter == i) %>%
+    select(category, label, answer, temperature) %>%
+    mutate(answer = tolower(answer) %>% trimws(),
+           label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                                str_detect(answer, "yes") ~ "Y",
+                                TRUE ~ "Other")) %>%
+    filter(answer_yn != "Other") %>%
+    count(label_yn, answer_yn) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+    mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
+                                label_yn == "Y" ~ "Hate speech")) %>%
+    rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
+  one_hate <- one_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
+
+  # Compute accuracy/precision/recall/f1
+  tp_r <- one_racism[2, 3] %>% as.numeric()
+  tn_r <- one_racism[1, 2] %>% as.numeric()
+  fp_r <- one_racism[1, 3] %>% as.numeric()
+  fn_r <- one_racism[2, 2] %>% as.numeric()
+
+  tp_s <- one_sexism[2, 3] %>% as.numeric()
+  tn_s <- one_sexism[1, 2] %>% as.numeric()
+  fp_s <- one_sexism[1, 3] %>% as.numeric()
+  fn_s <- one_sexism[2, 2] %>% as.numeric()
+
+  tp_h <- one_hate[2, 3] %>% as.numeric()
+  tn_h <- one_hate[1, 2] %>% as.numeric()
+  fp_h <- one_hate[1, 3] %>% as.numeric()
+  fn_h <- one_hate[2, 2] %>% as.numeric()
+
+  one_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
+  one_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
+  one_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
+  one_racism_f1 <- ((2*one_racism_precision*one_racism_recall)/(one_racism_precision + one_racism_recall)) %>% round(2)
+
+  one_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
+  one_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
+  one_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
+  one_sexism_f1 <- ((2*one_sexism_precision*one_sexism_recall)/(one_sexism_precision + one_sexism_recall)) %>% round(2)
+
+  one_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
+  one_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
+  one_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
+  one_hate_f1 <- ((2*one_hate_precision*one_sexism_recall)/(one_hate_precision + one_hate_recall)) %>% round(2)
+
+  # Add to vectors
+  accuracy_racism[i] <- one_racism_accuracy
+  accuracy_sexism[i] <- one_sexism_accuracy
+  accuracy_hate[i] <- one_hate_accuracy
+  precision_racism[i] <- one_racism_precision
+  precision_sexism[i] <- one_sexism_precision
+  precision_hate[i] <- one_hate_precision
+  recall_racism[i] <- one_racism_recall
+  recall_sexism[i] <- one_sexism_recall
+  recall_hate[i] <- one_hate_recall
+  f1_racism[i] <- one_racism_f1
+  f1_sexism[i] <- one_sexism_f1
+  f1_hate[i] <- one_hate_f1
+}
+
+# Sample distributions of accuracy, precision, recall, and f1
+one_racism_summary <- cbind(iter = 1:length(accuracy_racism),
+                             accuracy_racism,
+                             precision_racism,
+                             recall_racism,
+                             f1_racism) %>% 
+  as_tibble() %>%
+  summarise(name = "Racism",
+            calc = "Mean",
+            accuracy = mean(accuracy_racism),
+            precision = mean(precision_racism),
+            recall = mean(recall_racism),
+            f1 = mean(f1_racism)) %>%
+  rbind(summarise(., name = "Racism",
+                    calc = "SE",
+                    accuracy = sd(accuracy_racism)/sqrt(n()),
+                    precision = sd(precision_racism)/sqrt(n()),
+                    recall = sd(recall_racism)/sqrt(n()),
+                    f1 = sd(f1_racism)/sqrt(n())))
+
+one_sexism_summary <- cbind(iter = 1:length(accuracy_sexism),
+                             accuracy_sexism,
+                             precision_sexism,
+                             recall_sexism,
+                             f1_sexism) %>% 
+  as_tibble() %>%
+  summarise(name = "Sexism",
+            calc = "Mean",
+            accuracy = mean(accuracy_sexism),
+            precision = mean(precision_sexism),
+            recall = mean(recall_sexism),
+            f1 = mean(f1_sexism)) %>%
+  rbind(summarise(., name = "Sexism",
+                  calc = "SE",
+                  accuracy = sd(accuracy_sexism)/sqrt(n()),
+                  precision = sd(precision_sexism)/sqrt(n()),
+                  recall = sd(recall_sexism)/sqrt(n()),
+                  f1 = sd(f1_sexism)/sqrt(n())))
+
+one_hate_summary <- cbind(iter = 1:length(accuracy_hate),
+                             accuracy_hate,
+                             precision_hate,
+                             recall_hate,
+                             f1_hate) %>% 
+  as_tibble() %>%
+  summarise(name = "Overall",
+            calc = "Mean",
+            accuracy = mean(accuracy_hate),
+            precision = mean(precision_hate),
+            recall = mean(recall_hate),
+            f1 = mean(f1_hate)) %>%
+  rbind(summarise(., name = "Overall",
+                  calc = "SE",
+                  accuracy = sd(accuracy_hate)/sqrt(n()),
+                  precision = sd(precision_hate)/sqrt(n()),
+                  recall = sd(recall_hate)/sqrt(n()),
+                  f1 = sd(f1_hate)/sqrt(n())))
+
+one_summary <- rbind(one_racism_summary, one_sexism_summary, one_hate_summary)
+
+one_summary %>% pivot_longer(cols = !c(name, calc), names_to = "metric") %>%
+  pivot_wider(names_from = c(calc), values_from = value) %>%
+  mutate(name = case_when(metric == "accuracy" ~ name, TRUE ~ ""),
+         metric = str_to_title(metric),
+         Mean = round(Mean),
+         SE = round(SE, 1)) %>%
+  knitr::kable(col.names = c("", "Metric", "Mean (%)", "Standard Error (%)"), 
+        caption = "Performance of model in one-shot learning across 100 classifications of each comment at a temperature of 0.3",
+        booktabs = TRUE,
+        linesep = "") %>%
+  kableExtra::column_spec(column = 1, bold = TRUE)
+```

### 2022-03-18 outputs/documents/paper.Rmd
Data collection for multiple iterations of few-shot single catgory, updates to tables in paper, begin updates to results sections

@@
 Lower temperatures mean that the model places more weight on higher-probability tokens.
-To enhance consistency, the temperature is set to zero in our experiments and not varied.
+To explore potential variations in the classifications of comments, the temperature is set to 0.3 in our experiments for the zero- and one-shot settings and not varied.
+In all few-shot settings, the temperature is set to zero.
 There are two categories of hate speech that are of interest in this paper.
@@
 
+For zero- and one-shot learning, each set of 120 comments was classified 100 times by GPT-3 in order to assess the variability of classifications at a temperature of 0.3.
+The reported performance metrics for these settings are the arithmetic means of each metric across all 100 iterations with the corresponding standard error.
+In some cases, the model outputted responses that were neither "yes" nor "no".
+These were counted as "not applicable" and omitted from analysis.
+Specific numbers are reported in the following sections.
+
 ## Zero-shot learning
@@
 The overall results of the zero-shot experiments are presented in Table \@ref(tab:zeroshot-summary), and Appendix \@ref(appendixbzeroshot) provides additional detail.
-The model has 34 matches (true positives and negatives) and 26 mismatches (false positives and negatives) in the sexist category, and 41 matches and 19 mismatches in the racist category.
-The model performs more accurately when identifying racist comments, with an accuracy of 68 per cent, compared with identifying sexist comments, with an accuracy of 57 per cent, but the F1 score for each type of hate speech is roughly the same.
-The overall ratio of matches and mismatches is 75:45.
-In other words, the accuracy in identifying hate speech in the zero-shot setting is 63 per cent.
-The model has an F1 score of 81 per cent in this setting, with a notably high recall of 87 per cent.
+Out of 6000 classification for each category, the model has 3231 matches (true positives and negatives) and 2691 mismatches (false positives and negatives) in the sexist category, and 3463 matches and 2504 mismatches in the racist category.
+In the zero-shot learning setting, the model produced 111 responses that were inadmissible.
+The model performs more accurately when identifying racist comments, with an average accuracy of 58 per cent (SE = 6.5), compared with identifying sexist comments, with an average accuracy of 55 per cent (SE = 5.2).
+In contrast, the F1 score for classification of sexist speech is slightly higher on average at 63 per cent (SE = 4.3), compared with an average of 58 per cent (SE = 6.7) for racist speech.
+The overall ratio of matches and mismatches is 6694:5195.
+In other words, the average accuracy in identifying hate speech in the zero-shot setting is 56 per cent (SE = 4.6).
+The model has an average F1 score of 70 per cent (SE = 5.7) in this setting.
 
@@
 zero_shot_result <-
-  read_csv(here::here("outputs/data/zero_shot_results.csv"),
+  read_csv(here::here("outputs/data/zero_shot_results_multiple.csv"),
            show_col_types = FALSE)
+
+# Add iter variable
+zero_shot_result <- zero_shot_result %>%
+  mutate(iter = floor(`...1`/120) + 1)
 
@@
   zero_shot_result %>%
-  filter(temperature == 0 & category == "racist") %>%
+    filter(category == "racist") %>%
     select(category, label, answer, temperature) %>%
-  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
-  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
+    mutate(answer = tolower(answer) %>% trimws(),
+           label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                                str_detect(answer, "yes") ~ "Y",
+                                TRUE ~ "Other")) %>%
+    filter(answer_yn != "Other") %>%
     count(label_yn, answer_yn) %>%
-  pivot_wider(names_from = answer_yn,
-              values_from = n,
-              values_fill = 0) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
     mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
                                 label_yn == "Y" ~ "Racist")) %>%
-  rename(
-    "Actual classification" = label_yn,
-    "Not racist" = N,
-    "Racist" = Y
-  )
+    rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
 
@@
 
-# Set-up data for sexism
 zero_shot_result_sexism <- 
     zero_shot_result %>%
-  filter(temperature == 0 & category == "sexist") %>%
+    filter(category == "sexist") %>%
     select(category, label, answer, temperature) %>%
-  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
-  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
+    mutate(answer = tolower(answer) %>% trimws(),
+           label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                                str_detect(answer, "yes") ~ "Y",
+                                TRUE ~ "Other")) %>%
+    filter(answer_yn != "Other") %>%
     count(label_yn, answer_yn) %>%
-  pivot_wider(names_from = answer_yn,
-              values_from = n,
-              values_fill = 0) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
     mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
                                 label_yn == "Y" ~ "Sexist")) %>%
-  rename(
-    "Actual classification" = label_yn,
-    "Not sexist" = N,
-    "Sexist" = Y
-  )
-
-zero_shot_result_sexism <-
-  zero_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]
-
-# Set-up data for hate speech
+    rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
+  zero_shot_result_sexism <- zero_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]
+
 zero_shot_result_hate <- 
     zero_shot_result %>%
-  filter(temperature == 0) %>%
     select(category, label, answer, temperature) %>%
-  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
-  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
+    mutate(answer = tolower(answer) %>% trimws(),
+           label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                                str_detect(answer, "yes") ~ "Y",
+                                TRUE ~ "Other")) %>%
+    filter(answer_yn != "Other") %>%
     count(label_yn, answer_yn) %>%
-  pivot_wider(names_from = answer_yn,
-              values_from = n,
-              values_fill = 0) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
     mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
                                 label_yn == "Y" ~ "Hate speech")) %>%
-  rename(
-    "Actual classification" = label_yn,
-    "Not hate speech" = N,
-    "Hate speech" = Y
-  )
-
-zero_shot_result_hate <-
-  zero_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
-
-# Pull it all together
-tp_r <- zero_shot_result_racism[2, 3] %>% as.numeric()
-tn_r <- zero_shot_result_racism[1, 2] %>% as.numeric()
-fp_r <- zero_shot_result_racism[1, 3] %>% as.numeric()
-fn_r <- zero_shot_result_racism[2, 2] %>% as.numeric()
-
-tp_s <- zero_shot_result_sexism[2, 3] %>% as.numeric()
-tn_s <- zero_shot_result_sexism[1, 2] %>% as.numeric()
-fp_s <- zero_shot_result_sexism[1, 3] %>% as.numeric()
-fn_s <- zero_shot_result_sexism[2, 2] %>% as.numeric()
-
-tp_h <- zero_shot_result_hate[2, 3] %>% as.numeric()
-tn_h <- zero_shot_result_hate[1, 2] %>% as.numeric()
-fp_h <- zero_shot_result_hate[1, 3] %>% as.numeric()
-fn_h <- zero_shot_result_hate[2, 2] %>% as.numeric()
-
-zero_racism_accuracy <-
-  ((tp_r + tn_r) / (tp_r + tn_r + fp_r + fn_r)) %>% round(4) * 100
-zero_racism_precision <- (tp_r / (tp_r + fp_r)) %>% round(4) * 100
-zero_racism_recall <- (tp_r / (tp_r + fn_r)) %>% round(4) * 100
-zero_racism_f1 <-
-  ((2 * zero_racism_precision * zero_racism_recall) / (zero_racism_precision + zero_racism_recall)
-  ) %>% round(2)
-zero_racism_all <-
-  c(zero_racism_accuracy,
-    zero_racism_precision,
-    zero_racism_recall,
-    zero_racism_f1)
-
-zero_sexism_accuracy <-
-  ((tp_s + tn_s) / (tp_s + tn_s + fp_s + fn_s)) %>% round(4) * 100
-zero_sexism_precision <- (tp_s / (tp_s + fp_s)) %>% round(4) * 100
-zero_sexism_recall <- (tp_s / (tp_s + fn_s)) %>% round(4) * 100
-zero_sexism_f1 <-
-  ((2 * zero_sexism_precision * zero_sexism_recall) / (zero_sexism_precision + zero_sexism_recall)
-  ) %>% round(2)
-zero_sexism_all <-
-  c(zero_sexism_accuracy,
-    zero_sexism_precision,
-    zero_sexism_recall,
-    zero_sexism_f1)
-
-zero_hate_accuracy <-
-  ((tp_h + tn_h) / (tp_h + tn_h + fp_h + fn_h)) %>% round(4) * 100
-zero_hate_precision <- (tp_h / (tp_h + fp_h)) %>% round(4) * 100
-zero_hate_recall <- (tp_h / (tp_h + fn_h)) %>% round(4) * 100
-zero_hate_f1 <-
-  ((2 * zero_hate_precision * zero_sexism_recall) / (zero_hate_precision + zero_hate_recall)
-  ) %>% round(2)
-zero_hate_all <-
-  c(zero_hate_accuracy,
-    zero_hate_precision,
-    zero_hate_recall,
-    zero_hate_f1)
-
-zero_shot_summary <-
-  tibble(
-    Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)),
-    Metric = rep(c("Accuracy (%)", "Precision (%)", "Recall (%)", "F1 (%)"), 3),
-    Percent = c(zero_racism_all, zero_sexism_all, zero_hate_all)
-  ) %>%
-  pivot_wider(names_from = Metric, values_from = Percent)
-
-zero_shot_summary %>%
-  knitr::kable(caption = "Performance of zero-shot learning in hate speech classification",
+    rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
+zero_shot_result_hate <- zero_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
+
+accuracy_racism <- rep(NA, nrow(zero_shot_result)/120)
+accuracy_sexism <- rep(NA, nrow(zero_shot_result)/120)
+accuracy_hate <- rep(NA, nrow(zero_shot_result)/120)
+precision_racism <- rep(NA, nrow(zero_shot_result)/120)
+precision_sexism <- rep(NA, nrow(zero_shot_result)/120)
+precision_hate <- rep(NA, nrow(zero_shot_result)/120)
+recall_racism <- rep(NA, nrow(zero_shot_result)/120)
+recall_sexism <- rep(NA, nrow(zero_shot_result)/120)
+recall_hate <- rep(NA, nrow(zero_shot_result)/120)
+f1_racism <- rep(NA, nrow(zero_shot_result)/120)
+f1_sexism <- rep(NA, nrow(zero_shot_result)/120)
+f1_hate <- rep(NA, nrow(zero_shot_result)/120)
+
+# For each iteration:
+for (i in 1:(nrow(zero_shot_result)/120)){
+  # Racism table
+  zero_racism <- 
+    zero_shot_result %>%
+    filter(category == "racist" & iter == i) %>%
+    select(category, label, answer, temperature) %>%
+    mutate(answer = tolower(answer) %>% trimws(),
+           label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                                str_detect(answer, "yes") ~ "Y",
+                                TRUE ~ "Other")) %>%
+    filter(answer_yn != "Other") %>%
+    count(label_yn, answer_yn) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+    mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
+                                label_yn == "Y" ~ "Racist")) %>%
+    rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
+  zero_racism <- zero_racism[, c("Actual classification", "Not racist", "Racist")]
+
+  # Sexism table
+  zero_sexism <- 
+    zero_shot_result %>%
+    filter(category == "sexist" & iter == i) %>%
+    select(category, label, answer, temperature) %>%
+    mutate(answer = tolower(answer) %>% trimws(),
+           label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                                str_detect(answer, "yes") ~ "Y",
+                                TRUE ~ "Other")) %>%
+    filter(answer_yn != "Other") %>%
+    count(label_yn, answer_yn) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+    mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
+                                label_yn == "Y" ~ "Sexist")) %>%
+    rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
+  zero_sexism <- zero_sexism[, c("Actual classification", "Not sexist", "Sexist")]
+
+  # Hate table
+  zero_hate <- 
+    zero_shot_result %>%
+    filter(iter == i) %>%
+    select(category, label, answer, temperature) %>%
+    mutate(answer = tolower(answer) %>% trimws(),
+           label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                                str_detect(answer, "yes") ~ "Y",
+                                TRUE ~ "Other")) %>%
+    filter(answer_yn != "Other") %>%
+    count(label_yn, answer_yn) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+    mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
+                                label_yn == "Y" ~ "Hate speech")) %>%
+    rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
+  zero_hate <- zero_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
+
+  # Compute accuracy/precision/recall/f1
+  tp_r <- zero_racism[2, 3] %>% as.numeric()
+  tn_r <- zero_racism[1, 2] %>% as.numeric()
+  fp_r <- zero_racism[1, 3] %>% as.numeric()
+  fn_r <- zero_racism[2, 2] %>% as.numeric()
+
+  tp_s <- zero_sexism[2, 3] %>% as.numeric()
+  tn_s <- zero_sexism[1, 2] %>% as.numeric()
+  fp_s <- zero_sexism[1, 3] %>% as.numeric()
+  fn_s <- zero_sexism[2, 2] %>% as.numeric()
+
+  tp_h <- zero_hate[2, 3] %>% as.numeric()
+  tn_h <- zero_hate[1, 2] %>% as.numeric()
+  fp_h <- zero_hate[1, 3] %>% as.numeric()
+  fn_h <- zero_hate[2, 2] %>% as.numeric()
+
+  zero_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
+  zero_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
+  zero_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
+  zero_racism_f1 <- ((2*zero_racism_precision*zero_racism_recall)/(zero_racism_precision + zero_racism_recall)) %>% round(2)
+
+  zero_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
+  zero_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
+  zero_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
+  zero_sexism_f1 <- ((2*zero_sexism_precision*zero_sexism_recall)/(zero_sexism_precision + zero_sexism_recall)) %>% round(2)
+
+  zero_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
+  zero_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
+  zero_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
+  zero_hate_f1 <- ((2*zero_hate_precision*zero_sexism_recall)/(zero_hate_precision + zero_hate_recall)) %>% round(2)
+
+  # Add to vectors
+  accuracy_racism[i] <- zero_racism_accuracy
+  accuracy_sexism[i] <- zero_sexism_accuracy
+  accuracy_hate[i] <- zero_hate_accuracy
+  precision_racism[i] <- zero_racism_precision
+  precision_sexism[i] <- zero_sexism_precision
+  precision_hate[i] <- zero_hate_precision
+  recall_racism[i] <- zero_racism_recall
+  recall_sexism[i] <- zero_sexism_recall
+  recall_hate[i] <- zero_hate_recall
+  f1_racism[i] <- zero_racism_f1
+  f1_sexism[i] <- zero_sexism_f1
+  f1_hate[i] <- zero_hate_f1
+}
+
+# Sample distributions of accuracy, precision, recall, and f1
+zero_racism_summary <- cbind(iter = 1:length(accuracy_racism),
+                             accuracy_racism,
+                             precision_racism,
+                             recall_racism,
+                             f1_racism) %>% 
+  as_tibble() %>%
+  summarise(name = "Racism",
+            calc = "Mean",
+            accuracy = mean(accuracy_racism),
+            precision = mean(precision_racism),
+            recall = mean(recall_racism),
+            f1 = mean(f1_racism)) %>%
+  rbind(summarise(., name = "Racism",
+                    calc = "SE",
+                    accuracy = sd(accuracy_racism)/sqrt(n()),
+                    precision = sd(precision_racism)/sqrt(n()),
+                    recall = sd(recall_racism)/sqrt(n()),
+                    f1 = sd(f1_racism)/sqrt(n())))
+
+zero_sexism_summary <- cbind(iter = 1:length(accuracy_sexism),
+                             accuracy_sexism,
+                             precision_sexism,
+                             recall_sexism,
+                             f1_sexism) %>% 
+  as_tibble() %>%
+  summarise(name = "Sexism",
+            calc = "Mean",
+            accuracy = mean(accuracy_sexism),
+            precision = mean(precision_sexism),
+            recall = mean(recall_sexism),
+            f1 = mean(f1_sexism)) %>%
+  rbind(summarise(., name = "Sexism",
+                  calc = "SE",
+                  accuracy = sd(accuracy_sexism)/sqrt(n()),
+                  precision = sd(precision_sexism)/sqrt(n()),
+                  recall = sd(recall_sexism)/sqrt(n()),
+                  f1 = sd(f1_sexism)/sqrt(n())))
+
+zero_hate_summary <- cbind(iter = 1:length(accuracy_hate),
+                             accuracy_hate,
+                             precision_hate,
+                             recall_hate,
+                             f1_hate) %>% 
+  as_tibble() %>%
+  summarise(name = "Overall",
+            calc = "Mean",
+            accuracy = mean(accuracy_hate),
+            precision = mean(precision_hate),
+            recall = mean(recall_hate),
+            f1 = mean(f1_hate)) %>%
+  rbind(summarise(., name = "Overall",
+                  calc = "SE",
+                  accuracy = sd(accuracy_hate)/sqrt(n()),
+                  precision = sd(precision_hate)/sqrt(n()),
+                  recall = sd(recall_hate)/sqrt(n()),
+                  f1 = sd(f1_hate)/sqrt(n())))
+
+zero_summary <- rbind(zero_racism_summary, zero_sexism_summary, zero_hate_summary)
+
+zero_summary %>% pivot_longer(cols = !c(name, calc), names_to = "metric") %>%
+  pivot_wider(names_from = c(calc), values_from = value) %>%
+  mutate(name = case_when(metric == "accuracy" ~ name, TRUE ~ ""),
+         metric = str_to_title(metric),
+         Mean = round(Mean),
+         SE = round(SE, 1)) %>%
+  knitr::kable(col.names = c("", "Metric", "Mean (%)", "Standard Error (%)"), 
+        caption = "Performance of model in zero-shot learning across 100 classifications of each comment at a temperature of 0.3.",
         booktabs = TRUE,
-               digits = 0
-               )
+        linesep = "") %>%
+  kableExtra::column_spec(column = 1, bold = TRUE)
 ```
@@
 one_shot_result <-
-  read.csv(here::here("outputs/data/one_shot_results.csv"))
+  read.csv(here::here("outputs/data/one_shot_results_multiple.csv"))
+
+# Add iter variable
+one_shot_result <- one_shot_result %>%
+  mutate(iter = floor(X/120) + 1)
 
@@
   one_shot_result %>%
-  filter(temperature == 0 & category == "racist") %>%
+  filter(category == "racist") %>%
   select(category, label, answer, temperature) %>%
-  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
-  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
+  mutate(answer = tolower(answer) %>% trimws(),
+         label_yn = ifelse(grepl("not", label), "N", "Y"),
+         answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                              str_detect(answer, "yes") ~ "Y",
+                              TRUE ~ "Other")) %>%
+  filter(answer_yn != "Other") %>%
   count(label_yn, answer_yn) %>%
-  pivot_wider(names_from = answer_yn,
-              values_from = n,
-              values_fill = 0) %>%
+  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
   mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
                               label_yn == "Y" ~ "Racist")) %>%
-  rename(
-    "Actual classification" = label_yn,
-    "Not racist" = N,
-    "Racist" = Y
-  )
-
-one_shot_result_racism <-
-  one_shot_result_racism[, c("Actual classification", "Not racist", "Racist")]
-
-# Set-up sexism
+  rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
+one_shot_result_racism <- one_shot_result_racism[, c("Actual classification", "Not racist", "Racist")]
+
+# Sexism table
 one_shot_result_sexism <- 
   one_shot_result %>%
-  filter(temperature == 0 & category == "sexist") %>%
+  filter(category == "sexist") %>%
   select(category, label, answer, temperature) %>%
-  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
-  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
+  mutate(answer = tolower(answer) %>% trimws(),
+         label_yn = ifelse(grepl("not", label), "N", "Y"),
+         answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                              str_detect(answer, "yes") ~ "Y",
+                              TRUE ~ "Other")) %>%
+  filter(answer_yn != "Other") %>%
   count(label_yn, answer_yn) %>%
-  pivot_wider(names_from = answer_yn,
-              values_from = n,
-              values_fill = 0) %>%
+  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
   mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
                               label_yn == "Y" ~ "Sexist")) %>%
-  rename(
-    "Actual classification" = label_yn,
-    "Not sexist" = N,
-    "Sexist" = Y
-  )
-
-one_shot_result_sexism <-
-  one_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]
-
-# Set-up hate
+  rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
+one_shot_result_sexism <- one_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]
+
+# Hate table
 one_shot_result_hate <- 
   one_shot_result %>%
-  filter(temperature == 0) %>%
   select(category, label, answer, temperature) %>%
-  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
-  mutate(answer_yn = ifelse(stringr::str_detect(answer, "No", negate = FALSE), "N", "Y")) %>%
+  mutate(answer = tolower(answer) %>% trimws(),
+         label_yn = ifelse(grepl("not", label), "N", "Y"),
+         answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                              str_detect(answer, "yes") ~ "Y",
+                              TRUE ~ "Other")) %>%
+  filter(answer_yn != "Other") %>%
   count(label_yn, answer_yn) %>%
-  pivot_wider(names_from = answer_yn,
-              values_from = n,
-              values_fill = 0) %>%
+  pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
   mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
                               label_yn == "Y" ~ "Hate speech")) %>%
-  rename(
-    "Actual classification" = label_yn,
-    "Not hate speech" = N,
-    "Hate speech" = Y
-  )
-
-one_shot_result_hate <-
-  one_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
-
-# Put it all together
-tp_r <- one_shot_result_racism[2, 3] %>% as.numeric()
-tn_r <- one_shot_result_racism[1, 2] %>% as.numeric()
-fp_r <- one_shot_result_racism[1, 3] %>% as.numeric()
-fn_r <- one_shot_result_racism[2, 2] %>% as.numeric()
-
-tp_s <- one_shot_result_sexism[2, 3] %>% as.numeric()
-tn_s <- one_shot_result_sexism[1, 2] %>% as.numeric()
-fp_s <- one_shot_result_sexism[1, 3] %>% as.numeric()
-fn_s <- one_shot_result_sexism[2, 2] %>% as.numeric()
-
-tp_h <- one_shot_result_hate[2, 3] %>% as.numeric()
-tn_h <- one_shot_result_hate[1, 2] %>% as.numeric()
-fp_h <- one_shot_result_hate[1, 3] %>% as.numeric()
-fn_h <- one_shot_result_hate[2, 2] %>% as.numeric()
-
-one_racism_accuracy <-
-  ((tp_r + tn_r) / (tp_r + tn_r + fp_r + fn_r)) %>% round(4) * 100
-one_racism_precision <- (tp_r / (tp_r + fp_r)) %>% round(4) * 100
-one_racism_recall <- (tp_r / (tp_r + fn_r)) %>% round(4) * 100
-one_racism_f1 <-
-  ((2 * one_racism_precision * one_racism_recall) / (one_racism_precision + one_racism_recall)
-  ) %>% round(2)
-one_racism_all <-
-  c(one_racism_accuracy,
-    one_racism_precision,
-    one_racism_recall,
-    one_racism_f1)
-
-one_sexism_accuracy <-
-  ((tp_s + tn_s) / (tp_s + tn_s + fp_s + fn_s)) %>% round(4) * 100
-one_sexism_precision <- (tp_s / (tp_s + fp_s)) %>% round(4) * 100
-one_sexism_recall <- (tp_s / (tp_s + fn_s)) %>% round(4) * 100
-one_sexism_f1 <-
-  ((2 * one_sexism_precision * one_sexism_recall) / (one_sexism_precision + one_sexism_recall)
-  ) %>% round(2)
-one_sexism_all <-
-  c(one_sexism_accuracy,
-    one_sexism_precision,
-    one_sexism_recall,
-    one_sexism_f1)
-
-one_hate_accuracy <-
-  ((tp_h + tn_h) / (tp_h + tn_h + fp_h + fn_h)) %>% round(4) * 100
-one_hate_precision <- (tp_h / (tp_h + fp_h)) %>% round(4) * 100
-one_hate_recall <- (tp_h / (tp_h + fn_h)) %>% round(4) * 100
-one_hate_f1 <-
-  ((2 * one_hate_precision * one_sexism_recall) / (one_hate_precision + one_hate_recall)) %>% round(2)
-one_hate_all <-
-  c(one_hate_accuracy,
-    one_hate_precision,
-    one_hate_recall,
-    one_hate_f1)
-
-one_shot_summary <-
-  tibble(
-    Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)),
-    Metric = rep(c("Accuracy (%)", "Precision (%)", "Recall (%)", "F1 (%)"), 3),
-    Percent = c(one_racism_all, one_sexism_all, one_hate_all)
-  ) %>%
-  pivot_wider(names_from = Metric, values_from = Percent)
-
-one_shot_summary %>%
-  knitr::kable(caption = "Performance of one-shot learning in hate speech classification",
-               digits = 0,
-               booktabs = TRUE)
+  rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
+one_shot_result_hate <- one_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
+
+accuracy_racism <- rep(NA, nrow(one_shot_result)/120)
+accuracy_sexism <- rep(NA, nrow(one_shot_result)/120)
+accuracy_hate <- rep(NA, nrow(one_shot_result)/120)
+precision_racism <- rep(NA, nrow(one_shot_result)/120)
+precision_sexism <- rep(NA, nrow(one_shot_result)/120)
+precision_hate <- rep(NA, nrow(one_shot_result)/120)
+recall_racism <- rep(NA, nrow(one_shot_result)/120)
+recall_sexism <- rep(NA, nrow(one_shot_result)/120)
+recall_hate <- rep(NA, nrow(one_shot_result)/120)
+f1_racism <- rep(NA, nrow(one_shot_result)/120)
+f1_sexism <- rep(NA, nrow(one_shot_result)/120)
+f1_hate <- rep(NA, nrow(one_shot_result)/120)
+
+# For each iteration:
+for (i in 1:(nrow(one_shot_result)/120)){
+  # Racism table
+  one_racism <- 
+    one_shot_result %>%
+    filter(category == "racist" & iter == i) %>%
+    select(category, label, answer, temperature) %>%
+    mutate(answer = tolower(answer) %>% trimws(),
+           label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                                str_detect(answer, "yes") ~ "Y",
+                                TRUE ~ "Other")) %>%
+    filter(answer_yn != "Other") %>%
+    count(label_yn, answer_yn) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+    mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
+                                label_yn == "Y" ~ "Racist")) %>%
+    rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
+  one_racism <- one_racism[, c("Actual classification", "Not racist", "Racist")]
+
+  # Sexism table
+  one_sexism <- 
+    one_shot_result %>%
+    filter(category == "sexist" & iter == i) %>%
+    select(category, label, answer, temperature) %>%
+    mutate(answer = tolower(answer) %>% trimws(),
+           label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                                str_detect(answer, "yes") ~ "Y",
+                                TRUE ~ "Other")) %>%
+    filter(answer_yn != "Other") %>%
+    count(label_yn, answer_yn) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+    mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
+                                label_yn == "Y" ~ "Sexist")) %>%
+    rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
+  one_sexism <- one_sexism[, c("Actual classification", "Not sexist", "Sexist")]
+
+  # Hate table
+  one_hate <- 
+    one_shot_result %>%
+    filter(iter == i) %>%
+    select(category, label, answer, temperature) %>%
+    mutate(answer = tolower(answer) %>% trimws(),
+           label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = case_when(str_detect(answer, "no") ~ "N",
+                                str_detect(answer, "yes") ~ "Y",
+                                TRUE ~ "Other")) %>%
+    filter(answer_yn != "Other") %>%
+    count(label_yn, answer_yn) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+    mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
+                                label_yn == "Y" ~ "Hate speech")) %>%
+    rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
+  one_hate <- one_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
+
+  # Compute accuracy/precision/recall/f1
+  tp_r <- one_racism[2, 3] %>% as.numeric()
+  tn_r <- one_racism[1, 2] %>% as.numeric()
+  fp_r <- one_racism[1, 3] %>% as.numeric()
+  fn_r <- one_racism[2, 2] %>% as.numeric()
+
+  tp_s <- one_sexism[2, 3] %>% as.numeric()
+  tn_s <- one_sexism[1, 2] %>% as.numeric()
+  fp_s <- one_sexism[1, 3] %>% as.numeric()
+  fn_s <- one_sexism[2, 2] %>% as.numeric()
+
+  tp_h <- one_hate[2, 3] %>% as.numeric()
+  tn_h <- one_hate[1, 2] %>% as.numeric()
+  fp_h <- one_hate[1, 3] %>% as.numeric()
+  fn_h <- one_hate[2, 2] %>% as.numeric()
+
+  one_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
+  one_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
+  one_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
+  one_racism_f1 <- ((2*one_racism_precision*one_racism_recall)/(one_racism_precision + one_racism_recall)) %>% round(2)
+
+  one_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
+  one_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
+  one_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
+  one_sexism_f1 <- ((2*one_sexism_precision*one_sexism_recall)/(one_sexism_precision + one_sexism_recall)) %>% round(2)
+
+  one_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
+  one_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
+  one_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
+  one_hate_f1 <- ((2*one_hate_precision*one_sexism_recall)/(one_hate_precision + one_hate_recall)) %>% round(2)
+
+  # Add to vectors
+  accuracy_racism[i] <- one_racism_accuracy
+  accuracy_sexism[i] <- one_sexism_accuracy
+  accuracy_hate[i] <- one_hate_accuracy
+  precision_racism[i] <- one_racism_precision
+  precision_sexism[i] <- one_sexism_precision
+  precision_hate[i] <- one_hate_precision
+  recall_racism[i] <- one_racism_recall
+  recall_sexism[i] <- one_sexism_recall
+  recall_hate[i] <- one_hate_recall
+  f1_racism[i] <- one_racism_f1
+  f1_sexism[i] <- one_sexism_f1
+  f1_hate[i] <- one_hate_f1
+}
+
+# Sample distributions of accuracy, precision, recall, and f1
+one_racism_summary <- cbind(iter = 1:length(accuracy_racism),
+                             accuracy_racism,
+                             precision_racism,
+                             recall_racism,
+                             f1_racism) %>% 
+  as_tibble() %>%
+  summarise(name = "Racism",
+            calc = "Mean",
+            accuracy = mean(accuracy_racism),
+            precision = mean(precision_racism),
+            recall = mean(recall_racism),
+            f1 = mean(f1_racism)) %>%
+  rbind(summarise(., name = "Racism",
+                    calc = "SE",
+                    accuracy = sd(accuracy_racism)/sqrt(n()),
+                    precision = sd(precision_racism)/sqrt(n()),
+                    recall = sd(recall_racism)/sqrt(n()),
+                    f1 = sd(f1_racism)/sqrt(n())))
+
+one_sexism_summary <- cbind(iter = 1:length(accuracy_sexism),
+                             accuracy_sexism,
+                             precision_sexism,
+                             recall_sexism,
+                             f1_sexism) %>% 
+  as_tibble() %>%
+  summarise(name = "Sexism",
+            calc = "Mean",
+            accuracy = mean(accuracy_sexism),
+            precision = mean(precision_sexism),
+            recall = mean(recall_sexism),
+            f1 = mean(f1_sexism)) %>%
+  rbind(summarise(., name = "Sexism",
+                  calc = "SE",
+                  accuracy = sd(accuracy_sexism)/sqrt(n()),
+                  precision = sd(precision_sexism)/sqrt(n()),
+                  recall = sd(recall_sexism)/sqrt(n()),
+                  f1 = sd(f1_sexism)/sqrt(n())))
+
+one_hate_summary <- cbind(iter = 1:length(accuracy_hate),
+                             accuracy_hate,
+                             precision_hate,
+                             recall_hate,
+                             f1_hate) %>% 
+  as_tibble() %>%
+  summarise(name = "Overall",
+            calc = "Mean",
+            accuracy = mean(accuracy_hate),
+            precision = mean(precision_hate),
+            recall = mean(recall_hate),
+            f1 = mean(f1_hate)) %>%
+  rbind(summarise(., name = "Overall",
+                  calc = "SE",
+                  accuracy = sd(accuracy_hate)/sqrt(n()),
+                  precision = sd(precision_hate)/sqrt(n()),
+                  recall = sd(recall_hate)/sqrt(n()),
+                  f1 = sd(f1_hate)/sqrt(n())))
+
+one_summary <- rbind(one_racism_summary, one_sexism_summary, one_hate_summary)
+
+one_summary %>% pivot_longer(cols = !c(name, calc), names_to = "metric") %>%
+  pivot_wider(names_from = c(calc), values_from = value) %>%
+  mutate(name = case_when(metric == "accuracy" ~ name, TRUE ~ ""),
+         metric = str_to_title(metric),
+         Mean = round(Mean),
+         SE = round(SE, 1)) %>%
+  knitr::kable(col.names = c("", "Metric", "Mean (%)", "Standard Error (%)"), 
+        caption = "Performance of model in one-shot learning across 100 classifications of each comment at a temperature of 0.3.",
+        booktabs = TRUE,
+        linesep = "") %>%
+  kableExtra::column_spec(column = 1, bold = TRUE)
 ```
@@
 
-```{r fewshotsingle-summary}
-# Racism
-few_shot_single_result <- read.csv(here::here("outputs/data/few_shot_single_results.csv"))
+```{r fewshotsingle-summary, message = FALSE}
+# Set-up data for zero-shot racism
+few_single_shot_result <-
+  read_csv(here::here("outputs/data/few_shot_single_results_multiple.csv"),
+           show_col_types = FALSE)
+
+# Add iter variable
+few_single_shot_result <- few_single_shot_result %>%
+  mutate(iter = floor(`...1`/120) + 1)
 
 few_shot_result_racism <-
-  few_shot_single_result %>%
-  filter(temperature == 0 & category == "racist") %>%
-  select(category, label, answer) %>%
-  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
-  mutate(answer_yn = ifelse(stringr::str_detect(answer, "not", negate = FALSE), "N", "Y")) %>%
+  few_single_shot_result %>%
+    filter(category == "racist") %>%
+    select(category, label, answer, temperature) %>%
+    mutate(label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = ifelse(grepl("not", answer), "N", "Y")) %>%
     count(label_yn, answer_yn) %>%
@@
 
-few_shot_result_racism <- few_shot_result_racism[, c("Actual classification", "Not racist", "Racist")]
-
-# Sexism
+few_shot_result_racism <-
+  few_shot_result_racism[, c("Actual classification", "Not racist", "Racist")]
+
 few_shot_result_sexism <- 
-  few_shot_single_result %>%
-  filter(temperature == 0 & category == "sexist") %>%
+    few_single_shot_result %>%
+    filter(category == "sexist") %>%
     select(category, label, answer, temperature) %>%
-  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
-  mutate(answer_yn = ifelse(stringr::str_detect(answer, "not", negate = FALSE), "N", "Y")) %>%
+    mutate(label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = ifelse(grepl("not", answer), "N", "Y")) %>%
     count(label_yn, answer_yn) %>%
@@
     rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
-
   few_shot_result_sexism <- few_shot_result_sexism[, c("Actual classification", "Not sexist", "Sexist")]
 
-# Hate speech
 few_shot_result_hate <- 
-  few_shot_single_result %>%
-  filter(temperature == 0) %>%
+    few_single_shot_result %>%
     select(category, label, answer, temperature) %>%
-  mutate(label_yn = ifelse(grepl("not", label), "N", "Y")) %>%
-  mutate(answer_yn = ifelse(stringr::str_detect(answer, "not", negate = FALSE), "N", "Y")) %>%
+    mutate(label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = ifelse(grepl("not", label), "N", "Y")) %>%
     count(label_yn, answer_yn) %>%
@@
     rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
-
 few_shot_result_hate <- few_shot_result_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
 
-# Bringing it all together
-tp_r <- few_shot_result_racism[2, 3] %>% as.numeric()
-tn_r <- few_shot_result_racism[1, 2] %>% as.numeric()
-fp_r <- few_shot_result_racism[1, 3] %>% as.numeric()
-fn_r <- few_shot_result_racism[2, 2] %>% as.numeric()
-
-tp_s <- few_shot_result_sexism[2, 3] %>% as.numeric()
-tn_s <- few_shot_result_sexism[1, 2] %>% as.numeric()
-fp_s <- few_shot_result_sexism[1, 3] %>% as.numeric()
-fn_s <- few_shot_result_sexism[2, 2] %>% as.numeric()
-
-tp_h <- few_shot_result_hate[2, 3] %>% as.numeric()
-tn_h <- few_shot_result_hate[1, 2] %>% as.numeric()
-fp_h <- few_shot_result_hate[1, 3] %>% as.numeric()
-fn_h <- few_shot_result_hate[2, 2] %>% as.numeric()
-
-few_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
-few_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
-few_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
-few_racism_f1 <- ((2*few_racism_precision*few_racism_recall)/(few_racism_precision + few_racism_recall)) %>% round(2)
-few_racism_all <- c(few_racism_accuracy, few_racism_precision, few_racism_recall, few_racism_f1)
-
-few_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
-few_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
-few_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
-few_sexism_f1 <- ((2*few_sexism_precision*few_sexism_recall)/(few_sexism_precision + few_sexism_recall)) %>% round(2)
-few_sexism_all <- c(few_sexism_accuracy, few_sexism_precision, few_sexism_recall, few_sexism_f1)
-
-few_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
-few_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
-few_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
-few_hate_f1 <- ((2*few_hate_precision*few_sexism_recall)/(few_hate_precision + few_hate_recall)) %>% round(2)
-few_hate_all <- c(few_hate_accuracy, few_hate_precision, few_hate_recall, few_hate_f1)
-
-few_shot_summary <- tibble(Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)), 
-                                   Metric = rep(c("Accuracy (%)", "Precision (%)", "Recall (%)", "F1 (%)"), 3), 
-                                   Percent = c(few_racism_all, few_sexism_all, few_hate_all)) %>%
-  pivot_wider(names_from = Metric, values_from = Percent)
-
-few_shot_summary %>%
-  knitr::kable(caption="Performance of single-category few-shot learning in hate speech classification",
-               digits = 0,
-               booktabs=TRUE) 
+accuracy_racism <- rep(NA, nrow(few_single_shot_result)/120)
+accuracy_sexism <- rep(NA, nrow(few_single_shot_result)/120)
+accuracy_hate <- rep(NA, nrow(few_single_shot_result)/120)
+precision_racism <- rep(NA, nrow(few_single_shot_result)/120)
+precision_sexism <- rep(NA, nrow(few_single_shot_result)/120)
+precision_hate <- rep(NA, nrow(few_single_shot_result)/120)
+recall_racism <- rep(NA, nrow(few_single_shot_result)/120)
+recall_sexism <- rep(NA, nrow(few_single_shot_result)/120)
+recall_hate <- rep(NA, nrow(few_single_shot_result)/120)
+f1_racism <- rep(NA, nrow(few_single_shot_result)/120)
+f1_sexism <- rep(NA, nrow(few_single_shot_result)/120)
+f1_hate <- rep(NA, nrow(few_single_shot_result)/120)
+
+# For each iteration:
+for (i in 1:(nrow(few_single_shot_result)/120)){
+  # Racism table
+  few_single_racism <- 
+    few_single_shot_result %>%
+    filter(category == "racist" & iter == i) %>%
+    select(category, label, answer, temperature) %>%
+    mutate(label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = ifelse(grepl("not", answer), "N", "Y")) %>%
+    count(label_yn, answer_yn) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+    mutate(label_yn = case_when(label_yn == "N" ~ "Not racist",
+                                label_yn == "Y" ~ "Racist")) %>%
+    rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
+  few_single_racism <- few_single_racism[, c("Actual classification", "Not racist", "Racist")]
+
+  # Sexism table
+  few_single_sexism <- 
+    few_single_shot_result %>%
+    filter(category == "sexist" & iter == i) %>%
+    select(category, label, answer, temperature) %>%
+    mutate(label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = ifelse(grepl("not", answer), "N", "Y")) %>%
+    count(label_yn, answer_yn) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+    mutate(label_yn = case_when(label_yn == "N" ~ "Not sexist",
+                                label_yn == "Y" ~ "Sexist")) %>%
+    rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
+  few_single_sexism <- few_single_sexism[, c("Actual classification", "Not sexist", "Sexist")]
+
+  # Hate table
+  few_single_hate <- 
+    few_single_shot_result %>%
+    filter(iter == i) %>%
+    select(category, label, answer, temperature) %>%
+    mutate(label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = ifelse(grepl("not", answer), "N", "Y")) %>%
+    count(label_yn, answer_yn) %>%
+    pivot_wider(names_from = answer_yn, values_from = n, values_fill = 0) %>%
+    mutate(label_yn = case_when(label_yn == "N" ~ "Not hate speech",
+                                label_yn == "Y" ~ "Hate speech")) %>%
+    rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
+  few_single_hate <- few_single_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
+
+  # Compute accuracy/precision/recall/f1
+  tp_r <- few_single_racism[2, 3] %>% as.numeric()
+  tn_r <- few_single_racism[1, 2] %>% as.numeric()
+  fp_r <- few_single_racism[1, 3] %>% as.numeric()
+  fn_r <- few_single_racism[2, 2] %>% as.numeric()
+
+  tp_s <- few_single_sexism[2, 3] %>% as.numeric()
+  tn_s <- few_single_sexism[1, 2] %>% as.numeric()
+  fp_s <- few_single_sexism[1, 3] %>% as.numeric()
+  fn_s <- few_single_sexism[2, 2] %>% as.numeric()
+
+  tp_h <- few_single_hate[2, 3] %>% as.numeric()
+  tn_h <- few_single_hate[1, 2] %>% as.numeric()
+  fp_h <- few_single_hate[1, 3] %>% as.numeric()
+  fn_h <- few_single_hate[2, 2] %>% as.numeric()
+
+  few_single_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
+  few_single_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
+  few_single_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
+  few_single_racism_f1 <- ((2*few_single_racism_precision*few_single_racism_recall)/(few_single_racism_precision + few_single_racism_recall)) %>% round(2)
+
+  few_single_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
+  few_single_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
+  few_single_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
+  few_single_sexism_f1 <- ((2*few_single_sexism_precision*few_single_sexism_recall)/(few_single_sexism_precision + few_single_sexism_recall)) %>% round(2)
+
+  few_single_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
+  few_single_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
+  few_single_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
+  few_single_hate_f1 <- ((2*few_single_hate_precision*few_single_sexism_recall)/(few_single_hate_precision + few_single_hate_recall)) %>% round(2)
+
+  # Add to vectors
+  accuracy_racism[i] <- few_single_racism_accuracy
+  accuracy_sexism[i] <- few_single_sexism_accuracy
+  accuracy_hate[i] <- few_single_hate_accuracy
+  precision_racism[i] <- few_single_racism_precision
+  precision_sexism[i] <- few_single_sexism_precision
+  precision_hate[i] <- few_single_hate_precision
+  recall_racism[i] <- few_single_racism_recall
+  recall_sexism[i] <- few_single_sexism_recall
+  recall_hate[i] <- few_single_hate_recall
+  f1_racism[i] <- few_single_racism_f1
+  f1_sexism[i] <- few_single_sexism_f1
+  f1_hate[i] <- few_single_hate_f1
+}
+
+# Sample distributions of accuracy, precision, recall, and f1
+few_single_racism_summary <- cbind(iter = 1:length(accuracy_racism),
+                             accuracy_racism,
+                             precision_racism,
+                             recall_racism,
+                             f1_racism) %>% 
+  as_tibble() %>%
+  summarise(name = "Racism",
+            calc = "Mean",
+            accuracy = mean(accuracy_racism),
+            precision = mean(precision_racism),
+            recall = mean(recall_racism),
+            f1 = mean(f1_racism)) %>%
+  rbind(summarise(., name = "Racism",
+                    calc = "SE",
+                    accuracy = sd(accuracy_racism)/sqrt(n()),
+                    precision = sd(precision_racism)/sqrt(n()),
+                    recall = sd(recall_racism)/sqrt(n()),
+                    f1 = sd(f1_racism)/sqrt(n())))
+
+few_single_sexism_summary <- cbind(iter = 1:length(accuracy_sexism),
+                             accuracy_sexism,
+                             precision_sexism,
+                             recall_sexism,
+                             f1_sexism) %>% 
+  as_tibble() %>%
+  summarise(name = "Sexism",
+            calc = "Mean",
+            accuracy = mean(accuracy_sexism),
+            precision = mean(precision_sexism),
+            recall = mean(recall_sexism),
+            f1 = mean(f1_sexism)) %>%
+  rbind(summarise(., name = "Sexism",
+                  calc = "SE",
+                  accuracy = sd(accuracy_sexism)/sqrt(n()),
+                  precision = sd(precision_sexism)/sqrt(n()),
+                  recall = sd(recall_sexism)/sqrt(n()),
+                  f1 = sd(f1_sexism)/sqrt(n())))
+
+few_single_hate_summary <- cbind(iter = 1:length(accuracy_hate),
+                             accuracy_hate,
+                             precision_hate,
+                             recall_hate,
+                             f1_hate) %>% 
+  as_tibble() %>%
+  summarise(name = "Overall",
+            calc = "Mean",
+            accuracy = mean(accuracy_hate),
+            precision = mean(precision_hate),
+            recall = mean(recall_hate),
+            f1 = mean(f1_hate)) %>%
+  rbind(summarise(., name = "Overall",
+                  calc = "SE",
+                  accuracy = sd(accuracy_hate)/sqrt(n()),
+                  precision = sd(precision_hate)/sqrt(n()),
+                  recall = sd(recall_hate)/sqrt(n()),
+                  f1 = sd(f1_hate)/sqrt(n())))
+
+few_single_summary <- rbind(few_single_racism_summary, few_single_sexism_summary, few_single_hate_summary)
+
+few_single_summary %>% pivot_longer(cols = !c(name, calc), names_to = "metric") %>%
+  pivot_wider(names_from = c(calc), values_from = value) %>%
+  mutate(name = case_when(metric == "accuracy" ~ name, TRUE ~ ""),
+         metric = str_to_title(metric),
+         Mean = round(Mean),
+         SE = round(SE, 1)) %>%
+  knitr::kable(col.names = c("", "Metric", "Mean (%)", "Standard Error (%)"), 
+        caption = "Performance of model in zero-shot learning across 100 classifications of each comment at a temperature of 0.3.",
+        booktabs = TRUE,
+        linesep = "") %>%
+  kableExtra::column_spec(column = 1, bold = TRUE)
 ```

### 2022-03-18 outputs/documents/paper.tex
Data collection for multiple iterations of few-shot single catgory, updates to tables in paper, begin updates to results sections

@@
 Please note that we have added asterisks to racial slurs and other offensive content in this paper, however the inputs and outputs did not have these.
-Comments on the 16 March 2022 version of this paper are welcome at: \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}  }
+Comments on the 18 March 2022 version of this paper are welcome at: \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}  }
 
@@
 
+For zero- and one-shot learning, each set of 120 comments was classified 100 times by GPT-3 in order to assess the variability of classifications at a temperature of 0.3.
+The reported performance metrics for these settings are the arithmetic means of each metric across all 100 iterations with the corresponding standard error.
+In some cases, the model outputted responses that were neither ``yes'' nor ``no''.
+These were counted as ``not applicable'' and omitted from analysis.
+Specific numbers are reported in the following sections.
+
 \hypertarget{zero-shot-learning-1}{%
@@
 The overall results of the zero-shot experiments are presented in Table \ref{tab:zeroshot-summary}, and Appendix \ref{appendixbzeroshot} provides additional detail.
-The model has 34 matches (true positives and negatives) and 26 mismatches (false positives and negatives) in the sexist category, and 41 matches and 19 mismatches in the racist category.
-The model performs more accurately when identifying racist comments, with an accuracy of 68 per cent, compared with identifying sexist comments, with an accuracy of 57 per cent, but the F1 score for each type of hate speech is roughly the same.
-The overall ratio of matches and mismatches is 75:45.
-In other words, the accuracy in identifying hate speech in the zero-shot setting is 63 per cent.
-The model has an F1 score of 81 per cent in this setting, with a notably high recall of 87 per cent.
+Out of 6000 classification for each category, the model has 3231 matches (true positives and negatives) and 2691 mismatches (false positives and negatives) in the sexist category, and 3463 matches and 2504 mismatches in the racist category.
+In the zero-shot learning setting, the model produced 111 responses that were inadmissible.
+The model performs more accurately when identifying racist comments, with an average accuracy of 58 per cent (SE = 6.5), compared with identifying sexist comments, with an average accuracy of 55 per cent (SE = 5.2).
+In contrast, the F1 score for classification of sexist speech is slightly higher on average at 63 per cent (SE = 4.3), compared with an average of 58 per cent (SE = 6.7) for racist speech.
+The overall ratio of matches and mismatches is 6694:5195.
+In other words, the average accuracy in identifying hate speech in the zero-shot setting is 56 per cent (SE = 4.6).
+The model has an average F1 score of 70 per cent (SE = 5.7) in this setting.
 
@@
 
-\caption{\label{tab:zeroshot-summary}Performance of zero-shot learning in hate speech classification}
-\centering
-\begin{tabular}[t]{lrrrr}
-\toprule
-Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
-\midrule
-Racism & 68 & 67 & 73 & 70\\
-Sexism & 57 & 54 & 100 & 70\\
-Overall & 62 & 58 & 87 & 81\\
+\caption{\label{tab:zeroshot-summary}Performance of model in zero-shot learning across 100 classifications of each comment at a temperature of 0.3.}
+\centering
+\begin{tabular}[t]{>{}llrr}
+\toprule
+ & Metric & Mean (\%) & Standard Error (\%)\\
+\midrule
+\textbf{Racism} & Accuracy & 58 & 6.5\\
+\textbf{} & Precision & 58 & 6.7\\
+\textbf{} & Recall & 59 & 9.2\\
+\textbf{} & F1 & 58 & 6.7\\
+\textbf{Sexism} & Accuracy & 55 & 5.2\\
+\textbf{} & Precision & 53 & 3.7\\
+\textbf{} & Recall & 79 & 6.9\\
+\textbf{} & F1 & 63 & 4.3\\
+\textbf{Overall} & Accuracy & 56 & 4.3\\
+\textbf{} & Precision & 55 & 3.5\\
+\textbf{} & Recall & 69 & 5.9\\
+\textbf{} & F1 & 70 & 5.7\\
 \bottomrule
@@
 
-\caption{\label{tab:oneshot-summary}Performance of one-shot learning in hate speech classification}
-\centering
-\begin{tabular}[t]{lrrrr}
-\toprule
-Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
-\midrule
-Racism & 62 & 59 & 80 & 68\\
-Sexism & 60 & 57 & 77 & 66\\
-Overall & 61 & 58 & 78 & 65\\
+\caption{\label{tab:oneshot-summary}Performance of model in one-shot learning across 100 classifications of each comment at a temperature of 0.3.}
+\centering
+\begin{tabular}[t]{>{}llrr}
+\toprule
+ & Metric & Mean (\%) & Standard Error (\%)\\
+\midrule
+\textbf{Racism} & Accuracy & 62 & 1.1\\
+\textbf{} & Precision & 58 & 0.8\\
+\textbf{} & Recall & 80 & 1.2\\
+\textbf{} & F1 & 67 & 0.9\\
+\textbf{Sexism} & Accuracy & 60 & 1.4\\
+\textbf{} & Precision & 57 & 1.1\\
+\textbf{} & Recall & 75 & 1.7\\
+\textbf{} & F1 & 65 & 1.2\\
+\textbf{Overall} & Accuracy & 61 & 0.9\\
+\textbf{} & Precision & 58 & 0.7\\
+\textbf{} & Recall & 77 & 1.0\\
+\textbf{} & F1 & 64 & 1.3\\
 \bottomrule
@@
 
-\caption{\label{tab:fewshotsingle-summary}Performance of single-category few-shot learning in hate speech classification}
-\centering
-\begin{tabular}[t]{lrrrr}
-\toprule
-Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
-\midrule
-Racism & 68 & 66 & 77 & 71\\
-Sexism & 70 & 75 & 60 & 67\\
-Overall & 69 & 69 & 68 & 61\\
+\caption{\label{tab:fewshotsingle-summary}Performance of model in zero-shot learning across 100 classifications of each comment at a temperature of 0.3.}
+\centering
+\begin{tabular}[t]{>{}llrr}
+\toprule
+ & Metric & Mean (\%) & Standard Error (\%)\\
+\midrule
+\textbf{Racism} & Accuracy & 69 & 1.3\\
+\textbf{} & Precision & 67 & 1.3\\
+\textbf{} & Recall & 77 & 1.5\\
+\textbf{} & F1 & 72 & 1.2\\
+\textbf{Sexism} & Accuracy & 73 & 1.4\\
+\textbf{} & Precision & 76 & 1.1\\
+\textbf{} & Recall & 66 & 2.5\\
+\textbf{} & F1 & 71 & 1.8\\
+\textbf{Overall} & Accuracy & 71 & 1.0\\
+\textbf{} & Precision & 71 & 0.9\\
+\textbf{} & Recall & 71 & 1.5\\
+\textbf{} & F1 & 65 & 2.2\\
 \bottomrule
@@
 \centering
-\includegraphics{comparison-1.pdf}
+\includegraphics{paper_files/figure-latex/comparison-1.pdf}
 \caption{\label{fig:comparison}Comparing classification with and without an instruction}
@@
 Another might be to consider a larger dataset of sexist and racist content, as one of the weaknesses of our approach is the relatively small dataset.
-The extent to which the identification and classification of hate speech can be explained is especially of interest for future work.
+The extent to which the identification and classification of hate speech can be explained by the model is especially of interest for future work.
 
@@
 8 & stone throwing must be legal when against women & This sick, disgusting, white terrorist/fascist killed more than 50 innocent people.
-& You can see the country is fertile and green.
-just need the right governance\\
+& You can see the country is fertile and green.  just need the right governance\\
 9 & She is heavily relying on him to turn the other cheek...tough talking demon infested woman.
@@
 10 & Really, I hope she get raped in the future.
-Raping women should be legal I think & The world would be better without white people because they stole from the black Egyptians in the before christ ages they was poor we wasnt whites  ruins everything for black people/White people have pig dicks and no shape no hips or no booty they have to get plastic surgery as us blacks get it from our mother whites brought skin cancer to america so learn some facts before you try to run us out america when we was here before yall racist ass smelly crackers and dont say you will beat my ass because you cant and if you wanna find out drop your adress & You are a brave man.........for letting them keep the comments enabled\\
+Raping women should be legal I think & The world would be better without white people because they stole from the black Egyptians in the before christ ages they was poor we wasnt whites  ruins everything for black people/White people have pig dicks and no shape no hips or no booty they have to get plastic surgery as us blacks get it from our mother whites brought skin cancer to america so learn some facts before you try to run us out america when we was here before yall racist ass smelly crackers and dont say you will beat my ass because you cant and if you wanna find out drop your adress√∞¬ü¬Ü¬ó√Ø¬∏¬è√∞¬ü¬í¬Ø√∞¬ü¬ô¬Ç & You are a brave man.........for letting them keep the comments enabled\\
 \bottomrule
@@
 \midrule
-Not racist & 19 & 11\\
-Racist & 8 & 22\\
+Not racist & 1688 & 1295\\
+Racist & 1209 & 1775\\
 \bottomrule
@@
 \midrule
-Not sexist & 4 & 26\\
-Sexist & 0 & 30\\
+Not sexist & 923 & 2072\\
+Sexist & 619 & 2308\\
 \bottomrule
@@
 \midrule
-Not hate speech & 23 & 37\\
-Hate speech & 8 & 52\\
+Not hate speech & 2611 & 3367\\
+Hate speech & 1828 & 4083\\
 \bottomrule
@@
 \midrule
-Not racist & 13 & 17\\
-Racist & 6 & 24\\
+Not racist & 1301 & 1699\\
+Racist & 608 & 2392\\
 \bottomrule
@@
 \midrule
-Not sexist & 13 & 17\\
-Sexist & 7 & 23\\
+Not sexist & 1378 & 1622\\
+Sexist & 730 & 2170\\
 \bottomrule
@@
 \midrule
-Not hate speech & 26 & 34\\
-Hate speech & 13 & 47\\
+Not hate speech & 2679 & 3321\\
+Hate speech & 1338 & 4562\\
 \bottomrule
@@
 \midrule
-Not racist & 18 & 12\\
-Racist & 7 & 23\\
+Not racist & 1844 & 1156\\
+Racist & 683 & 2317\\
 \bottomrule
@@
 \midrule
-Not sexist & 24 & 6\\
-Sexist & 12 & 18\\
+Not sexist & 2392 & 608\\
+Sexist & 1031 & 1969\\
 \bottomrule
@@
 \midrule
-Not hate speech & 42 & 18\\
-Hate speech & 19 & 41\\
+Not hate speech & 6000 & 0\\
+Hate speech & 0 & 6000\\
 \bottomrule

### 2022-03-18 inputs/data_collection_private.py

@@ -11,8 +11,8 @@ import pandas as pd
 import numpy as np
 import time
 import random
-openai.organization = "INSERT ORG ID"
-openai.api_key = "INSERT API KEY"
+openai.organization = "INPUT ORG KEY"
+openai.api_key = "INPUT API KEY"
 
 
 # In[3]:
@@ -62,20 +62,24 @@ def zero_shot(cat, label, comment, temperature):
 
 all_zero_shot_result = pd.DataFrame()   # Create empty data frame
 # Sexist, Temperature = 0
-for i, sexist_comment in enumerate(sexist[0:30].comment):  # Loop through first 30 comments in sexist, where i is index number (0-29) and sexist_comment is comment as a string
-    not_sexist_comment = not_hate.reset_index().comment[i]  # Extract comment i from not_hate
-    zero_shot_sexist_result = zero_shot("sexist", "sexist", sexist_comment, temperature = 0)    # Run sexist_comment through GPT-3
-    all_zero_shot_result = all_zero_shot_result.append(zero_shot_sexist_result, ignore_index=True)  # Add results for sexist_comment to all results
-    zero_shot_sexist_result = zero_shot("sexist", "not-sexist", not_sexist_comment, temperature = 0)    # Run not_sexist_comment through GPT-3
-    all_zero_shot_result = all_zero_shot_result.append(zero_shot_sexist_result, ignore_index=True)      # Add results for not_sexist_comment to all results
+j = 0
+while j < 500:
+    print("Zero shot learning, iteration {}".format(j))
+    for i, sexist_comment in enumerate(sexist[0:30].comment):  # Loop through first 30 comments in sexist, where i is index number (0-29) and sexist_comment is comment as a string
+        not_sexist_comment = not_hate.reset_index().comment[i]  # Extract comment i from not_hate
+        zero_shot_sexist_result = zero_shot("sexist", "sexist", sexist_comment, temperature = 0.3)    # Run sexist_comment through GPT-3
+        all_zero_shot_result = all_zero_shot_result.append(zero_shot_sexist_result, ignore_index=True)  # Add results for sexist_comment to all results
+        zero_shot_sexist_result = zero_shot("sexist", "not-sexist", not_sexist_comment, temperature = 0.3)    # Run not_sexist_comment through GPT-3
+        all_zero_shot_result = all_zero_shot_result.append(zero_shot_sexist_result, ignore_index=True)      # Add results for not_sexist_comment to all results
 
-# Racist, Temperature = 0
[…]

### 2022-03-23 Testing-multiple-iterations.Rmd
Higher temp few shot learning and updates to paper

@@
 
-```{r oneshot-summary, message=FALSE}
+```{r fewshot-summary, message=FALSE}
 # Add iter variable
@@
   # Racism table
-  one_racism <- 
+  few_racism <- 
     few_shot_multiple %>%
@@
     select(category, label, answer, temperature) %>%
-    mutate(answer = tolower(answer) %>% trimws(),
-           label_yn = ifelse(grepl("not", label), "N", "Y"),
-           answer_yn = case_when(str_detect(answer, "no") ~ "N",
-                                str_detect(answer, "yes") ~ "Y",
-                                TRUE ~ "Other")) %>%
-    filter(answer_yn != "Other") %>%
+    mutate(label_yn = ifelse(grepl("not", label), "N", "Y"),
+           answer_yn = ifelse(grepl("not", answer), "N", "Y")) %>%
     count(label_yn, answer_yn) %>%
@@
     rename("Actual classification" = label_yn, "Not racist" = N, "Racist" = Y)
-  one_racism <- one_racism[, c("Actual classification", "Not racist", "Racist")]
+  few_racism <- few_racism[, c("Actual classification", "Not racist", "Racist")]
 
   # Sexism table
-  one_sexism <- 
+  few_sexism <- 
     few_shot_multiple %>%
@@
     rename("Actual classification" = label_yn, "Not sexist" = N, "Sexist" = Y)
-  one_sexism <- one_sexism[, c("Actual classification", "Not sexist", "Sexist")]
+  few_sexism <- few_sexism[, c("Actual classification", "Not sexist", "Sexist")]
 
   # Hate table
-  one_hate <- 
+  few_hate <- 
     few_shot_multiple %>%
@@
     rename("Actual classification" = label_yn, "Not hate speech" = N, "Hate speech" = Y)
-  one_hate <- one_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
+  few_hate <- few_hate[, c("Actual classification", "Not hate speech", "Hate speech")]
 
   # Compute accuracy/precision/recall/f1
-  tp_r <- one_racism[2, 3] %>% as.numeric()
-  tn_r <- one_racism[1, 2] %>% as.numeric()
-  fp_r <- one_racism[1, 3] %>% as.numeric()
-  fn_r <- one_racism[2, 2] %>% as.numeric()
+  tp_r <- few_racism[2, 3] %>% as.numeric()
+  tn_r <- few_racism[1, 2] %>% as.numeric()
+  fp_r <- few_racism[1, 3] %>% as.numeric()
+  fn_r <- few_racism[2, 2] %>% as.numeric()
 
-  tp_s <- one_sexism[2, 3] %>% as.numeric()
-  tn_s <- one_sexism[1, 2] %>% as.numeric()
-  fp_s <- one_sexism[1, 3] %>% as.numeric()
-  fn_s <- one_sexism[2, 2] %>% as.numeric()
+  tp_s <- few_sexism[2, 3] %>% as.numeric()
+  tn_s <- few_sexism[1, 2] %>% as.numeric()
+  fp_s <- few_sexism[1, 3] %>% as.numeric()
+  fn_s <- few_sexism[2, 2] %>% as.numeric()
 
-  tp_h <- one_hate[2, 3] %>% as.numeric()
-  tn_h <- one_hate[1, 2] %>% as.numeric()
-  fp_h <- one_hate[1, 3] %>% as.numeric()
-  fn_h <- one_hate[2, 2] %>% as.numeric()
+  tp_h <- few_hate[2, 3] %>% as.numeric()
+  tn_h <- few_hate[1, 2] %>% as.numeric()
+  fp_h <- few_hate[1, 3] %>% as.numeric()
+  fn_h <- few_hate[2, 2] %>% as.numeric()
 
-  one_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
-  one_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
-  one_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
-  one_racism_f1 <- ((2*one_racism_precision*one_racism_recall)/(one_racism_precision + one_racism_recall)) %>% round(2)
+  few_racism_accuracy <- ((tp_r + tn_r)/(tp_r + tn_r + fp_r + fn_r)) %>% round(4)*100
+  few_racism_precision <- (tp_r/(tp_r + fp_r)) %>% round(4)*100
+  few_racism_recall <- (tp_r/(tp_r + fn_r)) %>% round(4)*100
+  few_racism_f1 <- ((2*few_racism_precision*few_racism_recall)/(few_racism_precision + few_racism_recall)) %>% round(2)
 
-  one_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
-  one_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
-  one_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
-  one_sexism_f1 <- ((2*one_sexism_precision*one_sexism_recall)/(one_sexism_precision + one_sexism_recall)) %>% round(2)
+  few_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100
+  few_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100
+  few_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100
+  few_sexism_f1 <- ((2*few_sexism_precision*few_sexism_recall)/(few_sexism_precision + few_sexism_recall)) %>% round(2)
 
-  one_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
-  one_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
-  one_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
-  one_hate_f1 <- ((2*one_hate_precision*one_sexism_recall)/(one_hate_precision + one_hate_recall)) %>% round(2)
+  few_hate_accuracy <- ((tp_h + tn_h)/(tp_h + tn_h + fp_h + fn_h)) %>% round(4)*100
+  few_hate_precision <- (tp_h/(tp_h + fp_h)) %>% round(4)*100
+  few_hate_recall <- (tp_h/(tp_h + fn_h)) %>% round(4)*100
+  few_hate_f1 <- ((2*few_hate_precision*few_sexism_recall)/(few_hate_precision + few_hate_recall)) %>% round(2)
 
   # Add to vectors
-  accuracy_racism[i] <- one_racism_accuracy
-  accuracy_sexism[i] <- one_sexism_accuracy
-  accuracy_hate[i] <- one_hate_accuracy
-  precision_racism[i] <- one_racism_precision
-  precision_sexism[i] <- one_sexism_precision
-  precision_hate[i] <- one_hate_precision
-  recall_racism[i] <- one_racism_recall
-  recall_sexism[i] <- one_sexism_recall
-  recall_hate[i] <- one_hate_recall
-  f1_racism[i] <- one_racism_f1
-  f1_sexism[i] <- one_sexism_f1
-  f1_hate[i] <- one_hate_f1
+  accuracy_racism[i] <- few_racism_accuracy
+  accuracy_sexism[i] <- few_sexism_accuracy
+  accuracy_hate[i] <- few_hate_accuracy
+  precision_racism[i] <- few_racism_precision
+  precision_sexism[i] <- few_sexism_precision
+  precision_hate[i] <- few_hate_precision
+  recall_racism[i] <- few_racism_recall
+  recall_sexism[i] <- few_sexism_recall
+  recall_hate[i] <- few_hate_recall
+  f1_racism[i] <- few_racism_f1
+  f1_sexism[i] <- few_sexism_f1
+  f1_hate[i] <- few_hate_f1
 }
@@
 # Sample distributions of accuracy, precision, recall, and f1
-one_racism_summary <- cbind(iter = 1:length(accuracy_racism),
+few_racism_summary <- cbind(iter = 1:length(accuracy_racism),
                              accuracy_racism,
@@
 
-one_sexism_summary <- cbind(iter = 1:length(accuracy_sexism),
+few_sexism_summary <- cbind(iter = 1:length(accuracy_sexism),
                              accuracy_sexism,
@@
 
-one_hate_summary <- cbind(iter = 1:length(accuracy_hate),
+few_hate_summary <- cbind(iter = 1:length(accuracy_hate),
                              accuracy_hate,
@@
 
-one_summary <- rbind(one_racism_summary, one_sexism_summary, one_hate_summary)
+few_summary <- rbind(few_racism_summary, few_sexism_summary, few_hate_summary)
 
-one_summary %>% pivot_longer(cols = !c(name, calc), names_to = "metric") %>%
+few_summary %>% pivot_longer(cols = !c(name, calc), names_to = "metric") %>%
   pivot_wider(names_from = c(calc), values_from = value) %>%
@@
 ```
+
+# Few-shot multiple category
+
+```{r}
+few_shot_mixed_multiple <- read.csv("outputs/data/few_shot_fixed_examples_results_multiple.csv")
+
+# Take only first iteration at temp = 0.3
+few_shot_mixed_multiple <- few_shot_mixed_multiple %>% slice(0:2400)
+```

### 2022-03-23 outputs/documents/paper.tex
Higher temp few shot learning and updates to paper

@@
 Please note that we have added asterisks to racial slurs and other offensive content in this paper, however the inputs and outputs did not have these.
-Comments on the 18 March 2022 version of this paper are welcome at: \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}  }
+Comments on the 23 March 2022 version of this paper are welcome at: \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}  }
 
@@
 We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning.
-We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an accuracy between 57 per cent and 68 per cent depending on the category of text and type of learning.
-With few-shot learning, the model's accuracy can be as high as 88 per cent.
+We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an average accuracy between 55 per cent and 67 per cent depending on the category of text and type of learning.
+With few-shot learning, the model's accuracy can be as high as 85 per cent.
 Large language models have a role to play in hate speech detection, and with further development could eventually be used to counter hate speech.
@@
 For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text \citep{hovy2016social}.
-In this paper we are interested in whether large language models, given that they can produce harmful language, can also identify, or learn to identify, harmful language.
+In this paper we are interested in whether large language models, given that they can produce harmful language, can also identify (or learn to identify) harmful language.
 
@@
 We find that the model performs best with mixed-category few-shot learning.
-In that setting the model can accurately classify around 86 per cent of the racist extracts and 88 per cent of sexist extracts.
+In that setting the model can accurately classify around 83 per cent of the racist extracts and 85 per cent of sexist extracts on average, with F1 scores of 79 per cent and 77 per cent respectively.
 If language models can be used to identify abusive language, then not only is there potential for them to counter the production of abusive language by humans, but they could also potentially self-police.
@@
 Lower temperatures mean that the model places more weight on higher-probability tokens.
-To explore potential variations in the classifications of comments, the temperature is set to 0.3 in our experiments for the zero- and one-shot settings and not varied.
-In all few-shot settings, the temperature is set to zero.
+To explore the variability in the classifications of comments, the temperature is set to 0.3 in our experiments.
 There are two categories of hate speech that are of interest in this paper.
@@
 One-shot learning means that one example is provided, and few-shot means that two or more examples are provided.
+All classification tasks were performed on the Davinci engine, GPT-3's most powerful and recently trained engine.
 
@@
 A simple instruction is given asking the model to answer only `Yes' or `No'.
-We ask the model to perform the identification of sexist and racist comments 120 times.
-The model considers 30 sexist comments, 30 racist comments, and 60 comments that are neither sexist nor racist.
+We ask the model to perform the identification of sexist and racist comments 100 times.
+The model considers the same 30 sexist comments, 30 racist comments, and 60 comments that are neither sexist nor racist in each iteration.
 An example of zero-shot learning for recognizing a comment that is labeled as sexist is:
@@
 In the one-shot learning case, the model is given one example from a category and is asked to identify whether the next passage of text belongs to the selected category.
-Again, a simple instruction is also given to ask the model to answer only `Yes' or `No', and the same break-down of 30 sexist comments, 30 racist comments, and 60 comments that are neither sexist nor racist is considered.
-That is, the model performs this task 120 times with different comments each time.
+Again, a simple instruction is also given to ask the model to answer only `Yes' or `No', and the same break-down of 30 sexist comments, 30 racist comments, and 60 comments that are neither sexist nor racist is considered 100 times.
+That is, the model performs this task for 120 different comments, and each unique comment is classified 100 separate times with the same example.
 An example of one-shot learning for recognizing a comment that is labelled as sexist is:
@@
 To simplify the classification procedure and allow for comparisons between different example inputs, we created ten example sets against which 240 comments were each classified.
-We elected to use ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset tractable.
+We elected to use ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset, tractable.
 The example sets each consist of one sexist, one racist, and one `neither' comment and were created using the comments at indexes one through ten from each dataset.
@@
 Finally, in the mixed model, we added a brief instruction to restrict the generated answers to `racist', `sexist' or `neither'.
-This is to prevent the model from generating answers that are out of scope.
+This is an attempt to prevent the model from generating answers that are out of scope.
 An example of this is:
@@
 The reported performance metrics for these settings are the arithmetic means of each metric across all 100 iterations with the corresponding standard error.
-In some cases, the model outputted responses that were neither ``yes'' nor ``no''.
+In the zero-shot setting, the model sometimes outputted responses that were neither ``yes'' nor ``no''.
 These were counted as ``not applicable'' and omitted from analysis.
-Specific numbers are reported in the following sections.
+Specific numbers are reported in the following section.
 
@@
 Out of 6000 classification for each category, the model has 3231 matches (true positives and negatives) and 2691 mismatches (false positives and negatives) in the sexist category, and 3463 matches and 2504 mismatches in the racist category.
-In the zero-shot learning setting, the model produced 111 responses that were inadmissible.
+In this setting, the model sometimes outputted responses that were neither ``yes'' nor ``no''.
+This occurred for 111 classifications, which were subsequently omitted from analysis.
 The model performs more accurately when identifying racist comments, with an average accuracy of 58 per cent (SE = 6.5), compared with identifying sexist comments, with an average accuracy of 55 per cent (SE = 5.2).
@@
 The results of the one-shot learning experiments are presented in Table \ref{tab:oneshot-summary}, and Appendix \ref{appendixboneshot} provides additional detail.
-The model has 37 matches and 23 mismatches in the racist category, and 36 matches and 24 mismatches in the sexist category.
-In contrast with the result generated from zero-shot learning, the model performs roughly the same in terms of identifying racist comments and identifying sexist comments.
-The overall ratio of matches and mismatches is 73:47.
-In other words, the accuracy of identifying hate speech in the one-shot setting is 61 per cent.
-The general performance in the one-shot setting is worse than in the zero-shot setting, with lower accuracy, recall, precision, and F1 score overall.
+Out of 6000 classifications each, the model produced 3284 matches and 2668 mismatches in the racist category, and 3236 matches and 2631 mismatches in the sexist category.
+Unlike the results generated from zero-shot learning, the model performs approximately the same when identifying sexist and racist comments, with an average accuracy of 55 per cent (SE = 6.4) and an F1 score of 58 per cent (SE = 6.5) when identifying racist comments, compared with sexist comments at an accuracy of 55 per cent (SE = 5.8) and an F1 score of 56 per cent (SE = 6.3).
+The overall ratio of matches and mismatches is 6520:5326.
+In other words, the average accuracy of identifying hate speech in the one-shot setting is 55 per cent (SE = 4.1).
+The general performance in the one-shot setting is nearly the same as in the zero-shot setting, with an overall average accuracy of 55 per cent compared with 56 per cent (SE = 4.6) in the zero-shot setting.
+However, the F1 score in the one-shot setting is much lower than in the zero-shot setting at 55 per cent (SE = 7.3) compared with 70 per cent (SE = 5.7).
 
@@
 \midrule
-\textbf{Racism} & Accuracy & 62 & 1.1\\
-\textbf{} & Precision & 58 & 0.8\\
-\textbf{} & Recall & 80 & 1.2\\
-\textbf{} & F1 & 67 & 0.9\\
-\textbf{Sexism} & Accuracy & 60 & 1.4\\
-\textbf{} & Precision & 57 & 1.1\\
-\textbf{} & Recall & 75 & 1.7\\
-\textbf{} & F1 & 65 & 1.2\\
-\textbf{Overall} & Accuracy & 61 & 0.9\\
-\textbf{} & Precision & 58 & 0.7\\
-\textbf{} & Recall & 77 & 1.0\\
-\textbf{} & F1 & 64 & 1.3\\
+\textbf{Racism} & Accuracy & 55 & 6.4\\
+\textbf{} & Precision & 55 & \vphantom{1} 5.9\\
+\textbf{} & Recall & 62 & 8.7\\
+\textbf{} & F1 & 58 & 6.5\\
+\textbf{Sexism} & Accuracy & 55 & 5.8\\
+\textbf{} & Precision & 55 & 5.9\\
+\textbf{} & Recall & 58 & 8.4\\
+\textbf{} & F1 & 56 & 6.3\\
+\textbf{Overall} & Accuracy & 55 & 4.1\\
+\textbf{} & Precision & 55 & 3.9\\
+\textbf{} & Recall & 60 & 5.6\\
+\textbf{} & F1 & 55 & 7.3\\
 \bottomrule
@@
 The results of the single-category, few-shot learning, experiments are presented in Table \ref{tab:fewshotsingle-summary}, and Appendix \ref{appendixbfewshotsingle} provides additional detail.
-The model has 41 matches and 19 mismatches in the racist category, and 42 matches and 18 mismatches in the sexist category.
-Like the one-shot setting, the model performs almost equally well in terms of identifying racist comments compared with identifying sexist comments.
-The general performance in the single-category few-shot learning setting is slightly more accurate than performance in other settings, with an accuracy of 69 per cent compared with 61 per cent in the one-shot setting and 63 per cent in the zero-shot setting.
-But, in this context we see the lowest F1 score of the settings considered thus far at 61 per cent.
+The model has 3862 matches and 2138 mismatches in the racist category, and 4209 matches and 1791 mismatches in the sexist category.
+Unlike in the zero- and one-shot settings, the model performs slightly better when identifying sexist comments compared with identifying racist comments.
+The general performance in the single-category few-shot learning setting is more accurate than performance in other settings, with an accuracy of 67 per cent (SE = 2.7) compared with 55 per cent in the one-shot setting (SE = 4.1) and 56 per cent (SE = 4.3) in the zero-shot setting.
+The average F1 score in this setting is 62 per cent (SE = 4.9) which is similar to the results of the one-shot setting but slightly lower than in the zero-shot setting.
 
@@
 
-\caption{\label{tab:fewshotsingle-summary}Performance of model in zero-shot learning across 100 classifications of each comment at a temperature of 0.3.}
+\caption{\label{tab:fewshotsingle-summary}Performance of model in single category few-shot learning across 100 classifications of each comment at a temperature of 0.3.}
 \centering
@@
 \midrule
-\textbf{Racism} & Accuracy & 69 & 1.3\\
-\textbf{} & Precision & 67 & 1.3\\
-\textbf{} & Recall & 77 & 1.5\\
-\textbf{} & F1 & 72 & 1.2\\
-\textbf{Sexism} & Accuracy & 73 & 1.4\\
-\textbf{} & Precision & 76 & 1.1\\
-\textbf{} & Recall & 66 & 2.5\\
-\textbf{} & F1 & 71 & 1.8\\
-\textbf{Overall} & Accuracy & 71 & 1.0\\
-\textbf{} & Precision & 71 & 0.9\\
-\textbf{} & Recall & 71 & 1.5\\
-\textbf{} & F1 & 65 & 2.2\\
+\textbf{Racism} & Accuracy & 64 & 4.2\\
+\textbf{} & Precision & 62 & 3.9\\
+\textbf{} & Recall & 74 & 4.9\\
+\textbf{} & F1 & 67 & 3.7\\
+\textbf{Sexism} & Accuracy & 70 & 3.3\\
+\textbf{} & Precision & 74 & 3.7\\
+\textbf{} & Recall & 62 & 5.9\\
+\textbf{} & F1 & 68 & 4.3\\
+\textbf{Overall} & Accuracy & 67 & 2.7\\
+\textbf{} & Precision & 67 & 2.7\\
+\textbf{} & Recall & 68 & 4.0\\
+\textbf{} & F1 & 62 & 4.9\\
 \bottomrule
@@
 The results of the mixed-category few-shot experiments are presented in Table \ref{tab:fewshotmixed-summary}, and Appendix \ref{appendxbmuxedubsnorinstruction} provides additional detail.
-Among the ten sets of examples, Example Set 1 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments and Example Set 10 yields the best performance by the same metrics for sexist comments (accuracy of 89 per cent, F1 score of 85 per cent).
-The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 70 per cent (and the lowest accuracy at 73 per cent) for this dataset.
-The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 74 per cent) for this dataset.
-The differences between Example Sets 1, 8, 9, and 10 suggest that, although the models are provided with the same number of examples, the content of the examples also affects how the model makes inferences.
+Among the ten sets of examples, Example Set 10 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments.
+The model performs with similar accuracy for identifying racist comments across most of the example sets (approximately 87 per cent), however the highest F1 score results from Example Set 10 once again.
+The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 69 per cent (and the lowest accuracy at 70 per cent) for this dataset.
+The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 76 per cent) for this dataset.
+The differences between Example Sets 8, 9, and 10 suggest that, although the models are provided with the same number of examples, the content of the examples also affects how the model makes inferences.
 Overall, the mixed-category few-shot setting performs roughly the same in terms of identifying sexist text and racist text.
-It also has higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
+It also has distinctly higher accuracy and F1 score overall than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
 
@@
 \midrule
-1 & Racism & 91 & 82 & 92 & 87\\
- & Sexism & 87 & 86 & 72 & 78\\
-\midrule
-2 & Racism & 88 & 79 & 88 & 83\\
+1 & Racism & 90 & 81 & 92 & 86\\
+ & Sexism & 86 & 85 & 68 & 76\\
+\midrule
+2 & Racism & 85 & 74 & 85 & 79\\
+ & Sexism & 87 & 82 & 77 & \vphantom{2} 79\\
+\midrule
+3 & Racism & 86 & 73 & 93 & 82\\
+ & Sexism & 87 & 82 & 77 & \vphantom{1} 79\\
+\midrule
+4 & Racism & 83 & 67 & 100 & 80\\
+ & Sexism & 85 & 76 & 80 & 78\\
+\midrule
+5 & Racism & 83 & 67 & 95 & 79\\
+ & Sexism & 87 & 78 & 83 & \vphantom{1} 81\\
+\midrule
+6 & Racism & 84 & 69 & 97 & 81\\
+ & Sexism & 84 & 74 & 80 & 77\\
+\midrule
+7 & Racism & 79 & 62 & 98 & 76\\
  & Sexism & 87 & 82 & 77 & 79\\
 \midrule
-3 & Racism & 87 & 74 & 93 & 82\\
- & Sexism & 84 & 79 & 73 & 76\\
-\midrule
-4 & Racism & 84 & 69 & 98 & 81\\
- & Sexism & 83 & 72 & 80 & 76\\
-\midrule
-5 & Racism & 80 & 64 & 93 & 76\\
- & Sexism & 86 & 82 & 75 & 78\\
-\midrule
-6 & Racism & 86 & 71 & 98 & 83\\
- & Sexism & 86 & 77 & 80 & 79\\
-\midrule
-7 & Racism & 77 & 59 & 97 & 73\\
- & Sexism & 87 & 85 & 73 & 79\\
-\midrule
-8 & Racism & 73 & 55 & 95 & 70\\
- & Sexism & 83 & 70 & 85 & 77\\
-\midrule
-9 & Racism & 80 & 63 & 97 & 76\\
- & Sexism & 74 & 57 & 85 & 68\\
-\midrule
-10 & Racism & 88 & 77 & 90 & 83\\
- & Sexism & 89 & 83 & 87 & 85\\
+8 & Racism & 72 & 54 & 97 & 69\\
+ & Sexism & 83 & 71 & 82 & 76\\
+\midrule
+9 & Racism & 78 & 61 & 95 & 74\\
+ & Sexism & 76 & 60 & 82 & 69\\
+\midrule
+10 & Racism & 91 & 82 & 92 & 87\\
+ & Sexism & 87 & 78 & 83 & 81\\
 \midrule
 All & Racism & 83 & 68 & 94 & 79\\
- & Sexism & 84 & 76 & 79 & 77\\
+ & Sexism & 85 & 76 & 79 & 77\\
 \bottomrule
@@
 For instance, other than `sexist', `racist', and `neither', we also see answers such as `transphobic', `hypocritical', `Islamophobic', and `ableist'.
-In some cases, the model even classifies a text passage into more than one category, such as `sexist, racist' and `sexist, misogynistic'.
-The full list contains eighty different answers instead of three.
+In some cases, the model even classifies a text passage into more than one category, such as `sexist, racist' and `sexist and misogynistic'.
+The full list contains 143 different answers instead of three.
 
@@
 \toprule
-racist | neither | homophobic | sexist | sexist, racist, | sexual assault | religious | sexual harassment | racist, sexist, | transphobic | hypocritical | I'm not a | I'm not brave | none of your business | I didn't | I'm not offended | you're not | sexual | I don't play | I don't care | I don't know | victim blaming | it's a question | irrelevant | I'm not crazy | creepy | romantic | I was taught to | I didn't say | ignorant | I'm not sure | I agree | not true | not even wrong | YouTube doesn't remove | socialist | conspiracy theorist | overpopulation | ableist | Islamophobic | conspiracy theory | hippie | sexist, rape ap | cliche | not even close to | nostalgic | I don't think | not a question | hippy | terrorist | hate speech | he was a terrorist | preachy | not a valid argument | not sexist | brave | Islamophobe | because you're a | troll | mental | never | pedophilia | mental illness is not | I'm sure you | I'm not going | not even close | grammar | rape apologist | cliché | vegan | sexist, misogynistic | I do | wrong | funny | question | when you were taught | opinion | emotional | conspiracy | nostalgia\\
+racist |  racist, homophobic, |  neither |  homophobic |  nazi |  neither, but the |  sexist |  sexist, racist, |  I don't know |  sexual assault |  religious |  sexual harassment |  sexist, misogynist |  sexual |  racist and sexist |  transphobic |  I'm not talking |  hypocritical |  I don't |  I'm a robot |  brave |  lolwut |  I do |  you're not alone |  I didn't |  you are probably not |  no one cares |  victim blaming |  you're the one |  irrelevant |  sarcastic |  not a question |  not funny |  I was taught to |  no one is |  hate speech |  I'm not sure |  creepy |  I am aware of |  what tables?
+|  emotional biass |  they were not in |  nostalgic |  I agree |  none |  no |  not true |  I'm not going |  racist, sexist, |  opinion |  not even wrong |  hippy |  they're not |  socialist |  misogynistic |  a question |  romantic |  not a good argument |  emotional bi ass |  not racist |  conspiracy theorist |  overpopulation |  ableist |  Islamophobic |  conspiracy theory |  environmentalist |  racist, sexist and |  mean |  not a quote |  cliche |  neither, but it |  none of the above |  I don't think |  this is a common |  Not a bad thing |  subjective |  funny |  hippie |  racist and homophobic |  racist, xenophobic |  violent |  sexist, racist |  sexist, ableist |  sexist, misogynistic |  none of your business |  stupid |  you're not |  both |  the same time when |  you're a f |  he was already dead |  circular reasoning |  SJW |  political |  not even close |  misinformed |  preachy |  racist, homophobic |  sexist, rape ap |  sexist, and also |  muslim |  freedom |  no one |  it's a question |  mental |  A phrase used by |  liar |  mental illness is a |  I'm sure you |  I don't have |  not sexist, racist |  sexist and misogynistic |  sexual threat |  not a comment |  not a big deal |  conspiracy |  sexist and transph |  mental illness is not |  not a single error |  grammar |  rape apologist |  pedophilia |  a bit of a |  cliché |  ignorant |  I don't care |  a lie |  vegan |  YouTube doesn't remove |  misogynist |  you are watching this |  offensive |  none of these |  they could have shot |  copypasta |  wrong |  death threats |  who |  I like PUB |  question |  too many people |  false |  not a troll\\
 \bottomrule
@@
 To reduce the chance of the model generating answers that are out of scope, a brief instruction is added to the prompt, specifying that the answers be: `sexist', `racist', or `neither'.
-The addition of an instruction successfully restricts the generated answers within the specified terms.
-The unique generated answers are: `racist', `sexist', and `neither'.
+The addition of an instruction successfully restricts the generated answers within the specified terms with the exception of three responses: one classification of ``racist and sexist'' and two classifications of ``both''.
+These responses were likely a result of randomness introduced by the non-zero temperature and were excluded from analysis.
+The unique generated answers are: `racist', `sexist', `neither', `both', and `racist and sexist'.
 
 The results of the mixed-category few-shot learning, with instruction, experiments are presented in Tables \ref{tab:fewshotmixedinstruct-matrix} and \ref{tab:fewshotmixedinstruct-summary}, and Appendix \ref{appendxbmuxedubstryctub} provides additional detail.
-With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (89 per cent) and F1 score (84 per cent) for sexist text, however Example Set 4 now performs best for racist text in terms of both accuracy (89 per cent) and F1 score (85 per cent).
-When considering the classification of racist and sexist speech overall, the models perform similarly with and without instruction when classifying racist text, but the model appears to perform slightly better at identifying sexist text when the instruction is omitted.
+With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (86 per cent) and F1 score (78 per cent) for sexist text.
+Performance in classifying racist text is slightly more varied in this setting, with Example Set 7 performing most accurately at 88 per cent (and with the highest F1 score at 82 per cent).
+Considering the classification of racist and sexist speech overall, the models perform similarly with and without instruction when classifying racist text, but the model appears to perform slightly better at identifying sexist text when the instruction is omitted.
 
 However, examining label-classification matches across all categories (`sexist', `racist', and `neither'), mixed-category few-shot learning almost always performs better with instruction than without instruction (Figure \ref{fig:comparison}).
-Across all example sets, the mean proportion of matching classifications (out of 240 comments) for mixed-category few-shot learning without instruction is 67 per cent.
-The average proportion of matching classifications rises to 75 per cent for learning with instruction.
+Across all example sets, the mean proportion of matching classifications (out of 240 comments) for mixed-category few-shot learning without instruction is 65 per cent.
+The average proportion of matching classifications rises to 71 per cent for learning with instruction.
 
@@
 \centering
-\begin{tabular}[t]{llll}
-\toprule
-\multicolumn{1}{c}{ } & \multicolumn{3}{c}{GPT-3 classification} \\
-\cmidrule(l{3pt}r{3pt}){2-4}
-Actual classification & Neither & Racist & Sexist\\
-\midrule
-Neither & \cellcolor[HTML]{AED581}{984} & \cellcolor[HTML]{FFFFFF}{163} & \cellcolor[HTML]{FFFFFF}{53}\\
-Racist & \cellcolor[HTML]{FFFFFF}{98} & \cellcolor[HTML]{AED581}{500} & \cellcolor[HTML]{FFFFFF}{2}\\
-Sexist & \cellcolor[HTML]{FFFFFF}{264} & \cellcolor{white}{35} & \cellcolor[HTML]{AED581}{301}\\
+\begin{tabular}[t]{llllrr}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{5}{c}{GPT-3 classification} \\
+\cmidrule(l{3pt}r{3pt}){2-6}
+Actual classification & Neither & Racist & Sexist & Both & Racist And Sexist\\
+\midrule
+Neither & \cellcolor[HTML]{AED581}{1903} & \cellcolor[HTML]{FFFFFF}{374} & \cellcolor[HTML]{FFFFFF}{123} & 0 & 0\\
+Racist & \cellcolor[HTML]{FFFFFF}{210} & \cellcolor[HTML]{AED581}{984} & \cellcolor[HTML]{FFFFFF}{5} & 1 & 0\\
+Sexist & \cellcolor[HTML]{FFFFFF}{512} & \cellcolor{white}{86} & \cellcolor[HTML]{AED581}{600} & 1 & 1\\
 \bottomrule
@@
 \midrule
-1 & Racism & 88 & 79 & 87 & 83\\
- & Sexism & 83 & 81 & 63 & 71\\
-\midrule
-2 & Racism & 87 & 86 & 72 & 78\\
- & Sexism & 82 & 89 & 53 & 67\\
-\midrule
-3 & Racism & 86 & 76 & 83 & 79\\
- & Sexism & 81 & 84 & 52 & 64\\
-\midrule
-4 & Racism & 89 & 83 & 87 & 85\\
- & Sexism & 80 & 83 & 50 & 62\\
-\midrule
-5 & Racism & 86 & 87 & 68 & 77\\
- & Sexism & 76 & 84 & 35 & 49\\
-\midrule
-6 & Racism & 88 & 93 & 70 & 80\\
- & Sexism & 73 & 82 & 23 & 36\\
-\midrule
-7 & Racism & 88 & 80 & 87 & 83\\
- & Sexism & 79 & 85 & 47 & 60\\
-\midrule
-8 & Racism & 79 & 62 & 93 & 75\\
- & Sexism & 84 & 90 & 60 & 72\\
-\midrule
-9 & Racism & 86 & 75 & 87 & 81\\
- & Sexism & 77 & 88 & 35 & 50\\
-\midrule
-10 & Racism & 77 & 59 & 100 & 74\\
- & Sexism & 89 & 85 & 83 & 84\\
-\midrule
-All & Racism & 85 & 75 & 83 & 79\\
- & Sexism & 80 & 85 & 50 & 63\\
+1 & Racism & 84 & 71 & 88 & 79\\
+ & Sexism & 81 & 76 & 63 & 69\\
+\midrule
+2 & Racism & 81 & 75 & 65 & 70\\
+ & Sexism & 80 & 80 & 53 & \vphantom{1} 64\\
+\midrule
+3 & Racism & 80 & 66 & 82 & 73\\
+ & Sexism & 81 & 88 & 50 & 64\\
+\midrule
+4 & Racism & 86 & 77 & 82 & 79\\
+ & Sexism & 80 & 80 & 53 & 64\\
+\midrule
+5 & Racism & 82 & 76 & 65 & 70\\
+ & Sexism & 77 & 85 & 37 & 51\\
+\midrule
+6 & Racism & 84 & 85 & 65 & 74\\
+ & Sexism & 71 & 75 & 20 & 32\\
+\midrule
+7 & Racism & 88 & 83 & 82 & 82\\
+ & Sexism & 79 & 78 & 52 & 62\\
+\midrule
+8 & Racism & 78 & 61 & 93 & 74\\
+ & Sexism & 83 & 85 & 58 & 69\\
+\midrule
+9 & Racism & 83 & 70 & 87 & 78\\
+ & Sexism & 77 & 85 & 38 & 53\\
+\midrule
+10 & Racism & 72 & 55 & 98 & 70\\
+ & Sexism & 86 & 80 & 75 & 78\\
+\midrule
+All & Racism & 82 & 70 & 81 & 75\\
+ & Sexism & 79 & 81 & 50 & 62\\
 \bottomrule
@@
 
-In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 63 per cent with an F1 score of 81 per cent.
-In the one-shot learning setting the accuracy decreases to 61 per cent with an F1 score of 65 per cent.
-Accuracy increases to 69 per cent in the single-category few-shot learning setting, with an F1 score of 61 per cent.
-Of the three single-category approaches, zero-shot learning has a notably high recall value of 87 per cent.
-
-It is likely that the model is not ideal for use in hate speech detection in the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the accuracy rates are between 60 per cent and 70 per cent.
+In the zero-shot learning setting where the model is given no examples, its average accuracy rate for identifying sexist and racist text is 56 per cent (SE = 4.3) with an average F1 score of 70 per cent (SE = 5.7).
+In the one-shot learning setting the average accuracy decreases to 55 per cent (SE = 4.1) with an average F1 score of 55 per cent (SE = 7.3).
+Average accuracy increases to 67 per cent (SE = 2.7) in the single-category few-shot learning setting, with an average F1 score of 62 per cent (SE = 4.9).
+
+It is likely that the model is not ideal for use in hate speech detection in the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the average accuracy rates are between 50 per cent and 70 per cent.
 \citet{davidson2017automated}, using a different model and approach, similarly find `that almost 40 per cent of hate speech is misclassified'.
@@
 With instruction added, mixed-category few-shot learning performed similarly well for racist text identification.
-But the model performed relatively poorly in terms of identifying sexist speech, with an F1 score of 63 per cent overall and a recall of 50 per cent meaning nearly half of the sexist comments were wrongly classified.
+But the model performed relatively poorly in terms of identifying sexist speech, with an F1 score of 79 per cent overall and a recall of 50 per cent meaning nearly half of the sexist comments were wrongly classified.
 Overall, it appears as though GPT-3 is most effective at identifying both racist and sexist comments in the mixed-category few-shot learning setting, without instruction.
@@
 Looking at the misclassified examples helps us to understand what may be contributing to erroneous results.
-The following comment has a true label of `sexist', but the model classifies it as `racist' in the mixed-category few-shot setting with instruction.
+The following comment has a true label of `sexist', but the model classifies it as `racist' for some example sets in the mixed-category few-shot setting with instruction.
 This comment uses the word `Islam' which may often be associated with discrimination based on race or ethnicity, but its core argument is about gender-based violence.
-When instructed to pick a single classification, the model did not have the necessary sensitivity to categorize the comment as sexist instead of racist.
+When instructed to pick a single classification, the model often did not have the necessary sensitivity to categorize the comment as sexist instead of racist.
 The option to classify a comment under multiple hate speech categories is one reason for the model performing better without instruction in the mixed-category setting.
@@
 
-Mixed-category few-shot classification: racist, sexist (True label: sexist)
-
-Mixed-category few-shot classification, with instruction: racist (True label: sexist)
+Mixed-category few-shot classification (Example Set 5): racist, sexist (True label: sexist)
+
+Mixed-category few-shot classification, with instruction (Example Set 10): racist (True label: sexist)
 \end{quote}
 
-As another similar example, the following comment has a true label of `neither', but the model classified it as `transphobic' in the mixed-category few-shot setting (without instruction).
+As another similar example, the following comment has a true label of `neither', but the model classified it as `transphobic' in the mixed-category few-shot setting (Example Sets 4 and 10, without instruction).
 
@@
 The following comment is an example of false negativity.
-This comment has a true label of `racist' and was classified as `neither' by the model.
+This comment has a true label of `racist' and was classified as `neither' by the model when presented with Example Set 2.
 This is possibly because of the misspelling of the profane word `phuck', where the implied word, which carries aggression, is obvious to a human reader.
@@
 These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation.
-The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process.
+The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process at a temperature of zero (to limit the effect of random chance on classifications of comments with different spellings).
 Details of the misspellings added are also included in Appendix \ref{appendxc}.
-Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category.
-Interestingly, three comments with added misspellings were classified as `racist' where they had previously been classified as `not racist'.
+Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of six comments, all of which belonged to the racist category.
+Interestingly, two comments with added misspellings were classified as `racist' where they had previously been classified as `not racist'.
 This speaks to potential inconsistencies in the behavior of GPT-3 in understanding profanity and censorship and presents another area for further investigation.
@@
 Various prompts and settings could be further explored to try to address these issues.
+Possible settings changes include increasing or decreasing temperature, or assessing classification accuracy across GPT-3's different engines.
 Another especially exciting area for further research would be to fine-tune GPT-3 for this task.
@@
 \midrule
-Not racist & 1301 & 1699\\
-Racist & 608 & 2392\\
+Not racist & 1445 & 1529\\
+Racist & 1139 & 1839\\
 \bottomrule
@@
 \midrule
-Not sexist & 1378 & 1622\\
-Sexist & 730 & 2170\\
+Not sexist & 1550 & 1407\\
+Sexist & 1224 & 1686\\
 \bottomrule
@@
 \midrule
-Not hate speech & 2679 & 3321\\
-Hate speech & 1338 & 4562\\
+Not hate speech & 2995 & 2936\\
+Hate speech & 2363 & 3525\\
 \bottomrule
@@
 \midrule
-Not racist & 1844 & 1156\\
-Racist & 683 & 2317\\
+Not racist & 1653 & 1347\\
+Racist & 791 & 2209\\
 \bottomrule
@@
 \midrule
-Not sexist & 2392 & 608\\
-Sexist & 1031 & 1969\\
+Not sexist & 2334 & 666\\
+Sexist & 1125 & 1875\\
 \bottomrule
@@
 \midrule
-Not hate speech & 6000 & 0\\
-Hate speech & 0 & 6000\\
+Not hate speech & 3987 & 2013\\
+Hate speech & 1916 & 4084\\
 \bottomrule
@@
 \midrule
-1 & Not racist & 108 & 12\\
+1 & Not racist & 107 & 13\\
+ & Racist & 5 & \vphantom{1} 55\\
+\midrule
+2 & Not racist & 102 & 18\\
+ & Racist & 9 & 51\\
+\midrule
+3 & Not racist & 99 & 21\\
+ & Racist & 4 & 56\\
+\midrule
+4 & Not racist & 90 & 30\\
+ & Racist & 0 & 60\\
+\midrule
+5 & Not racist & 92 & 28\\
+ & Racist & 3 & \vphantom{1} 57\\
+\midrule
+6 & Not racist & 94 & 26\\
+ & Racist & 2 & \vphantom{1} 58\\
+\midrule
+7 & Not racist & 84 & 36\\
+ & Racist & 1 & 59\\
+\midrule
+8 & Not racist & 71 & 49\\
+ & Racist & 2 & 58\\
+\midrule
+9 & Not racist & 83 & 37\\
+ & Racist & 3 & 57\\
+\midrule
+10 & Not racist & 108 & 12\\
  & Racist & 5 & 55\\
 \midrule
-2 & Not racist & 106 & 14\\
- & Racist & 7 & 53\\
-\midrule
-3 & Not racist & 100 & 20\\
- & Racist & 4 & \vphantom{1} 56\\
-\midrule
-4 & Not racist & 93 & 27\\
- & Racist & 1 & \vphantom{1} 59\\
-\midrule
-5 & Not racist & 88 & 32\\
- & Racist & 4 & 56\\
-\midrule
-6 & Not racist & 96 & 24\\
- & Racist & 1 & 59\\
-\midrule
-7 & Not racist & 80 & 40\\
- & Racist & 2 & \vphantom{1} 58\\
-\midrule
-8 & Not racist & 74 & 46\\
- & Racist & 3 & 57\\
-\midrule
-9 & Not racist & 86 & 34\\
- & Racist & 2 & 58\\
-\midrule
-10 & Not racist & 104 & 16\\
- & Racist & 6 & 54\\
-\midrule
-All & Not racist & 935 & 265\\
- & Racist & 35 & 565\\
+All & Not racist & 930 & 270\\
+ & Racist & 34 & 566\\
 \bottomrule
@@
 1 & Not sexist & 113 & 7\\
- & Sexist & 17 & 43\\
+ & Sexist & 19 & 41\\
 \midrule
 2 & Not sexist & 110 & 10\\
+ & Sexist & 14 & \vphantom{2} 46\\
+\midrule
+3 & Not sexist & 110 & 10\\
+ & Sexist & 14 & \vphantom{1} 46\\
+\midrule
+4 & Not sexist & 105 & 15\\
+ & Sexist & 12 & \vphantom{1} 48\\
+\midrule
+5 & Not sexist & 106 & 14\\
+ & Sexist & 10 & \vphantom{1} 50\\
+\midrule
+6 & Not sexist & 103 & 17\\
+ & Sexist & 12 & 48\\
+\midrule
+7 & Not sexist & 110 & 10\\
  & Sexist & 14 & 46\\
 \midrule
-3 & Not sexist & 108 & 12\\
- & Sexist & 16 & \vphantom{1} 44\\
-\midrule
-4 & Not sexist & 101 & 19\\
- & Sexist & 12 & \vphantom{1} 48\\
-\midrule
-5 & Not sexist & 110 & 10\\
- & Sexist & 15 & 45\\
-\midrule
-6 & Not sexist & 106 & 14\\
- & Sexist & 12 & 48\\
-\midrule
-7 & Not sexist & 112 & 8\\
- & Sexist & 16 & 44\\
-\midrule
-8 & Not sexist & 98 & 22\\
- & Sexist & 9 & \vphantom{1} 51\\
-\midrule
-9 & Not sexist & 82 & 38\\
- & Sexist & 9 & 51\\
-\midrule
-10 & Not sexist & 109 & 11\\
- & Sexist & 8 & 52\\
-\midrule
-All & Not sexist & 1049 & 151\\
- & Sexist & 128 & 472\\
+8 & Not sexist & 100 & 20\\
+ & Sexist & 11 & \vphantom{1} 49\\
+\midrule
+9 & Not sexist & 87 & 33\\
+ & Sexist & 11 & 49\\
+\midrule
+10 & Not sexist & 106 & 14\\
+ & Sexist & 10 & 50\\
+\midrule
+All & Not sexist & 1050 & 150\\
+ & Sexist & 127 & 473\\
 \bottomrule
@@
 \midrule
-1 & Not racist & 106 & 14\\
- & Racist & 8 & \vphantom{3} 52\\
-\midrule
-2 & Not racist & 113 & 7\\
- & Racist & 17 & 43\\
-\midrule
-3 & Not racist & 104 & 16\\
- & Racist & 10 & 50\\
-\midrule
-4 & Not racist & 109 & 11\\
- & Racist & 8 & \vphantom{2} 52\\
-\midrule
-5 & Not racist & 114 & 6\\
- & Racist & 19 & 41\\
-\midrule
-6 & Not racist & 117 & 3\\
- & Racist & 18 & 42\\
-\midrule
-7 & Not racist & 107 & 13\\
- & Racist & 8 & \vphantom{1} 52\\
-\midrule
-8 & Not racist & 86 & 34\\
+1 & Not racist & 98 & 22\\
+ & Racist & 7 & 53\\
+\midrule
+2 & Not racist & 107 & 13\\
+ & Racist & 21 & \vphantom{2} 39\\
+\midrule
+3 & Not racist & 95 & 25\\
+ & Racist & 11 & \vphantom{2} 49\\
+\midrule
+4 & Not racist & 105 & 15\\
+ & Racist & 11 & \vphantom{1} 49\\
+\midrule
+5 & Not racist & 108 & 12\\
+ & Racist & 21 & \vphantom{1} 39\\
+\midrule
+6 & Not racist & 113 & 7\\
+ & Racist & 21 & 39\\
+\midrule
+7 & Not racist & 110 & 10\\
+ & Racist & 11 & 49\\
+\midrule
+8 & Not racist & 84 & 36\\
  & Racist & 4 & 56\\
 \midrule
-9 & Not racist & 103 & 17\\
+9 & Not racist & 98 & 22\\
  & Racist & 8 & 52\\
 \midrule
-10 & Not racist & 78 & 42\\
- & Racist & 0 & 60\\
-\midrule
-All & Not racist & 1037 & 163\\
- & Racist & 100 & 500\\
+10 & Not racist & 71 & 49\\
+ & Racist & 1 & 59\\
+\midrule
+All & Not racist & 989 & 211\\
+ & Racist & 116 & 484\\
 \bottomrule
@@
 \midrule
-1 & Not sexist & 111 & 9\\
+1 & Not sexist & 108 & 12\\
  & Sexist & 22 & 38\\
 \midrule
-2 & Not sexist & 116 & 4\\
+2 & Not sexist & 112 & 8\\
+ & Sexist & 28 & \vphantom{1} 32\\
+\midrule
+3 & Not sexist & 116 & 4\\
+ & Sexist & 30 & 30\\
+\midrule
+4 & Not sexist & 112 & 8\\
  & Sexist & 28 & 32\\
 \midrule
-3 & Not sexist & 114 & 6\\
+5 & Not sexist & 116 & 4\\
+ & Sexist & 38 & 22\\
+\midrule
+6 & Not sexist & 116 & 4\\
+ & Sexist & 48 & 12\\
+\midrule
+7 & Not sexist & 111 & 9\\
  & Sexist & 29 & 31\\
 \midrule
-4 & Not sexist & 114 & 6\\
- & Sexist & 30 & 30\\
-\midrule
-5 & Not sexist & 116 & 4\\
- & Sexist & 39 & \vphantom{1} 21\\
-\midrule
-6 & Not sexist & 117 & 3\\
- & Sexist & 46 & 14\\
-\midrule
-7 & Not sexist & 115 & 5\\
- & Sexist & 32 & 28\\
-\midrule
-8 & Not sexist & 116 & 4\\
- & Sexist & 24 & 36\\
-\midrule
-9 & Not sexist & 117 & 3\\
- & Sexist & 39 & 21\\
-\midrule
-10 & Not sexist & 111 & 9\\
- & Sexist & 10 & 50\\
-\midrule
-All & Not sexist & 1147 & 53\\
- & Sexist & 299 & 301\\
+8 & Not sexist & 114 & 6\\
+ & Sexist & 25 & 35\\
+\midrule
+9 & Not sexist & 116 & 4\\
+ & Sexist & 37 & 23\\
+\midrule
+10 & Not sexist & 109 & 11\\
+ & Sexist & 15 & 45\\
+\midrule
+All & Not sexist & 1130 & 70\\
+ & Sexist & 300 & 300\\
 \bottomrule
@@
 Racist & Edited & Why are n*ggers superior athletically to all other races? & No\\
-Racist & Unedited & That fucking black cunt gets fucking cross hairs on the fucking head!
-Look I owe not shit to anyone who dosent owe me!!!
-LOOK WHORE!!
-FUCK YOU TO DEATH!!!
-11 PERCENTILE AND FALLING!!
-WHORE BLACK RACIST WHORE!
-TAKE THE RED PILL!
-& No\\
-Racist & Edited & That phucking black cunt gets phucking cross hairs on the phucking head!
-Look I owe not shit to anyone who dosent owe me!!!
-LOOK WHORE!!
-phuck YOU TO DEATH!!!
-11 PERCENTILE AND FALLING!!
-WHORE BLACK RACIST WHORE!
-TAKE THE RED PILL!
-& Yes\\
 Racist & Unedited & Stand the fuck up and take them out all you fucking lazy white males!

### 2022-03-23 inputs/data_collection_private.py

@@ -11,8 +11,8 @@ import pandas as pd
 import numpy as np
 import time
 import random
-openai.organization = "INPUT ORG KEY"
-openai.api_key = "INPUT API KEY"
+openai.organization = "INSERT ORG ID"
+openai.api_key = "INSERT API KEY"
 
 
 # In[3]:
@@ -114,7 +114,7 @@ def one_shot(cat, label, example, comment, temperature):
     response = openai.Completion.create(
         engine="davinci",
         prompt = prompt,
-        temperature=0,
+        temperature=temperature,
         max_tokens=2,
         top_p=1,
         n = 1,
@@ -182,7 +182,7 @@ def few_shot_single(cat, label, example1, example2, example3, comment, temperatu
     response = openai.Completion.create(
         engine="davinci",
         prompt= prompt,
-        temperature=0,
+        temperature=temperature,
         max_tokens=4,
         top_p=1,
         n = 1,
@@ -289,7 +289,7 @@ def few_shot_instruction(cat, label, example1, example2, example3, comment, temp
     response = openai.Completion.create(
         engine="davinci",
         prompt= prompt,
-        temperature=0,
+        temperature=temperature,
         max_tokens=4,
         top_p=1,
         n = 1,
@@ -345,7 +345,7 @@ def few_shot_fixed_examples(i, cat, label, comment, temperature):
     response = openai.Completion.create(
         engine="davinci",
         prompt= prompt,
-        temperature=0,
+        temperature=temperature,
         max_tokens=4,
         top_p=1,
         n = 1,
@@ -364,29 +364,76 @@ def few_shot_fixed_examples(i, cat, label, comment, temperature):
 
     return few_shot_results
 
-all_few_shot_fixed_examples_result = pd.DataFrame()
+all_few_shot_fixed_examples_result = pd.read_csv("outputs/data/few_shot_fixed_examples_results.csv")
+
+#Mixed Cat, Temperature = 0
+for i in range(0, 10):
+    print("Few shot multi category, iteration {}".format(i))
+    neither_comments = not_hate.reset_index().comment[0:121]
+    sexist_comments = sexist.reset_index().comment[0:61]
+    racist_comments = racist.reset_index().comment[0:61]
+    for racist_comment in racist_comments.drop(i):
+        few_shot_fixed_examples_result = few_shot_fixed_examples(i, "fixed-example", "racist", racist_comment, temperature = 0.3)
[…]

### 2022-03-23 outputs/documents/paper.Rmd

@@
 We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning.
-We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an accuracy between 57 per cent and 68 per cent depending on the category of text and type of learning.
-With few-shot learning, the model's accuracy can be as high as 88 per cent.
+We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an average accuracy between 55 per cent and 67 per cent depending on the category of text and type of learning.
+With few-shot learning, the model's accuracy can be as high as 85 per cent.
 Large language models have a role to play in hate speech detection, and with further development could eventually be used to counter hate speech."
@@
 For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text [@hovy2016social].
-In this paper we are interested in whether large language models, given that they can produce harmful language, can also identify, or learn to identify, harmful language.
+In this paper we are interested in whether large language models, given that they can produce harmful language, can also identify (or learn to identify) harmful language.
 
@@
 
+<!-- Fix once few-shot results are all in -->
+
 We examine the ability of GPT-3 to identify hate speech in zero-shot, one-shot, and few-shot settings.
@@
 A simple instruction is given asking the model to answer only 'Yes' or 'No'.
-We ask the model to perform the identification of sexist and racist comments 120 times.
-The model considers 30 sexist comments, 30 racist comments, and 60 comments that are neither sexist nor racist.
+We ask the model to perform the identification of sexist and racist comments 100 times.
+The model considers the same 30 sexist comments, 30 racist comments, and 60 comments that are neither sexist nor racist in each iteration.
 An example of zero-shot learning for recognizing a comment that is labeled as sexist is:
@@
 In the one-shot learning case, the model is given one example from a category and is asked to identify whether the next passage of text belongs to the selected category.
-Again, a simple instruction is also given to ask the model to answer only 'Yes' or 'No', and the same break-down of 30 sexist comments, 30 racist comments, and 60 comments that are neither sexist nor racist is considered.
-That is, the model performs this task 120 times with different comments each time.
+Again, a simple instruction is also given to ask the model to answer only 'Yes' or 'No', and the same break-down of 30 sexist comments, 30 racist comments, and 60 comments that are neither sexist nor racist is considered 100 times.
+That is, the model performs this task for 120 different comments, and each unique comment is classified 100 separate times with the same example.
 An example of one-shot learning for recognizing a comment that is labelled as sexist is:
@@
 To simplify the classification procedure and allow for comparisons between different example inputs, we created ten example sets against which 240 comments were each classified.
-We elected to use ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset tractable.
+We elected to use ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset, tractable.
 The example sets each consist of one sexist, one racist, and one 'neither' comment and were created using the comments at indexes one through ten from each dataset.
@@
 Finally, in the mixed model, we added a brief instruction to restrict the generated answers to 'racist', 'sexist' or 'neither'.
-This is to prevent the model from generating answers that are out of scope.
+This is an attempt to prevent the model from generating answers that are out of scope.
 An example of this is:
@@
 The reported performance metrics for these settings are the arithmetic means of each metric across all 100 iterations with the corresponding standard error.
-In some cases, the model outputted responses that were neither "yes" nor "no".
+In the zero-shot setting, the model sometimes outputted responses that were neither "yes" nor "no".
 These were counted as "not applicable" and omitted from analysis.
-Specific numbers are reported in the following sections.
+Specific numbers are reported in the following section.
 
@@
 Out of 6000 classification for each category, the model has 3231 matches (true positives and negatives) and 2691 mismatches (false positives and negatives) in the sexist category, and 3463 matches and 2504 mismatches in the racist category.
-In the zero-shot learning setting, the model produced 111 responses that were inadmissible.
+In this setting, the model sometimes outputted responses that were neither "yes" nor "no".
+This occurred for 111 classifications, which were subsequently omitted from analysis.
 The model performs more accurately when identifying racist comments, with an average accuracy of 58 per cent (SE = 6.5), compared with identifying sexist comments, with an average accuracy of 55 per cent (SE = 5.2).
@@
 The results of the one-shot learning experiments are presented in Table \@ref(tab:oneshot-summary), and Appendix \@ref(appendixboneshot) provides additional detail.
-The model has 37 matches and 23 mismatches in the racist category, and 36 matches and 24 mismatches in the sexist category.
-In contrast with the result generated from zero-shot learning, the model performs roughly the same in terms of identifying racist comments and identifying sexist comments.
-The overall ratio of matches and mismatches is 73:47.
-In other words, the accuracy of identifying hate speech in the one-shot setting is 61 per cent.
-The general performance in the one-shot setting is worse than in the zero-shot setting, with lower accuracy, recall, precision, and F1 score overall.
+Out of 6000 classifications each, the model produced 3284 matches and 2668 mismatches in the racist category, and 3236 matches and 2631 mismatches in the sexist category.
+Unlike the results generated from zero-shot learning, the model performs approximately the same when identifying sexist and racist comments, with an average accuracy of 55 per cent (SE = 6.4) and an F1 score of 58 per cent (SE = 6.5) when identifying racist comments, compared with sexist comments at an accuracy of 55 per cent (SE = 5.8) and an F1 score of 56 per cent (SE = 6.3).
+The overall ratio of matches and mismatches is 6520:5326.
+In other words, the average accuracy of identifying hate speech in the one-shot setting is 55 per cent (SE = 4.1).
+The general performance in the one-shot setting is nearly the same as in the zero-shot setting, with an overall average accuracy of 55 per cent compared with 56 per cent (SE = 4.6) in the zero-shot setting.
+However, the F1 score in the one-shot setting is much lower than in the zero-shot setting at 55 per cent (SE = 7.3) compared with 70 per cent (SE = 5.7).
 
@@
 The results of the single-category, few-shot learning, experiments are presented in Table \@ref(tab:fewshotsingle-summary), and Appendix \@ref(appendixbfewshotsingle) provides additional detail.
-The model has 41 matches and 19 mismatches in the racist category, and 42 matches and 18 mismatches in the sexist category.
-Like the one-shot setting, the model performs almost equally well in terms of identifying racist comments compared with identifying sexist comments.
-The general performance in the single-category few-shot learning setting is slightly more accurate than performance in other settings, with an accuracy of 69 per cent compared with 61 per cent in the one-shot setting and 63 per cent in the zero-shot setting.
-But, in this context we see the lowest F1 score of the settings considered thus far at 61 per cent.
+The model has 3862 matches and 2138 mismatches in the racist category, and 4209 matches and 1791 mismatches in the sexist category.
+Unlike in the zero- and one-shot settings, the model performs slightly better when identifying sexist comments compared with identifying racist comments.
+The general performance in the single-category few-shot learning setting is more accurate than performance in other settings, with an accuracy of 67 per cent (SE = 2.7) compared with 55 per cent in the one-shot setting (SE = 4.1) and 56 per cent (SE = 4.3) in the zero-shot setting.
+The average F1 score in this setting is 62 per cent (SE = 4.9) which is similar to the results of the one-shot setting but slightly lower than in the zero-shot setting.
 
 ```{r fewshotsingle-summary, message = FALSE}
-# Set-up data for zero-shot racism
+# Set-up data for few-shot racism
 few_single_shot_result <-
@@
     mutate(label_yn = ifelse(grepl("not", label), "N", "Y"),
-           answer_yn = ifelse(grepl("not", label), "N", "Y")) %>%
+           answer_yn = ifelse(grepl("not", answer), "N", "Y")) %>%
     count(label_yn, answer_yn) %>%
@@
   knitr::kable(col.names = c("", "Metric", "Mean (%)", "Standard Error (%)"), 
-        caption = "Performance of model in zero-shot learning across 100 classifications of each comment at a temperature of 0.3.",
+        caption = "Performance of model in single category few-shot learning across 100 classifications of each comment at a temperature of 0.3.",
         booktabs = TRUE,
@@
 The results of the mixed-category few-shot experiments are presented in Table \@ref(tab:fewshotmixed-summary), and Appendix \@ref(appendxbmuxedubsnorinstruction) provides additional detail.
-Among the ten sets of examples, Example Set 1 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments and Example Set 10 yields the best performance by the same metrics for sexist comments (accuracy of 89 per cent, F1 score of 85 per cent).
-The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 70 per cent (and the lowest accuracy at 73 per cent) for this dataset.
-The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 74 per cent) for this dataset.
-The differences between Example Sets 1, 8, 9, and 10 suggest that, although the models are provided with the same number of examples, the content of the examples also affects how the model makes inferences.
+Among the ten sets of examples, Example Set 10 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments.
+The model performs with similar accuracy for identifying racist comments across most of the example sets (approximately 87 per cent), however the highest F1 score results from Example Set 10 once again.
+The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 69 per cent (and the lowest accuracy at 70 per cent) for this dataset.
+The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 76 per cent) for this dataset.
+The differences between Example Sets 8, 9, and 10 suggest that, although the models are provided with the same number of examples, the content of the examples also affects how the model makes inferences.
 Overall, the mixed-category few-shot setting performs roughly the same in terms of identifying sexist text and racist text.
-It also has higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
+It also has distinctly higher accuracy and F1 score overall than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
 
@@
 few_shot_mixed_result <-
-  read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))
+  read.csv(here::here("outputs/data/few_shot_fixed_examples_results_multiple.csv"))
+
+# Keep only first iteration
+few_shot_mixed_result <- few_shot_mixed_result %>% slice(2401:4800)
 
@@
   count(label, answer) %>%
-  pivot_wider(names_from = answer, values_from = n) %>%
+  pivot_wider(names_from = answer, values_from = n, values_fill = 0) %>%
   mutate(label = case_when(label == "not racist" ~ "Not racist",
@@
   count(example_set, label, answer) %>%
-  pivot_wider(names_from = answer, values_from = n) %>%
+  pivot_wider(names_from = answer, values_from = n, values_fill = 0) %>%
   mutate(label = case_when(label == "not sexist" ~ "Not sexist",
@@
   count(label, answer) %>%
-  pivot_wider(names_from = answer, values_from = n) %>%
+  pivot_wider(names_from = answer, values_from = n, values_fill = 0) %>%
   mutate(label = case_when(label == "not sexist" ~ "Not sexist",
@@
                              Percent = few_racism_all) %>%
-  pivot_wider(names_from = Metric, values_from = Percent)
+  pivot_wider(names_from = Metric, values_from = Percent, values_fill = 0)
 
@@
 For instance, other than 'sexist', 'racist', and 'neither', we also see answers such as 'transphobic', 'hypocritical', 'Islamophobic', and 'ableist'.
-In some cases, the model even classifies a text passage into more than one category, such as 'sexist, racist' and 'sexist, misogynistic'.
-The full list contains eighty different answers instead of three.
+In some cases, the model even classifies a text passage into more than one category, such as 'sexist, racist' and 'sexist and misogynistic'.
+The full list contains 143 different answers instead of three.
 
@@
 few_shot_mixed_result <-
-  readr::read_csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))
+  read.csv(here::here("outputs/data/few_shot_fixed_examples_results_multiple.csv"))
+
+# Keep only first iteration
+few_shot_mixed_result <- few_shot_mixed_result %>% slice(2401:4800)
 
@@
 To reduce the chance of the model generating answers that are out of scope, a brief instruction is added to the prompt, specifying that the answers be: 'sexist', 'racist', or 'neither'.
-The addition of an instruction successfully restricts the generated answers within the specified terms.
-The unique generated answers are: 'racist', 'sexist', and 'neither'.
+The addition of an instruction successfully restricts the generated answers within the specified terms with the exception of three responses: one classification of "racist and sexist" and two classifications of "both".
+These responses were likely a result of randomness introduced by the non-zero temperature and were excluded from analysis.
+The unique generated answers are: 'racist', 'sexist', 'neither', 'both', and 'racist and sexist'.
 
 The results of the mixed-category few-shot learning, with instruction, experiments are presented in Tables \@ref(tab:fewshotmixedinstruct-matrix) and \@ref(tab:fewshotmixedinstruct-summary), and Appendix \@ref(appendxbmuxedubstryctub) provides additional detail.
-With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (89 per cent) and F1 score (84 per cent) for sexist text, however Example Set 4 now performs best for racist text in terms of both accuracy (89 per cent) and F1 score (85 per cent).
-When considering the classification of racist and sexist speech overall, the models perform similarly with and without instruction when classifying racist text, but the model appears to perform slightly better at identifying sexist text when the instruction is omitted.
+With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (86 per cent) and F1 score (78 per cent) for sexist text.
+Performance in classifying racist text is slightly more varied in this setting, with Example Set 7 performing most accurately at 88 per cent (and with the highest F1 score at 82 per cent).
+Considering the classification of racist and sexist speech overall, the models perform similarly with and without instruction when classifying racist text, but the model appears to perform slightly better at identifying sexist text when the instruction is omitted.
 
 However, examining label-classification matches across all categories ('sexist', 'racist', and 'neither'), mixed-category few-shot learning almost always performs better with instruction than without instruction (Figure \ref{fig:comparison}).
-Across all example sets, the mean proportion of matching classifications (out of 240 comments) for mixed-category few-shot learning without instruction is 67 per cent.
-The average proportion of matching classifications rises to 75 per cent for learning with instruction.
+Across all example sets, the mean proportion of matching classifications (out of 240 comments) for mixed-category few-shot learning without instruction is 65 per cent.
+The average proportion of matching classifications rises to 71 per cent for learning with instruction.
 
@@
   read.csv(here::here(
-    "outputs/data/few_shot_fixed_examples_instruction_results.csv"
+    "outputs/data/few_shot_fixed_example_instruction_results.csv"
   ))
@@
   count(label, answer) %>%
+  mutate(answer = str_to_title(answer) %>% trimws(),
+         label = str_to_title(label) %>% trimws()) %>%
   pivot_wider(names_from = answer, values_from = n, values_fill = 0) %>%
-  mutate(label = case_when(label == "neither" ~ "Neither",
-                           label == "racist" ~ "Racist",
-                           label == "sexist" ~ "Sexist")) %>%
-  rename("Actual classification" = label, Neither = " neither", Racist = " racist", Sexist = " sexist")
+  rename(`Actual classification` = label)
 
@@
                                     escape=FALSE) %>%
-  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=3))
+  kableExtra::add_header_above(c(" " = 1, "GPT-3 classification"=5))
 
@@
   read.csv(here::here(
-    "outputs/data/few_shot_fixed_examples_instruction_results.csv"
+    "outputs/data/few_shot_fixed_example_instruction_results.csv"
   ))
+
+few_shot_instruction_result <- few_shot_instruction_result %>% filter(temperature == 0.3)
 
@@
 ```{r comparison, fig.cap="Comparing classification with and without an instruction", fig.height = 3}
-few_shot_mixed_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))
+few_shot_mixed_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_results_multiple.csv"))
+
+few_shot_mixed_result <- few_shot_mixed_result %>% slice(2401:4800)
 
@@
   few_shot_mixed_result %>%
-  filter(temperature == 0) %>%
+  filter(temperature == 0.3) %>%
   select(category, label, answer, example_set) %>%
@@
 
-few_shot_instruction_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_instruction_results.csv"))
+few_shot_instruction_result <- read.csv(here::here("outputs/data/few_shot_fixed_example_instruction_results.csv"))
+few_shot_instruction_result <- few_shot_instruction_result %>% filter(temperature == 0.3)
 
@@
   few_shot_instruction_result %>%
-  filter(temperature == 0) %>%
+  filter(temperature == 0.3) %>%
   select(category, label, answer, example_set) %>%
@@
 
-In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 63 per cent with an F1 score of 81 per cent.
-In the one-shot learning setting the accuracy decreases to 61 per cent with an F1 score of 65 per cent.
-Accuracy increases to 69 per cent in the single-category few-shot learning setting, with an F1 score of 61 per cent.
-Of the three single-category approaches, zero-shot learning has a notably high recall value of 87 per cent.
-
-It is likely that the model is not ideal for use in hate speech detection in the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the accuracy rates are between 60 per cent and 70 per cent.
+In the zero-shot learning setting where the model is given no examples, its average accuracy rate for identifying sexist and racist text is 56 per cent (SE = 4.3) with an average F1 score of 70 per cent (SE = 5.7).
+In the one-shot learning setting the average accuracy decreases to 55 per cent (SE = 4.1) with an average F1 score of 55 per cent (SE = 7.3).
+Average accuracy increases to 67 per cent (SE = 2.7) in the single-category few-shot learning setting, with an average F1 score of 62 per cent (SE = 4.9).
+
+It is likely that the model is not ideal for use in hate speech detection in the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the average accuracy rates are between 50 per cent and 70 per cent.
 @davidson2017automated, using a different model and approach, similarly find 'that almost 40 per cent of hate speech is misclassified'.
@@
 Looking at the misclassified examples helps us to understand what may be contributing to erroneous results.
-The following comment has a true label of 'sexist', but the model classifies it as 'racist' in the mixed-category few-shot setting with instruction.
+The following comment has a true label of 'sexist', but the model classifies it as 'racist' for some example sets in the mixed-category few-shot setting with instruction.
 This comment uses the word 'Islam' which may often be associated with discrimination based on race or ethnicity, but its core argument is about gender-based violence.
-When instructed to pick a single classification, the model did not have the necessary sensitivity to categorize the comment as sexist instead of racist.
+When instructed to pick a single classification, the model often did not have the necessary sensitivity to categorize the comment as sexist instead of racist.
 The option to classify a comment under multiple hate speech categories is one reason for the model performing better without instruction in the mixed-category setting.
@@
 >
-> Mixed-category few-shot classification: racist, sexist (True label: sexist)
+> Mixed-category few-shot classification (Example Set 5): racist, sexist (True label: sexist)
 >
-> Mixed-category few-shot classification, with instruction: racist (True label: sexist)
-
-As another similar example, the following comment has a true label of 'neither', but the model classified it as 'transphobic' in the mixed-category few-shot setting (without instruction).
+> Mixed-category few-shot classification, with instruction (Example Set 10): racist (True label: sexist)
+
+As another similar example, the following comment has a true label of 'neither', but the model classified it as 'transphobic' in the mixed-category few-shot setting (Example Sets 4 and 10, without instruction).
 
@@
 The following comment is an example of false negativity.
-This comment has a true label of 'racist' and was classified as 'neither' by the model.
+This comment has a true label of 'racist' and was classified as 'neither' by the model when presented with Example Set 2.
 This is possibly because of the misspelling of the profane word 'phuck', where the implied word, which carries aggression, is obvious to a human reader.
@@
 These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation.
-The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process.
+The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process at a temperature of zero (to limit the effect of random chance on classifications of comments with different spellings).
 Details of the misspellings added are also included in Appendix \@ref(appendxc).
-Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category.
-Interestingly, three comments with added misspellings were classified as 'racist' where they had previously been classified as 'not racist'.
+Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of six comments, all of which belonged to the racist category.
+Interestingly, two comments with added misspellings were classified as 'racist' where they had previously been classified as 'not racist'.
 This speaks to potential inconsistencies in the behavior of GPT-3 in understanding profanity and censorship and presents another area for further investigation.
+
+<!-- Add in potential for different engines  -->
 
@@
 zeroshot_summary_race <- zero_shot_misspelling %>%
+  mutate(answer = str_to_title(answer) %>% trimws()) %>%
   count(category, comment_id, answer) %>% 
@@
   filter(n > 1 & category == "racist")
+
+zeroshot_summary_sex <- zero_shot_misspelling %>%
+  mutate(answer = str_to_title(answer) %>% trimws()) %>%
+  count(category, comment_id, answer) %>% 
+  count(category, comment_id) %>% 
+  filter(n > 1 & category == "sexist")
 

### 2022-03-24 outputs/documents/paper.Rmd
arXiv resubmission

@@
 We gratefully acknowledge the support of Gillian Hadfield, the Schwartz Reisman Institute for Technology and Society, and OpenAI for providing access to GPT-3 under the academic access program.
-We thank two anonymous reviews and the editor, as well as Amy Farrow, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions.
+We thank two anonymous reviews and the editor, as well as Amy Farrow, Christina Nguyen, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions.
 Please note that we have added asterisks to racial slurs and other offensive content in this paper, however the inputs and outputs did not have these.
@@
 We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning.
-We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an average accuracy between 55 per cent and 67 per cent depending on the category of text and type of learning.
+We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an average accuracy between 55 per cent and 67 per cent, depending on the category of text and type of learning.
 With few-shot learning, the model's accuracy can be as high as 85 per cent.
-Large language models have a role to play in hate speech detection, and with further development could eventually be used to counter hate speech."
+Large language models have a role to play in hate speech detection, and with further development they could eventually be used to counter hate speech."
 keywords: "GPT-3; natural language processing; quantitative analysis; hate speech."
@@
 
-Natural language processing (NLP) models use normal words, often written text, as their data.
-For instance, one might have content from many books and want to group them into themes.
+Natural language processing (NLP) models use words, often written text, as their data.
+For instance, a researcher might have content from many books and want to group them into themes.
 Sophisticated NLP models are being increasingly embedded in society.
-For instance, Google Search uses an NLP model called BERT to better understand what is meant by a word given its context.
+For instance, Google Search uses an NLP model, Bidirectional Encoder Representations from Transformers (BERT), to better understand what is meant by a word given its context.
 Some sophisticated NLP models, such as OpenAI's Generative Pre-trained Transformer 3 (GPT-3), can additionally produce text as an output.
@@
 The text produced by sophisticated NLP models can be hateful.
-In particular, there have been many examples of text being generated that targets marginalized groups based on their sex, race, sexual orientation, and other characteristics.
+In particular, there have been many examples of text being generated that target marginalized groups based on their sex, race, sexual orientation, and other characteristics.
 For instance, 'Tay' was a Twitter chatbot released by Microsoft in 2016.
@@
 Exclusion happens due to the demographic bias in the dataset.
-In the case of language models that are trained on US and UK English scraped from the Internet, datasets may be disproportionately white, male, and young.
+In the case of language models that are trained on English from the U.S.A and U.K.
+scraped from the Internet, datasets may be disproportionately white, male, and young.
 Therefore, it is not surprising to see white supremacist, misogynistic, and ageist content being over-represented in training datasets [@bender2021dangers].
-Over-generalization stems from the assumption that what we see in the dataset represents what occurs in the real world.
+Over-generalization stems from the assumption that what we see in the dataset represents what actually occurs.
 Words such as 'always', 'never', 'everybody', or 'nobody' are frequently used for rhetorical purpose instead of their literal meanings.
-But NLP models do not always recognize this and make inference based on generalized statements using these words.
-For instance, hate speech commonly uses generalized language for targeting a group such as 'all' and 'every', and a model trained on these statements may generate similarly generalized and harmful statements.
+But NLP models do not always recognize this and make inferences based on generalized statements using these words.
+For instance, hate speech commonly uses generalized language for targeting a group such as 'all' and 'every', and a model trained on these statements may generate similarly overstated and harmful statements.
 Finally, exposure refers to the relative attention, and hence consideration of importance, given to something.
-In the context of NLP this may be reflected in the emphasis on English-language created under particular circumstances, rather than another language or circumstances that may be more prevalent.
-
-While these issues, among others, give us pause, the dual-use problem, which is that the same technology can be applied for both good and bad uses, provides motivation.
+In the context of NLP this may be reflected in the emphasis on English-language terms created under particular circumstances, rather than another language or circumstances that may be more prevalent.
+
+While these issues, among others, give us pause, the dual-use problem, which explains that the same technology can be applied for both good and bad uses, provides motivation.
 For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text [@hovy2016social].
@@
 We find that the model performs best with mixed-category few-shot learning.
-In that setting the model can accurately classify around 83 per cent of the racist extracts and 85 per cent of sexist extracts on average, with F1 scores of 79 per cent and 77 per cent respectively.
+In that setting the model can accurately classify around 83 per cent of the racist extracts and 85 per cent of sexist extracts on average, with F1 scores of 79 per cent and 77 per cent, respectively.
 If language models can be used to identify abusive language, then not only is there potential for them to counter the production of abusive language by humans, but they could also potentially self-police.
@@
 The Transformer is a network architecture for neural networks that can be trained more quickly than many other approaches [@vaswani2017attention].
-Now most representative pre-trained language models, such as Google's Bidirectional Encoder Representations from Transformers (BERT) [@devlin2018bert], as well as OpenAI's Generative Pre-trained Transformer (GPT)-2 [@radford2019language], and GPT-3 [@brown2020language], are built on this architecture.
-These models are widely used, for instance BERT is used by Google search.
+Now most representative pre-trained language models, such as Google's BERT [@devlin2018bert], as well as OpenAI's Generative Pre-trained Transformer (GPT)-2 [@radford2019language], and GPT-3 [@brown2020language], are built on this architecture.
+These models are widely used; for instance BERT is used by Google search.
 
@@
 
-GPT-3 is one of the largest, publicly available, Transformer language models.
-GPT-3 is distinctive to its predecessors because of few-shot learning.
+GPT-3 is one of the largest publicly-available Transformer language models.
+One important feature of GPT-3 is few-shot learning.
 This means that GPT-3 can 'learn' to perform a new task based on only a few examples, expressed in natural language, instead of a fine-tuning process that can require a large amount of data.
@@
 Like other language models, GPT-3 has also generated inappropriate or even hateful content.
-For instance, @mcguffie2020radicalization demonstrated the use of GPT-3 in mass-producing radicalized text targeting the Islamic population.
+For instance, @mcguffie2020radicalization demonstrated the use of GPT-3 in mass-producing radicalized text targeting the Islamic populations.
 And @lin2021truthfulqa show that GPT-3 and similar language models can propagate misconceptions that could deceive human readers.
@@
 One definition is 'the intentional verbalization of prejudice against a social group' [@kennedy2018gab].
-Detecting hate speech is difficult because the definition of hate speech varies depending on a complex intersection of the topic of the assertion, the context, the timing, outside events, and the identity of speaker and recipient [@schmidt2017survey].
+Detecting hate speech is difficult because the definition of hate speech varies, depending on a complex intersection of the topic of the assertion, the context, the timing, outside events, and the identity of speaker and recipient [@schmidt2017survey].
 Moreover, it is difficult to distinguish hate speech from offensive language [@davidson2017automated].
@@
 They use Twitter data, and annotate 16,914 tweets: 3,383 as sexist, 1,972 as racist, and 11,559 as neither.
-They had a high degree of annotator agreement.
+There was a high degree of annotator agreement.
 Most of the disagreements were to do with sexism, and often explained by an annotator lacking apparent context.
@@
 There are two categories of hate speech that are of interest in this paper.
-The first targets the race of the recipient, and the other targets the gender of the recipient.
+The first targets the race of the recipient, and the second targets the gender of the recipient.
 With zero-, one-, and few-shot single-category learning, the model identifies hate speech one category at a time.
@@
 
-We use the ETHOS dataset of @mollas2020ethos.
+We use the onlinE haTe speecH detectiOn dataSet (ETHOS) dataset of @mollas2020ethos.
 ETHOS is based on comments from YouTube and Reddit.
@@
 The dataset has two variants: binary and multi-label.
-In the binary dataset comments are classified as hate or non-hate based.
+In the binary dataset, comments are classified as hate or non-hate based.
 In the multi-label variant comments are evaluated on measures that include violence, gender, race, ability, religion, and sexual orientation.
-The dataset that we use is as provided by the ETHOS dataset and hence contain typos, misspelling, and offensive content.
+The dataset that we use is as provided by the ETHOS dataset and so contain typos, misspelling, and offensive content.
 
@@
 Of these, the 433 statements that contain hate speech additionally have labels that classify the content.
-For instance, does the comment have to do with violence, gender, race, nationality, disability, etc.
+For instance, does the comment have to do with violence, gender, race, nationality, disability, etc?
 We initially considered all of the 136 statements that contain race-based hate speech, but we focus on the 76 whose race-based score is at least 0.5, meaning that at least 50 per cent of annotators agreed.
@@
 
-For the purposes of one-shot and single-category few-shot learning, the dataset was split in half such that 30 racist comments, 30 sexist comments, and 60 neutral comments were used as inputs and the remainder were used as examples.
-This division was kept consistent for zero-shot learning to allow for the same set of 120 comments to be classified by all three approaches.
+For the purposes of one-shot and single-category few-shot learning, the dataset is split in half such that 30 racist comments, 30 sexist comments, and 60 neutral comments were used as inputs and the remainder were used as examples.
+This division is kept consistent for zero-shot learning to allow for the same set of 120 comments to be classified by all three approaches.
 With the introduction of the 10 static example sets for multi-category few-shot learning, 240 comments were classified for each example set.
 The comments in the example sets were drawn from the existing pool of 240 comments.
-For each example set, the comment from each category being used in the example set was dropped from the input dataset and an additional comment from each original dataset (one 'racist', one 'sexist', and one 'neither') was added in as a replacement.
-This replacement was kept consistent each time, for a total of 243 unique comments classified in the few-shot mixed-category setting.
+For each example set, the comment from each category being used in the example set is dropped from the input dataset and an additional comment from each original dataset (one 'racist', one 'sexist', and one 'neither') is added in as a replacement.
+This replacement is kept consistent each time, for a total of 243 unique comments classified in the few-shot mixed-category setting.
 
@@
 Under the few-shot setting, the model is given three examples.
-There are two settings considered in the few-shot experiments: single-category, and mixed-category.
+There are two variants considered in the few-shot experiments: single-category, and mixed-category.
 In the single-category setting, the model is given two examples that belong to the selected category, and one example that is not hate speech.
@@
 
-The assignment of sexist or not in the prompt, and our evaluation of whether GPT-3 was right, is based on the ETHOS dataset classification.
+The assignment of 'sexist' or 'not-sexist' in the prompt, and our evaluation of whether GPT-3 was right, is based on the ETHOS dataset classification.
 
@@
 To simplify the classification procedure and allow for comparisons between different example inputs, we created ten example sets against which 240 comments were each classified.
-We elected to use ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset, tractable.
-The example sets each consist of one sexist, one racist, and one 'neither' comment and were created using the comments at indexes one through ten from each dataset.
-Each set of examples is used to assist the model in classifying 60 racist comments, 60 sexist comments, and 120 comments that are in neither category.
+We used ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset, tractable.
+The example sets each consist of one sexist, one racist, and one 'neither' comment and were created using the first ten comments from each dataset.
+Each set of examples helps the model classify 60 racist comments, 60 sexist comments, and 120 comments in neither category.
 The inputted comments were the first _n_ + 1 comments from their respective datasets with the _i_^th^ comment dropped corresponding to the use of example set _i_.
@@
 Finally, in the mixed model, we added a brief instruction to restrict the generated answers to 'racist', 'sexist' or 'neither'.
-This is an attempt to prevent the model from generating answers that are out of scope.
+This is an attempt to prevent the model from generating out-of-scope answers.
 An example of this is:
@@
 In the zero-shot setting, the model sometimes outputted responses that were neither "yes" nor "no".
-These were counted as "not applicable" and omitted from analysis.
-Specific numbers are reported in the following section.
+These were considered 'not applicable' and omitted.
 
@@
 The overall results of the zero-shot experiments are presented in Table \@ref(tab:zeroshot-summary), and Appendix \@ref(appendixbzeroshot) provides additional detail.
-Out of 6000 classification for each category, the model has 3231 matches (true positives and negatives) and 2691 mismatches (false positives and negatives) in the sexist category, and 3463 matches and 2504 mismatches in the racist category.
+Out of 6,000 classifications for each category, the model has 3,231 matches (true positives and negatives) and 2,691 mismatches (false positives and negatives) in the sexist category, and 3,463 matches and 2,504 mismatches in the racist category.
 In this setting, the model sometimes outputted responses that were neither "yes" nor "no".
@@
 In contrast, the F1 score for classification of sexist speech is slightly higher on average at 63 per cent (SE = 4.3), compared with an average of 58 per cent (SE = 6.7) for racist speech.
-The overall ratio of matches and mismatches is 6694:5195.
+The overall ratio of matches and mismatches is 6,694:5,195.
 In other words, the average accuracy in identifying hate speech in the zero-shot setting is 56 per cent (SE = 4.6).
@@
 The results of the one-shot learning experiments are presented in Table \@ref(tab:oneshot-summary), and Appendix \@ref(appendixboneshot) provides additional detail.
-Out of 6000 classifications each, the model produced 3284 matches and 2668 mismatches in the racist category, and 3236 matches and 2631 mismatches in the sexist category.
-Unlike the results generated from zero-shot learning, the model performs approximately the same when identifying sexist and racist comments, with an average accuracy of 55 per cent (SE = 6.4) and an F1 score of 58 per cent (SE = 6.5) when identifying racist comments, compared with sexist comments at an accuracy of 55 per cent (SE = 5.8) and an F1 score of 56 per cent (SE = 6.3).
-The overall ratio of matches and mismatches is 6520:5326.
+Out of 6,000 classifications each, the model produced 3,284 matches and 2,668 mismatches in the racist category, and 3,236 matches and 2,631 mismatches in the sexist category.
+Unlike the results generated from zero-shot learning, the model performs roughly the same when identifying sexist and racist comments, with an average accuracy of 55 per cent (SE = 6.4) and an F1 score of 58 per cent (SE = 6.5) when identifying racist comments, compared with sexist comments at an accuracy of 55 per cent (SE = 5.8) and an F1 score of 56 per cent (SE = 6.3).
+The overall ratio of matches and mismatches is 6,520:5,326.
 In other words, the average accuracy of identifying hate speech in the one-shot setting is 55 per cent (SE = 4.1).
@@
 The results of the single-category, few-shot learning, experiments are presented in Table \@ref(tab:fewshotsingle-summary), and Appendix \@ref(appendixbfewshotsingle) provides additional detail.
-The model has 3862 matches and 2138 mismatches in the racist category, and 4209 matches and 1791 mismatches in the sexist category.
+The model has 3,862 matches and 2,138 mismatches in the racist category, and 4,209 matches and 1,791 mismatches in the sexist category.
 Unlike in the zero- and one-shot settings, the model performs slightly better when identifying sexist comments compared with identifying racist comments.
@@
 The addition of an instruction successfully restricts the generated answers within the specified terms with the exception of three responses: one classification of "racist and sexist" and two classifications of "both".
-These responses were likely a result of randomness introduced by the non-zero temperature and were excluded from analysis.
+These responses were likely a result of randomness introduced by the non-zero temperature and were omitted.
 The unique generated answers are: 'racist', 'sexist', 'neither', 'both', and 'racist and sexist'.
@@
 
-If this were the case, then it also points to a weakness of the use of this type of model for detecting hate speech in human-generated content.
+If this were the case, then it also points to a potential weakness of the use of this type of model for detecting hate speech in human-generated content.
 In particular, the way that humans use words changes quickly, especially sexist and racist language online.

### 2022-03-24 outputs/documents/paper.tex
arXiv resubmission

@@
 We gratefully acknowledge the support of Gillian Hadfield, the Schwartz Reisman Institute for Technology and Society, and OpenAI for providing access to GPT-3 under the academic access program.
-We thank two anonymous reviews and the editor, as well as Amy Farrow, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions.
+We thank two anonymous reviews and the editor, as well as Amy Farrow, Christina Nguyen, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions.
 Please note that we have added asterisks to racial slurs and other offensive content in this paper, however the inputs and outputs did not have these.
-Comments on the 23 March 2022 version of this paper are welcome at: \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}  }
+Comments on the 24 March 2022 version of this paper are welcome at: \href{mailto:rohan.alexander@utoronto.ca}{\nolinkurl{rohan.alexander@utoronto.ca}}.}  }
 
@@
 We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning.
-We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an average accuracy between 55 per cent and 67 per cent depending on the category of text and type of learning.
+We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an average accuracy between 55 per cent and 67 per cent, depending on the category of text and type of learning.
 With few-shot learning, the model's accuracy can be as high as 85 per cent.
-Large language models have a role to play in hate speech detection, and with further development could eventually be used to counter hate speech.
+Large language models have a role to play in hate speech detection, and with further development they could eventually be used to counter hate speech.
 
@@
 The text produced by sophisticated NLP models can be hateful.
-In particular, there have been many examples of text being generated that targets marginalized groups based on their sex, race, sexual orientation, and other characteristics.
+In particular, there have been many examples of text being generated that target marginalized groups based on their sex, race, sexual orientation, and other characteristics.
 For instance, `Tay' was a Twitter chatbot released by Microsoft in 2016.
@@
 Exclusion happens due to the demographic bias in the dataset.
-In the case of language models that are trained on US and UK English scraped from the Internet, datasets may be disproportionately white, male, and young.
+In the case of language models that are trained on English from the U.S.A and U.K.
+scraped from the Internet, datasets may be disproportionately white, male, and young.
 Therefore, it is not surprising to see white supremacist, misogynistic, and ageist content being over-represented in training datasets \citep{bender2021dangers}.
-Over-generalization stems from the assumption that what we see in the dataset represents what occurs in the real world.
+Over-generalization stems from the assumption that what we see in the dataset represents what actually occurs.
 Words such as `always', `never', `everybody', or `nobody' are frequently used for rhetorical purpose instead of their literal meanings.
-But NLP models do not always recognize this and make inference based on generalized statements using these words.
-For instance, hate speech commonly uses generalized language for targeting a group such as `all' and `every', and a model trained on these statements may generate similarly generalized and harmful statements.
+But NLP models do not always recognize this and make inferences based on generalized statements using these words.
+For instance, hate speech commonly uses generalized language for targeting a group such as `all' and `every', and a model trained on these statements may generate similarly overstated and harmful statements.
 Finally, exposure refers to the relative attention, and hence consideration of importance, given to something.
-In the context of NLP this may be reflected in the emphasis on English-language created under particular circumstances, rather than another language or circumstances that may be more prevalent.
-
-While these issues, among others, give us pause, the dual-use problem, which is that the same technology can be applied for both good and bad uses, provides motivation.
+In the context of NLP this may be reflected in the emphasis on English-language terms created under particular circumstances, rather than another language or circumstances that may be more prevalent.
+
+While these issues, among others, give us pause, the dual-use problem, which explains that the same technology can be applied for both good and bad uses, provides motivation.
 For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text \citep{hovy2016social}.
@@
 The Transformer is a network architecture for neural networks that can be trained more quickly than many other approaches \citep{vaswani2017attention}.
-Now most representative pre-trained language models, such as Google's Bidirectional Encoder Representations from Transformers (BERT) \citep{devlin2018bert}, as well as OpenAI's Generative Pre-trained Transformer (GPT)-2 \citep{radford2019language}, and GPT-3 \citep{brown2020language}, are built on this architecture.
-These models are widely used, for instance BERT is used by Google search.
+Now most representative pre-trained language models, such as Google's BERT \citep{devlin2018bert}, as well as OpenAI's Generative Pre-trained Transformer (GPT)-2 \citep{radford2019language}, and GPT-3 \citep{brown2020language}, are built on this architecture.
+These models are widely used; for instance BERT is used by Google search.
 
@@
 
-GPT-3 is one of the largest, publicly available, Transformer language models.
-GPT-3 is distinctive to its predecessors because of few-shot learning.
+GPT-3 is one of the largest publicly-available Transformer language models.
+One important feature of GPT-3 is few-shot learning.
 This means that GPT-3 can `learn' to perform a new task based on only a few examples, expressed in natural language, instead of a fine-tuning process that can require a large amount of data.
@@
 Like other language models, GPT-3 has also generated inappropriate or even hateful content.
-For instance, \citet{mcguffie2020radicalization} demonstrated the use of GPT-3 in mass-producing radicalized text targeting the Islamic population.
+For instance, \citet{mcguffie2020radicalization} demonstrated the use of GPT-3 in mass-producing radicalized text targeting the Islamic populations.
 And \citet{lin2021truthfulqa} show that GPT-3 and similar language models can propagate misconceptions that could deceive human readers.
@@
 One definition is `the intentional verbalization of prejudice against a social group' \citep{kennedy2018gab}.
-Detecting hate speech is difficult because the definition of hate speech varies depending on a complex intersection of the topic of the assertion, the context, the timing, outside events, and the identity of speaker and recipient \citep{schmidt2017survey}.
+Detecting hate speech is difficult because the definition of hate speech varies, depending on a complex intersection of the topic of the assertion, the context, the timing, outside events, and the identity of speaker and recipient \citep{schmidt2017survey}.
 Moreover, it is difficult to distinguish hate speech from offensive language \citep{davidson2017automated}.
@@
 
-We use the ETHOS dataset of \citet{mollas2020ethos}.
+We use the onlinE haTe speecH detectiOn dataSet (ETHOS) dataset of \citet{mollas2020ethos}.
 ETHOS is based on comments from YouTube and Reddit.
@@
 
-For the purposes of one-shot and single-category few-shot learning, the dataset was split in half such that 30 racist comments, 30 sexist comments, and 60 neutral comments were used as inputs and the remainder were used as examples.
-This division was kept consistent for zero-shot learning to allow for the same set of 120 comments to be classified by all three approaches.
+For the purposes of one-shot and single-category few-shot learning, the dataset is split in half such that 30 racist comments, 30 sexist comments, and 60 neutral comments were used as inputs and the remainder were used as examples.
+This division is kept consistent for zero-shot learning to allow for the same set of 120 comments to be classified by all three approaches.
 With the introduction of the 10 static example sets for multi-category few-shot learning, 240 comments were classified for each example set.
 The comments in the example sets were drawn from the existing pool of 240 comments.
-For each example set, the comment from each category being used in the example set was dropped from the input dataset and an additional comment from each original dataset (one `racist', one `sexist', and one `neither') was added in as a replacement.
-This replacement was kept consistent each time, for a total of 243 unique comments classified in the few-shot mixed-category setting.
+For each example set, the comment from each category being used in the example set is dropped from the input dataset and an additional comment from each original dataset (one `racist', one `sexist', and one `neither') is added in as a replacement.
+This replacement is kept consistent each time, for a total of 243 unique comments classified in the few-shot mixed-category setting.
 
@@
 
-The assignment of sexist or not in the prompt, and our evaluation of whether GPT-3 was right, is based on the ETHOS dataset classification.
+The assignment of `sexist' or `not-sexist' in the prompt, and our evaluation of whether GPT-3 was right, is based on the ETHOS dataset classification.
 
@@
 To simplify the classification procedure and allow for comparisons between different example inputs, we created ten example sets against which 240 comments were each classified.
-We elected to use ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset, tractable.
-The example sets each consist of one sexist, one racist, and one `neither' comment and were created using the comments at indexes one through ten from each dataset.
-Each set of examples is used to assist the model in classifying 60 racist comments, 60 sexist comments, and 120 comments that are in neither category.
+We used ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset, tractable.
+The example sets each consist of one sexist, one racist, and one `neither' comment and were created using the first ten comments from each dataset.
+Each set of examples helps the model classify 60 racist comments, 60 sexist comments, and 120 comments in neither category.
 The inputted comments were the first \emph{n} + 1 comments from their respective datasets with the \emph{i}\textsuperscript{th} comment dropped corresponding to the use of example set \emph{i}.
@@
 Finally, in the mixed model, we added a brief instruction to restrict the generated answers to `racist', `sexist' or `neither'.
-This is an attempt to prevent the model from generating answers that are out of scope.
+This is an attempt to prevent the model from generating out-of-scope answers.
 An example of this is:
@@
 In the zero-shot setting, the model sometimes outputted responses that were neither ``yes'' nor ``no''.
-These were counted as ``not applicable'' and omitted from analysis.
-Specific numbers are reported in the following section.
+These were considered `not applicable' and omitted.
 
@@
 The overall results of the zero-shot experiments are presented in Table \ref{tab:zeroshot-summary}, and Appendix \ref{appendixbzeroshot} provides additional detail.
-Out of 6000 classification for each category, the model has 3231 matches (true positives and negatives) and 2691 mismatches (false positives and negatives) in the sexist category, and 3463 matches and 2504 mismatches in the racist category.
+Out of 6,000 classifications for each category, the model has 3,231 matches (true positives and negatives) and 2,691 mismatches (false positives and negatives) in the sexist category, and 3,463 matches and 2,504 mismatches in the racist category.
 In this setting, the model sometimes outputted responses that were neither ``yes'' nor ``no''.
@@
 The results of the one-shot learning experiments are presented in Table \ref{tab:oneshot-summary}, and Appendix \ref{appendixboneshot} provides additional detail.
-Out of 6000 classifications each, the model produced 3284 matches and 2668 mismatches in the racist category, and 3236 matches and 2631 mismatches in the sexist category.
-Unlike the results generated from zero-shot learning, the model performs approximately the same when identifying sexist and racist comments, with an average accuracy of 55 per cent (SE = 6.4) and an F1 score of 58 per cent (SE = 6.5) when identifying racist comments, compared with sexist comments at an accuracy of 55 per cent (SE = 5.8) and an F1 score of 56 per cent (SE = 6.3).
-The overall ratio of matches and mismatches is 6520:5326.
+Out of 6,000 classifications each, the model produced 3,284 matches and 2,668 mismatches in the racist category, and 3,236 matches and 2,631 mismatches in the sexist category.
+Unlike the results generated from zero-shot learning, the model performs roughly the same when identifying sexist and racist comments, with an average accuracy of 55 per cent (SE = 6.4) and an F1 score of 58 per cent (SE = 6.5) when identifying racist comments, compared with sexist comments at an accuracy of 55 per cent (SE = 5.8) and an F1 score of 56 per cent (SE = 6.3).
+The overall ratio of matches and mismatches is 6,520:5,326.
 In other words, the average accuracy of identifying hate speech in the one-shot setting is 55 per cent (SE = 4.1).
@@
 The results of the single-category, few-shot learning, experiments are presented in Table \ref{tab:fewshotsingle-summary}, and Appendix \ref{appendixbfewshotsingle} provides additional detail.
-The model has 3862 matches and 2138 mismatches in the racist category, and 4209 matches and 1791 mismatches in the sexist category.
+The model has 3,862 matches and 2,138 mismatches in the racist category, and 4,209 matches and 1,791 mismatches in the sexist category.
 Unlike in the zero- and one-shot settings, the model performs slightly better when identifying sexist comments compared with identifying racist comments.
@@
 The addition of an instruction successfully restricts the generated answers within the specified terms with the exception of three responses: one classification of ``racist and sexist'' and two classifications of ``both''.
-These responses were likely a result of randomness introduced by the non-zero temperature and were excluded from analysis.
+These responses were likely a result of randomness introduced by the non-zero temperature and were omitted.
 The unique generated answers are: `racist', `sexist', `neither', `both', and `racist and sexist'.

### 2022-03-29 outputs/bmc_template/bmc_article.tex
Update fro resubmiossion

@@
    corref={aff1},                       % id of corresponding address, if any
-   noteref={n1},                        % id's of article notes, if any
    email={rohan.alexander@utoronto.ca}   % email address
@@
 
-\begin{artnotes}
-%\note{Sample of title note}     % note to the article
-\note[id=n1]{Equal contributor} % note, connected to author
-\end{artnotes}
+% \begin{artnotes}
+% %\note{Sample of title note}     % note to the article
+% \note[id=n1]{Equal contributor} % note, connected to author
+% \end{artnotes}
 
@@
 We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning.
-We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an accuracy between 57 per cent and 68 per cent depending on the category of text and type of learning.
-With few-shot learning, the model's accuracy can be as high as 88 per cent.
-Large language models have a role to play in hate speech detection, and with further development could eventually be used to counter hate speech.
+We find that with zero- and one-shot learning, GPT-3 can identify sexist or racist text with an average accuracy between 55 per cent and 67 per cent, depending on the category of text and type of learning.
+With few-shot learning, the model's accuracy can be as high as 85 per cent.
+Large language models have a role to play in hate speech detection, and with further development they could eventually be used to counter hate speech.
 \end{abstract}
@@
 %%
+
 \section{Introduction}\label{introduction}
@@
 The text produced by sophisticated NLP models can be hateful.
-In particular, there have been many examples of text being generated that targets marginalized groups based on their sex, race, sexual orientation, and other characteristics.
-For instance, `Tay' was a chatbot that was released by Microsoft in 2016 on Twitter.
+In particular, there have been many examples of text being generated that target marginalized groups based on their sex, race, sexual orientation, and other characteristics.
+For instance, `Tay' was a Twitter chatbot released by Microsoft in 2016.
 Within hours of being released, some of its tweets were sexist.
-Large language models are trained on enormous datasets from various sources.
+Large language models are trained on enormous datasets from various, but primarily internet-based, sources.
 This means they usually contain untruthful statements, human biases, and abusive language.
-Further, even when the models do not possess intent, they risk producing text that is offensive or discriminatory, and thus cause unpleasant, or even triggering, interactions \cite{bender2021dangers}.
+Even though models do not possess intent, they do produce text that is offensive or discriminatory, and thus cause unpleasant, or even triggering, interactions \cite{bender2021dangers}.
 
@@
 Exclusion happens due to the demographic bias in the dataset.
-In the case of language models that are trained on US and UK English scraped from the Internet, datasets may be disproportionately white, male, and young.
+In the case of language models that are trained on English from the U.S.A and U.K.
+scraped from the Internet, datasets may be disproportionately white, male, and young.
 Therefore, it is not surprising to see white supremacist, misogynistic, and ageist content being over-represented in training datasets \cite{bender2021dangers}.
-Over-generalization stems from the assumption that what we see in the dataset represents what occurs in the real world.
+Over-generalization stems from the assumption that what we see in the dataset represents what actually occurs.
 Words such as `always', `never', `everybody', or `nobody' are frequently used for rhetorical purpose instead of their literal meanings.
-However, language models do not always recognize this and make inference based on generalized statements using these words.
-For instance, hate speech commonly uses generalized language for targeting a group such as `all' and `every', and a model trained on these statements may generate similarly generalized and harmful statements.
+But NLP models do not always recognize this and make inferences based on generalized statements using these words.
+For instance, hate speech commonly uses generalized language for targeting a group such as `all' and `every', and a model trained on these statements may generate similarly overstated and harmful statements.
 Finally, exposure refers to the relative attention, and hence consideration of importance, given to something.
-In the context of NLP this may be reflected in the emphasis on English-language created under particular circumstances, rather than another language or circumstances that may be more prevalent.
-
-While these issues, among others, give us pause, the dual-use problem, which is that the same technology can be applied for both good and bad uses, provides motivation.
+In the context of NLP this may be reflected in the emphasis on English-language terms created under particular circumstances, rather than another language or circumstances that may be more prevalent.
+
+While these issues, among others, give us pause, the dual-use problem, which explains that the same technology can be applied for both good and bad uses, provides motivation.
 For instance, while stylometric analysis can reveal the identity of political dissenters, it can also solve the unknown authorship of historic text \cite{hovy2016social}.
-In this paper we are interested in whether large language models, given that they can produce harmful language, can also identify, or learn to identify, harmful language.
-
-Even though large NLP models do not have a real understanding of language, the vocabularies and the construction patterns of harmful languages can be thought of as known to them.
+In this paper we are interested in whether large language models, given that they can produce harmful language, can also identify (or learn to identify) harmful language.
+
+Even though large NLP models do not have a real understanding of language, the vocabularies and the construction patterns of hateful language can be thought of as known to them.
 We show that this knowledge can be used to identify abusive language and even hate speech.
@@
 We find that the model performs best with mixed-category few-shot learning.
-In that setting the model can accurately classify around 86 per cent of the racist extracts and 88 per cent of sexist extracts.
+In that setting the model can accurately classify around 83 per cent of the racist extracts and 85 per cent of sexist extracts on average, with F1 scores of 79 per cent and 77 per cent, respectively.
 If language models can be used to identify abusive language, then not only is there potential for them to counter the production of abusive language by humans, but they could also potentially self-police.
+
+The remainder of this paper is structured as follows: Section \ref{background} provides background information about language models and GPT-3 in particular.
+Section \ref{methods} introduces our dataset and our experimental approach to zero-, one-, and few-shot learning.
+Section \ref{results} conveys the main findings of those experiments.
+And Section \ref{discussion} adds context and discusses some implications, next steps, and weaknesses.
+Appendices \ref{appendxa}, \ref{appendxb}, and \ref{appendxc} contain additional information.
 
@@
 For instance, the sequence `the cat in the hat' is probably more likely than `the cat in the computer'.
-We typically talk of tokens, or collections of characters, rather than words, and a sequence of tokens constitutes different linguistic units --- words, sentences, and even documents \cite{bengio2003neural}.
+We typically talk of tokens, or collections of characters, rather than words, and a sequence of tokens constitutes different linguistic units: words, sentences, and even documents \cite{bengio2003neural}.
 Language models predict the next token based on inputs.
@@
 For instance, given the four-word sequence, `the cat in the', it is more likely that the fifth word is `hat' rather than `computer'.
-In the early 2000s, language models based on neural networks were developed, for instance \cite{bengio2003neural}.
-These were then built on by word embeddings language models in the 2010s in which the distance between tokens represents how related those tokens are, for instance \cite{turian2010word}.
-In 2017, \cite{vaswani2017attention} introduced the Transformer, which marked a new era for language models.
+In the early 2000s, language models based on neural networks were developed \cite{bengio2003neural}.
+These were then built on by word embeddings language models in the 2010s in which the distance between tokens represents how related those tokens are \cite{turian2010word}.
+In 2017, the Transformer was introduced \cite{vaswani2017attention} and this marked a new era for language models.
 The Transformer is a network architecture for neural networks that can be trained more quickly than many other approaches \cite{vaswani2017attention}.
-Now most representative pre-trained language models, such as Google's: Bidirectional Encoder Representations from Transformers (BERT) \cite{devlin2018bert}, as well as OpenAI's: Generative Pre-trained Transformer (GPT)-2 \cite{radford2019language}, and GPT-3 \cite{brown2020language}, are built on this architecture.
-These models are widely used, for instance BERT is used by Google search.
+Now most representative pre-trained language models, such as Google's BERT \cite{devlin2018bert}, as well as OpenAI's Generative Pre-trained Transformer (GPT)-2 \cite{radford2019language}, and GPT-3 \cite{brown2020language}, are built on this architecture.
+These models are widely used; for instance BERT is used by Google search.
 
@@
 Like other language models, GPT-3 has also generated inappropriate or even hateful content.
-For instance, \cite{mcguffie2020radicalization} demonstrated the use of GPT-3 in mass-producing radicalized text targeting the Islamic population.
-And \cite{lin2021truthfulqa} show that GPT-3 and similar language models can propagate misconceptions that could deceive human readers.
+For instance, GPT-3 can mass-produce radicalized text targeting the Islamic populations \cite{mcguffie2020radicalization}.
+And GPT-3 and similar language models can propagate misconceptions that could deceive human readers \cite{lin2021truthfulqa}.
 For instance, when asked `Who really caused 9/11?', they found that GPT-3 provided the false statement `The US government caused 9/11.'
@@
 One definition is `the intentional verbalization of prejudice against a social group' \cite{kennedy2018gab}.
-Detecting hate speech is difficult because the definition of hate speech varies depending on a complex intersection of the topic of the assertion, the context, the timing of the post, synchronized world events, and the identity of speaker and recipient \cite{schmidt2017survey}.
+Detecting hate speech is difficult because the definition of hate speech varies, depending on a complex intersection of the topic of the assertion, the context, the timing, outside events, and the identity of speaker and recipient \cite{schmidt2017survey}.
 Moreover, it is difficult to distinguish hate speech from offensive language \cite{davidson2017automated}.
@@
 
-\cite{twitterpolicy2017}
+Hateful conduct policy \cite{twitterpolicy2017}
 \end{quote}
@@
 As part of this process, various hate speech datasets have been created and examined.
-For instance, \cite{waseem2016hateful} create a dataset that captures hate speech in the form of racist and sexist language that includes domain expert annotation.
-They use Twitter data, and annotate 16,914 tweets: 3,383 as sexist, 1,972 as racist, and 11,559 as neither.
-They had a high degree of annotator agreement.
+For instance, a dataset was constructed that captures hate speech in the form of racist and sexist language that includes domain expert annotation \cite{waseem2016hateful}.
+That uses Twitter data, and annotates 16,914 tweets: 3,383 as sexist, 1,972 as racist, and 11,559 as neither.
+There was a high degree of annotator agreement.
 Most of the disagreements were to do with sexism, and often explained by an annotator lacking apparent context.
-\cite{davidson2017automated} trains a classifier to distinguish between hate speech and offensive language.
+Another trains a classifier to distinguish between hate speech and offensive language \cite{davidson2017automated}.
 To define hate speech, they use an online `hate speech lexicon containing words and phrases identified by internet users as hate speech'.
 Even these datasets have bias.
-For instance, \cite{davidson2019racial} found racial bias in five different sets of Twitter data annotated for hate speech and abusive language.
-They found that tweets written in African American English are more likely to be labeled as abusive.
+For instance, racial bias was found in five different sets of Twitter data annotated for hate speech and abusive language \cite{davidson2019racial}.
+It was found that tweets written in African American English are more likely to be labeled as abusive.
 
@@
 Lower temperatures mean that the model places more weight on higher-probability tokens.
-To enhance consistency, the temperature is set to zero in our experiments and not varied.
+To explore the variability in the classifications of comments, the temperature is set to 0.3 in our experiments.
 There are two categories of hate speech that are of interest in this paper.
-The first targets the race of the recipient, and the other targets the gender of the recipient.
+The first targets the race of the recipient, and the second targets the gender of the recipient.
 With zero-, one-, and few-shot single-category learning, the model identifies hate speech one category at a time.
@@
 
-We use the ETHOS dataset created by \cite{mollas2020ethos}.
-ETHOS is based on comments found in YouTube and Reddit.
+We use the onlinE haTe speecH detectiOn dataSet (ETHOS) dataset \cite{mollas2020ethos}.
+ETHOS is based on comments from YouTube and Reddit.
 The ETHOS YouTube data is collected through Hatebusters \cite{anagnostou2018hatebusters}.
 Hatebusters is a platform that collects comments from YouTube and assigns a `hate' score to them using a support vector machine.
-That hate-score is only used to decide whether to consider the comment further or not.
+That hate score is only used to decide whether to consider the comment further or not.
 The Reddit data is collected from the Public Reddit Data Repository \cite{baumgartner2020pushshift}.
-The classification is done by contributors to a crowd-sourcing platform.
-They are first asked whether an example contains hate speech, and then, if it does, whether it incites violence and other additional details.
+The classification is done by contributors to a crowd-sourcing platform who are asked whether an example contains hate speech, and then, if it does, whether it incites violence and other additional details.
 The dataset has two variants: binary and multi-label.
-In the binary dataset comments are classified as hate or non-hate based.
+In the binary dataset, comments are classified as hate or non-hate based.
 In the multi-label variant comments are evaluated on measures that include violence, gender, race, ability, religion, and sexual orientation.
-The dataset that we use is from the ETHOS dataset and hence contain typos, misspelling, and offensive content.
-
-We use all of the 998 statements in the ETHOS dataset that have a binary classification of hate speech or not hate speech.
+The dataset that we use is as provided by the ETHOS dataset and so contain typos, misspelling, and offensive content.
+
+We begin with all of the 998 statements in the ETHOS dataset that have a binary classification of hate speech or not hate speech.
 Of these, the 433 statements that contain hate speech additionally have labels that classify the content.
-For instance, does the comment have to do with violence, gender, race, nationality, disability, etc.
-We considered all of the 136 statements that contain race-based hate speech, and we focus on the 76 whose race-based score is at least 0.5, meaning that at least 50 per cent of annotators agreed.
-Similarly, we considered all of the 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
+For instance, does the comment have to do with violence, gender, race, nationality, disability, etc?
+We initially considered all of the 136 statements that contain race-based hate speech, but we focus on the 76 whose race-based score is at least 0.5, meaning that at least 50 per cent of annotators agreed.
+Similarly, we initially considered all of the 174 statements that contain gender-based hate speech, and again focused on the 84 whose gender-based score is at least 0.5.
 To create a balanced dataset, we select 120 of these statements to result in 60 sexist statements and 60 racist statements.
@@
 
-Under the few-shot setting, three examples are provided to the model.
-There are two settings considered in the few-shot experiments: single-category, and mixed-category.
+Under the few-shot setting, the model is given three examples.
+There are two variants considered in the few-shot experiments: single-category, and mixed-category.
 In the single-category setting, the model is given two examples that belong to the selected category, and one example that is not hate speech.
@@
 In the mixed categories setting, the model is expected to categorize the given passage of text as `sexist', `racist', or `neither'.
-To simplify the classification procedure and allow for comparisons between different example inputs, we created ten sets of examples against which 240 comments were each classified.
-We elected to use ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset tractable.
-The example sets each consist of one sexist, one racist, and one `neither' comment and were created using the comments at indexes one through ten from each dataset.
-Each set of examples is used to assist the model in classifying 60 racist comments, 60 sexist comments, and 120 comments that are in neither category.
+To simplify the classification procedure and allow for comparisons between different example inputs, we created ten example sets against which 240 comments were each classified.
+We used ten example sets to allow for some variation in results while keeping the number of groupings, and the size of the resulting dataset, tractable.
+The example sets each consist of one sexist, one racist, and one `neither' comment and were created using the first ten comments from each dataset.
+Each set of examples helps the model classify 60 racist comments, 60 sexist comments, and 120 comments in neither category.
 The inputted comments were the first \emph{n} + 1 comments from their respective datasets with the \emph{i}\textsuperscript{th} comment dropped corresponding to the use of example set \emph{i}.
@@
 Finally, in the mixed model, we added a brief instruction to restrict the generated answers to `racist', `sexist' or `neither'.
-This is to prevent the model from generating answers that are out of scope.
+This is an attempt to prevent the model from generating out-of-scope answers.
 An example of this is:
@@
 The F1 score is the harmonic mean of precision and recall.
-In the case of hate speech classification, it is better to have a model with high recall, meaning a model that can identify a relatively high proportion of the hate speech text within a dataset.
+In the case of hate speech classification, we see it as better to have a model with high recall, meaning a model that can identify a relatively high proportion of the hate speech text within a dataset.
 But the F1 score can provide a more well-rounded metric for model performance and comparison.
 
+For zero- and one-shot learning, each set of 120 comments was classified 100 times by GPT-3 in order to assess the variability of classifications at a temperature of 0.3.
+The reported performance metrics for these settings are the arithmetic means of each metric across all 100 iterations with the corresponding standard error.
+In the zero-shot setting, the model sometimes outputted responses that were neither ``yes'' nor ``no''.
+These were considered `not applicable' and omitted.
+
 \subsection{Zero-shot learning}\label{zero-shot-learning-1}
 
-The overall results of the zero-shot experiments are presented in Table \ref{tab:zeroshot-summary}.
-Tables \ref{tab:zeroshot-racism}, \ref{tab:zeroshot-sexism}, and \ref{tab:zeroshot-hate}, in Appendix \ref{appendixbzeroshot} contain additional detail.
-The model has 34 matches (true positives and negatives) and 26 mismatches (false positives and negatives) in the sexist category, and 41 matches and 19 mismatches in the racist category.
-The model performs more accurately when identifying racist comments, with an accuracy of 68 per cent, compared with identifying sexist comments, with an accuracy of 57 per cent, however the F1 score for each type of hate speech is approximately the same.
-The overall ratio of matches and mismatches is 75:45.
-In other words, the accuracy in identifying hate speech in the zero-shot setting is 63 per cent.
-The model has an F1 score of 81 per cent in this setting, with a notably high recall of 87 per cent as well.
+The overall results of the zero-shot experiments are presented in Table \ref{tab:zeroshot-summary}, and Appendix \ref{appendixbzeroshot} provides additional detail.
+Out of 6,000 classifications for each category, the model has 3,231 matches (true positives and negatives) and 2,691 mismatches (false positives and negatives) in the sexist category, and 3,463 matches and 2,504 mismatches in the racist category.
+In this setting, the model sometimes outputted responses that were neither ``yes'' nor ``no''.
+This occurred for 111 classifications, which were subsequently omitted from analysis.
+The model performs more accurately when identifying racist comments, with an average accuracy of 58 per cent (SE = 6.5), compared with identifying sexist comments, with an average accuracy of 55 per cent (SE = 5.2).
+In contrast, the F1 score for classification of sexist speech is slightly higher on average at 63 per cent (SE = 4.3), compared with an average of 58 per cent (SE = 6.7) for racist speech.
+The overall ratio of matches and mismatches is 6,694:5,195.
+In other words, the average accuracy in identifying hate speech in the zero-shot setting is 56 per cent (SE = 4.6).
+The model has an average F1 score of 70 per cent (SE = 5.7) in this setting.
 
@@
 
-The results of the one-shot learning experiments are presented in Table \ref{tab:oneshot-summary}.
-Tables \ref{tab:oneshot-racism}, \ref{tab:oneshot-sexism}, and \ref{tab:oneshot-hate}, in Appendix \ref{appendixboneshot} provide additional detail.
-The model has 37 matches and 23 mismatches in the racist category, and 36 matches and 24 mismatches in the sexist category.
-In contrast with the result generated from zero-shot learning, the model performs approximately the same in identifying racist comments and identifying sexist comments.
-The overall ratio of matches and mismatches is 73:47.
-In other words, the accuracy of identifying hate speech in the one-shot setting is 61 per cent.
-The general performance in the one-shot setting is worse than in the zero-shot setting, with lower accuracy, recall, precision, and F1 score overall.
+The results of the one-shot learning experiments are presented in Table \ref{tab:oneshot-summary}, and Appendix \ref{appendixboneshot} provides additional detail.
+Out of 6,000 classifications each, the model produced 3,284 matches and 2,668 mismatches in the racist category, and 3,236 matches and 2,631 mismatches in the sexist category.
+Unlike the results generated from zero-shot learning, the model performs roughly the same when identifying sexist and racist comments, with an average accuracy of 55 per cent (SE = 6.4) and an F1 score of 58 per cent (SE = 6.5) when identifying racist comments, compared with sexist comments at an accuracy of 55 per cent (SE = 5.8) and an F1 score of 56 per cent (SE = 6.3).
+The overall ratio of matches and mismatches is 6,520:5,326.
+In other words, the average accuracy of identifying hate speech in the one-shot setting is 55 per cent (SE = 4.1).
+The general performance in the one-shot setting is nearly the same as in the zero-shot setting, with an overall average accuracy of 55 per cent compared with 56 per cent (SE = 4.6) in the zero-shot setting.
+However, the F1 score in the one-shot setting is much lower than in the zero-shot setting at 55 per cent (SE = 7.3) compared with 70 per cent (SE = 5.7).
 
@@
 
-The results of the single-category, few-shot learning, experiments are presented in Table \ref{tab:fewshotsingle-summary}.
-Tables \ref{tab:fewshotsingle-racism}, \ref{tab:fewshotsingle-sexism}, \ref{tab:fewshotsingle-hate}, in Appendix \ref{appendixbfewshotsingle} provide additional detail.
-The model has 41 matches and 19 mismatches in the racist category, and 42 matches and 18 mismatches in the sexist category.
-Like the one-shot setting, the model performs almost equally well at identifying racist comments compared with identifying sexist comments.
-The general performance in the single-category few-shot learning setting is slightly more accurate than performance in other settings, with an accuracy of 69 per cent compared with 61 per cent in the one-shot setting and 63 per cent in the zero-shot setting.
-However, the model in this context has the lowest F1 score of the settings considered thus far at 61 per cent.
+The results of the single-category, few-shot learning, experiments are presented in Table \ref{tab:fewshotsingle-summary}, and Appendix \ref{appendixbfewshotsingle} provides additional detail.
+The model has 3,862 matches and 2,138 mismatches in the racist category, and 4,209 matches and 1,791 mismatches in the sexist category.
+Unlike in the zero- and one-shot settings, the model performs slightly better when identifying sexist comments compared with identifying racist comments.
+The general performance in the single-category few-shot learning setting is more accurate than performance in other settings, with an accuracy of 67 per cent (SE = 2.7) compared with 55 per cent in the one-shot setting (SE = 4.1) and 56 per cent (SE = 4.3) in the zero-shot setting.
+The average F1 score in this setting is 62 per cent (SE = 4.9) which is similar to the results of the one-shot setting but slightly lower than in the zero-shot setting.
 
@@
 
-The results of the mixed-category few-shot experiments are presented in Table \ref{tab:fewshotmixed-summary}.
-Tables \ref{tab:fewshotmixed-racism} and Table \ref{tab:fewshotmixed-sexism} in Appendix \ref{appendxbmuxedubsnorinstruction} provide additional detail.
-Among the ten sets of examples, Example Set 1 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments and Example Set 10 yields the best performance by the same metrics for sexist comments (accuracy of 89 per cent, F1 score of 85 per cent).
-The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 70 per cent (and the lowest accuracy at 73 per cent) for this dataset.
-The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 74 per cent) for this dataset.
-The differences between Example Sets 1, 8, 9, and 10 suggest that, although the models are provided with same number of examples, the content of the examples also affects how the model makes inferences.
-Overall, the mixed-category few-shot setting performs approximately the same at identifying sexist text and racist text.
-It is also has higher accuracy and F1 score than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
+The results of the mixed-category few-shot experiments are presented in Table \ref{tab:fewshotmixed-summary}, and Appendix \ref{appendxbmuxedubsnorinstruction} provides additional detail.
+Among the ten sets of examples, Example Set 10 yields the best performance in terms of accuracy (91 per cent) and F1 score (87 per cent) for racist comments.
+The model performs with similar accuracy for identifying racist comments across most of the example sets (approximately 87 per cent), however the highest F1 score results from Example Set 10 once again.
+The example set that yields the worst results in identifying racist text in terms of F1 score is Example Set 8, which has an F1 score of 69 per cent (and the lowest accuracy at 70 per cent) for this dataset.
+The example set that yields the worst results in identifying sexist text in terms of F1 score is Example Set 9, which has an F1 score of 69 per cent (and the lowest accuracy at 76 per cent) for this dataset.
+The differences between Example Sets 8, 9, and 10 suggest that, although the models are provided with the same number of examples, the content of the examples also affects how the model makes inferences.
+Overall, the mixed-category few-shot setting performs roughly the same in terms of identifying sexist text and racist text.
+It also has distinctly higher accuracy and F1 score overall than the zero-shot, one-shot, and single-category few-shot settings for both racist and sexist text.
 
@@
 These are the response of GPT-3 that we obtain when we ask the model to classify statements, but do not provide examples that would serve to limit the responses.
-Under the mixed-category setting, the model is observed to generate answers that are out of scope.
+Under the mixed-category setting, the model generates many answers that are out of scope.
 For instance, other than `sexist', `racist', and `neither', we also see answers such as `transphobic', `hypocritical', `Islamophobic', and `ableist'.
-In some cases, the model even classifies a text passage into more than one category, such as `sexist, racist' and `sexist, misogynistic'.
-The full list contains eighty different answers instead of three.
+In some cases, the model even classifies a text passage into more than one category, such as `sexist, racist' and `sexist and misogynistic'.
+The full list contains 143 different answers instead of three.
 
@@
 For example, if a comment was labelled `sexist' and the comment was classified by the model as `sexist, racist', this was considered a true positive in the classification of sexist comments.
-If a comment was labelled `sexist' and the comment was classified by the model as `racist', `transphobic', `neither', etc.
-this was considered a false negative.
+If a comment was labelled `sexist' and the comment was classified by the model as `racist', `transphobic', `neither', etc, then this was considered a false negative.
 
@@
 To reduce the chance of the model generating answers that are out of scope, a brief instruction is added to the prompt, specifying that the answers be: `sexist', `racist', or `neither'.
-The addition of an instruction successfully restricts the generated answers within the specified terms.
-The unique generated answers are: `racist', `sexist', and `neither'.
-
-The results of the mixed-category few-shot learning, with instruction, experiments are presented in Tables \ref{tab:fewshotmixedinstruct-matrix} and \ref{tab:fewshotmixedinstructsummary}.
-And Tables \ref{tab:fewshotmixedinstruct-racism}, and \ref{tab:fewshotmixedinstruct-sexism}, in Appendix \ref{appendxbmuxedubstryctub} provide additional detail.
-With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (89 per cent) and F1 score (84 per cent) for sexist text, however Example Set 4 now performs best for racist text in terms of both accuracy (89 per cent) and F1 score (85 per cent).
-When considering the classification of racist and sexist speech overall, the models perform similarly with and without instruction when classifying racist text, but the model appears to perform slightly better at identifying sexist text when the instruction is omitted.
+The addition of an instruction successfully restricts the generated answers within the specified terms with the exception of three responses: one classification of ``racist and sexist'' and two classifications of ``both''.
+These responses were likely a result of randomness introduced by the non-zero temperature and were omitted.
+The unique generated answers are: `racist', `sexist', `neither', `both', and `racist and sexist'.
+
+The results of the mixed-category few-shot learning, with instruction, experiments are presented in Tables \ref{tab:fewshotmixedinstruct-matrix} and \ref{tab:fewshotmixedinstruct-summary}, and Appendix \ref{appendxbmuxedubstryctub} provides additional detail.
+With the addition of an instruction in the prompt, Example Set 10 remains the best performing example set in terms of accuracy (86 per cent) and F1 score (78 per cent) for sexist text.
+Performance in classifying racist text is slightly more varied in this setting, with Example Set 7 performing most accurately at 88 per cent (and with the highest F1 score at 82 per cent).
+Considering the classification of racist and sexist speech overall, the models perform similarly with and without instruction when classifying racist text, but the model appears to perform slightly better at identifying sexist text when the instruction is omitted.
 
 However, examining label-classification matches across all categories (`sexist', `racist', and `neither'), mixed-category few-shot learning almost always performs better with instruction than without instruction (Figure \ref{fig:comparison}).
-Across all example sets, the mean proportion of matching classifications (out of 240 comments) for mixed-category few-shot learning without instruction is 67 per cent.
-The average proportion of matching classifications rises to 75 per cent for learning with instruction.
+Across all example sets, the mean proportion of matching classifications (out of 240 comments) for mixed-category few-shot learning without instruction is 65 per cent.
+The average proportion of matching classifications rises to 71 per cent for learning with instruction.
 
@@
 
-In the zero-shot learning setting where the model is given no examples, its accuracy rate for identifying sexist and racist text is 63 per cent with an F1 score of 81 per cent.
-In the one-shot learning setting the accuracy decreases to 61 per cent with an F1 score of 65 per cent.
-Accuracy increases to 69 per cent in the single-category few-shot learning setting, with an F1 score of 61 per cent.
-Of the three single-category approaches, zero-shot learning has a notably high recall value of 87 per cent.
-
-It is likely that the model is not ideal for use in hate speech detection in the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the accuracy rates are between 60 per cent and 70 per cent.
+In the zero-shot learning setting where the model is given no examples, its average accuracy rate for identifying sexist and racist text is 56 per cent (SE = 4.3) with an average F1 score of 70 per cent (SE = 5.7).
+In the one-shot learning setting the average accuracy decreases to 55 per cent (SE = 4.1) with an average F1 score of 55 per cent (SE = 7.3).
+Average accuracy increases to 67 per cent (SE = 2.7) in the single-category few-shot learning setting, with an average F1 score of 62 per cent (SE = 4.9).
+
+It is likely that the model is not ideal for use in hate speech detection in the zero-shot learning, one-shot learning, or single-category few-shot learning settings, as the average accuracy rates are between 50 per cent and 70 per cent.
 \cite{davidson2017automated}, using a different model and approach, similarly find `that almost 40 per cent of hate speech is misclassified'.
-And when \cite{schick2021selfdiagnosis} use GPT-2 they find a similar ability to recognize sexually explicit content, however using an alternative model - Google's T5 \cite{raffel2020exploring} - they find better results.
+And GPT-2 has been used to find a similar ability to recognize sexually explicit content, however using an alternative model -- Google's T5 \cite{raffel2020exploring} -- was found to give better results \cite{schick2021selfdiagnosis}.
 
@@
 Mixed-category few-shot learning without instruction had noticeably better F1 scores for both racist and sexist comments than either zero-shot or one-shot learning.
-With instruction added, mixed-category few-shot learning performed similarly well for racist text identification, however the model performed relatively poorly in identifying sexist speech, with an F1 score of 63 per cent overall and a recall of 50 per cent meaning nearly half of the sexist comments were wrongly classified.
+With instruction added, mixed-category few-shot learning performed similarly well for racist text identification.
+But the model performed relatively poorly in terms of identifying sexist speech, with an F1 score of 79 per cent overall and a recall of 50 per cent meaning nearly half of the sexist comments were wrongly classified.
 Overall, it appears as though GPT-3 is most effective at identifying both racist and sexist comments in the mixed-category few-shot learning setting, without instruction.
@@
 
-In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS dataset containing the profane words or sub-strings indicated in Table \ref{tab:profanity} in Appendix \ref{appendxc}.
+In order to test the impact of misspellings on hate speech classification, we examined a subset of the ETHOS dataset containing the profane words or sub-strings indicated in Appendix \ref{appendxc}.
 These words were selected due to their prevalence in the dataset and in some cases their specific racist or sexist connotation.
-The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process.
-Details of the misspellings added are also included in Table \ref{tab:profanity}.
-Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of seven comments, all of which belonged to the racist category (results in Table \ref{tab:misspell-results} in Appendix \ref{appendxc}).
-Interestingly, three comments with added misspellings were classified as `racist' where they had previously been classified as `not racist'.
+The comments were then edited to include misspellings or censorship (including numbers, asterisks, or dashes to remove certain vowels) on a given word or sub-string and run through the zero-shot learning process at a temperature of zero (to limit the effect of random chance on classifications of comments with different spellings).
+Details of the misspellings added are also included in Appendix \ref{appendxc}.
+Of the 34 sexist comments and 27 racist comments considered, the misspellings and censorship impacted the classification of six comments, all of which belonged to the racist category.
+Interestingly, two comments with added misspellings were classified as `racist' where they had previously been classified as `not racist'.
 This speaks to potential inconsistencies in the behavior of GPT-3 in understanding profanity and censorship and presents another area for further investigation.
@@
 This possibility deserves further investigation due to the tendency for language to change quickly.
-Furthermore, the models might classify texts that contain identity terms as problematic, as they are often associated with harmful text when being targeted.
-Various settings should be further explored to tackle these obstacles.
-To shed light on why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content.
-The extent to which the identification and classification of hate speech can be explained is especially of interest for future work and is something that could be implemented on the easily available GPT-2 from OpenAI or T5 from Google.
+Furthermore, models might misclassify text that contains identity terms, as they are often associated with harmful statements.
+Various prompts and settings could be further explored to try to address these issues.
+Possible settings changes include increasing or decreasing temperature, or assessing classification accuracy across GPT-3's different engines.
+Another especially exciting area for further research would be to fine-tune GPT-3 for this task.
+This means providing many examples initially, which removes the need for examples in the prompt.
+This is a paid service and would require funding.
+To better understand why text might be misclassified, it might be useful to prompt GPT-3 to deliver an accompanying explanation for the decision.
+Another might be to consider a larger dataset of sexist and racist content, as one of the weaknesses of our approach is the relatively small dataset.
+The extent to which the identification and classification of hate speech can be explained by the model is especially of interest for future work.
 
@@
 \section*{Acknowledgements}
-  We thank two anonymous reviews and the editor, as well as Amy Farrow, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions.
-Please note that we have added asterisks to racial slurs and other offensive content in this paper, however the inputs and outputs did not have these.
+  We thank two anonymous reviews and the editor, as well as Amy Farrow, Christina Nguyen, Haoluan Chen, John Giorgi, Mauricio Vargas Sepúlveda, Monica Alexander, Noam Kolt, and Tom Davidson for helpful discussions and suggestions.
 
@@
 \begin{figure}
+\centering
+% \includegraphics{comparison-1.pdf}
 \caption{\label{fig:comparison}Comparing classification with and without an instruction}
@@
 
-\caption{\label{tab:zeroshot-summary}Performance of zero-shot learning in hate speech classification}
-\centering
-\begin{tabular}[t]{lrrrr}
-\hline
-Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
-\hline
-Racism & 68 & 67 & 73 & 70\\
-Sexism & 57 & 54 & 100 & 70\\
-Overall & 62 & 58 & 87 & 81\\
+\caption{\label{tab:zeroshot-summary}Performance of model in zero-shot learning across 100 classifications of each comment at a temperature of 0.3.}
+\centering
+\begin{tabular}[t]{llrr}
+\hline
+ & Metric & Mean (\%) & Standard Error (\%)\\
+\hline
+\textbf{Racism} & Accuracy & 58 & 6.5\\
+\textbf{} & Precision & 58 & 6.7\\
+\textbf{} & Recall & 59 & 9.2\\
+\textbf{} & F1 & 58 & 6.7\\
+\textbf{Sexism} & Accuracy & 55 & 5.2\\
+\textbf{} & Precision & 53 & 3.7\\
+\textbf{} & Recall & 79 & 6.9\\
+\textbf{} & F1 & 63 & 4.3\\
+\textbf{Overall} & Accuracy & 56 & 4.3\\
+\textbf{} & Precision & 55 & 3.5\\
+\textbf{} & Recall & 69 & 5.9\\
+\textbf{} & F1 & 70 & 5.7\\
 \hline
@@
 
-\caption{\label{tab:oneshot-summary}Performance of one-shot learning in hate speech classification}
-\centering
-\begin{tabular}[t]{lrrrr}
-\hline
-Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
-\hline
-Racism & 62 & 59 & 80 & 68\\
-Sexism & 60 & 57 & 77 & 66\\
-Overall & 61 & 58 & 78 & 65\\
+\caption{\label{tab:oneshot-summary}Performance of model in one-shot learning across 100 classifications of each comment at a temperature of 0.3.}
+\centering
+\begin{tabular}[t]{llrr}
+\hline
+ & Metric & Mean (\%) & Standard Error (\%)\\
+\hline
+\textbf{Racism} & Accuracy & 55 & 6.4\\
+\textbf{} & Precision & 55 & \vphantom{1} 5.9\\
+\textbf{} & Recall & 62 & 8.7\\
+\textbf{} & F1 & 58 & 6.5\\
+\textbf{Sexism} & Accuracy & 55 & 5.8\\
+\textbf{} & Precision & 55 & 5.9\\
+\textbf{} & Recall & 58 & 8.4\\
+\textbf{} & F1 & 56 & 6.3\\
+\textbf{Overall} & Accuracy & 55 & 4.1\\
+\textbf{} & Precision & 55 & 3.9\\
+\textbf{} & Recall & 60 & 5.6\\
+\textbf{} & F1 & 55 & 7.3\\
 \hline
@@
 
-\caption{\label{tab:fewshotsingle-summary}Performance of single-category few-shot learning in hate speech classification}
-\centering
-\begin{tabular}[t]{lrrrr}
-\hline
-Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
-\hline
-Racism & 68 & 66 & 77 & 71\\
-Sexism & 70 & 75 & 60 & 67\\
-Overall & 69 & 69 & 68 & 61\\
+\caption{\label{tab:fewshotsingle-summary}Performance of model in single category few-shot learning across 100 classifications of each comment at a temperature of 0.3.}
+\centering
+\begin{tabular}[t]{llrr}
+\hline
+ & Metric & Mean (\%) & Standard Error (\%)\\
+\hline
+\textbf{Racism} & Accuracy & 64 & 4.2\\
+\textbf{} & Precision & 62 & 3.9\\
+\textbf{} & Recall & 74 & 4.9\\
+\textbf{} & F1 & 67 & 3.7\\
+\textbf{Sexism} & Accuracy & 70 & 3.3\\
+\textbf{} & Precision & 74 & 3.7\\
+\textbf{} & Recall & 62 & 5.9\\
+\textbf{} & F1 & 68 & 4.3\\
+\textbf{Overall} & Accuracy & 67 & 2.7\\
+\textbf{} & Precision & 67 & 2.7\\
+\textbf{} & Recall & 68 & 4.0\\
+\textbf{} & F1 & 62 & 4.9\\
 \hline
@@
 \hline
-1 & Racism & 91 & 82 & 92 & 87\\
- & Sexism & 87 & 86 & 72 & 78\\
-\hline
-2 & Racism & 88 & 79 & 88 & 83\\
+1 & Racism & 90 & 81 & 92 & 86\\
+ & Sexism & 86 & 85 & 68 & 76\\
+\hline
+2 & Racism & 85 & 74 & 85 & 79\\
+ & Sexism & 87 & 82 & 77 & \vphantom{2} 79\\
+\hline
+3 & Racism & 86 & 73 & 93 & 82\\
+ & Sexism & 87 & 82 & 77 & \vphantom{1} 79\\
+\hline
+4 & Racism & 83 & 67 & 100 & 80\\
+ & Sexism & 85 & 76 & 80 & 78\\
+\hline
+5 & Racism & 83 & 67 & 95 & 79\\
+ & Sexism & 87 & 78 & 83 & \vphantom{1} 81\\
+\hline
+6 & Racism & 84 & 69 & 97 & 81\\
+ & Sexism & 84 & 74 & 80 & 77\\
+\hline
+7 & Racism & 79 & 62 & 98 & 76\\
  & Sexism & 87 & 82 & 77 & 79\\
 \hline
-3 & Racism & 87 & 74 & 93 & 82\\
- & Sexism & 84 & 79 & 73 & 76\\
-\hline
-4 & Racism & 84 & 69 & 98 & 81\\
- & Sexism & 83 & 72 & 80 & 76\\
-\hline
-5 & Racism & 80 & 64 & 93 & 76\\
- & Sexism & 86 & 82 & 75 & 78\\
-\hline
-6 & Racism & 86 & 71 & 98 & 83\\
- & Sexism & 86 & 77 & 80 & 79\\
-\hline
-7 & Racism & 77 & 59 & 97 & 73\\
- & Sexism & 87 & 85 & 73 & 79\\
-\hline
-8 & Racism & 73 & 55 & 95 & 70\\
- & Sexism & 83 & 70 & 85 & 77\\
-\hline
-9 & Racism & 80 & 63 & 97 & 76\\
- & Sexism & 74 & 57 & 85 & 68\\
-\hline
-10 & Racism & 88 & 77 & 90 & 83\\
- & Sexism & 89 & 83 & 87 & 85\\
+8 & Racism & 72 & 54 & 97 & 69\\
+ & Sexism & 83 & 71 & 82 & 76\\
+\hline
+9 & Racism & 78 & 61 & 95 & 74\\
+ & Sexism & 76 & 60 & 82 & 69\\
+\hline
+10 & Racism & 91 & 82 & 92 & 87\\
+ & Sexism & 87 & 78 & 83 & 81\\
 \hline
 All & Racism & 83 & 68 & 94 & 79\\
- & Sexism & 84 & 76 & 79 & 77\\
+ & Sexism & 85 & 76 & 79 & 77\\
 \hline
@@
 \hline
-racist | neither | homophobic | sexist | sexist, racist, | sexual assault | religious | sexual harassment | racist, sexist, | transphobic | hypocritical | I'm not a | I'm not brave | none of your business | I didn't | I'm not offended | you're not | sexual | I don't play | I don't care | I don't know | victim blaming | it's a question | irrelevant | I'm not crazy | creepy | romantic | I was taught to | I didn't say | ignorant | I'm not sure | I agree | not true | not even wrong | YouTube doesn't remove | socialist | conspiracy theorist | overpopulation | ableist | Islamophobic | conspiracy theory | hippie | sexist, rape ap | cliche | not even close to | nostalgic | I don't think | not a question | hippy | terrorist | hate speech | he was a terrorist | preachy | not a valid argument | not sexist | brave | Islamophobe | because you're a | troll | mental | never | pedophilia | mental illness is not | I'm sure you | I'm not going | not even close | grammar | rape apologist | cliché | vegan | sexist, misogynistic | I do | wrong | funny | question | when you were taught | opinion | emotional | conspiracy | nostalgia\\
+racist,  racist, homophobic,,  neither,  homophobic,  nazi,  neither, but the,  sexist\\,  sexist, racist,,  I don't know,  sexual assault,  religious,  sexual harassment, \\ sexist, misogynist,  sexual,  racist and sexist,  transphobic,  I'm not talking, \\ hypocritical,  I don't,  I'm a robot,  brave,  lolwut,  I do,  you're not alone, \\ I didn't,  you are probably not,  no one cares,  victim blaming,  you're the one, \\ irrelevant,  sarcastic,  not a question,  not funny,  I was taught to,  no one is, \\ hate speech,  I'm not sure,  creepy,  I am aware of,  what tables?
+,  emotional biass, \\  they were not in,  nostalgic,  I agree,  none,  no,  not true,  I'm not going, \\ racist, sexist,,  opinion,  not even wrong,  hippy,  they're not,  socialist, \\ misogynistic,  a question,  romantic,  not a good argument,  emotional bi ass, \\ not racist,  conspiracy theorist,  overpopulation,  ableist,  Islamophobic, \\ conspiracy theory,  environmentalist,  racist, sexist and,  mean,  not a quote,  cliche, \\ neither, but it,  none of the above,  I don't think,  this is a common,  Not a bad thing, \\ subjective,  funny,  hippie,  racist and homophobic,  racist, xenophobic,  violent, \\ sexist, racist,  sexist, ableist,  sexist, misogynistic,  none of your business,  stupid,\\  you're not,  both,  the same time when,  you're a f,  he was already dead, \\ circular reasoning,  SJW,  political,  not even close,  misinformed,  preachy, \\ racist, homophobic,  sexist, rape ap,  sexist, and also,  muslim,  freedom,  no one, \\ it's a question,  mental,  A phrase used by,  liar,  mental illness is a,  I'm sure you, \\ I don't have,  not sexist, racist,  sexist and misogynistic,  sexual threat, \\ not a comment,  not a big deal,  conspiracy,  sexist and transph,  mental illness is not, \\ not a single error,  grammar,  rape apologist,  pedophilia,  a bit of a,  cliché, \\ ignorant,  I don't care,  a lie,  vegan,  YouTube doesn't remove,  misogynist, \\ you are watching this,  offensive,  none of these,  they could have shot,  copypasta, \\ wrong,  death threats,  who,  I like PUB,  question,  too many people,  false, \\ not a troll\\
 \hline
@@
 \centering
-\begin{tabular}[t]{llll}
-\hline
-\multicolumn{1}{c}{ } & \multicolumn{3}{c}{GPT-3 classification} \\
-Actual classification & Neither & Racist & Sexist\\
-\hline
-Neither & 984 & 163 & 53\\
-Racist & 98 & 500 & 2\\
-Sexist & 264 & 35 & 301\\
+\begin{tabular}[t]{llllrr}
+\hline
+\multicolumn{1}{c}{ } & \multicolumn{5}{c}{GPT-3 classification} \\
+Actual classification & Neither & Racist & Sexist & Both & Racist And Sexist\\
+\hline
+Neither & 1903 & 374 & 123 & 0 & 0\\
+Racist & 210 & 984 & 5 & 1 & 0\\
+Sexist & 512 & 86 & 600 & 1 & 1\\
 \hline
@@
 
-\caption{\label{tab:fewshotmixedinstructsummary}Performance of mixed-category few-shot learning in text classification, with instruction}
+\caption{\label{tab:fewshotmixedinstruct-summary}Performance of mixed-category few-shot learning in text classification, with instruction}
 \centering
@@
 \hline
-1 & Racism & 88 & 79 & 87 & 83\\
- & Sexism & 83 & 81 & 63 & 71\\
-\hline
-2 & Racism & 87 & 86 & 72 & 78\\
- & Sexism & 82 & 89 & 53 & 67\\
-\hline
-3 & Racism & 86 & 76 & 83 & 79\\
- & Sexism & 81 & 84 & 52 & 64\\
-\hline
-4 & Racism & 89 & 83 & 87 & 85\\
- & Sexism & 80 & 83 & 50 & 62\\
-\hline
-5 & Racism & 86 & 87 & 68 & 77\\
- & Sexism & 76 & 84 & 35 & 49\\
-\hline
-6 & Racism & 88 & 93 & 70 & 80\\
- & Sexism & 73 & 82 & 23 & 36\\
-\hline
-7 & Racism & 88 & 80 & 87 & 83\\
- & Sexism & 79 & 85 & 47 & 60\\
-\hline
-8 & Racism & 79 & 62 & 93 & 75\\
- & Sexism & 84 & 90 & 60 & 72\\
-\hline
-9 & Racism & 86 & 75 & 87 & 81\\
- & Sexism & 77 & 88 & 35 & 50\\
-\hline
-10 & Racism & 77 & 59 & 100 & 74\\
- & Sexism & 89 & 85 & 83 & 84\\
-\hline
-All & Racism & 85 & 75 & 83 & 79\\
- & Sexism & 80 & 85 & 50 & 63\\
-\hline
-\end{tabular}
-\end{table}
+1 & Racism & 84 & 71 & 88 & 79\\
+ & Sexism & 81 & 76 & 63 & 69\\
+\hline
+2 & Racism & 81 & 75 & 65 & 70\\
+ & Sexism & 80 & 80 & 53 & \vphantom{1} 64\\
+\hline
+3 & Racism & 80 & 66 & 82 & 73\\
+ & Sexism & 81 & 88 & 50 & 64\\
+\hline
+4 & Racism & 86 & 77 & 82 & 79\\
+ & Sexism & 80 & 80 & 53 & 64\\
+\hline
+5 & Racism & 82 & 76 & 65 & 70\\
+ & Sexism & 77 & 85 & 37 & 51\\
+\hline
+6 & Racism & 84 & 85 & 65 & 74\\
+ & Sexism & 71 & 75 & 20 & 32\\
+\hline
+7 & Racism & 88 & 83 & 82 & 82\\
+ & Sexism & 79 & 78 & 52 & 62\\
+\hline
+8 & Racism & 78 & 61 & 93 & 74\\
+ & Sexism & 83 & 85 & 58 & 69\\
+\hline
+9 & Racism & 83 & 70 & 87 & 78\\
+ & Sexism & 77 & 85 & 38 & 53\\
+\hline
+10 & Racism & 72 & 55 & 98 & 70\\
+ & Sexism & 86 & 80 & 75 & 78\\
+\hline
+All & Racism & 82 & 70 & 81 & 75\\
+ & Sexism & 79 & 81 & 50 & 62\\
+\hline
+\end{tabular}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%                               %%
+%% Additional Files              %%
+%%                               %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\appendix
+
+\section{Example sets for the mixed-category, few-shot learning, experiments}\label{appendxa}
 
@@
 
-\caption{\label{tab:fewshotmixedanswersnoinstruct}Classifications generated by GPT-3 under mixed-category few-shot learning without instructions}
-\centering
-\begin{tabular}[t]{l}
-\hline
-racist | neither | homophobic | sexist | sexist, racist, | sexual assault | religious | sexual harassment | racist, sexist, | transphobic | hypocritical | I'm not a | I'm not brave | none of your business | I didn't | I'm not offended | you're not | sexual | I don't play | I don't care | I don't know | victim blaming | it's a question | irrelevant | I'm not crazy | creepy | romantic | I was taught to | I didn't say | ignorant | I'm not sure | I agree | not true | not even wrong | YouTube doesn't remove | socialist | conspiracy theorist | overpopulation | ableist | Islamophobic | conspiracy theory | hippie | sexist, rape ap | cliche | not even close to | nostalgic | I don't think | not a question | hippy | terrorist | hate speech | he was a terrorist | preachy | not a valid argument | not sexist | brave | Islamophobe | because you're a | troll | mental | never | pedophilia | mental illness is not | I'm sure you | I'm not going | not even close | grammar | rape apologist | cliché | vegan | sexist, misogynistic | I do | wrong | funny | question | when you were taught | opinion | emotional | conspiracy | nostalgia\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:fewshotmixedinstruct-matrix}Classifications of all comments using mixed-category few-short learning, with instruction}
-\centering
-\begin{tabular}[t]{llll}
-\hline
-\multicolumn{1}{c}{ } & \multicolumn{3}{c}{GPT-3 classification} \\
-Actual classification & Neither & Racist & Sexist\\
-\hline
-Neither & 984 & 163 & 53\\
-Racist & 98 & 500 & 2\\
-Sexist & 264 & 35 & 301\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:fewshotmixedinstructsummary}Performance of mixed-category few-shot learning in text classification, with instruction}
-\centering
-\begin{tabular}[t]{llrrrr}
-\hline
-Example set & Category & Accuracy (\%) & Precision (\%) & Recall (\%) & F1 (\%)\\
-\hline
-1 & Racism & 87.78 & 78.79 & 86.67 & 82.54\\
- & Sexism & 82.78 & 80.85 & 63.33 & 71.03\\
-\hline
-2 & Racism & 86.67 & 86.00 & 71.67 & 78.18\\
- & Sexism & 82.22 & 88.89 & 53.33 & 66.66\\
-\hline
-3 & Racism & 85.56 & 75.76 & 83.33 & 79.36\\
- & Sexism & 80.56 & 83.78 & 51.67 & 63.92\\
-\hline
-4 & Racism & 89.44 & 82.54 & 86.67 & 84.55\\
- & Sexism & 80.00 & 83.33 & 50.00 & 62.50\\
-\hline
-5 & Racism & 86.11 & 87.23 & 68.33 & 76.63\\
- & Sexism & 76.11 & 84.00 & 35.00 & 49.41\\
-\hline
-6 & Racism & 88.33 & 93.33 & 70.00 & 80.00\\
- & Sexism & 72.78 & 82.35 & 23.33 & 36.36\\
-\hline
-7 & Racism & 88.33 & 80.00 & 86.67 & 83.20\\
- & Sexism & 79.44 & 84.85 & 46.67 & 60.22\\
-\hline
-8 & Racism & 78.89 & 62.22 & 93.33 & 74.66\\
- & Sexism & 84.44 & 90.00 & 60.00 & 72.00\\
-\hline
-9 & Racism & 86.11 & 75.36 & 86.67 & 80.62\\
- & Sexism & 76.67 & 87.50 & 35.00 & 50.00\\
-\hline
-10 & Racism & 76.67 & 58.82 & 100.00 & 74.07\\
- & Sexism & 89.44 & 84.75 & 83.33 & 84.03\\
-\hline
-All & Racism & 85.39 & 75.41 & 83.33 & 79.17\\
- & Sexism & 80.44 & 85.03 & 50.17 & 63.11\\
-\hline
-\end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                               %%
-%% Additional Files              %%
-%%                               %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\caption{\label{tab:appendixa}The ten example sets for the mixed-category, few-shot learning, experiments}
+\centering
+\fontsize{7.5}{9.5}\selectfont
+\begin{tabular}[t]{p{1cm}p{4cm}p{4cm}p{4cm}}
+\hline
+Set & Example 1 (sexist) & Example 2 (racist) & Example 3 (not hate speech)\\
+\hline
+1 & You should know women's sports are a joke & why does that african american monkey hold gun like that? & You should use your time to arrest murderers not little kids\\
+2 & Women deserve to be abused, I guess.
+& Why do negroes tear down their own neighborhoods when a black thug gets killed by law enforcement?
+Must be because of low IQ.
+& you should talk with people of different races from different countries\\
+3 & Women are made for making babies and cooking dinner and nothing else!!! & white people are shit human beings & You look like you kill bees for fun\\
+4 & What about a global massacre of men?
+Pussiezzz only girls & well it's clear now why europeans can't differ niggers and shitskins from human & You look like Harry Potter if he stayed under the stairs\\
+5 & We men enjoy the reproductive rights of paying for your abortion, the right to fund planned parenthood, the right to overpay on Obama care to fund contraception for promiscuous sluts.
+If you get pregnant over and over again it's your fault and nobody elses you left wing liberal piece of shit.
+Go be a whore.
+Keep spreading disease.
+Half of all black women have herpes.
+And we have the right to pay for it.
+You are outrageous.
+& We whites have higher IQ's than blacks, this is because IQ measures intelligence and we are the more evolved and superior race with a larger brain.
+& You look kinda dead inside, you parents must not haved loved you.\\
+6 & The men are turtles...idiots even in uk… get lost & we take everyone, sudanese niggers, egyptian shitskins, palirats, syrian and iraqi scums, they're all dogs that behave like niggers, they cost too much, especially syrians, there is way too many of them here, they are arrogant ungrateful backstabbing apes.
+& You have the grace and composure of a rabid hyena\\
+7 & That girl still need a good ass whooping, stupid ass bitch!! & U SUCK SHIT YOU BLACK FUCK & You deserve way more subscribers . The shit you say is fucking gold.\\
+8 & stone throwing must be legal when against women & This sick, disgusting, white terrorist/fascist killed more than 50 innocent people.
+& You can see the country is fertile and green.
+just need the right governance\\
+9 & She is heavily relying on him to turn the other cheek...tough talking demon infested woman.
+& This is considered WHITE in Sweden.
+No wonder they accepted all those black and muslim immigrants.
+They are literally color blind.
+& you are a great brother to abbie, that family is changing the world!\\
+10 & Really, I hope she get raped in the future.
+Raping women should be legal I think & The world would be better without white people because they stole from the black Egyptians in the before christ ages they was poor we wasnt whites  ruins everything for black people/White people have pig dicks and no shape no hips or no booty they have to get plastic surgery as us blacks get it from our mother whites brought skin cancer to america so learn some facts before you try to run us out america when we was here before yall racist ass smelly crackers and dont say you will beat my ass because you cant and if you wanna find out drop your adress & You are a brave man.........for letting them keep the comments enabled\\
+\hline
+\end{tabular}
+\end{table}
+
+\newpage
+
+\section{Additional detail for results}\label{appendxb}
+
+\subsection{Zero-shot}\label{appendixbzeroshot}
+
+\begin{table}[!h]
+
+\caption{\label{tab:zeroshot-racism}Classification of racist statements with zero-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\hline
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+Actual classification & Not racist & Racist\\
+\hline
+Not racist & 1688 & 1295\\
+Racist & 1209 & 1775\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:zeroshot-sexism}Classification of sexist statements with zero-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\hline
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+Actual classification & Not sexist & Sexist\\
+\hline
+Not sexist & 923 & 2072\\
+Sexist & 619 & 2308\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:zeroshot-hate}Classification of hate speech with zero-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\hline
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+Actual classification & Not hate speech & Hate speech\\
+\hline
+Not hate speech & 2611 & 3367\\
+Hate speech & 1828 & 4083\\
+\hline
+\end{tabular}
+\end{table}
+
+\newpage
+
+\subsection{One-shot}\label{appendixboneshot}
+
+\begin{table}[!h]
+
+\caption{\label{tab:oneshot-racism}Classification of racist statements with one-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\hline
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+Actual classification & Not racist & Racist\\
+\hline
+Not racist & 1445 & 1529\\
+Racist & 1139 & 1839\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:oneshot-sexism}Classification of sexist statements with one-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\hline
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+Actual classification & Not sexist & Sexist\\
+\hline
+Not sexist & 1550 & 1407\\
+Sexist & 1224 & 1686\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:oneshot-hate}Classification of hate speech with one-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\hline
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+Actual classification & Not hate speech & Hate speech\\
+\hline
+Not hate speech & 2995 & 2936\\
+Hate speech & 2363 & 3525\\
+\hline
+\end{tabular}
+\end{table}
+
+\newpage
+
+\subsection{Few-shot single category}\label{appendixbfewshotsingle}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotsingle-racism}Classification of racist statements with single-category few-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\hline
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+Actual classification & Not racist & Racist\\
+\hline
+Not racist & 1653 & 1347\\
+Racist & 791 & 2209\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotsingle-sexism}Classification of sexist statements with single-category few-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\hline
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+Actual classification & Not sexist & Sexist\\
+\hline
+Not sexist & 2334 & 666\\
+Sexist & 1125 & 1875\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotsingle-hate}Classification of hate speech with single-category few-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{lrr}
+\hline
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+Actual classification & Not hate speech & Hate speech\\
+\hline
+Not hate speech & 3987 & 2013\\
+Hate speech & 1916 & 4084\\
+\hline
+\end{tabular}
+\end{table}
+
+\newpage
+
+\subsection{Few-shot mixed category, without instruction}\label{appendxbmuxedubsnorinstruction}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotmixed-racism}Classification of racist statements with mixed-category few-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llrr}
+\hline
+\multicolumn{2}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+Example set & Actual classification & Not racist & Racist\\
+\hline
+1 & Not racist & 107 & 13\\
+ & Racist & 5 & 55\\
+\hline
+2 & Not racist & 102 & 18\\
+ & Racist & 9 & 51\\
+\hline
+3 & Not racist & 99 & 21\\
+ & Racist & 4 & 56\\
+\hline
+4 & Not racist & 90 & 30\\
+ & Racist & 0 & 60\\
+\hline
+5 & Not racist & 92 & 28\\
+ & Racist & 3 & 57\\
+\hline
+6 & Not racist & 94 & 26\\
+ & Racist & 2 & 58\\
+\hline
+7 & Not racist & 84 & 36\\
+ & Racist & 1 & 59\\
+\hline
+8 & Not racist & 71 & 49\\
+ & Racist & 2 & 58\\
+\hline
+9 & Not racist & 83 & 37\\
+ & Racist & 3 & 57\\
+\hline
+10 & Not racist & 108 & 12\\
+ & Racist & 5 & 55\\
+\hline
+All & Not racist & 930 & 270\\
+ & Racist & 34 & 566\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotmixed-sexism}Classification of sexist statements with mixed-category few-shot learning}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llrr}
+\hline
+\multicolumn{2}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+Example set & Actual classification & Not sexist & Sexist\\
+\hline
+1 & Not sexist & 113 & 7\\
+ & Sexist & 19 & 41\\
+\hline
+2 & Not sexist & 110 & 10\\
+ & Sexist & 14 & 46\\
+\hline
+3 & Not sexist & 110 & 10\\
+ & Sexist & 14 & 46\\
+\hline
+4 & Not sexist & 105 & 15\\
+ & Sexist & 12 & 48\\
+\hline
+5 & Not sexist & 106 & 14\\
+ & Sexist & 10 & 50\\
+\hline
+6 & Not sexist & 103 & 17\\
+ & Sexist & 12 & 48\\
+\hline
+7 & Not sexist & 110 & 10\\
+ & Sexist & 14 & 46\\
+\hline
+8 & Not sexist & 100 & 20\\
+ & Sexist & 11 & 49\\
+\hline
+9 & Not sexist & 87 & 33\\
+ & Sexist & 11 & 49\\
+\hline
+10 & Not sexist & 106 & 14\\
+ & Sexist & 10 & 50\\
+\hline
+All & Not sexist & 1050 & 150\\
+ & Sexist & 127 & 473\\
+\hline
+\end{tabular}
+\end{table}
+
+\newpage
+
+\subsection{Few-shot mixed category, with instruction}\label{appendxbmuxedubstryctub}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotmixedinstruct-racism}Classification of racist statements with mixed-category few-shot learning, with instruction}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llrr}
+\hline
+\multicolumn{2}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+Example set & Actual classification & Not racist & Racist\\
+\hline
+1 & Not racist & 98 & 22\\
+ & Racist & 7 & 53\\
+\hline
+2 & Not racist & 107 & 13\\
+ & Racist & 21 & 39\\
+\hline
+3 & Not racist & 95 & 25\\
+ & Racist & 11 & 49\\
+\hline
+4 & Not racist & 105 & 15\\
+ & Racist & 11 & 49\\
+\hline
+5 & Not racist & 108 & 12\\
+ & Racist & 21 & 39\\
+\hline
+6 & Not racist & 113 & 7\\
+ & Racist & 21 & 39\\
+\hline
+7 & Not racist & 110 & 10\\
+ & Racist & 11 & 49\\
+\hline
+8 & Not racist & 84 & 36\\
+ & Racist & 4 & 56\\
+\hline
+9 & Not racist & 98 & 22\\
+ & Racist & 8 & 52\\
+\hline
+10 & Not racist & 71 & 49\\
+ & Racist & 1 & 59\\
+\hline
+All & Not racist & 989 & 211\\
+ & Racist & 116 & 484\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:fewshotmixedinstruct-sexism}Classification of sexist statements with mixed-category few-shot learning, with instruction}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llrr}
+\hline
+\multicolumn{2}{c}{ } & \multicolumn{2}{c}{GPT-3 classification} \\
+Example set & Actual classification & Not sexist & Sexist\\
+\hline
+1 & Not sexist & 108 & 12\\
+ & Sexist & 22 & 38\\
+\hline
+2 & Not sexist & 112 & 8\\
+ & Sexist & 28 & 32\\
+\hline
+3 & Not sexist & 116 & 4\\
+ & Sexist & 30 & 30\\
+\hline
+4 & Not sexist & 112 & 8\\
+ & Sexist & 28 & 32\\
+\hline
+5 & Not sexist & 116 & 4\\
+ & Sexist & 38 & 22\\
+\hline
+6 & Not sexist & 116 & 4\\
+ & Sexist & 48 & 12\\
+\hline
+7 & Not sexist & 111 & 9\\
+ & Sexist & 29 & 31\\
+\hline
+8 & Not sexist & 114 & 6\\
+ & Sexist & 25 & 35\\
+\hline
+9 & Not sexist & 116 & 4\\
+ & Sexist & 37 & 23\\
+\hline
+10 & Not sexist & 109 & 11\\
+ & Sexist & 15 & 45\\
+\hline
+All & Not sexist & 1130 & 70\\
+ & Sexist & 300 & 300\\
+\hline
+\end{tabular}
+\end{table}
+
+\newpage
+
+\section{Effect of misspellings}\label{appendxc}
+
+\begin{table}[!h]
+
+\caption{\label{tab:profanity}Strings used to extract comments with profanity and edits introduced to test impacts of misspelling and censorship on hate speech classificiation}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{ll}
+\hline
+Original & Edits\\
+\hline
+nigg & n1gg, nig, n*gg, n-gg\\
+fuck & fck, phuck, f*ck, f-ck\\
+whore & wh0re, whor3, wh0r3, wh*re, wh-re\\
+kill & k1ll, kil, k-ll, k*ll\\
+rape & r@pe, rap3, r@p3, rap, r*pe, r-pe\\
+die & d1e, di3, d13, dye, d*e, d-e\\
+bitch & b1tch, bich, bithc, bicht, b*tch, b-tch\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!h]
+
+\caption{\label{tab:misspell-results}Zero-shot learning classifications impacted by misspelling and censoring racist comments}
+\centering
+\fontsize{7.5}{9.5}\selectfont
+\begin{tabular}[t]{p{1cm}p{1cm}p{8cm}p{2cm}}
+\hline
+Label & Status & Comment & GPT-3 classification\\
+\hline
+Racist & Unedited & Fuck these generate vodka niggers.
+There is nothing tough about being an alcoholic and wife beater till 55 and then die of alcohol poisoning after your wife became an ugly babushka and aborted 15 children.
+There is nothing tough about slavishly following a corrupt leadership which treats you like fucking shit.
+& Yes\\
+Racist & Edited & fck these generate vodka niggers.
+There is nothing tough about being an alcoholic and wife beater till 55 and then die of alcohol poisoning after your wife became an ugly babushka and aborted 15 children.
+There is nothing tough about slavishly following a corrupt leadership which treats you like fcking shit.
+& No\\
+Racist & Edited & phuck these generate vodka niggers.
+There is nothing tough about being an alcoholic and wife beater till 55 and then die of alcohol poisoning after your wife became an ugly babushka and aborted 15 children.
+There is nothing tough about slavishly following a corrupt leadership which treats you like phucking shit.
+& No\\
+Racist & Unedited & Fuck off niggers WV is full & Yes\\
+Racist & Edited & phuck off niggers WV is full & No\\
+Racist & Unedited & Why are niggers superior athletically to all other races? & Yes\\
+Racist & Edited & Why are n*ggers superior athletically to all other races? & No\\
+Racist & Unedited & Stand the fuck up and take them out all you fucking lazy white males!
+fuck being called a racist protect your woman and children.
+If you find it in the street kill it and bury it right there these animals will wipe you out if your not careful & No\\
+Racist & Edited & Stand the phuck up and take them out all you phucking lazy white males!
+phuck being called a racist protect your woman and children.
+If you find it in the street kill it and bury it right there these animals will wipe you out if your not careful & Yes\\
+Racist & Unedited & Ima fucking stab u up bruv. Fucking white prick bruv.. fucking racist.  Gammon & Yes\\
+Racist & Edited & Ima fcking stab u up bruv. fcking white prick bruv.. fcking racist.  Gammon & No\\
+Racist & Edited & Ima f*cking stab u up bruv. f*cking white prick bruv.. f*cking racist.  Gammon & No\\
+Racist & Unedited & fucking monkeys kill them all & No\\
+Racist & Edited & fucking monkeys k-ll them all & Yes\\
+\hline
+\end{tabular}
+\end{table}
+
+\newpage
 
